### 2022-04-11 Definitions/journalnames.tex
Initial Overleaf Import

%%Updated on 24 March 2022
%,% Website Name,%,%,% Website Name,%%,% Full Name,%%,% Short Name,%%,% DOI abbr,%%,% ISSN,% \continuouspages
%\DeclareOption{}{\gdef\@journal{}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{acoustics}{\gdef\@journal{acoustics}\gdef\@journalfull{Acoustics}\gdef\@journalshort{Acoustics}\gdef\@doiabbr{acoustics}\gdef\@ISSN{2624-599X}\gdef\@continuouspages{yes}}
\DeclareOption{actuators}{\gdef\@journal{actuators}\gdef\@journalfull{Actuators}\gdef\@journalshort{Actuators}\gdef\@doiabbr{act}\gdef\@ISSN{2076-0825}}
\DeclareOption{addictions}{\gdef\@journal{addictions}\gdef\@journalfull{Addictions}\gdef\@journalshort{Addictions}\gdef\@doiabbr{}\gdef\@ISSN{0006-0006}}
\DeclareOption{admsci}{\gdef\@journal{admsci}\gdef\@journalfull{Administrative Sciences}\gdef\@journalshort{Adm. Sci.}\gdef\@doiabbr{admsci}\gdef\@ISSN{2076-3387}}
\DeclareOption{adolescents}{\gdef\@journal{adolescents}\gdef\@journalfull{Adolescents}\gdef\@journalshort{Adolescents}\gdef\@doiabbr{adolescents}\gdef\@ISSN{2673-7051}\gdef\@continuouspages{yes}}
\DeclareOption{aerospace}{\gdef\@journal{aerospace}\gdef\@journalfull{Aerospace}\gdef\@journalshort{Aerospace}\gdef\@doiabbr{aerospace}\gdef\@ISSN{2226-4310}}
\DeclareOption{agriculture}{\gdef\@journal{agriculture}\gdef\@journalfull{Agriculture}\gdef\@journalshort{Agriculture}\gdef\@doiabbr{agriculture}\gdef\@ISSN{2077-0472}}
\DeclareOption{agriengineering}{\gdef\@journal{agriengineering}\gdef\@journalfull{AgriEngineering}\gdef\@journalshort{AgriEngineering}\gdef\@doiabbr{agriengineering}\gdef\@ISSN{2624-7402}\gdef\@continuouspages{yes}}
\DeclareOption{agrochemicals}{\gdef\@journal{agrochemicals}\gdef\@journalfull{Agrochemicals}\gdef\@journalshort{Agrochemicals}\gdef\@doiabbr{agrochemicals}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{agronomy}{\gdef\@journal{agronomy}\gdef\@journalfull{Agronomy}\gdef\@journalshort{Agronomy}\gdef\@doiabbr{agronomy}\gdef\@ISSN{2073-4395}}
\DeclareOption{ai}{\gdef\@journal{ai}\gdef\@journalfull{AI}\gdef\@journalshort{AI}\gdef\@doiabbr{ai}\gdef\@ISSN{2673-2688}\gdef\@continuouspages{yes}}
\DeclareOption{air}{\gdef\@journal{air}\gdef\@journalfull{Air}\gdef\@journalshort{Air}\gdef\@doiabbr{air}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{algorithms}{\gdef\@journal{algorithms}\gdef\@journalfull{Algorithms}\gdef\@journalshort{Algorithms}\gdef\@doiabbr{a}\gdef\@ISSN{1999-4893}}
\DeclareOption{allergies}{\gdef\@journal{allergies}\gdef\@journalfull{Allergies}\gdef\@journalshort{Allergies}\gdef\@doiabbr{allergies}\gdef\@ISSN{2313-5786}}
\DeclareOption{alloys}{\gdef\@journal{alloys}\gdef\@journalfull{Alloys}\gdef\@journalshort{Alloys}\gdef\@doiabbr{alloys}\gdef\@ISSN{2674-063X}\gdef\@continuouspages{yes}}
\DeclareOption{analytica}{\gdef\@journal{analytica}\gdef\@journalfull{Analytica}\gdef\@journalshort{Analytica}\gdef\@doiabbr{analytica}\gdef\@ISSN{2673-4532}\gdef\@continuouspages{yes}}
\DeclareOption{analytics}{\gdef\@journal{analytics}\gdef\@journalfull{Analytics}\gdef\@journalshort{Analytics}\gdef\@doiabbr{analytics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{anatomia}{\gdef\@journal{anatomia}\gdef\@journalfull{Anatomia}\gdef\@journalshort{Anatomia}\gdef\@doiabbr{anatomia}\gdef\@ISSN{2813-0545}\gdef\@continuouspages{yes}}
\DeclareOption{animals}{\gdef\@journal{animals}\gdef\@journalfull{Animals}\gdef\@journalshort{Animals}\gdef\@doiabbr{ani}\gdef\@ISSN{2076-2615}}
\DeclareOption{antibiotics}{\gdef\@journal{antibiotics}\gdef\@journalfull{Antibiotics}\gdef\@journalshort{Antibiotics}\gdef\@doiabbr{antibiotics}\gdef\@ISSN{2079-6382}}
\DeclareOption{antibodies}{\gdef\@journal{antibodies}\gdef\@journalfull{Antibodies}\gdef\@journalshort{Antibodies}\gdef\@doiabbr{antib}\gdef\@ISSN{2073-4468}}
\DeclareOption{antioxidants}{\gdef\@journal{antioxidants}\gdef\@journalfull{Antioxidants}\gdef\@journalshort{Antioxidants}\gdef\@doiabbr{antiox}\gdef\@ISSN{2076-3921}}
\DeclareOption{applbiosci}{\gdef\@journal{applbiosci}\gdef\@journalfull{Applied Biosciences}\gdef\@journalshort{Appl. Biosci.}\gdef\@doiabbr{applbiosci}\gdef\@ISSN{2813-0464}\gdef\@continuouspages{yes}}
\DeclareOption{appliedchem}{\gdef\@journal{appliedchem}\gdef\@journalfull{AppliedChem}\gdef\@journalshort{AppliedChem}\gdef\@doiabbr{appliedchem}\gdef\@ISSN{2673-9623}\gdef\@continuouspages{yes}}
\DeclareOption{appliedmath}{\gdef\@journal{appliedmath}\gdef\@journalfull{AppliedMath}\gdef\@journalshort{AppliedMath}\gdef\@doiabbr{appliedmath}\gdef\@ISSN{2673-9909}\gdef\@continuouspages{yes}}
\DeclareOption{applmech}{\gdef\@journal{applmech}\gdef\@journalfull{Applied Mechanics}\gdef\@journalshort{Appl. Mech.}\gdef\@doiabbr{applmech}\gdef\@ISSN{2673-3161}\gdef\@continuouspages{yes}}
\DeclareOption{applmicrobiol}{\gdef\@journal{applmicrobiol}\gdef\@journalfull{Applied Microbiology}\gdef\@journalshort{Appl. Microbiol.}\gdef\@doiabbr{applmicrobiol}\gdef\@ISSN{2673-8007}\gdef\@continuouspages{yes}}
\DeclareOption{applnano}{\gdef\@journal{applnano}\gdef\@journalfull{Applied Nano}\gdef\@journalshort{Appl. Nano}\gdef\@doiabbr{applnano}\gdef\@ISSN{2673-3501}\gdef\@continuouspages{yes}}
\DeclareOption{applsci}{\gdef\@journal{applsci}\gdef\@journalfull{Applied Sciences}\gdef\@journalshort{Appl. Sci.}\gdef\@doiabbr{app}\gdef\@ISSN{2076-3417}}
\DeclareOption{aquacj}{\gdef\@journal{aquacj}\gdef\@journalfull{Aquaculture Journal}\gdef\@journalshort{Aquac. J.}\gdef\@doiabbr{aj}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{architecture}{\gdef\@journal{architecture}\gdef\@journalfull{Architecture}\gdef\@journalshort{Architecture}\gdef\@doiabbr{architecture}\gdef\@ISSN{2673-8945}\gdef\@continuouspages{yes}}
\DeclareOption{arts}{\gdef\@journal{arts}\gdef\@journalfull{Arts}\gdef\@journalshort{Arts}\gdef\@doiabbr{arts}\gdef\@ISSN{2076-0752}}
\DeclareOption{asc}{\gdef\@journal{asc}\gdef\@journalfull{Automatic Systems and Control}\gdef\@journalshort{Autom. Syst. Control}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{asi}{\gdef\@journal{asi}\gdef\@journalfull{Applied System Innovation}\gdef\@journalshort{Appl. Syst. Innov.}\gdef\@doiabbr{asi}\gdef\@ISSN{2571-5577}}
\DeclareOption{astronomy}{\gdef\@journal{astronomy}\gdef\@journalfull{Astronomy}\gdef\@journalshort{Astronomy}\gdef\@doiabbr{astronomy}\gdef\@ISSN{2674-0346}\gdef\@continuouspages{yes}}
\DeclareOption{atmosphere}{\gdef\@journal{atmosphere}\gdef\@journalfull{Atmosphere}\gdef\@journalshort{Atmosphere}\gdef\@doiabbr{atmos}\gdef\@ISSN{2073-4433}}
\DeclareOption{atoms}{\gdef\@journal{atoms}\gdef\@journalfull{Atoms}\gdef\@journalshort{Atoms}\gdef\@doiabbr{atoms}\gdef\@ISSN{2218-2004}}
\DeclareOption{audiolres}{\gdef\@journal{audiolres}\gdef\@journalfull{Audiology Research}\gdef\@journalshort{Audiol. Res.}\gdef\@doiabbr{audiolres}\gdef\@ISSN{2039-4349}\gdef\@continuouspages{yes}}
\DeclareOption{automation}{\gdef\@journal{automation}\gdef\@journalfull{Automation}\gdef\@journalshort{Automation}\gdef\@doiabbr{automation}\gdef\@ISSN{2673-4052}\gdef\@continuouspages{yes}}
\DeclareOption{axioms}{\gdef\@journal{axioms}\gdef\@journalfull{Axioms}\gdef\@journalshort{Axioms}\gdef\@doiabbr{axioms}\gdef\@ISSN{2075-1680}}
\DeclareOption{bacteria}{\gdef\@journal{bacteria}\gdef\@journalfull{Bacteria}\gdef\@journalshort{Bacteria}\gdef\@doiabbr{bacteria}\gdef\@ISSN{2674-1334}\gdef\@continuouspages{yes}}
\DeclareOption{batteries}{\gdef\@journal{batteries}\gdef\@journalfull{Batteries}\gdef\@journalshort{Batteries}\gdef\@doiabbr{batteries}\gdef\@ISSN{2313-0105}}
\DeclareOption{bdcc}{\gdef\@journal{bdcc}\gdef\@journalfull{Big Data and Cognitive Computing}\gdef\@journalshort{Big Data Cogn. Comput.}\gdef\@doiabbr{bdcc}\gdef\@ISSN{2504-2289}}
\DeclareOption{behavsci}{\gdef\@journal{behavsci}\gdef\@journalfull{Behavioral Sciences}\gdef\@journalshort{Behav. Sci.}\gdef\@doiabbr{bs}\gdef\@ISSN{2076-328X}}
\DeclareOption{beverages}{\gdef\@journal{beverages}\gdef\@journalfull{Beverages}\gdef\@journalshort{Beverages}\gdef\@doiabbr{beverages}\gdef\@ISSN{2306-5710}}
\DeclareOption{biochem}{\gdef\@journal{biochem}\gdef\@journalfull{BioChem}\gdef\@journalshort{BioChem}\gdef\@doiabbr{biochem}\gdef\@ISSN{2673-6411}\gdef\@continuouspages{yes}}
\DeclareOption{bioengineering}{\gdef\@journal{bioengineering}\gdef\@journalfull{Bioengineering}\gdef\@journalshort{Bioengineering}\gdef\@doiabbr{bioengineering}\gdef\@ISSN{2306-5354}}
\DeclareOption{biologics}{\gdef\@journal{biologics}\gdef\@journalfull{Biologics}\gdef\@journalshort{Biologics}\gdef\@doiabbr{biologics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biology}{\gdef\@journal{biology}\gdef\@journalfull{Biology}\gdef\@journalshort{Biology}\gdef\@doiabbr{biology}\gdef\@ISSN{2079-7737}}
\DeclareOption{biomass}{\gdef\@journal{biomass}\gdef\@journalfull{Biomass}\gdef\@journalshort{Biomass}\gdef\@doiabbr{biomass}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomechanics}{\gdef\@journal{biomechanics}\gdef\@journalfull{Biomechanics}\gdef\@journalshort{Biomechanics}\gdef\@doiabbr{biomechanics}\gdef\@ISSN{2673-7078}\gdef\@continuouspages{yes}}
\DeclareOption{biomed}{\gdef\@journal{biomed}\gdef\@journalfull{BioMed}\gdef\@journalshort{BioMed}\gdef\@doiabbr{biomed}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomedicines}{\gdef\@journal{biomedicines}\gdef\@journalfull{Biomedicines}\gdef\@journalshort{Biomedicines}\gdef\@doiabbr{biomedicines}\gdef\@ISSN{2227-9059}}
\DeclareOption{biomedinformatics}{\gdef\@journal{biomedinformatics}\gdef\@journalfull{Biomedinformatics}\gdef\@journalshort{Biomedinformatics}\gdef\@doiabbr{biomedinformatics}\gdef\@ISSN{2673-7426}\gdef\@continuouspages{yes}}
\DeclareOption{biomimetics}{\gdef\@journal{biomimetics}\gdef\@journalfull{Biomimetics}\gdef\@journalshort{Biomimetics}\gdef\@doiabbr{biomimetics}\gdef\@ISSN{2313-7673}}
\DeclareOption{biomolecules}{\gdef\@journal{biomolecules}\gdef\@journalfull{Biomolecules}\gdef\@journalshort{Biomolecules}\gdef\@doiabbr{biom}\gdef\@ISSN{2218-273X}}
\DeclareOption{biophysica}{\gdef\@journal{biophysica}\gdef\@journalfull{Biophysica}\gdef\@journalshort{Biophysica}\gdef\@doiabbr{biophysica}\gdef\@ISSN{2673-4125}\gdef\@continuouspages{yes}}
\DeclareOption{biosensors}{\gdef\@journal{biosensors}\gdef\@journalfull{Biosensors}\gdef\@journalshort{Biosensors}\gdef\@doiabbr{bios}\gdef\@ISSN{2079-6374}}
\DeclareOption{biotech}{\gdef\@journal{biotech}\gdef\@journalfull{BioTech}\gdef\@journalshort{BioTech}\gdef\@doiabbr{biotech}\gdef\@ISSN{2673-6284}}
\DeclareOption{birds}{\gdef\@journal{birds}\gdef\@journalfull{Birds}\gdef\@journalshort{Birds}\gdef\@doiabbr{birds}\gdef\@ISSN{2673-6004}\gdef\@continuouspages{yes}}
\DeclareOption{bloods}{\gdef\@journal{bloods}\gdef\@journalfull{Bloods}\gdef\@journalshort{Bloods}\gdef\@doiabbr{bloods}\gdef\@ISSN{2673-415X}}
\DeclareOption{blsf}{\gdef\@journal{blsf}\gdef\@journalfull{Biology and Life Sciences Forum}\gdef\@journalshort{Biol. Life Sci. Forum}\gdef\@doiabbr{blsf	}\gdef\@ISSN{2673-9976}}
\DeclareOption{brainsci}{\gdef\@journal{brainsci}\gdef\@journalfull{Brain Sciences}\gdef\@journalshort{Brain Sci.}\gdef\@doiabbr{brainsci}\gdef\@ISSN{2076-3425}}
\DeclareOption{breath}{\gdef\@journal{breath}\gdef\@journalfull{Breath}\gdef\@journalshort{Breath}\gdef\@doiabbr{breath}\gdef\@ISSN{}}
\DeclareOption{buildings}{\gdef\@journal{buildings}\gdef\@journalfull{Buildings}\gdef\@journalshort{Buildings}\gdef\@doiabbr{buildings}\gdef\@ISSN{2075-5309}}
\DeclareOption{businesses}{\gdef\@journal{businesses}\gdef\@journalfull{Businesses}\gdef\@journalshort{Businesses}\gdef\@doiabbr{businesses}\gdef\@ISSN{2673-7116}\gdef\@continuouspages{yes}}
\DeclareOption{cancers}{\gdef\@journal{cancers}\gdef\@journalfull{Cancers}\gdef\@journalshort{Cancers}\gdef\@doiabbr{cancers}\gdef\@ISSN{2072-6694}}
\DeclareOption{carbon}{\gdef\@journal{carbon}\gdef\@journalfull{C}\gdef\@journalshort{C}\gdef\@doiabbr{c}\gdef\@ISSN{2311-5629}}
\DeclareOption{cardiogenetics}{\gdef\@journal{cardiogenetics}\gdef\@journalfull{Cardiogenetics}\gdef\@journalshort{Cardiogenetics}\gdef\@doiabbr{cardiogenetics}\gdef\@ISSN{2035-8148}\gdef\@continuouspages{yes}}
\DeclareOption{catalysts}{\gdef\@journal{catalysts}\gdef\@journalfull{Catalysts}\gdef\@journalshort{Catalysts}\gdef\@doiabbr{catal}\gdef\@ISSN{2073-4344}}
\DeclareOption{cells}{\gdef\@journal{cells}\gdef\@journalfull{Cells}\gdef\@journalshort{Cells}\gdef\@doiabbr{cells}\gdef\@ISSN{2073-4409}}
\DeclareOption{ceramics}{\gdef\@journal{ceramics}\gdef\@journalfull{Ceramics}\gdef\@journalshort{Ceramics}\gdef\@doiabbr{ceramics}\gdef\@ISSN{2571-6131}\gdef\@continuouspages{yes}}
\DeclareOption{challenges}{\gdef\@journal{challenges}\gdef\@journalfull{Challenges}\gdef\@journalshort{Challenges}\gdef\@doiabbr{challe}\gdef\@ISSN{2078-1547}}
\DeclareOption{chemengineering}{\gdef\@journal{chemengineering}\gdef\@journalfull{ChemEngineering}\gdef\@journalshort{ChemEngineering}\gdef\@doiabbr{chemengineering}\gdef\@ISSN{2305-7084}}
\DeclareOption{chemistry}{\gdef\@journal{chemistry}\gdef\@journalfull{Chemistry}\gdef\@journalshort{Chemistry}\gdef\@doiabbr{chemistry}\gdef\@ISSN{2624-8549}\gdef\@continuouspages{yes}}
\DeclareOption{chemosensors}{\gdef\@journal{chemosensors}\gdef\@journalfull{Chemosensors}\gdef\@journalshort{Chemosensors}\gdef\@doiabbr{chemosensors}\gdef\@ISSN{2227-9040}}
\DeclareOption{chemproc}{\gdef\@journal{chemproc}\gdef\@journalfull{Chemistry Proceedings}\gdef\@journalshort{Chem. Proc.}\gdef\@doiabbr{chemproc}\gdef\@ISSN{2673-4583}}
\DeclareOption{children}{\gdef\@journal{children}\gdef\@journalfull{Children}\gdef\@journalshort{Children}\gdef\@doiabbr{children}\gdef\@ISSN{2227-9067}}
\DeclareOption{chips}{\gdef\@journal{chips}\gdef\@journalfull{Chips}\gdef\@journalshort{Chips}\gdef\@doiabbr{chips}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{cimb}{\gdef\@journal{cimb}\gdef\@journalfull{Current Issues in Molecular Biology}\gdef\@journalshort{Curr. Issues Mol. Biol.}\gdef\@doiabbr{cimb}\gdef\@ISSN{1467-3045}\gdef\@continuouspages{yes}}
\DeclareOption{civileng}{\gdef\@journal{civileng}\gdef\@journalfull{CivilEng}\gdef\@journalshort{CivilEng}\gdef\@doiabbr{civileng}\gdef\@ISSN{2673-4109}\gdef\@continuouspages{yes}}
\DeclareOption{cleantechnol}{\gdef\@journal{cleantechnol}\gdef\@journalfull{Clean Technologies}\gdef\@journalshort{Clean Technol.}\gdef\@doiabbr{cleantechnol}\gdef\@ISSN{2571-8797}\gdef\@continuouspages{yes}}
\DeclareOption{climate}{\gdef\@journal{climate}\gdef\@journalfull{Climate}\gdef\@journalshort{Climate}\gdef\@doiabbr{cli}\gdef\@ISSN{2225-1154}}
\DeclareOption{clinpract}{\gdef\@journal{clinpract}\gdef\@journalfull{Clinics and Practice}\gdef\@journalshort{Clin. Pract.}\gdef\@doiabbr{clinpract}\gdef\@ISSN{2039-7283}\gdef\@continuouspages{yes}}
\DeclareOption{clockssleep}{\gdef\@journal{clockssleep}\gdef\@journalfull{Clocks \& Sleep}\gdef\@journalshort{Clocks\&Sleep}\gdef\@doiabbr{clockssleep}\gdef\@ISSN{2624-5175}\gdef\@continuouspages{yes}}
\DeclareOption{cmd}{\gdef\@journal{cmd}\gdef\@journalfull{Corrosion and Materials Degradation}\gdef\@journalshort{Corros. Mater. Degrad.}\gdef\@doiabbr{cmd}\gdef\@ISSN{2624-5558}\gdef\@continuouspages{yes}}
\DeclareOption{coasts}{\gdef\@journal{coasts}\gdef\@journalfull{Coasts}\gdef\@journalshort{Coasts}\gdef\@doiabbr{coasts}\gdef\@ISSN{2673-964X}\gdef\@continuouspages{yes}}
\DeclareOption{coatings}{\gdef\@journal{coatings}\gdef\@journalfull{Coatings}\gdef\@journalshort{Coatings}\gdef\@doiabbr{coatings}\gdef\@ISSN{2079-6412}}
\DeclareOption{colloids}{\gdef\@journal{colloids}\gdef\@journalfull{Colloids Interfaces}\gdef\@journalshort{Colloids Interfaces}\gdef\@doiabbr{colloids}\gdef\@ISSN{2504-5377}}
\DeclareOption{colorants}{\gdef\@journal{colorants}\gdef\@journalfull{Colorants}\gdef\@journalshort{Colorants}\gdef\@doiabbr{colorants}\gdef\@ISSN{2079-6447}\gdef\@continuouspages{yes}}
\DeclareOption{commodities}{\gdef\@journal{commodities}\gdef\@journalfull{Commodities}\gdef\@journalshort{Commodities}\gdef\@doiabbr{commodities}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{compounds}{\gdef\@journal{compounds}\gdef\@journalfull{Compounds}\gdef\@journalshort{Compounds}\gdef\@doiabbr{compounds}\gdef\@ISSN{2673-6918}\gdef\@continuouspages{yes}}
\DeclareOption{computation}{\gdef\@journal{computation}\gdef\@journalfull{Computation}\gdef\@journalshort{Computation}\gdef\@doiabbr{computation}\gdef\@ISSN{2079-3197}}
\DeclareOption{computers}{\gdef\@journal{computers}\gdef\@journalfull{Computers}\gdef\@journalshort{Computers}\gdef\@doiabbr{computers}\gdef\@ISSN{2073-431X}}
\DeclareOption{condensedmatter}{\gdef\@journal{condensedmatter}\gdef\@journalfull{Condensed Matter}\gdef\@journalshort{Condens. Matter}\gdef\@doiabbr{condmat}\gdef\@ISSN{2410-3896}}
\DeclareOption{conservation}{\gdef\@journal{conservation}\gdef\@journalfull{Conservation}\gdef\@journalshort{Conservation}\gdef\@doiabbr{conservation}\gdef\@ISSN{2673-7159}\gdef\@continuouspages{yes}}
\DeclareOption{constrmater}{\gdef\@journal{constrmater}\gdef\@journalfull{Construction Materials}\gdef\@journalshort{Constr. Mater.}\gdef\@doiabbr{constrmater}\gdef\@ISSN{2673-7108}\gdef\@continuouspages{yes}}
\DeclareOption{cosmetics}{\gdef\@journal{cosmetics}\gdef\@journalfull{Cosmetics}\gdef\@journalshort{Cosmetics}\gdef\@doiabbr{cosmetics}\gdef\@ISSN{2079-9284}}
\DeclareOption{covid}{\gdef\@journal{covid}\gdef\@journalfull{COVID}\gdef\@journalshort{COVID}\gdef\@doiabbr{covid}\gdef\@ISSN{2673-8112}\gdef\@continuouspages{yes}}
\DeclareOption{crops}{\gdef\@journal{crops}\gdef\@journalfull{Crops}\gdef\@journalshort{Crops}\gdef\@doiabbr{crops}\gdef\@ISSN{2673-7655}\gdef\@continuouspages{yes}}
\DeclareOption{cryptography}{\gdef\@journal{cryptography}\gdef\@journalfull{Cryptography}\gdef\@journalshort{Cryptography}\gdef\@doiabbr{cryptography}\gdef\@ISSN{2410-387X}}
\DeclareOption{crystals}{\gdef\@journal{crystals}\gdef\@journalfull{Crystals}\gdef\@journalshort{Crystals}\gdef\@doiabbr{cryst}\gdef\@ISSN{2073-4352}}
\DeclareOption{csmf}{\gdef\@journal{csmf}\gdef\@journalfull{Computer Sciences \& Mathematics Forum}\gdef\@journalshort{Comput. Sci. Math. Forum}\gdef\@doiabbr{csmf}\gdef\@ISSN{2813-0324}\gdef\@continuouspages{yes}}
\DeclareOption{ctn}{\gdef\@journal{ctn}\gdef\@journalfull{Clinical and Translational Neuroscience}\gdef\@journalshort{CTN}\gdef\@doiabbr{Clin. Transl. Neurosci.}\gdef\@ISSN{2514-183X}}
\DeclareOption{curroncol}{\gdef\@journal{curroncol}\gdef\@journalfull{Current Oncology}\gdef\@journalshort{Curr. Oncol.}\gdef\@doiabbr{curroncol}\gdef\@ISSN{1718-7729}\gdef\@continuouspages{yes}}
\DeclareOption{cyber}{\gdef\@journal{cyber}\gdef\@journalfull{Cyber}\gdef\@journalshort{Cyber}\gdef\@doiabbr{cyber}\gdef\@ISSN{2624-800X}}
\DeclareOption{dairy}{\gdef\@journal{dairy}\gdef\@journalfull{Dairy}\gdef\@journalshort{Dairy}\gdef\@doiabbr{dairy}\gdef\@ISSN{2624-862X}\gdef\@continuouspages{yes}}
\DeclareOption{data}{\gdef\@journal{data}\gdef\@journalfull{Data}\gdef\@journalshort{Data}\gdef\@doiabbr{data}\gdef\@ISSN{2306-5729}}
\DeclareOption{dentistry}{\gdef\@journal{dentistry}\gdef\@journalfull{Dentistry Journal}\gdef\@journalshort{Dent. J.}\gdef\@doiabbr{dj}\gdef\@ISSN{2304-6767}}
\DeclareOption{dermato}{\gdef\@journal{dermato}\gdef\@journalfull{Dermato}\gdef\@journalshort{Dermato}\gdef\@doiabbr{dermato}\gdef\@ISSN{2673-6179}\gdef\@continuouspages{yes}}
\DeclareOption{dermatopathology}{\gdef\@journal{dermatopathology}\gdef\@journalfull{Dermatopathology}\gdef\@journalshort{Dermatopathology}\gdef\@doiabbr{dermatopathology}\gdef\@ISSN{2296-3529}\gdef\@continuouspages{yes}}
\DeclareOption{designs}{\gdef\@journal{designs}\gdef\@journalfull{Designs}\gdef\@journalshort{Designs}\gdef\@doiabbr{designs}\gdef\@ISSN{2411-9660}}
\DeclareOption{diabetology}{\gdef\@journal{diabetology}\gdef\@journalfull{Diabetology}\gdef\@journalshort{Diabetology}\gdef\@doiabbr{diabetology}\gdef\@ISSN{2673-4540}\gdef\@continuouspages{yes}}
\DeclareOption{diagnostics}{\gdef\@journal{diagnostics}\gdef\@journalfull{Diagnostics}\gdef\@journalshort{Diagnostics}\gdef\@doiabbr{diagnostics}\gdef\@ISSN{2075-4418}}
\DeclareOption{dietetics}{\gdef\@journal{dietetics}\gdef\@journalfull{Dietetics}\gdef\@journalshort{Dietetics}\gdef\@doiabbr{dietetics}\gdef\@ISSN{2674-0311}\gdef\@continuouspages{yes}}
\DeclareOption{digital}{\gdef\@journal{digital}\gdef\@journalfull{Digital}\gdef\@journalshort{Digital}\gdef\@doiabbr{digital}\gdef\@ISSN{2673-6470}\gdef\@continuouspages{yes}}
\DeclareOption{disabilities}{\gdef\@journal{disabilities}\gdef\@journalfull{Disabilities}\gdef\@journalshort{Disabilities}\gdef\@doiabbr{disabilities}\gdef\@ISSN{2673-7272}\gdef\@continuouspages{yes}}
\DeclareOption{diseases}{\gdef\@journal{diseases}\gdef\@journalfull{Diseases}\gdef\@journalshort{Diseases}\gdef\@doiabbr{diseases}\gdef\@ISSN{2079-9721}}
\DeclareOption{diversity}{\gdef\@journal{diversity}\gdef\@journalfull{Diversity}\gdef\@journalshort{Diversity}\gdef\@doiabbr{d}\gdef\@ISSN{1424-2818}}
\DeclareOption{dna}{\gdef\@journal{dna}\gdef\@journalfull{DNA}\gdef\@journalshort{DNA}\gdef\@doiabbr{dna}\gdef\@ISSN{2673-8856}\gdef\@continuouspages{yes}}
\DeclareOption{drones}{\gdef\@journal{drones}\gdef\@journalfull{Drones}\gdef\@journalshort{Drones}\gdef\@doiabbr{drones}\gdef\@ISSN{2504-446X}}
\DeclareOption{dynamics}{\gdef\@journal{dynamics}\gdef\@journalfull{Dynamics}\gdef\@journalshort{Dynamics}\gdef\@doiabbr{dynamics}\gdef\@ISSN{2673-8716}\gdef\@continuouspages{yes}}
\DeclareOption{earth}{\gdef\@journal{earth}\gdef\@journalfull{Earth}\gdef\@journalshort{Earth}\gdef\@doiabbr{earth}\gdef\@ISSN{2673-4834}\gdef\@continuouspages{yes}}
\DeclareOption{ebj}{\gdef\@journal{ebj}\gdef\@journalfull{European Burn Journal}\gdef\@journalshort{Eur. Burn J.}\gdef\@doiabbr{ebj}\gdef\@ISSN{2673-1991}\gdef\@continuouspages{yes}}
\DeclareOption{ecologies}{\gdef\@journal{ecologies}\gdef\@journalfull{Ecologies}\gdef\@journalshort{Ecologies}\gdef\@doiabbr{ecologies}\gdef\@ISSN{2673-4133}\gdef\@continuouspages{yes}}
\DeclareOption{econometrics}{\gdef\@journal{econometrics}\gdef\@journalfull{Econometrics}\gdef\@journalshort{Econometrics}\gdef\@doiabbr{econometrics}\gdef\@ISSN{2225-1146}}
\DeclareOption{economies}{\gdef\@journal{economies}\gdef\@journalfull{Economies}\gdef\@journalshort{Economies}\gdef\@doiabbr{economies}\gdef\@ISSN{2227-7099}}
\DeclareOption{education}{\gdef\@journal{education}\gdef\@journalfull{Education Sciences}\gdef\@journalshort{Educ. Sci.}\gdef\@doiabbr{educsci}\gdef\@ISSN{2227-7102}}
\DeclareOption{ejihpe}{\gdef\@journal{ejihpe}\gdef\@journalfull{European Journal of Investigation in Health Psychology and Education}\gdef\@journalshort{Eur. J. Investig. Health Psychol. Educ.}\gdef\@doiabbr{ejihpe}\gdef\@ISSN{2254-9625}\gdef\@continuouspages{yes}}
\DeclareOption{electricity}{\gdef\@journal{electricity}\gdef\@journalfull{Electricity}\gdef\@journalshort{Electricity}\gdef\@doiabbr{electricity}\gdef\@ISSN{2673-4826}\gdef\@continuouspages{yes}}
\DeclareOption{electrochem}{\gdef\@journal{electrochem}\gdef\@journalfull{Electrochem}\gdef\@journalshort{Electrochem}\gdef\@doiabbr{electrochem}\gdef\@ISSN{2673-3293}\gdef\@continuouspages{yes}}
\DeclareOption{electronicmat}{\gdef\@journal{electronicmat}\gdef\@journalfull{Electronic Materials}\gdef\@journalshort{Electron. Mater.}\gdef\@doiabbr{electronicmat}\gdef\@ISSN{2673-3978}\gdef\@continuouspages{yes}}
\DeclareOption{electronics}{\gdef\@journal{electronics}\gdef\@journalfull{Electronics}\gdef\@journalshort{Electronics}\gdef\@doiabbr{electronics}\gdef\@ISSN{2079-9292}}
\DeclareOption{encyclopedia}{\gdef\@journal{encyclopedia}\gdef\@journalfull{Encyclopedia}\gdef\@journalshort{Encyclopedia}\gdef\@doiabbr{encyclopedia}\gdef\@ISSN{2673-8392}\gdef\@continuouspages{yes}}
\DeclareOption{endocrines}{\gdef\@journal{endocrines}\gdef\@journalfull{Endocrines}\gdef\@journalshort{Endocrines}\gdef\@doiabbr{endocrines}\gdef\@ISSN{2673-396X}\gdef\@continuouspages{yes}}
\DeclareOption{energies}{\gdef\@journal{energies}\gdef\@journalfull{Energies}\gdef\@journalshort{Energies}\gdef\@doiabbr{en}\gdef\@ISSN{1996-1073}}
\DeclareOption{eng}{\gdef\@journal{eng}\gdef\@journalfull{Eng-Advances in Engineering}\gdef\@journalshort{Eng}\gdef\@doiabbr{eng}\gdef\@ISSN{2673-4117}\gdef\@continuouspages{yes}}
\DeclareOption{engproc}{\gdef\@journal{engproc}\gdef\@journalfull{Engineering Proceedings}\gdef\@journalshort{Eng. Proc.}\gdef\@doiabbr{engproc}\gdef\@ISSN{2673-4591}}
%\DeclareOption{ent}{\gdef\@journal{ent}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{entomology}{\gdef\@journal{entomology}\gdef\@journalfull{Entomology}\gdef\@journalshort{Entomology}\gdef\@doiabbr{entomology}\gdef\@ISSN{2813-0502}\gdef\@continuouspages{yes}}	
\DeclareOption{entropy}{\gdef\@journal{entropy}\gdef\@journalfull{Entropy}\gdef\@journalshort{Entropy}\gdef\@doiabbr{e}\gdef\@ISSN{1099-4300}}
\DeclareOption{environments}{\gdef\@journal{environments}\gdef\@journalfull{Environments}\gdef\@journalshort{Environments}\gdef\@doiabbr{environments}\gdef\@ISSN{2076-3298}}
\DeclareOption{environsciproc}{\gdef\@journal{environsciproc}\gdef\@journalfull{Environmental Sciences Proceedings}\gdef\@journalshort{Environ. Sci. Proc.}\gdef\@doiabbr{environsciproc}\gdef\@ISSN{2673-4931}}
\DeclareOption{epidemiologia}{\gdef\@journal{epidemiologia}\gdef\@journalfull{Epidemiologia}\gdef\@journalshort{Epidemiologia}\gdef\@doiabbr{epidemiologia}\gdef\@ISSN{2673-3986}\gdef\@continuouspages{yes}}
\DeclareOption{epigenomes}{\gdef\@journal{epigenomes}\gdef\@journalfull{Epigenomes}\gdef\@journalshort{Epigenomes}\gdef\@doiabbr{epigenomes}\gdef\@ISSN{2075-4655}}
\DeclareOption{est}{\gdef\@journal{est}\gdef\@journalfull{Electrochemical Science and Technology}\gdef\@journalshort{Electrochem. Sci. Technol.}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{fermentation}{\gdef\@journal{fermentation}\gdef\@journalfull{Fermentation}\gdef\@journalshort{Fermentation}\gdef\@doiabbr{fermentation}\gdef\@ISSN{2311-5637}}
\DeclareOption{fibers}{\gdef\@journal{fibers}\gdef\@journalfull{Fibers}\gdef\@journalshort{Fibers}\gdef\@doiabbr{fib}\gdef\@ISSN{2079-6439}}
\DeclareOption{fintech}{\gdef\@journal{fintech}\gdef\@journalfull{FinTech}\gdef\@journalshort{FinTech}\gdef\@doiabbr{fintech}\gdef\@ISSN{2674-1032}\gdef\@continuouspages{yes}}
\DeclareOption{fire}{\gdef\@journal{fire}\gdef\@journalfull{Fire}\gdef\@journalshort{Fire}\gdef\@doiabbr{fire}\gdef\@ISSN{2571-6255}}
\DeclareOption{fishes}{\gdef\@journal{fishes}\gdef\@journalfull{Fishes}\gdef\@journalshort{Fishes}\gdef\@doiabbr{fishes}\gdef\@ISSN{2410-3888}}
\DeclareOption{fluids}{\gdef\@journal{fluids}\gdef\@journalfull{Fluids}\gdef\@journalshort{Fluids}\gdef\@doiabbr{fluids}\gdef\@ISSN{2311-5521}}
\DeclareOption{foods}{\gdef\@journal{foods}\gdef\@journalfull{Foods}\gdef\@journalshort{Foods}\gdef\@doiabbr{foods}\gdef\@ISSN{2304-8158}}
\DeclareOption{forecasting}{\gdef\@journal{forecasting}\gdef\@journalfull{Forecasting}\gdef\@journalshort{Forecasting}\gdef\@doiabbr{forecast}\gdef\@ISSN{2571-9394}\gdef\@continuouspages{yes}}
\DeclareOption{forensicsci}{\gdef\@journal{forensicsci}\gdef\@journalfull{Forensic Sciences}\gdef\@journalshort{Forensic Sci.}\gdef\@doiabbr{forensicsci}\gdef\@ISSN{2673-6756}\gdef\@continuouspages{yes}}
\DeclareOption{forests}{\gdef\@journal{forests}\gdef\@journalfull{Forests}\gdef\@journalshort{Forests}\gdef\@doiabbr{f}\gdef\@ISSN{1999-4907}}
\DeclareOption{foundations}{\gdef\@journal{foundations}\gdef\@journalfull{Foundations}\gdef\@journalshort{Foundations}\gdef\@doiabbr{foundations}\gdef\@ISSN{2673-9321}\gdef\@continuouspages{yes}}
\DeclareOption{fractalfract}{\gdef\@journal{fractalfract}\gdef\@journalfull{Fractal and Fractional}\gdef\@journalshort{Fractal Fract.}\gdef\@doiabbr{fractalfract}\gdef\@ISSN{2504-3110}}
\DeclareOption{fuels}{\gdef\@journal{fuels}\gdef\@journalfull{Fuels}\gdef\@journalshort{Fuels}\gdef\@doiabbr{fuels}\gdef\@ISSN{2673-3994}\gdef\@continuouspages{yes}}
\DeclareOption{futureinternet}{\gdef\@journal{futureinternet}\gdef\@journalfull{Future Internet}\gdef\@journalshort{Future Internet}\gdef\@doiabbr{fi}\gdef\@ISSN{1999-5903}}
%\DeclareOption{futureparasites}{\gdef\@journal{futureparasites}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{futurepharmacol}{\gdef\@journal{futurepharmacol}\gdef\@journalfull{Future Pharmacology}\gdef\@journalshort{Future Pharm.}\gdef\@doiabbr{futurepharmacol}\gdef\@ISSN{2673-9879}\gdef\@continuouspages{yes}}
\DeclareOption{futurephys}{\gdef\@journal{futurephys}\gdef\@journalfull{Future Physics}\gdef\@journalshort{Future Phys.}\gdef\@doiabbr{futurephys}\gdef\@ISSN{2624-6503}}
\DeclareOption{futuretransp}{\gdef\@journal{futuretransp}\gdef\@journalfull{Future Transportation}\gdef\@journalshort{Future Transp.}\gdef\@doiabbr{futuretransp}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{galaxies}{\gdef\@journal{galaxies}\gdef\@journalfull{Galaxies}\gdef\@journalshort{Galaxies}\gdef\@doiabbr{galaxies}\gdef\@ISSN{2075-4434}}
\DeclareOption{games}{\gdef\@journal{games}\gdef\@journalfull{Games}\gdef\@journalshort{Games}\gdef\@doiabbr{g}\gdef\@ISSN{2073-4336}}
\DeclareOption{gases}{\gdef\@journal{gases}\gdef\@journalfull{Gases}\gdef\@journalshort{Gases}\gdef\@doiabbr{gases}\gdef\@ISSN{2673-5628}\gdef\@continuouspages{yes}}
\DeclareOption{gastroent}{\gdef\@journal{gastroent}\gdef\@journalfull{Gastroenterology Insights}\gdef\@journalshort{Gastroenterol. Insights}\gdef\@doiabbr{gastroent}\gdef\@ISSN{2036-7422}\gdef\@continuouspages{yes}}
\DeclareOption{gastrointestdisord}{\gdef\@journal{gastrointestdisord}\gdef\@journalfull{Gastrointestinal Disorders}\gdef\@journalshort{Gastrointest. Disord.}\gdef\@doiabbr{gidisord}\gdef\@ISSN{2624-5647}\gdef\@continuouspages{yes}}
\DeclareOption{gels}{\gdef\@journal{gels}\gdef\@journalfull{Gels}\gdef\@journalshort{Gels}\gdef\@doiabbr{gels}\gdef\@ISSN{2310-2861}}
\DeclareOption{genealogy}{\gdef\@journal{genealogy}\gdef\@journalfull{Genealogy}\gdef\@journalshort{Genealogy}\gdef\@doiabbr{genealogy}\gdef\@ISSN{2313-5778}}
\DeclareOption{genes}{\gdef\@journal{genes}\gdef\@journalfull{Genes}\gdef\@journalshort{Genes}\gdef\@doiabbr{genes}\gdef\@ISSN{2073-4425}}
\DeclareOption{geographies}{\gdef\@journal{geographies}\gdef\@journalfull{Geographies}\gdef\@journalshort{Geographies}\gdef\@doiabbr{geographies}\gdef\@ISSN{2673-7086}\gdef\@continuouspages{yes}}
\DeclareOption{geohazards}{\gdef\@journal{geohazards}\gdef\@journalfull{GeoHazards}\gdef\@journalshort{GeoHazards}\gdef\@doiabbr{geohazards}\gdef\@ISSN{2624-795X}\gdef\@continuouspages{yes}}
\DeclareOption{geomatics}{\gdef\@journal{geomatics}\gdef\@journalfull{Geomatics}\gdef\@journalshort{Geomatics}\gdef\@doiabbr{geomatics}\gdef\@ISSN{2673-7418}\gdef\@continuouspages{yes}}
\DeclareOption{geosciences}{\gdef\@journal{geosciences}\gdef\@journalfull{Geosciences}\gdef\@journalshort{Geosciences}\gdef\@doiabbr{geosciences}\gdef\@ISSN{2076-3263}}
\DeclareOption{geotechnics}{\gdef\@journal{geotechnics}\gdef\@journalfull{Geotechnics}\gdef\@journalshort{Geotechnics}\gdef\@doiabbr{geotechnics}\gdef\@ISSN{2673-7094}\gdef\@continuouspages{yes}}
\DeclareOption{geriatrics}{\gdef\@journal{geriatrics}\gdef\@journalfull{Geriatrics}\gdef\@journalshort{Geriatrics}\gdef\@doiabbr{geriatrics}\gdef\@ISSN{2308-3417}}
\DeclareOption{grasses}{\gdef\@journal{grasses}\gdef\@journalfull{Grasses}\gdef\@journalshort{Grasses}\gdef\@doiabbr{grasses}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{hazardousmatters}{\gdef\@journal{hazardousmatters}\gdef\@journalfull{Hazardous Matters}\gdef\@journalshort{Hazard. Matters}\gdef\@doiabbr{}\gdef\@ISSN{0014-0014}}
\DeclareOption{healthcare}{\gdef\@journal{healthcare}\gdef\@journalfull{Healthcare}\gdef\@journalshort{Healthcare}\gdef\@doiabbr{healthcare}\gdef\@ISSN{2227-9032}}
\DeclareOption{hearts}{\gdef\@journal{hearts}\gdef\@journalfull{Hearts}\gdef\@journalshort{Hearts}\gdef\@doiabbr{hearts}\gdef\@ISSN{2673-3846}\gdef\@continuouspages{yes}}
\DeclareOption{hemato}{\gdef\@journal{hemato}\gdef\@journalfull{Hemato}\gdef\@journalshort{Hemato}\gdef\@doiabbr{hemato}\gdef\@ISSN{2673-6357}\gdef\@continuouspages{yes}}
\DeclareOption{hematolrep}{\gdef\@journal{hematolrep}\gdef\@journalfull{Hematology Reports}\gdef\@journalshort{Hematol. Rep.}\gdef\@doiabbr{hematolrep}\gdef\@ISSN{2038-8330}\gdef\@continuouspages{yes}}
\DeclareOption{heritage}{\gdef\@journal{heritage}\gdef\@journalfull{Heritage}\gdef\@journalshort{Heritage}\gdef\@doiabbr{heritage}\gdef\@ISSN{2571-9408}\gdef\@continuouspages{yes}}
\DeclareOption{highthroughput}{\gdef\@journal{highthroughput}\gdef\@journalfull{High-Throughput}\gdef\@journalshort{High-Throughput}\gdef\@doiabbr{ht}\gdef\@ISSN{2571-5135}}
\DeclareOption{histories}{\gdef\@journal{histories}\gdef\@journalfull{Histories}\gdef\@journalshort{Histories}\gdef\@doiabbr{histories}\gdef\@ISSN{2409-9252}\gdef\@continuouspages{yes}}
\DeclareOption{horticulturae}{\gdef\@journal{horticulturae}\gdef\@journalfull{Horticulturae}\gdef\@journalshort{Horticulturae}\gdef\@doiabbr{horticulturae}\gdef\@ISSN{2311-7524}}
\DeclareOption{humanities}{\gdef\@journal{humanities}\gdef\@journalfull{Humanities}\gdef\@journalshort{Humanities}\gdef\@doiabbr{h}\gdef\@ISSN{2076-0787}}
\DeclareOption{humans}{\gdef\@journal{humans}\gdef\@journalfull{Humans}\gdef\@journalshort{Humans}\gdef\@doiabbr{humans}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{hydrobiology}{\gdef\@journal{hydrobiology}\gdef\@journalfull{Hydrobiology}\gdef\@journalshort{Hydrobiology	}\gdef\@doiabbr{hydrobiology}\gdef\@ISSN{2673-9917}\gdef\@continuouspages{yes}}
\DeclareOption{hydrogen}{\gdef\@journal{hydrogen}\gdef\@journalfull{Hydrogen}\gdef\@journalshort{Hydrogen}\gdef\@doiabbr{hydrogen}\gdef\@ISSN{2673-4141}\gdef\@continuouspages{yes}}
\DeclareOption{hydrology}{\gdef\@journal{hydrology}\gdef\@journalfull{Hydrology}\gdef\@journalshort{Hydrology}\gdef\@doiabbr{hydrology}\gdef\@ISSN{2306-5338}}
\DeclareOption{hygiene}{\gdef\@journal{hygiene}\gdef\@journalfull{Hygiene}\gdef\@journalshort{Hygiene}\gdef\@doiabbr{hygiene}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{idr}{\gdef\@journal{idr}\gdef\@journalfull{Infectious Disease Reports}\gdef\@journalshort{Infect. Dis. Rep.}\gdef\@doiabbr{idr}\gdef\@ISSN{2036-7449}\gdef\@continuouspages{yes}}
\DeclareOption{ijerph}{\gdef\@journal{ijerph}\gdef\@journalfull{International Journal of Environmental Research and Public Health}\gdef\@journalshort{Int. J. Environ. Res. Public Health}\gdef\@doiabbr{ijerph}\gdef\@ISSN{1660-4601}}
\DeclareOption{ijfs}{\gdef\@journal{ijfs}\gdef\@journalfull{International Journal of Financial Studies}\gdef\@journalshort{Int. J. Financial Stud.}\gdef\@doiabbr{ijfs}\gdef\@ISSN{2227-7072}}
\DeclareOption{ijgi}{\gdef\@journal{ijgi}\gdef\@journalfull{ISPRS International Journal of Geo-Information}\gdef\@journalshort{ISPRS Int. J. Geo-Inf.}\gdef\@doiabbr{ijgi}\gdef\@ISSN{2220-9964}}
\DeclareOption{ijms}{\gdef\@journal{ijms}\gdef\@journalfull{International Journal of Molecular Sciences}\gdef\@journalshort{Int. J. Mol. Sci.}\gdef\@doiabbr{ijms}\gdef\@ISSN{1422-0067}}
\DeclareOption{ijns}{\gdef\@journal{ijns}\gdef\@journalfull{International Journal of Neonatal Screening}\gdef\@journalshort{Int. J. Neonatal Screen.}\gdef\@doiabbr{ijns}\gdef\@ISSN{2409-515X}}
\DeclareOption{ijpb}{\gdef\@journal{ijpb}\gdef\@journalfull{International Journal of Plant Biology}\gdef\@journalshort{Int. J. Plant Biol.}\gdef\@doiabbr{ijpb}\gdef\@ISSN{2037-0164}\gdef\@continuouspages{yes}}
\DeclareOption{ijtm}{\gdef\@journal{ijtm}\gdef\@journalfull{International Journal of Translational Medicine}\gdef\@journalshort{Int. J. Transl. Med.}\gdef\@doiabbr{ijtm}\gdef\@ISSN{2673-8937}\gdef\@continuouspages{yes}}
\DeclareOption{ijtpp}{\gdef\@journal{ijtpp}\gdef\@journalfull{International Journal of Turbomachinery Propulsion and Power}\gdef\@journalshort{Int. J. Turbomach. Propuls. Power}\gdef\@doiabbr{ijtpp}\gdef\@ISSN{2504-186X}}
\DeclareOption{ime}{\gdef\@journal{ime}\gdef\@journalfull{International Medical Education}\gdef\@journalshort{Int. Med. Educ.}\gdef\@doiabbr{ime}\gdef\@ISSN{2813-141X}\gdef\@continuouspages{yes}}
\DeclareOption{immuno}{\gdef\@journal{immuno}\gdef\@journalfull{Immuno}\gdef\@journalshort{Immuno}\gdef\@doiabbr{immuno}\gdef\@ISSN{2673-5601}\gdef\@continuouspages{yes}}
\DeclareOption{informatics}{\gdef\@journal{informatics}\gdef\@journalfull{Informatics}\gdef\@journalshort{Informatics}\gdef\@doiabbr{informatics}\gdef\@ISSN{2227-9709}}
\DeclareOption{information}{\gdef\@journal{information}\gdef\@journalfull{Information}\gdef\@journalshort{Information}\gdef\@doiabbr{info}\gdef\@ISSN{2078-2489}}
\DeclareOption{infrastructures}{\gdef\@journal{infrastructures}\gdef\@journalfull{Infrastructures}\gdef\@journalshort{Infrastructures}\gdef\@doiabbr{infrastructures}\gdef\@ISSN{2412-3811}}
\DeclareOption{inorganics}{\gdef\@journal{inorganics}\gdef\@journalfull{Inorganics}\gdef\@journalshort{Inorganics}\gdef\@doiabbr{inorganics}\gdef\@ISSN{2304-6740}}
\DeclareOption{insects}{\gdef\@journal{insects}\gdef\@journalfull{Insects}\gdef\@journalshort{Insects}\gdef\@doiabbr{insects}\gdef\@ISSN{2075-4450}}
\DeclareOption{instruments}{\gdef\@journal{instruments}\gdef\@journalfull{Instruments}\gdef\@journalshort{Instruments}\gdef\@doiabbr{instruments}\gdef\@ISSN{2410-390X}}
\DeclareOption{inventions}{\gdef\@journal{inventions}\gdef\@journalfull{Inventions}\gdef\@journalshort{Inventions}\gdef\@doiabbr{inventions}\gdef\@ISSN{2411-5134}}
\DeclareOption{iot}{\gdef\@journal{iot}\gdef\@journalfull{IoT}\gdef\@journalshort{IoT}\gdef\@doiabbr{iot}\gdef\@ISSN{2624-831X}\gdef\@continuouspages{yes}}
\DeclareOption{j}{\gdef\@journal{j}\gdef\@journalfull{J}\gdef\@journalshort{J}\gdef\@doiabbr{j}\gdef\@ISSN{2571-8800}\gdef\@continuouspages{yes}}
\DeclareOption{jal}{\gdef\@journal{jal}\gdef\@journalfull{Journal of Ageing and Longevity}\gdef\@journalshort{J. Ageing Longev.}\gdef\@doiabbr{jal}\gdef\@ISSN{2673-9259}\gdef\@continuouspages{yes}}
\DeclareOption{jcdd}{\gdef\@journal{jcdd}\gdef\@journalfull{Journal of Cardiovascular Development and Disease}\gdef\@journalshort{J. Cardiovasc. Dev. Dis.}\gdef\@doiabbr{jcdd}\gdef\@ISSN{2308-3425}}
\DeclareOption{jcm}{\gdef\@journal{jcm}\gdef\@journalfull{Journal of Clinical Medicine}\gdef\@journalshort{J. Clin. Med.}\gdef\@doiabbr{jcm}\gdef\@ISSN{2077-0383}}
\DeclareOption{jcp}{\gdef\@journal{jcp}\gdef\@journalfull{Journal of Cybersecurity and Privacy}\gdef\@journalshort{J. Cybersecur. Priv.}\gdef\@doiabbr{jcp}\gdef\@ISSN{2624-800X}\gdef\@continuouspages{yes}}
\DeclareOption{jcs}{\gdef\@journal{jcs}\gdef\@journalfull{Journal of Composites Science}\gdef\@journalshort{J. Compos. Sci.}\gdef\@doiabbr{jcs}\gdef\@ISSN{2504-477X}}
\DeclareOption{jcto}{\gdef\@journal{jcto}\gdef\@journalfull{Journal of Clinical \& Translational Ophthalmology}\gdef\@journalshort{J. Clin. Transl. Ophthalmol.}\gdef\@doiabbr{jcto}\gdef\@ISSN{2813-1053}\gdef\@continuouspages{yes}}
\DeclareOption{jdb}{\gdef\@journal{jdb}\gdef\@journalfull{Journal of Developmental Biology}\gdef\@journalshort{J. Dev. Biol.}\gdef\@doiabbr{jdb}\gdef\@ISSN{2221-3759}}
\DeclareOption{jeta}{\gdef\@journal{jeta}\gdef\@journalfull{Journal of Experimental and Theoretical Analyses}\gdef\@journalshort{J. Exp. Theor. Anal.}\gdef\@doiabbr{jeta}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{jfb}{\gdef\@journal{jfb}\gdef\@journalfull{Journal of Functional Biomaterials}\gdef\@journalshort{J. Funct. Biomater.}\gdef\@doiabbr{jfb}\gdef\@ISSN{2079-4983}}
\DeclareOption{jfmk}{\gdef\@journal{jfmk}\gdef\@journalfull{Journal of Functional Morphology and Kinesiology}\gdef\@journalshort{J. Funct. Morphol. Kinesiol.}\gdef\@doiabbr{jfmk}\gdef\@ISSN{2411-5142}}
\DeclareOption{jimaging}{\gdef\@journal{jimaging}\gdef\@journalfull{Journal of Imaging}\gdef\@journalshort{J. Imaging}\gdef\@doiabbr{jimaging}\gdef\@ISSN{2313-433X}}
\DeclareOption{jintelligence}{\gdef\@journal{jintelligence}\gdef\@journalfull{Journal of Intelligence}\gdef\@journalshort{J. Intell.}\gdef\@doiabbr{jintelligence}\gdef\@ISSN{2079-3200}}
\DeclareOption{jlpea}{\gdef\@journal{jlpea}\gdef\@journalfull{Journal of Low Power Electronics and Applications}\gdef\@journalshort{J. Low Power Electron. Appl.}\gdef\@doiabbr{jlpea}\gdef\@ISSN{2079-9268}}
\DeclareOption{jmmp}{\gdef\@journal{jmmp}\gdef\@journalfull{Journal of Manufacturing and Materials Processing}\gdef\@journalshort{J. Manuf. Mater. Process.}\gdef\@doiabbr{jmmp}\gdef\@ISSN{2504-4494}}
\DeclareOption{jmp}{\gdef\@journal{jmp}\gdef\@journalfull{Journal of Molecular Pathology}\gdef\@journalshort{J. Mol. Pathol.}\gdef\@doiabbr{jmp}\gdef\@ISSN{2673-5261}\gdef\@continuouspages{yes}}
\DeclareOption{jmse}{\gdef\@journal{jmse}\gdef\@journalfull{Journal of Marine Science and Engineering}\gdef\@journalshort{J. Mar. Sci. Eng.}\gdef\@doiabbr{jmse}\gdef\@ISSN{2077-1312}}
\DeclareOption{jne}{\gdef\@journal{jne}\gdef\@journalfull{Journal of Nuclear Engineering}\gdef\@journalshort{J. Nucl. Eng.}\gdef\@doiabbr{jne}\gdef\@ISSN{2673-4362}\gdef\@continuouspages{yes}}
\DeclareOption{jnt}{\gdef\@journal{jnt}\gdef\@journalfull{Journal of Nanotheranostics}\gdef\@journalshort{J. Nanotheranostics}\gdef\@doiabbr{jnt}\gdef\@ISSN{2624-845X}\gdef\@continuouspages{yes}}
\DeclareOption{jof}{\gdef\@journal{jof}\gdef\@journalfull{Journal of Fungi}\gdef\@journalshort{J. Fungi}\gdef\@doiabbr{jof}\gdef\@ISSN{2309-608X}}
\DeclareOption{joitmc}{\gdef\@journal{joitmc}\gdef\@journalfull{Journal of Open Innovation: Technology Market and Complexity}\gdef\@journalshort{J. Open Innov. Technol. Mark. Complex.}\gdef\@doiabbr{joitmc}\gdef\@ISSN{2199-8531}}
\DeclareOption{jor}{\gdef\@journal{jor}\gdef\@journalfull{Journal of Respiration}\gdef\@journalshort{J. Respir.}\gdef\@doiabbr{jor}\gdef\@ISSN{2673-527X}\gdef\@continuouspages{yes}}
\DeclareOption{journalmedia}{\gdef\@journal{journalmedia}\gdef\@journalfull{Journalism and Media}\gdef\@journalshort{Journal. Media}\gdef\@doiabbr{journalmedia}\gdef\@ISSN{2673-5172}\gdef\@continuouspages{yes}}
\DeclareOption{jox}{\gdef\@journal{jox}\gdef\@journalfull{Journal of Xenobiotics}\gdef\@journalshort{J. Xenobiot.}\gdef\@doiabbr{jox}\gdef\@ISSN{2039-4713}\gdef\@continuouspages{yes}}
\DeclareOption{jpm}{\gdef\@journal{jpm}\gdef\@journalfull{Journal of Personalized Medicine}\gdef\@journalshort{J. Pers. Med.}\gdef\@doiabbr{jpm}\gdef\@ISSN{2075-4426}}
\DeclareOption{jrfm}{\gdef\@journal{jrfm}\gdef\@journalfull{Journal of Risk and Financial Management}\gdef\@journalshort{J. Risk Financial Manag.}\gdef\@doiabbr{jrfm}\gdef\@ISSN{1911-8074}}
\DeclareOption{jsan}{\gdef\@journal{jsan}\gdef\@journalfull{Journal of Sensor and Actuator Networks}\gdef\@journalshort{J. Sens. Actuator Netw.}\gdef\@doiabbr{jsan}\gdef\@ISSN{2224-2708}}
\DeclareOption{jtaer}{\gdef\@journal{jtaer}\gdef\@journalfull{Journal of Theoretical and Applied Electronic Commerce Research}\gdef\@journalshort{J. Theor. Appl. Electron. Commer. Res.}\gdef\@doiabbr{jtaer}\gdef\@ISSN{0718-1876}\gdef\@continuouspages{yes}}
\DeclareOption{jvd}{\gdef\@journal{jvd}\gdef\@journalfull{Journal of Vascular Diseases}\gdef\@journalshort{JVD}\gdef\@doiabbr{jvd}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{jzbg}{\gdef\@journal{jzbg}\gdef\@journalfull{Journal of Zoological and Botanical Gardens}\gdef\@journalshort{J. Zool. Bot. Gard.}\gdef\@doiabbr{jzbg}\gdef\@ISSN{2673-5636}\gdef\@continuouspages{yes}}
%\DeclareOption{kidney}{\gdef\@journal{kidney}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{kidneydial}{\gdef\@journal{kidneydial}\gdef\@journalfull{Kidney and Dialysis}\gdef\@journalshort{Kidney Dial.}\gdef\@doiabbr{kinasesphosphatases}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{kinasesphosphatases}{\gdef\@journal{kinasesphosphatases}\gdef\@journalfull{Kinases and Phosphatases}\gdef\@journalshort{Kinases Phosphatases}\gdef\@doiabbr{kinasesphosphatases}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{knowledge}{\gdef\@journal{knowledge}\gdef\@journalfull{Knowledge}\gdef\@journalshort{Knowledge}\gdef\@doiabbr{knowledge}\gdef\@ISSN{2673-9585}\gdef\@continuouspages{yes}}
\DeclareOption{land}{\gdef\@journal{land}\gdef\@journalfull{Land}\gdef\@journalshort{Land}\gdef\@doiabbr{land}\gdef\@ISSN{2073-445X}}
\DeclareOption{languages}{\gdef\@journal{languages}\gdef\@journalfull{Languages}\gdef\@journalshort{Languages}\gdef\@doiabbr{languages}\gdef\@ISSN{2226-471X}}
\DeclareOption{laws}{\gdef\@journal{laws}\gdef\@journalfull{Laws}\gdef\@journalshort{Laws}\gdef\@doiabbr{laws}\gdef\@ISSN{2075-471X}}
\DeclareOption{life}{\gdef\@journal{life}\gdef\@journalfull{Life}\gdef\@journalshort{Life}\gdef\@doiabbr{life}\gdef\@ISSN{2075-1729}}
\DeclareOption{liquids}{\gdef\@journal{liquids}\gdef\@journalfull{Liquids}\gdef\@journalshort{Liquids}\gdef\@doiabbr{liquids}\gdef\@ISSN{2673-8015}\gdef\@continuouspages{yes}}
\DeclareOption{literature}{\gdef\@journal{literature}\gdef\@journalfull{Literature}\gdef\@journalshort{Literature}\gdef\@doiabbr{literature}\gdef\@ISSN{2410-9789}\gdef\@continuouspages{yes}}
\DeclareOption{livers}{\gdef\@journal{livers}\gdef\@journalfull{Livers}\gdef\@journalshort{Livers}\gdef\@doiabbr{livers}\gdef\@ISSN{2673-4389}\gdef\@continuouspages{yes}}
\DeclareOption{logics}{\gdef\@journal{logics}\gdef\@journalfull{Logics}\gdef\@journalshort{Logics}\gdef\@doiabbr{logics}\gdef\@ISSN{2813-0405}\gdef\@continuouspages{yes}}
\DeclareOption{logistics}{\gdef\@journal{logistics}\gdef\@journalfull{Logistics}\gdef\@journalshort{Logistics}\gdef\@doiabbr{logistics}\gdef\@ISSN{2305-6290}}
\DeclareOption{lubricants}{\gdef\@journal{lubricants}\gdef\@journalfull{Lubricants}\gdef\@journalshort{Lubricants}\gdef\@doiabbr{lubricants}\gdef\@ISSN{2075-4442}}
\DeclareOption{lymphatics}{\gdef\@journal{lymphatics}\gdef\@journalfull{Lymphatics}\gdef\@journalshort{Lymphatics}\gdef\@doiabbr{lymphatics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}	
\DeclareOption{machines}{\gdef\@journal{machines}\gdef\@journalfull{Machines}\gdef\@journalshort{Machines}\gdef\@doiabbr{machines}\gdef\@ISSN{2075-1702}}
\DeclareOption{macromol}{\gdef\@journal{macromol}\gdef\@journalfull{Macromol}\gdef\@journalshort{Macromol}\gdef\@doiabbr{macromol}\gdef\@ISSN{2673-6209}\gdef\@continuouspages{yes}}
\DeclareOption{magnetism}{\gdef\@journal{magnetism}\gdef\@journalfull{Magnetism}\gdef\@journalshort{Magnetism}\gdef\@doiabbr{magnetism}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{magnetochemistry}{\gdef\@journal{magnetochemistry}\gdef\@journalfull{Magnetochemistry}\gdef\@journalshort{Magnetochemistry}\gdef\@doiabbr{magnetochemistry}\gdef\@ISSN{2312-7481}}
\DeclareOption{make}{\gdef\@journal{make}\gdef\@journalfull{Machine Learning and Knowledge Extraction}\gdef\@journalshort{Mach. Learn. Knowl. Extr.}\gdef\@doiabbr{make}\gdef\@ISSN{2504-4990}\gdef\@continuouspages{yes}}
\DeclareOption{marinedrugs}{\gdef\@journal{marinedrugs}\gdef\@journalfull{Marine Drugs}\gdef\@journalshort{Mar. Drugs}\gdef\@doiabbr{md}\gdef\@ISSN{1660-3397}}
\DeclareOption{materials}{\gdef\@journal{materials}\gdef\@journalfull{Materials}\gdef\@journalshort{Materials}\gdef\@doiabbr{ma}\gdef\@ISSN{1996-1944}}
\DeclareOption{materproc}{\gdef\@journal{materproc}\gdef\@journalfull{Materials Proceedings}\gdef\@journalshort{Mater. Proc.}\gdef\@doiabbr{materproc}\gdef\@ISSN{2673-4605}}
\DeclareOption{mathematics}{\gdef\@journal{mathematics}\gdef\@journalfull{Mathematics}\gdef\@journalshort{Mathematics}\gdef\@doiabbr{math}\gdef\@ISSN{2227-7390}}
\DeclareOption{mca}{\gdef\@journal{mca}\gdef\@journalfull{Mathematical and Computational Applications}\gdef\@journalshort{Math. Comput. Appl.}\gdef\@doiabbr{mca}\gdef\@ISSN{2297-8747}}
\DeclareOption{measurements}{\gdef\@journal{measurements}\gdef\@journalfull{Measurements}\gdef\@journalshort{Measurements}\gdef\@doiabbr{measurements}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{medicina}{\gdef\@journal{medicina}\gdef\@journalfull{Medicina}\gdef\@journalshort{Medicina}\gdef\@doiabbr{medicina}\gdef\@ISSN{1648-9144}}
\DeclareOption{medicines}{\gdef\@journal{medicines}\gdef\@journalfull{Medicines}\gdef\@journalshort{Medicines}\gdef\@doiabbr{medicines}\gdef\@ISSN{2305-6320}}
\DeclareOption{medsci}{\gdef\@journal{medsci}\gdef\@journalfull{Medical Sciences}\gdef\@journalshort{Med. Sci.}\gdef\@doiabbr{medsci}\gdef\@ISSN{2076-3271}}
\DeclareOption{membranes}{\gdef\@journal{membranes}\gdef\@journalfull{Membranes}\gdef\@journalshort{Membranes}\gdef\@doiabbr{membranes}\gdef\@ISSN{2077-0375}}
\DeclareOption{merits}{\gdef\@journal{merits}\gdef\@journalfull{Merits}\gdef\@journalshort{Merits}\gdef\@doiabbr{merits}\gdef\@ISSN{2673-8104}\gdef\@continuouspages{yes}}
\DeclareOption{metabolites}{\gdef\@journal{metabolites}\gdef\@journalfull{Metabolites}\gdef\@journalshort{Metabolites}\gdef\@doiabbr{metabo}\gdef\@ISSN{2218-1989}}
\DeclareOption{metals}{\gdef\@journal{metals}\gdef\@journalfull{Metals}\gdef\@journalshort{Metals}\gdef\@doiabbr{met}\gdef\@ISSN{2075-4701}}
\DeclareOption{meteorology}{\gdef\@journal{meteorology}\gdef\@journalfull{Meteorology}\gdef\@journalshort{Meteorology}\gdef\@doiabbr{meteorology}\gdef\@ISSN{2674-0494}\gdef\@continuouspages{yes}}
\DeclareOption{methane}{\gdef\@journal{methane}\gdef\@journalfull{Methane}\gdef\@journalshort{Methane}\gdef\@doiabbr{methane}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{metrology}{\gdef\@journal{metrology}\gdef\@journalfull{Metrology}\gdef\@journalshort{Metrology}\gdef\@doiabbr{metrology}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{micro}{\gdef\@journal{micro}\gdef\@journalfull{Micro}\gdef\@journalshort{Micro}\gdef\@doiabbr{micro}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{microarrays}{\gdef\@journal{microarrays}\gdef\@journalfull{Microarrays}\gdef\@journalshort{Microarrays}\gdef\@doiabbr{microarrays}\gdef\@ISSN{2076-3905}}
\DeclareOption{microbiolres}{\gdef\@journal{microbiolres}\gdef\@journalfull{Microbiology Research}\gdef\@journalshort{Microbiol. Res.}\gdef\@doiabbr{microbiolres}\gdef\@ISSN{2036-7481}\gdef\@continuouspages{yes}}
\DeclareOption{micromachines}{\gdef\@journal{micromachines}\gdef\@journalfull{Micromachines}\gdef\@journalshort{Micromachines}\gdef\@doiabbr{mi}\gdef\@ISSN{2072-666X}}
\DeclareOption{microorganisms}{\gdef\@journal{microorganisms}\gdef\@journalfull{Microorganisms}\gdef\@journalshort{Microorganisms}\gdef\@doiabbr{microorganisms}\gdef\@ISSN{2076-2607}}
\DeclareOption{microplastics}{\gdef\@journal{microplastics}\gdef\@journalfull{Microplastics}\gdef\@journalshort{Microplastics}\gdef\@doiabbr{microplastics}\gdef\@ISSN{2673-8929}\gdef\@continuouspages{yes}}
\DeclareOption{minerals}{\gdef\@journal{minerals}\gdef\@journalfull{Minerals}\gdef\@journalshort{Minerals}\gdef\@doiabbr{min}\gdef\@ISSN{2075-163X}}
\DeclareOption{mining}{\gdef\@journal{mining}\gdef\@journalfull{Mining}\gdef\@journalshort{Mining}\gdef\@doiabbr{mining}\gdef\@ISSN{2673-6489}\gdef\@continuouspages{yes}}
\DeclareOption{modelling}{\gdef\@journal{modelling}\gdef\@journalfull{Modelling}\gdef\@journalshort{Modelling}\gdef\@doiabbr{modelling}\gdef\@ISSN{2673-3951}\gdef\@continuouspages{yes}}
\DeclareOption{molbank}{\gdef\@journal{molbank}\gdef\@journalfull{Molbank}\gdef\@journalshort{Molbank}\gdef\@doiabbr{M}\gdef\@ISSN{1422-8599}}
\DeclareOption{molecules}{\gdef\@journal{molecules}\gdef\@journalfull{Molecules}\gdef\@journalshort{Molecules}\gdef\@doiabbr{molecules}\gdef\@ISSN{1420-3049}}
\DeclareOption{mps}{\gdef\@journal{mps}\gdef\@journalfull{Methods and Protocols}\gdef\@journalshort{Methods Protoc.}\gdef\@doiabbr{mps}\gdef\@ISSN{2409-9279}}
\DeclareOption{msf}{\gdef\@journal{msf}\gdef\@journalfull{Medical Sciences Forum}\gdef\@journalshort{Med. Sci. Forum}\gdef\@doiabbr{msf}\gdef\@ISSN{2673-9992}}
\DeclareOption{mti}{\gdef\@journal{mti}\gdef\@journalfull{Multimodal Technologies and Interaction}\gdef\@journalshort{Multimodal Technol. Interact.}\gdef\@doiabbr{mti}\gdef\@ISSN{2414-4088}}
\DeclareOption{muscles}{\gdef\@journal{muscles}\gdef\@journalfull{Muscles}\gdef\@journalshort{Muscles}\gdef\@doiabbr{muscles}\gdef\@ISSN{2813-0413}\gdef\@continuouspages{yes}}
\DeclareOption{nanoenergyadv}{\gdef\@journal{nanoenergyadv}\gdef\@journalfull{Nanoenergy Advances}\gdef\@journalshort{Nanoenergy Adv.}\gdef\@doiabbr{nanoenergyadv}\gdef\@ISSN{2673-706X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomanufacturing}{\gdef\@journal{nanomanufacturing}\gdef\@journalfull{Nanomanufacturing}\gdef\@journalshort{Nanomanufacturing}\gdef\@doiabbr{nanomanufacturing}\gdef\@ISSN{2673-687X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomaterials}{\gdef\@journal{nanomaterials}\gdef\@journalfull{Nanomaterials}\gdef\@journalshort{Nanomaterials}\gdef\@doiabbr{nano}\gdef\@ISSN{2079-4991}}
\DeclareOption{ncrna}{\gdef\@journal{ncrna}\gdef\@journalfull{Non-Coding RNA}\gdef\@journalshort{Non-Coding RNA}\gdef\@doiabbr{ncrna}\gdef\@ISSN{2311-553X}}
\DeclareOption{network}{\gdef\@journal{network}\gdef\@journalfull{Network}\gdef\@journalshort{Network}\gdef\@doiabbr{network}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{neuroglia}{\gdef\@journal{neuroglia}\gdef\@journalfull{Neuroglia}\gdef\@journalshort{Neuroglia}\gdef\@doiabbr{neuroglia}\gdef\@ISSN{2571-6980}\gdef\@continuouspages{yes}}
\DeclareOption{neurolint}{\gdef\@journal{neurolint}\gdef\@journalfull{Neurology International}\gdef\@journalshort{Neurol. Int.}\gdef\@doiabbr{neurolint}\gdef\@ISSN{2035-8377}\gdef\@continuouspages{yes}}
\DeclareOption{neurosci}{\gdef\@journal{neurosci}\gdef\@journalfull{NeuroSci}\gdef\@journalshort{NeuroSci}\gdef\@doiabbr{neurosci}\gdef\@ISSN{2673-4087}\gdef\@continuouspages{yes}}
\DeclareOption{nitrogen}{\gdef\@journal{nitrogen}\gdef\@journalfull{Nitrogen}\gdef\@journalshort{Nitrogen}\gdef\@doiabbr{nitrogen}\gdef\@ISSN{2504-3129}\gdef\@continuouspages{yes}}
\DeclareOption{notspecified}{\gdef\@journal{notspecified}\gdef\@journalfull{Journal Not Specified}\gdef\@journalshort{Journal Not Specified}\gdef\@doiabbr{}\gdef\@ISSN{}}
%%\DeclareOption{nri}{\gdef\@journal{nri}\gdef\@journalfull{Natural Resources Informatics}\gdef\@journalshort{Nat. Resour. Inform.}\gdef\@doiabbr{nri}\gdef\@ISSN{2673-981X}\gdef\@continuouspages{yes}}
\DeclareOption{nursrep}{\gdef\@journal{nursrep}\gdef\@journalfull{Nursing Reports}\gdef\@journalshort{Nurs. Rep.}\gdef\@doiabbr{nursrep}\gdef\@ISSN{2039-4403}\gdef\@continuouspages{yes}}
\DeclareOption{nutraceuticals}{\gdef\@journal{nutraceuticals}\gdef\@journalfull{Nutraceuticals}\gdef\@journalshort{Nutraceuticals}\gdef\@doiabbr{nutraceuticals}\gdef\@ISSN{1661-3821}\gdef\@continuouspages{yes}}
\DeclareOption{nutrients}{\gdef\@journal{nutrients}\gdef\@journalfull{Nutrients}\gdef\@journalshort{Nutrients}\gdef\@doiabbr{nu}\gdef\@ISSN{2072-6643}}
\DeclareOption{obesities}{\gdef\@journal{obesities}\gdef\@journalfull{Obesities}\gdef\@journalshort{Obesities}\gdef\@doiabbr{obesities}\gdef\@ISSN{2673-4168}\gdef\@continuouspages{yes}}
\DeclareOption{oceans}{\gdef\@journal{oceans}\gdef\@journalfull{Oceans}\gdef\@journalshort{Oceans}\gdef\@doiabbr{oceans}\gdef\@ISSN{2673-1924}\gdef\@continuouspages{yes}}
\DeclareOption{ohbm}{\gdef\@journal{ohbm}\gdef\@journalfull{Journal of Otorhinolaryngology Hearing and Balance Medicine}\gdef\@journalshort{J. Otorhinolaryngol. Hear. Balance Med.}\gdef\@doiabbr{ohbm}\gdef\@ISSN{2504-463X}}
\DeclareOption{onco}{\gdef\@journal{onco}\gdef\@journalfull{Onco}\gdef\@journalshort{Onco}\gdef\@doiabbr{onco}\gdef\@ISSN{2673-7523}\gdef\@continuouspages{yes}}
%\DeclareOption{oncopathology}{\gdef\@journal{oncopathology}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{optics}{\gdef\@journal{optics}\gdef\@journalfull{Optics}\gdef\@journalshort{Optics}\gdef\@doiabbr{opt}\gdef\@ISSN{2673-3269}\gdef\@continuouspages{yes}}
\DeclareOption{oral}{\gdef\@journal{oral}\gdef\@journalfull{Oral}\gdef\@journalshort{Oral}\gdef\@doiabbr{oral}\gdef\@ISSN{2673-6373}\gdef\@continuouspages{yes}}
\DeclareOption{organics}{\gdef\@journal{organics}\gdef\@journalfull{Organics}\gdef\@journalshort{Organics}\gdef\@doiabbr{org}\gdef\@ISSN{2673-401X}\gdef\@continuouspages{yes}}
\DeclareOption{organoids}{\gdef\@journal{organoids}\gdef\@journalfull{Organoids}\gdef\@journalshort{Organoids}\gdef\@doiabbr{organoids}\gdef\@ISSN{2674-1172}\gdef\@continuouspages{yes}}
\DeclareOption{osteology}{\gdef\@journal{osteology}\gdef\@journalfull{Osteology}\gdef\@journalshort{Osteology}\gdef\@doiabbr{osteology}\gdef\@ISSN{2673-4036}\gdef\@continuouspages{yes}}
\DeclareOption{oxygen}{\gdef\@journal{oxygen}\gdef\@journalfull{Oxygen}\gdef\@journalshort{Oxygen}\gdef\@doiabbr{oxygen}\gdef\@ISSN{2673-9801}\gdef\@continuouspages{yes}}
\DeclareOption{parasites}{\gdef\@journal{parasites}\gdef\@journalfull{Parasites}\gdef\@journalshort{Parasites}\gdef\@doiabbr{parasites}\gdef\@ISSN{2673-5946}}
\DeclareOption{parasitologia}{\gdef\@journal{parasitologia}\gdef\@journalfull{Parasitologia}\gdef\@journalshort{Parasitologia}\gdef\@doiabbr{parasitologia}\gdef\@ISSN{2673-6772}\gdef\@continuouspages{yes}}
\DeclareOption{particles}{\gdef\@journal{particles}\gdef\@journalfull{Particles}\gdef\@journalshort{Particles}\gdef\@doiabbr{particles}\gdef\@ISSN{2571-712X}\gdef\@continuouspages{yes}}
\DeclareOption{pathogens}{\gdef\@journal{pathogens}\gdef\@journalfull{Pathogens}\gdef\@journalshort{Pathogens}\gdef\@doiabbr{pathogens}\gdef\@ISSN{2076-0817}}
\DeclareOption{pathophysiology}{\gdef\@journal{pathophysiology}\gdef\@journalfull{Pathophysiology}\gdef\@journalshort{Pathophysiology}\gdef\@doiabbr{pathophysiology}\gdef\@ISSN{0928-4680}\gdef\@continuouspages{yes}}
\DeclareOption{pediatrrep}{\gdef\@journal{pediatrrep}\gdef\@journalfull{Pediatric Reports}\gdef\@journalshort{Pediatr. Rep.}\gdef\@doiabbr{pediatric}\gdef\@ISSN{2036-7503}\gdef\@continuouspages{yes}}
\DeclareOption{pharmaceuticals}{\gdef\@journal{pharmaceuticals}\gdef\@journalfull{Pharmaceuticals}\gdef\@journalshort{Pharmaceuticals}\gdef\@doiabbr{ph}\gdef\@ISSN{1424-8247}}
\DeclareOption{pharmaceutics}{\gdef\@journal{pharmaceutics}\gdef\@journalfull{Pharmaceutics}\gdef\@journalshort{Pharmaceutics}\gdef\@doiabbr{pharmaceutics}\gdef\@ISSN{1999-4923}}
\DeclareOption{pharmacoepidemiology}{\gdef\@journal{pharmacoepidemiology}\gdef\@journalfull{Pharmacoepidemiology}\gdef\@journalshort{Pharmacoepidemiology}\gdef\@doiabbr{pharma}\gdef\@ISSN{2813-0618}\gdef\@continuouspages{yes}}
\DeclareOption{pharmacy}{\gdef\@journal{pharmacy}\gdef\@journalfull{Pharmacy}\gdef\@journalshort{Pharmacy}\gdef\@doiabbr{pharmacy}\gdef\@ISSN{2226-4787}}
\DeclareOption{philosophies}{\gdef\@journal{philosophies}\gdef\@journalfull{Philosophies}\gdef\@journalshort{Philosophies}\gdef\@doiabbr{philosophies}\gdef\@ISSN{2409-9287}}
\DeclareOption{photochem}{\gdef\@journal{photochem}\gdef\@journalfull{Photochem}\gdef\@journalshort{Photochem}\gdef\@doiabbr{photochem}\gdef\@ISSN{2673-7256}\gdef\@continuouspages{yes}}
\DeclareOption{photonics}{\gdef\@journal{photonics}\gdef\@journalfull{Photonics}\gdef\@journalshort{Photonics}\gdef\@doiabbr{photonics}\gdef\@ISSN{2304-6732}}
\DeclareOption{phycology}{\gdef\@journal{phycology}\gdef\@journalfull{Phycology}\gdef\@journalshort{Phycology}\gdef\@doiabbr{phycology}\gdef\@ISSN{2673-9410}\gdef\@continuouspages{yes}}
\DeclareOption{physchem}{\gdef\@journal{physchem}\gdef\@journalfull{Physchem}\gdef\@journalshort{Physchem}\gdef\@doiabbr{physchem}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{physics}{\gdef\@journal{physics}\gdef\@journalfull{Physics}\gdef\@journalshort{Physics}\gdef\@doiabbr{physics}\gdef\@ISSN{2624-8174}\gdef\@continuouspages{yes}}
\DeclareOption{physiologia}{\gdef\@journal{physiologia}\gdef\@journalfull{Physiologia}\gdef\@journalshort{Physiologia}\gdef\@doiabbr{physiologia}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{plants}{\gdef\@journal{plants}\gdef\@journalfull{Plants}\gdef\@journalshort{Plants}\gdef\@doiabbr{plants}\gdef\@ISSN{2223-7747}}
\DeclareOption{plasma}{\gdef\@journal{plasma}\gdef\@journalfull{Plasma}\gdef\@journalshort{Plasma}\gdef\@doiabbr{plasma}\gdef\@ISSN{2571-6182}\gdef\@continuouspages{yes}}
\DeclareOption{pollutants}{\gdef\@journal{pollutants}\gdef\@journalfull{Pollutants}\gdef\@journalshort{Pollutants}\gdef\@doiabbr{pollutants}\gdef\@ISSN{2673-4672}\gdef\@continuouspages{yes}}
\DeclareOption{polymers}{\gdef\@journal{polymers}\gdef\@journalfull{Polymers}\gdef\@journalshort{Polymers}\gdef\@doiabbr{polym}\gdef\@ISSN{2073-4360}}
\DeclareOption{polysaccharides}{\gdef\@journal{polysaccharides}\gdef\@journalfull{Polysaccharides}\gdef\@journalshort{Polysaccharides}\gdef\@doiabbr{polysaccharides}\gdef\@ISSN{2673-4176}\gdef\@continuouspages{yes}}
\DeclareOption{poultry}{\gdef\@journal{poultry}\gdef\@journalfull{Poultry}\gdef\@journalshort{Poultry}\gdef\@doiabbr{poultry}\gdef\@ISSN{2674-1164}\gdef\@continuouspages{yes}}
\DeclareOption{powders}{\gdef\@journal{powders}\gdef\@journalfull{Powders}\gdef\@journalshort{Powders}\gdef\@doiabbr{powders}\gdef\@ISSN{2674-0516}\gdef\@continuouspages{yes}}
\DeclareOption{preprints}{\gdef\@journal{preprints}\gdef\@journalfull{Preprints}\gdef\@journalshort{Preprints}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{proceedings}{\gdef\@journal{proceedings}\gdef\@journalfull{Proceedings}\gdef\@journalshort{Proceedings}\gdef\@doiabbr{proceedings}\gdef\@ISSN{2504-3900}}
\DeclareOption{processes}{\gdef\@journal{processes}\gdef\@journalfull{Processes}\gdef\@journalshort{Processes}\gdef\@doiabbr{pr}\gdef\@ISSN{2227-9717}}
\DeclareOption{prosthesis}{\gdef\@journal{prosthesis}\gdef\@journalfull{Prosthesis}\gdef\@journalshort{Prosthesis}\gdef\@doiabbr{prosthesis}\gdef\@ISSN{2673-1592}\gdef\@continuouspages{yes}}
\DeclareOption{proteomes}{\gdef\@journal{proteomes}\gdef\@journalfull{Proteomes}\gdef\@journalshort{Proteomes}\gdef\@doiabbr{proteomes}\gdef\@ISSN{2227-7382}}
\DeclareOption{psf}{\gdef\@journal{psf}\gdef\@journalfull{Physical Sciences Forum}\gdef\@journalshort{Phys. Sci. Forum}\gdef\@doiabbr{psf}\gdef\@ISSN{2673-9984}}
\DeclareOption{psych}{\gdef\@journal{psych}\gdef\@journalfull{Psych}\gdef\@journalshort{Psych}\gdef\@doiabbr{psych}\gdef\@ISSN{2624-8611}\gdef\@continuouspages{yes}}
\DeclareOption{psychiatryint}{\gdef\@journal{psychiatryint}\gdef\@journalfull{Psychiatry International}\gdef\@journalshort{Psychiatry Int.}\gdef\@doiabbr{psychiatryint}\gdef\@ISSN{2673-5318}\gdef\@continuouspages{yes}}
\DeclareOption{psychoactives}{\gdef\@journal{psychoactives}\gdef\@journalfull{Psychoactives}\gdef\@journalshort{Psychoactives}\gdef\@doiabbr{psychoactives}\gdef\@ISSN{2813-1851}\gdef\@continuouspages{yes}}
\DeclareOption{publications}{\gdef\@journal{publications}\gdef\@journalfull{Publications}\gdef\@journalshort{Publications}\gdef\@doiabbr{publications}\gdef\@ISSN{2304-6775}}
\DeclareOption{quantumrep}{\gdef\@journal{quantumrep}\gdef\@journalfull{Quantum Reports}\gdef\@journalshort{Quantum Rep.}\gdef\@doiabbr{quantum}\gdef\@ISSN{2624-960X}\gdef\@continuouspages{yes}}
\DeclareOption{quaternary}{\gdef\@journal{quaternary}\gdef\@journalfull{Quaternary}\gdef\@journalshort{Quaternary}\gdef\@doiabbr{quat}\gdef\@ISSN{2571-550X}}
\DeclareOption{qubs}{\gdef\@journal{qubs}\gdef\@journalfull{Quantum Beam Science}\gdef\@journalshort{Quantum Beam Sci.}\gdef\@doiabbr{qubs}\gdef\@ISSN{2412-382X}}
\DeclareOption{radiation}{\gdef\@journal{radiation}\gdef\@journalfull{Radiation}\gdef\@journalshort{Radiation}\gdef\@doiabbr{radiation}\gdef\@ISSN{2673-592X}\gdef\@continuouspages{yes}}
\DeclareOption{reactions}{\gdef\@journal{reactions}\gdef\@journalfull{Reactions}\gdef\@journalshort{Reactions}\gdef\@doiabbr{reactions}\gdef\@ISSN{2624-781X}\gdef\@continuouspages{yes}}
\DeclareOption{receptors}{\gdef\@journal{receptors}\gdef\@journalfull{Receptors}\gdef\@journalshort{Receptors}\gdef\@doiabbr{receptors}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{recycling}{\gdef\@journal{recycling}\gdef\@journalfull{Recycling}\gdef\@journalshort{Recycling}\gdef\@doiabbr{recycling}\gdef\@ISSN{2313-4321}}
\DeclareOption{regeneration}{\gdef\@journal{regeneration}\gdef\@journalfull{Regeneration}\gdef\@journalshort{Regeneration}\gdef\@doiabbr{regeneration}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{religions}{\gdef\@journal{religions}\gdef\@journalfull{Religions}\gdef\@journalshort{Religions}\gdef\@doiabbr{rel}\gdef\@ISSN{2077-1444}}
\DeclareOption{remotesensing}{\gdef\@journal{remotesensing}\gdef\@journalfull{Remote Sensing}\gdef\@journalshort{Remote Sens.}\gdef\@doiabbr{rs}\gdef\@ISSN{2072-4292}}
\DeclareOption{reports}{\gdef\@journal{reports}\gdef\@journalfull{Reports}\gdef\@journalshort{Reports}\gdef\@doiabbr{reports}\gdef\@ISSN{2571-841X}}
\DeclareOption{reprodmed}{\gdef\@journal{reprodmed}\gdef\@journalfull{Reproductive Medicine}\gdef\@journalshort{Reprod. Med.}\gdef\@doiabbr{reprodmed}\gdef\@ISSN{2673-3897}\gdef\@continuouspages{yes}}
\DeclareOption{resources}{\gdef\@journal{resources}\gdef\@journalfull{Resources}\gdef\@journalshort{Resources}\gdef\@doiabbr{resources}\gdef\@ISSN{2079-9276}}
\DeclareOption{rheumato}{\gdef\@journal{rheumato}\gdef\@journalfull{Rheumato}\gdef\@journalshort{Rheumato}\gdef\@doiabbr{rheumato}\gdef\@ISSN{2674-0621}\gdef\@continuouspages{yes}}
\DeclareOption{risks}{\gdef\@journal{risks}\gdef\@journalfull{Risks}\gdef\@journalshort{Risks}\gdef\@doiabbr{risks}\gdef\@ISSN{2227-9091}}
\DeclareOption{robotics}{\gdef\@journal{robotics}\gdef\@journalfull{Robotics}\gdef\@journalshort{Robotics}\gdef\@doiabbr{robotics}\gdef\@ISSN{2218-6581}}
\DeclareOption{ruminants}{\gdef\@journal{ruminants}\gdef\@journalfull{Ruminants}\gdef\@journalshort{Ruminants}\gdef\@doiabbr{ruminants}\gdef\@ISSN{2673-933X}\gdef\@continuouspages{yes}}
\DeclareOption{safety}{\gdef\@journal{safety}\gdef\@journalfull{Safety}\gdef\@journalshort{Safety}\gdef\@doiabbr{safety}\gdef\@ISSN{2313-576X}}
\DeclareOption{sci}{\gdef\@journal{sci}\gdef\@journalfull{Sci}\gdef\@journalshort{Sci}\gdef\@doiabbr{sci}\gdef\@ISSN{2413-4155}}
\DeclareOption{scipharm}{\gdef\@journal{scipharm}\gdef\@journalfull{Scientia Pharmaceutica}\gdef\@journalshort{Sci. Pharm.}\gdef\@doiabbr{scipharm}\gdef\@ISSN{2218-0532}}
\DeclareOption{seeds}{\gdef\@journal{seeds}\gdef\@journalfull{Seeds}\gdef\@journalshort{Seeds}\gdef\@doiabbr{seeds}\gdef\@ISSN{2674-1024}\gdef\@continuouspages{yes}}
\DeclareOption{sensors}{\gdef\@journal{sensors}\gdef\@journalfull{Sensors}\gdef\@journalshort{Sensors}\gdef\@doiabbr{s}\gdef\@ISSN{1424-8220}}
\DeclareOption{separations}{\gdef\@journal{separations}\gdef\@journalfull{Separations}\gdef\@journalshort{Separations}\gdef\@doiabbr{separations}\gdef\@ISSN{2297-8739}}
\DeclareOption{sexes}{\gdef\@journal{sexes}\gdef\@journalfull{Sexes}\gdef\@journalshort{Sexes}\gdef\@doiabbr{sexes}\gdef\@ISSN{2411-5118}\gdef\@continuouspages{yes}}
\DeclareOption{signals}{\gdef\@journal{signals}\gdef\@journalfull{Signals}\gdef\@journalshort{Signals}\gdef\@doiabbr{signals}\gdef\@ISSN{2624-6120}\gdef\@continuouspages{yes}}
\DeclareOption{sinusitis}{\gdef\@journal{sinusitis}\gdef\@journalfull{Sinusitis}\gdef\@journalshort{Sinusitis}\gdef\@doiabbr{sinusitis}\gdef\@ISSN{2309-107X}\gdef\@continuouspages{yes}}
\DeclareOption{skins}{\gdef\@journal{skins}\gdef\@journalfull{Skins}\gdef\@journalshort{Skins}\gdef\@doiabbr{skins}\gdef\@ISSN{}}
\DeclareOption{smartcities}{\gdef\@journal{smartcities}\gdef\@journalfull{Smart Cities}\gdef\@journalshort{Smart Cities}\gdef\@doiabbr{smartcities}\gdef\@ISSN{2624-6511}\gdef\@continuouspages{yes}}
\DeclareOption{sna}{\gdef\@journal{sna}\gdef\@journalfull{Sinusitis and Asthma}\gdef\@journalshort{Sinusitis Asthma}\gdef\@doiabbr{sna}\gdef\@ISSN{2624-7003}}
\DeclareOption{societies}{\gdef\@journal{societies}\gdef\@journalfull{Societies}\gdef\@journalshort{Societies}\gdef\@doiabbr{soc}\gdef\@ISSN{2075-4698}}
\DeclareOption{socsci}{\gdef\@journal{socsci}\gdef\@journalfull{Social Sciences}\gdef\@journalshort{Soc. Sci.}\gdef\@doiabbr{socsci}\gdef\@ISSN{2076-0760}}
\DeclareOption{software}{\gdef\@journal{software}\gdef\@journalfull{Software}\gdef\@journalshort{Software}\gdef\@doiabbr{software}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{soilsystems}{\gdef\@journal{soilsystems}\gdef\@journalfull{Soil Systems}\gdef\@journalshort{Soil Syst.}\gdef\@doiabbr{soilsystems}\gdef\@ISSN{2571-8789}}
\DeclareOption{solar}{\gdef\@journal{solar}\gdef\@journalfull{Solar}\gdef\@journalshort{Solar}\gdef\@doiabbr{solar}\gdef\@ISSN{2673-9941}\gdef\@continuouspages{yes}}
\DeclareOption{solids}{\gdef\@journal{solids}\gdef\@journalfull{Solids}\gdef\@journalshort{Solids}\gdef\@doiabbr{solids}\gdef\@ISSN{2673-6497}\gdef\@continuouspages{yes}}
\DeclareOption{spectroscj}{\gdef\@journal{spectroscj}\gdef\@journalfull{Spectroscopy Journal}\gdef\@journalshort{Spectrosc. J.}\gdef\@doiabbr{spectroscj}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{sports}{\gdef\@journal{sports}\gdef\@journalfull{Sports}\gdef\@journalshort{Sports}\gdef\@doiabbr{sports}\gdef\@ISSN{2075-4663}}
\DeclareOption{standards}{\gdef\@journal{standards}\gdef\@journalfull{Standards}\gdef\@journalshort{Standards}\gdef\@doiabbr{standards}\gdef\@ISSN{2305-6703}\gdef\@continuouspages{yes}}
\DeclareOption{stats}{\gdef\@journal{stats}\gdef\@journalfull{Stats}\gdef\@journalshort{Stats}\gdef\@doiabbr{stats}\gdef\@ISSN{2571-905X}\gdef\@continuouspages{yes}}
\DeclareOption{std}{\gdef\@journal{std}\gdef\@journalfull{Surgical Techniques Development}\gdef\@journalshort{Surg. Tech. Dev.}\gdef\@doiabbr{std}\gdef\@ISSN{2038-9582}\gdef\@continuouspages{yes}}
\DeclareOption{stresses}{\gdef\@journal{stresses}\gdef\@journalfull{Stresses}\gdef\@journalshort{Stresses}\gdef\@doiabbr{stresses}\gdef\@ISSN{2673-7140}\gdef\@continuouspages{yes}}
\DeclareOption{surfaces}{\gdef\@journal{surfaces}\gdef\@journalfull{Surfaces}\gdef\@journalshort{Surfaces}\gdef\@doiabbr{surfaces}\gdef\@ISSN{2571-9637}\gdef\@continuouspages{yes}}
\DeclareOption{surgeries}{\gdef\@journal{surgeries}\gdef\@journalfull{Surgeries}\gdef\@journalshort{Surgeries}\gdef\@doiabbr{surgeries}\gdef\@ISSN{2017-2017}\gdef\@continuouspages{yes}}
\DeclareOption{suschem}{\gdef\@journal{suschem}\gdef\@journalfull{Sustainable Chemistry}\gdef\@journalshort{Sustain. Chem.}\gdef\@doiabbr{suschem}\gdef\@ISSN{2673-4079}\gdef\@continuouspages{yes}}
\DeclareOption{sustainability}{\gdef\@journal{sustainability}\gdef\@journalfull{Sustainability}\gdef\@journalshort{Sustainability}\gdef\@doiabbr{su}\gdef\@ISSN{2071-1050}}
\DeclareOption{symmetry}{\gdef\@journal{symmetry}\gdef\@journalfull{Symmetry}\gdef\@journalshort{Symmetry}\gdef\@doiabbr{sym}\gdef\@ISSN{2073-8994}}
\DeclareOption{synbio}{\gdef\@journal{synbio}\gdef\@journalfull{Synbio}\gdef\@journalshort{Synbio}\gdef\@doiabbr{synbio}\gdef\@ISSN{2674-0583}\gdef\@continuouspages{yes}}
\DeclareOption{systems}{\gdef\@journal{systems}\gdef\@journalfull{Systems}\gdef\@journalshort{Systems}\gdef\@doiabbr{systems}\gdef\@ISSN{2079-8954}}
\DeclareOption{taxonomy}{\gdef\@journal{taxonomy}\gdef\@journalfull{Taxonomy}\gdef\@journalshort{Taxonomy}\gdef\@doiabbr{taxonomy}\gdef\@ISSN{2673-6500}\gdef\@continuouspages{yes}}
\DeclareOption{technologies}{\gdef\@journal{technologies}\gdef\@journalfull{Technologies}\gdef\@journalshort{Technologies}\gdef\@doiabbr{technologies}\gdef\@ISSN{2227-7080}}
\DeclareOption{telecom}{\gdef\@journal{telecom}\gdef\@journalfull{Telecom}\gdef\@journalshort{Telecom}\gdef\@doiabbr{telecom}\gdef\@ISSN{2673-4001}\gdef\@continuouspages{yes}}
\DeclareOption{test}{\gdef\@journal{test}\gdef\@journalfull{Test}\gdef\@journalshort{Test}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{textiles}{\gdef\@journal{textiles}\gdef\@journalfull{Textiles}\gdef\@journalshort{Textiles}\gdef\@doiabbr{textiles}\gdef\@ISSN{2673-7248}\gdef\@continuouspages{yes}}
\DeclareOption{thalassrep}{\gdef\@journal{thalassrep}\gdef\@journalfull{Thalassemia Reports}\gdef\@journalshort{Thalass. Rep.}\gdef\@doiabbr{thalassrep}\gdef\@ISSN{2039-4365}\gdef\@continuouspages{yes}}
\DeclareOption{thermo}{\gdef\@journal{thermo}\gdef\@journalfull{Thermo}\gdef\@journalshort{Thermo}\gdef\@doiabbr{thermo}\gdef\@ISSN{2673-7264}\gdef\@continuouspages{yes}}
\DeclareOption{tomography}{\gdef\@journal{tomography}\gdef\@journalfull{Tomography}\gdef\@journalshort{Tomography}\gdef\@doiabbr{tomography}\gdef\@ISSN{2379-139X}\gdef\@continuouspages{yes}}
\DeclareOption{tourismhosp}{\gdef\@journal{tourismhosp}\gdef\@journalfull{Tourism and Hospitality}\gdef\@journalshort{Tour. Hosp.}\gdef\@doiabbr{tourhosp}\gdef\@ISSN{2673-5768}\gdef\@continuouspages{yes}}
\DeclareOption{toxics}{\gdef\@journal{toxics}\gdef\@journalfull{Toxics}\gdef\@journalshort{Toxics}\gdef\@doiabbr{toxics}\gdef\@ISSN{2305-6304}}
\DeclareOption{toxins}{\gdef\@journal{toxins}\gdef\@journalfull{Toxins}\gdef\@journalshort{Toxins}\gdef\@doiabbr{toxins}\gdef\@ISSN{2072-6651}}
\DeclareOption{transplantology}{\gdef\@journal{transplantology}\gdef\@journalfull{Transplantology}\gdef\@journalshort{Transplantology}\gdef\@doiabbr{transplantology}\gdef\@ISSN{2673-3943}\gdef\@continuouspages{yes}}
\DeclareOption{transportation}{\gdef\@journal{transportation}\gdef\@journalfull{Transportation}\gdef\@journalshort{Transportation}\gdef\@doiabbr{transportation}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{traumacare}{\gdef\@journal{traumacare}\gdef\@journalfull{Trauma Care}\gdef\@journalshort{Trauma Care}\gdef\@doiabbr{traumacare}\gdef\@ISSN{2673-866X}\gdef\@continuouspages{yes}}
\DeclareOption{traumas}{\gdef\@journal{traumas}\gdef\@journalfull{Traumas}\gdef\@journalshort{Traumas}\gdef\@doiabbr{traumas}\gdef\@ISSN{2673-7477}\gdef\@continuouspages{yes}}
\DeclareOption{tropicalmed}{\gdef\@journal{tropicalmed}\gdef\@journalfull{Tropical Medicine and Infectious Disease}\gdef\@journalshort{Trop. Med. Infect. Dis.}\gdef\@doiabbr{tropicalmed}\gdef\@ISSN{2414-6366}}
\DeclareOption{universe}{\gdef\@journal{universe}\gdef\@journalfull{Universe}\gdef\@journalshort{Universe}\gdef\@doiabbr{universe}\gdef\@ISSN{2218-1997}}
\DeclareOption{urbansci}{\gdef\@journal{urbansci}\gdef\@journalfull{Urban Science}\gdef\@journalshort{Urban Sci.}\gdef\@doiabbr{urbansci}\gdef\@ISSN{2413-8851}}
\DeclareOption{uro}{\gdef\@journal{uro}\gdef\@journalfull{Uro}\gdef\@journalshort{Uro}\gdef\@doiabbr{uro}\gdef\@ISSN{2673-4397}\gdef\@continuouspages{yes}}
\DeclareOption{vaccines}{\gdef\@journal{vaccines}\gdef\@journalfull{Vaccines}\gdef\@journalshort{Vaccines}\gdef\@doiabbr{vaccines}\gdef\@ISSN{2076-393X}}
\DeclareOption{vehicles}{\gdef\@journal{vehicles}\gdef\@journalfull{Vehicles}\gdef\@journalshort{Vehicles}\gdef\@doiabbr{vehicles}\gdef\@ISSN{2624-8921}\gdef\@continuouspages{yes}}
\DeclareOption{venereology}{\gdef\@journal{venereology}\gdef\@journalfull{Venereology}\gdef\@journalshort{Venereology}\gdef\@doiabbr{venereology}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{vetsci}{\gdef\@journal{vetsci}\gdef\@journalfull{Veterinary Sciences}\gdef\@journalshort{Vet. Sci.}\gdef\@doiabbr{vetsci}\gdef\@ISSN{2306-7381}}
\DeclareOption{vibration}{\gdef\@journal{vibration}\gdef\@journalfull{Vibration}\gdef\@journalshort{Vibration}\gdef\@doiabbr{vibration}\gdef\@ISSN{2571-631X}\gdef\@continuouspages{yes}}
\DeclareOption{virtualworlds}{\gdef\@journal{virtualworlds}\gdef\@journalfull{Virtual Worlds}\gdef\@journalshort{Virtual Worlds}\gdef\@doiabbr{virtualworlds}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{viruses}{\gdef\@journal{viruses}\gdef\@journalfull{Viruses}\gdef\@journalshort{Viruses}\gdef\@doiabbr{v}\gdef\@ISSN{1999-4915}}
\DeclareOption{vision}{\gdef\@journal{vision}\gdef\@journalfull{Vision}\gdef\@journalshort{Vision}\gdef\@doiabbr{vision}\gdef\@ISSN{2411-5150}}
\DeclareOption{waste}{\gdef\@journal{waste}\gdef\@journalfull{Waste}\gdef\@journalshort{Waste}\gdef\@doiabbr{waste}\gdef\@ISSN{2813-0391}\gdef\@continuouspages{yes}}
\DeclareOption{water}{\gdef\@journal{water}\gdef\@journalfull{Water}\gdef\@journalshort{Water}\gdef\@doiabbr{w}\gdef\@ISSN{2073-4441}}
\DeclareOption{wem}{\gdef\@journal{wem}\gdef\@journalfull{Wildlife Ecology and Management}\gdef\@journalshort{Wildl. Ecol. Manag.}\gdef\@doiabbr{}\gdef\@ISSN{1234-4321}}
\DeclareOption{wevj}{\gdef\@journal{wevj}\gdef\@journalfull{World Electric Vehicle Journal}\gdef\@journalshort{World Electr. Veh. J.}\gdef\@doiabbr{wevj}\gdef\@ISSN{2032-6653}}
\DeclareOption{wind}{\gdef\@journal{wind}\gdef\@journalfull{Wind}\gdef\@journalshort{Wind}\gdef\@doiabbr{wind}\gdef\@ISSN{2674-032X}\gdef\@continuouspages{yes}}
\DeclareOption{women}{\gdef\@journal{women}\gdef\@journalfull{Women}\gdef\@journalshort{Women}\gdef\@doiabbr{women}\gdef\@ISSN{2673-4184}\gdef\@continuouspages{yes}}
\DeclareOption{world}{\gdef\@journal{world}\gdef\@journalfull{World}\gdef\@journalshort{World}\gdef\@doiabbr{world}\gdef\@ISSN{2673-4060}\gdef\@continuouspages{yes}}
\DeclareOption{youth}{\gdef\@journal{youth}\gdef\@journalfull{Youth}\gdef\@journalshort{Youth}\gdef\@doiabbr{youth}\gdef\@ISSN{2673-995X}\gdef\@continuouspages{yes}}
\DeclareOption{zoonoticdis}{\gdef\@journal{zoonoticdis}\gdef\@journalfull{Zoonotic Diseases}\gdef\@journalshort{Zoonotic Dis.}\gdef\@doiabbr{zoonoticdis}\gdef\@ISSN{2813-0227}\gdef\@continuouspages{yes}}

### 2022-04-11 template.tex
Initial Overleaf Import

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[vision,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
\datereceived{} 
\dateaccepted{} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Foraging: The Triumphant Return}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Alasdair Clarke $^{1,\dagger,\ddagger}$\orcidA{}, Amelia Hunt $^{1,\ddagger}$ and Anna Hughes $^{2,}$*}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusion: indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{Instead of the abstract}
%\entrylink{The Link to this entry published on the encyclopedia platform.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}

The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References). Only journal Laws uses \footnote.

% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
This is an example of a quote.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, Table~\ref{tab2}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}   
\unskip

\begin{table}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}
\unskip

\begin{table}[H]
\caption{This is a wide table.\label{tab2}}
	\begin{adjustwidth}{-\extralength}{0cm}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\fulllength}{CCCC}
			\toprule
			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
			\midrule
			Entry 1		& Data			& Data			& Data\\
			Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
			\bottomrule
		\end{tabularx}
	\end{adjustwidth}
	\noindent{\footnotesize{\textsuperscript{1} This is a table footnote.}}
\end{table}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{linenomath}
\begin{equation}
a = 1,
\end{equation}
\end{linenomath}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

% Example of a page in landscape format (with table and table footnote).
%\startlandscape
%\begin{table}[H] %% Table in wide page
%\caption{This is a very wide table.\label{tab3}}
%	\begin{tabularx}{\textwidth}{CCCC}
%		\toprule
%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
%		\midrule
%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
%		\bottomrule
%	\end{tabularx}
%	\begin{adjustwidth}{+\extralength}{0cm}
%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
%	\end{adjustwidth}
%\end{table}
%\finishlandscape

% Example of a figure that spans the whole page width. The same concept works for tables, too.
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=15cm]{Definitions/logo-mdpi}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals. Please note that the Editorial Office might ask you for further information. Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals. You might also choose to exclude this statement if the study did not involve humans or animals.}

\informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}. You might choose to exclude this statement if the study did not report any data.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}

%% Optional
\sampleavailability{Samples of the compounds ... are available from the authors.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & Linear dichroism
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}
\subsection[\appendixname~\thesubsection]{}
The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

\begin{table}[H] 
\caption{This is a table caption.\label{tab5}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}

\section[\appendixname~\thesection]{}
All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
\bibitem[Author2(year)]{ref-book1}
Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% Reference 3
\bibitem[Author3(year)]{ref-book2}
Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% Reference 4
\bibitem[Author4(year)]{ref-unpublish}
Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
% Reference 5
\bibitem[Author5(year)]{ref-communication}
Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% Reference 6
\bibitem[Author6(year)]{ref-proceeding}
Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
% Reference 7
\bibitem[Author7(year)]{ref-thesis}
Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% Reference 8
\bibitem[Author8(year)]{ref-url}
Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{adjustwidth}
\end{document}

### 2022-04-11 Analysis/comp_weights.R
code

@@ -1,0 +1,67 @@
+comp_weights <- function(trl, params, cond, obs)
+{
+  
+  d_trl <- filter(d, observer == obs, condition == cond, trial == trl)
+  
+  if (nrow(d_trl) == 0) {
+    
+    
+  }
+  else
+  {
+  
+  
+  d_trl$b = NaN
+  d_trl$bMax = NaN
+  d_trl$err = NaN
+  d_trl$model_pref = NaN
+  
+  
+  for (t in 2:40) {
+    
+    prev_targ <- d_trl$targ_type[t-1]
+    
+    
+    x0 <- d_trl$x[t-1]
+    y0 <- d_trl$y[t-1]
+    
+    x00 <- d_trl$x[t-2]
+    y00 <- d_trl$y[t-2]
+    
+    d_remain <- filter(d_trl, found>=t)
+    
+    match_prev = if_else(d_remain$targ_type == prev_targ, 1, -1)
+    
+    if (t == 2) {
+      d_remain %>% mutate(
+        dist = (x0 - x)^2 + (y0 - y)^2,
+        dist = sqrt(dist),
+        prox = exp((-params$bP * dist)),
+        b = params$pA * targ_type + params$pS * match_prev,
+        b = boot::inv.logit(b) * prox,
+        b = b/sum(b)) -> d_remain
+    } else {
+      d_remain %>% mutate(
+        dist = (x0 - x)^2 + (y0 - y)^2,
+        dist = sqrt(dist),
+        phi = atan2(( y0 - y00), (x0 - y00)) * 180/pi,
+        phi = (atan2((y - y0), (x - x0)) * 180/pi) - phi ,
+        phi = pmin(abs((phi %% 360)), abs((-phi %% 360))),
+        phi = phi/180,
+        prox = exp((-params$bP * dist) - (params$bM * phi)),
+        b = params$pA * targ_type + params$pS * match_prev,
+        b = boot::inv.logit(b) * prox,
+        b = b/sum(b)) -> d_remain
+      
+    }
+    
+    d_trl$b[t] <- d_remain$b[which(d_remain$found==t)]
+    d_trl$bMax[t] <- d_trl$b[t] == max(d_remain$b)
+    d_trl$err[t] <-  max(d_remain$b) - d_trl$b[t]
+    d_trl$model_pref[t] <- d_remain$found[which(d_remain$b == max(d_remain$b) )]
+    
+    
+  }}
+  
+  return(d_trl)
+}

### 2022-04-11 Analysis/functions/get_model_params.R

@@ -1,0 +1,43 @@
+get_model_params <- function() {
+  
+  
+  cond_levels = c("feature", "conjunction")
+  
+  m <- readRDS("../saved_models/all_qjep_2020.rds")
+  
+  
+  m %>% spread_draws(b[cond], u[cond, obs]) %>%
+    mutate(cond = as.factor(cond),
+           cond = fct_recode(cond, bA_1 = "1", bS_1 = "2", bP_1 = "3", bM_1 = "4", 
+                             bA_2 = "5", bS_2 = "6", bP_2 = "7", bM_2 = "8"), 
+           bZ = b + u,
+           pZ = boot::inv.logit(bZ)) %>%
+    separate(cond, into = c("param", "condition")) %>%
+    mutate(condition = factor(condition, labels = cond_levels)) -> fit1
+  
+  
+  fit1 %>% select(obs, condition, param, pZ) %>%
+    pivot_wider(names_from = "param", values_from = "pZ") %>%
+    select(obs, condition, bA, bS) %>%
+    pivot_longer(c('bA', 'bS'), names_to = "model", values_to = "bias") %>%
+    unnest() -> qs
+  
+  fit1 %>% select(obs, condition, param, bZ) %>%
+    pivot_wider(names_from = "param", values_from = "bZ") %>%
+    select(obs, condition, bP, bM) %>%
+    pivot_longer(c('bP', 'bM'), names_to = "model", values_to = "bias") %>%
+    unnest() -> qs_p
+  
+  qs_all <- rbind(qs, qs_p) %>%
+    mutate(model = fct_relevel(model, "bA", "bS", "bP", "bM"),
+           model = plyr::revalue(model, c("bA" = "pA", "bS" = "pS"))) %>%
+    group_by(obs, condition, model) %>%
+    summarise(bias = median(bias)) %>%
+    pivot_wider(names_from = "model", values_from = "bias")
+  
+  
+  return(qs_all)
+  
+}
+  
+  

### 2022-04-11 Analysis/functions/helper_functions.R

@@ -1,0 +1,176 @@
+prepare_stan_input <- function(d, stan_model_name, N = 1, nT, nF = NA,
+                               L = NA, prior_b = 1, prox_prior = NA) 
+{
+  
+  # define some default params
+  if (is.na(nF)) nF = nT
+
+  
+  # now setup list of inputs for our stan model
+  
+  if (stan_model_name == "bag_foraging_one_trial") 
+  {
+    Y = as.numeric(select(d, starts_with("t"), -"trial"))
+    
+    stan_data <- list(
+      nT = nT,
+      nA = d$nA,
+      nB = d$nB,
+      nF = nF,
+      Y = Y,
+      prior_sig_bS = prior_b)
+  }
+  
+  if (stan_model_name == "bag_foraging")
+  {
+    Y = as.matrix(select(d, starts_with("t"), -"trial"))
+    
+    stan_data <- list(
+      N = N,
+      K = length(unique(d$condition)),
+      nT = nT,
+      nA = d$nA,
+      nB = d$nB,
+      nF = d$n_found,
+      Y = Y,
+      X = as.numeric(d$condition),
+      prior_sig_bS = prior_b,
+      prior_sig_bA = prior_b)
+  }
+  
+  if (stan_model_name == "bag_foraging_mutli_level") 
+  {
+    Y = as.matrix(select(d, starts_with("t"), -"trial"))
+    
+    stan_data <- list(
+      N = N * n_conditions * L,
+      L = L,
+      K = length(unique(d$condition)),
+      nT = nT,
+      nA = d$nA,
+      nB = d$nB,
+      Y = Y,
+      X = as.numeric(d$condition),
+      Z = d$observer,
+      n_found = d$n_found,
+      prior_sig_b = prior_b,
+      prior_sig_z = 1)
+  }
+  
+  if (stan_model_name == "spatial_foraging")
+  {
+    stan_data <- prepare_prox_data(d, nT, prior_b, prox_prior)
+  }
+  
+  if (stan_model_name == "spatial_foraging_multi_level")
+  {
+    stan_data <- prepare_prox_data(d, nT, prior_b, prox_prior, ml = TRUE)
+  }
+  
+  
+  return(stan_data)
+  
+}
+
+
+
+prepare_prox_data <- function(d, nT, prior_b, prox_prior, ml = FALSE)
+{
+  
+  # function to take a tibble/dataframe of "spatial foraging" data, and prepare
+  # it for running through the stan model
+  
[…]

### 2022-04-11 Analysis/functions/plot_spatial_model.R

@@ -1,0 +1,197 @@
+library(tidyverse)
+library(tidybayes)
+library(rstan)
+library(patchwork)
+library(wesanderson)
+
+
+plot_multi_levels <- function(fit, cond_levels = c("value", "no value"))
+{
+  fit %>% spread_draws(b[cond], u[cond, obs]) %>%
+    mutate(cond = as.factor(cond),
+           cond = fct_recode(cond, bA_1 = "1", bS_1 = "2", bP_1 = "3", bM_1 = "4", 
+                             bA_2 = "5", bS_2 = "6", bP_2 = "7", bM_2 = "8"), 
+           bZ = b + u,
+           pZ = boot::inv.logit(bZ)) %>%
+    separate(cond, into = c("param", "condition")) %>%
+    mutate(condition = factor(condition, labels = cond_levels)) -> fit1
+  
+  fit1 %>% select(obs, condition, param, pZ) %>%
+    pivot_wider(names_from = "param", values_from = "pZ") %>%
+    select(obs, condition, bA, bS) %>%
+    pivot_longer(c('bA', 'bS'), names_to = "model", values_to = "bias") %>%
+    unnest() -> qs
+  
+  fit1 %>% select(obs, condition, param, bZ) %>%
+    pivot_wider(names_from = "param", values_from = "bZ") %>%
+    select(obs, condition, bP, bM) %>%
+    pivot_longer(c('bP', 'bM'), names_to = "model", values_to = "bias") %>%
+    unnest() -> qs_p
+
+  
+  qs_all <- rbind(qs, qs_p) %>%
+    mutate(model = fct_relevel(model, "bA", "bS", "bP", "bM"),
+           model = plyr::revalue(model, c("bA" = "pA", "bS" = "pS"))) %>%
+    group_by(obs, condition, model) %>%
+    summarise(bias = median(bias)) %>%
+    pivot_wider(names_from = "model", values_from = "bias")
+
+  ggplot(qs_all, aes(x = pA,  y = pS, colour = condition)) +
+    geom_point(alpha = 0.5) + 
+    scale_x_continuous("pA (preference for target A)", limits = c(0, 1), breaks = c(0, 0.5, 1)) +
+    scale_y_continuous("pS (stick preference)") + 
+    scale_colour_manual(values = c("#DDAA33", "#004488")) + 
+    facet_wrap(~condition) + 
+    theme_bw() -> pApS
+  
[…]

### 2022-04-11 Analysis/functions/plotting_functions.R

@@ -1,0 +1,281 @@
+library(RColorBrewer)
+library(wesanderson)
+library(latex2exp)
+library(ggridges)
+
+plot_a_trial <- function(trial, n_col = 20, colour_scheme = c("#FC8D62", "#66C2A5"), shapes = 18)
+  
+{
+  n <- length(trial)
+  
+  n_row = ceiling(n/n_col)
+  
+  # NA bad trial so that it is a multiple of n_col * n_row
+  trial <- c(trial, rep(NA, n_col*n_row - n))
+  
+  labs <- paste("targets", n_col*(seq(n_row, 1, -1))-(n_col-1), "-", seq(n_row, 1, -1)*n_col)
+  
+  tibble(x = rep(1:n_col, n_row), 
+         y = rep(seq(n_row, 1, -1), each = n_col),
+         target = as.factor(trial)) %>%
+    ggplot(aes(x, y, colour = target, fill = target)) +
+    geom_hline(yintercept = 1:n_row, linetype = 2) +
+    geom_point(size = 4, shape = shapes) +
+    scale_y_continuous(breaks = 1:n_row, labels = labs) +
+    scale_color_manual(values = colour_scheme) +
+    scale_fill_manual(values = colour_scheme) +
+    theme(legend.position = "none",
+          axis.title = element_blank(),
+          axis.text.x = element_blank()) -> plt
+  return(plt)
+}
+
+plot_model_dists <- function(d_plt) {
+  
+  ggplot(d_plt, aes(x = bias, colour = model, fill = model)) +
+    geom_density(alpha = 0.5) + 
+    geom_vline(xintercept = 0.5, linetype = 2) + 
+    scale_x_continuous(limits = c(0, 1), expand = c(0, 0)) + 
+    scale_y_continuous(expand = expansion(mult = c(0, .05))) +
+    ylab("") + 
+    scale_fill_manual(labels = TeX(levels(d_plt$model)), values = wes_palette("Royal1")) +
+    scale_colour_manual(labels = TeX(levels(d_plt$model)), values = wes_palette("Royal1")) +
+    theme(#legend.position = c(0.15, 0.65),
+          #plot.margin = margin(2,20,20,1),
+          panel.grid.major.y = element_blank(),
+          panel.grid.minor.y = element_blank()) 
+  
+}
+
+plot_simple_one_trial_model <- function(fit) {
+  
+  extract(fit, c("p_prior", "pS")) %>% 
[…]

### 2022-04-11 Analysis/functions/prep_stan_data_momentum.R

@@ -1,0 +1,116 @@
+prep_stan_data <- function(d)
+{
+  
+  # function to take a tibble/dataframe of "spatial foraging" data, and prepare
+  # it for running through the stan model
+  
+  # d should be a tibble with the following columns:
+  # - trial: 1-n_trials
+  # - id: target id 1:n_targets. If this does not exist, it will be created from "found"
+  # - targ_type: factor level of each target type. For now, = 0 or 1.  
+  # - x: hori position of target. Usually normalized to be [0, 1]
+  # - y: similar to x
+  # - found: the order in which the target was found. Set missed targets to -1
+  # - condition: 1, 2, 3, .etc
+  
+  if (!"condition" %in% names(d)) d$condition = 1
+  if (!"id" %in% names(d)) d$id = d$found
+  
+  d %>% mutate(trial = paste(observer, condition, trial, sep = "-"),
+                 trial = as_factor(trial),
+                 trial = as.numeric(trial),
+               targ_type = if_else(targ_type == 0, -1, targ_type)) -> d
+  
+  
+  # arrange by trial and id before calc distance matrix
+  d <- arrange(d, observer, condition, trial, id) 
+  
+  # for each trial, compute target-target distance matrix
+  # delta is indexed by ID
+  deltas <- tibble()
+  for (obs in unique(d$observer))  {
+    #print(obs)
+    for (cc in unique(d$condition))   {
+      for (trl in unique(d$trial))      {
+        d_trial <- filter(d, trial == trl, observer == obs, condition == cc) %>% select(x, y)
+        delta <- as.matrix(dist(d_trial, upper = TRUE, diag = TRUE))
+        delta <- as_tibble(delta) 
+        names(delta) = paste("dt", 1:nrow(d_trial), sep = "_")
+        deltas <- bind_rows(deltas, delta)
+      }
+    }
+  }
+  d <- bind_cols(d, deltas)
+ 
+  # put in first row
+ 
+  theta <- tibble()
+ 
+  for (ii in 1:nrow(d)) {
+    
+    #print(paste(ii, nrow(d)))
+   
+     d_trial <- filter(d, trial == d$trial[ii], 
+                       observer == d$observer[ii], 
+                       condition == d$condition[ii]) 
+   
+     if (d$found[ii] %in% c(-1, 1)) {
+      phi <- rep(0, nrow(d_trial))
[…]

### 2022-04-11 Analysis/functions/prep_stan_data_momentum_tagu.R

@@ -1,0 +1,116 @@
+prep_stan_data <- function(d)
+{
+  
+  # function to take a tibble/dataframe of "spatial foraging" data, and prepare
+  # it for running through the stan model
+  
+  # d should be a tibble with the following columns:
+  # - trial: 1-n_trials
+  # - id: target id 1:n_targets. If this does not exist, it will be created from "found"
+  # - targ_type: factor level of each target type. For now, = 0 or 1.  
+  # - x: hori position of target. Usually normalized to be [0, 1]
+  # - y: similar to x
+  # - found: the order in which the target was found. Set missed targets to -1
+  # - condition: 1, 2, 3, .etc
+  
+  if (!"condition" %in% names(d)) d$condition = 1
+  if (!"id" %in% names(d)) d$id = d$found
+  
+  d %>% mutate(trial = paste(observer, condition, trial, sep = "-"),
+                 trial = as_factor(trial),
+                 trial = as.numeric(trial),
+               targ_type = if_else(targ_type == 0, -1, targ_type)) -> d
+  
+  
+  # arrange by trial and id before calc distance matrix
+  d <- arrange(d, observer, condition, trial, id) 
+  
+  # for each trial, compute target-target distance matrix
+  # delta is indexed by ID
+  deltas <- tibble()
+  for (obs in unique(d$observer))  {
+    print(obs)
+    for (cc in unique(d$condition))   {
+      for (trl in unique(d$trial))      {
+        d_trial <- filter(d, trial == trl, observer == obs, condition == cc) %>% select(x, y)
+        delta <- as.matrix(dist(d_trial, upper = TRUE, diag = TRUE))
+        delta <- as_tibble(delta) 
+        names(delta) = paste("dt", 1:nrow(d_trial), sep = "_")
+        deltas <- bind_rows(deltas, delta)
+      }
+    }
+  }
+  d <- bind_cols(d, deltas)
+ 
+  # put in first row
+ 
+  theta <- tibble()
+ 
+  for (ii in 1:nrow(d)) {
+    
+    print(paste(ii, nrow(d)))
+   
+     d_trial <- filter(d, trial == d$trial[ii], 
+                       observer == d$observer[ii], 
+                       condition == d$condition[ii]) 
+   
+     if (d$found[ii] %in% c(-1, 1)) {
+      phi <- rep(0, nrow(d_trial))
+    } else
[…]

### 2022-04-11 Analysis/functions/sim_foraging_bag.R

@@ -1,0 +1,163 @@
+library(tidyverse)
+
+############################################
+# Functions for data generation
+############################################
+simulate_observer <- function(ob_id = 1, observer_sig = 0.1) {
+  
+  # generate random weights
+  obs_w_pref <- boot::inv.logit(boot::logit(prob_a) + rnorm(1, 0, observer_sig))
+  obs_w_stay <- boot::inv.logit(boot::logit(prob_s) + rnorm(1, 0, observer_sig))
+  
+  
+  d_ob <- map_df(1:n_conditions, 
+                 simulate_data, 
+                 n_trials = n_trials, n_targ = n_targ, prob_a =  obs_w_pref, prob_s =  obs_w_stay ) %>%
+    mutate(
+      observer = ob_id,
+      condition = as.factor(condition), 
+      obs_a = obs_w_pref[condition],
+      obs_s = obs_w_stay[condition])
+  
+  return(d_ob)
+  
+}
+
+
+simulate_data <- function(cc = 1, n_trials = 100, n_targ = 50, n_found =  NA, prob_a = 0.5, prob_s = 0.5, p_quit = 0.00) {
+  
+  # generate n_trials worth of data, all with the same parameters
+  # include some basic run length statistics in the output
+  
+  if (is.na(n_found)) {
+    n_found = n_targ
+  }
+  
+  d <- map_df(1:n_trials, gen_foraging_seq, 
+              ps = prob_s[cc], pa = prob_a[cc], n_tot = n_targ, n_found = n_found, p_q = p_quit) %>% 
+    pivot_wider(names_from = "pick", values_from = "found") 
+  
+  ## add run-length and number-of-run stats
+  d <- cbind(d, map_df(1:n_trials, get_run_info, d))
+  
+  d$condition = as.integer(cc)
+  d$prob_a = prob_a[cc]
+  d$prob_s = prob_s[cc]
+  d$nA = as.integer(ceiling(n_targ/2))
+  d$nB = as.integer(n_targ - d$nA)
+  
+  d <- select(d, condition, trial, nA, nB, prob_a, prob_s, n_found, max_run_length, all_run_lengths, n_runs, starts_with("t"))
+  
+  return(d)
+}
+
+gen_foraging_seq <- function(t = 1, ps = 0.5, pa = 0.5, p_q = 0, n_tot = 40, n_found = NA) {
+  
[…]

### 2022-04-11 Analysis/functions/sim_foraging_momentum.R

@@ -1,0 +1,218 @@
+library(tidyverse)
+
+
+sim_momentum_post <- function(df_params, n_trials = 10, n = 40)
+{
+  
+  d <- tibble()
+  
+  for (ii in 1:nrow(df_params)) {
+    
+    print(ii)
+    
+    sim_momentum_trials(n = n, m = n, 
+                        tune_prox = df_params$bP[ii], 
+                        tune_angle = df_params$bM[ii], 
+                        b_pref = df_params$bA[ii],
+                        b_switch = df_params$bS[ii], 
+                        n_trials = 10) %>%
+      mutate(observer = df_params$observer[ii],
+             condition = df_params$condition[ii],
+             draw = df_params$.draw[ii]) %>%
+      arrange(trial, found) %>%
+      bind_rows(d) -> d
+    
+  }
+  
+  return(d)
+  
+}
+  
+get_runs <- function(d) {
+  
+  dout <- tibble()
+  
+  for (obs in unique(d$observer)) {
+    for (cd in unique(d$condition)) {
+      for (trl in unique(d$trial)) {
+        
+        targs <- filter(d, observer == obs, condition == cd, trial == trl)$targ_type
+        
+        if (length(targs)>0) {
+          rl <- rle(targs)
+          
+          dout <- bind_rows(dout, 
+                            tibble(observer = obs,
+                                   trial = trl,
+                                   condition = cd, 
+                                   max_run = max(rl$lengths),
+                                   num_run = length(rl$lengths),
+                                   men_run = mean(rl$lengths)))
+        }
+      }
+    }
+  }
+  
+  return(dout)
+  
+}
+
+
+sim_momentum_trials <- function(n = 10, m = 10, tune_prox = 1, tune_angle = 5, b_pref = 0, b_switch = 0, n_trials = 10, spat_config = FALSE) 
+{
+  # n is number of targets present
+  # m is number of targets to find
+  
+  params <- list(
+    n = n,
+    m = m,
+    tune_prox = tune_prox,
+    tune_angle = tune_angle,
+    b_pref = b_pref,
+    b_switch = b_switch,
+    spat_config = spat_config
+  )
+  
[…]

### 2022-04-11 Analysis/functions/sim_foraging_spatial.R

@@ -1,0 +1,104 @@
+library(tidyverse)
+
+
+sim_spatial_trials <- function(n = 10, m = 10, tune_prox = 1, b_pref = 0, b_switch = 0, n_trials = 10, spat_config = FALSE) 
+{
+  # n is number of targets present
+  # m is number of targets to find
+  
+  params <- list(
+    n = n,
+    m = m,
+    tune_prox = tune_prox,
+    b_pref = b_pref,
+    b_switch = b_switch,
+    spat_config = spat_config
+  )
+  
+  dat <- map_df(1:n_trials, sim_spatial_trial, params = params)
+  
+  return(dat)
+}
+
+sim_spatial_trial <- function(params, trial = 1)
+{
+  
+  # n is total number of targets
+  # m is the number that we want to find
+
+  d_trial <- tibble(
+    trial = trial,
+    id = 1:params$n,
+    x  = runif(params$n),
+    y = runif(params$n),
+    type = rbinom(params$n, 1, 0.5),
+    found = -1,
+    dist = NA)
+  
+  if (params$spat_config==TRUE) 
+  {
+    
+    d_trial %>% mutate(
+      type = if_else(x < 0.5, 0, 1)
+    ) -> d_trial
+    
+  }
+  
+  #d_trial <- mutate(d_trial, type = if_else(type ==0, -1, 1))
+  
+  # compute proximity info
+  delta <- as.matrix(dist(select(d_trial, x, y), upper = TRUE, diag = TRUE))
+  delta <- as_tibble(delta) 
+  names(delta) = paste("dt", 1:params$n, sep = "_")
+  d_trial <- bind_cols(d_trial, delta)
+  
+  #### TODO
+  # use the precompute prox info in the simulation below
+  
+  d_remain <- d_trial %>% 
+    mutate(
+      dist = 0,
+      prox = 0,
+      b = boot::inv.logit(params$b_pref * type),
+      b = b/sum(b))
+  
+  # pick a first point at random
+  d_found <- sample_n(d_remain, 1, weight = b) %>%
+    mutate(t = 1)
+  
+  # remove this point from the stimuli
+  d_remain <- filter(d_remain, id != d_found$id)
+  d_trial$found[d_found$id[1]] <- 1
+  
+ # varname <- paste("dt",d_found$id[1], sep = "_" )
+ # d_trial[which(d_trial$found == -1),][varname] = 999
+  
+  for (t in 2:params$m) {
+    
[…]

### 2022-04-11 Analysis/testing_new_prox_function.R

@@ -1,0 +1,24 @@
+library(tidyverse)
+library(rstan)
+
+source("../functions/prep_stan_data_momentum.R")
+
+d <- read_csv("../reanalysis_data/clarke_2020_qjep.csv") %>%
+ # mutate(condition = as_factor(condition),
+ #        condition = fct_recode(condition, feature = "1", conjunction = "2")) %>% 
+  filter(observer == 1) 
+
+
+n_targets <- 40
+n_trials = max(d$trial)
+prior_b = 1
+
+stan_data <- prep_stan_data(d)
+stan_model_name <- "momentum_foraging"
+
+
+fit_ids <- stan(paste("../models/momentum_models/", stan_model_name, ".stan", sep = ""),
+                data = stan_data,
+                chains = 5,
+                iter = 1000,
+                refresh = 10)

### 2022-04-11 Analysis/trial_level_predictions.R

@@ -1,0 +1,87 @@
+library(tidyverse)
+library(rstan)
+library(tidybayes)
+library(patchwork)
+library(ggrepel)
+
+source("../functions/get_model_params.R")
+source("comp_weights.R")
+
+d <- read_csv("../reanalysis_data/clarke_2020_qjep.csv") %>%
+  mutate(condition = as_factor(condition),
+         condition = fct_recode(condition, feature = "1", conjunction = "2"))
+
+fit <- get_model_params() %>% rename(observer = "obs")
+
+comp_trials <- function(obs, cond) {
+  params <- filter(fit,  observer == obs, condition == cond )
+  a <- map_dfr(1:20, comp_weights, params = params, cond = cond, obs = obs)
+  return(a)
+}
+
+# a_feat <- map_dfr(unique(d$observer), comp_trials, cond = "feature")
+# a_conj <- map_dfr(unique(d$observer), comp_trials, cond = "conjunction")
+# a <- bind_rows(a_feat, a_conj)
+# rm(a_feat, a_conj)
+
+a <- readRDS("model_weights.rda")
+
+a %>% group_by(condition, observer, found) %>%
+  summarise(meanb = mean(b),
+            prop_best = mean(bMax)) %>%
+  filter(found > 1) %>%
+  mutate(chance = 1/(41-found))-> a_agg
+
+ggplot(a_agg, aes(x = found, y = meanb, colour = condition, fill = condition)) + 
+  geom_jitter(width = 0.2, height = 0, alpha = 0.25) + 
+  stat_lineribbon(alpha = 0.25) + 
+  geom_path(data = filter(a_agg, observer == 1, condition == "feature"), 
+                          aes(y = chance), linetype = 2, colour = "black") + 
+  theme_minimal() +
+  ggthemes::scale_fill_fivethirtyeight() + 
+  ggthemes::scale_colour_fivethirtyeight() +
+  scale_x_continuous("target selection") + 
+  scale_y_continuous("average weight from model") -> plt_b
+
+ggplot(a_agg, aes(x = found, y = prop_best, colour = condition, fill = condition)) + 
+  geom_jitter(width = 0.2, height = 0, alpha = 0.25) + 
+  stat_lineribbon(alpha = 0.25) + 
+  geom_path(data = filter(a_agg, observer == 1, condition == "feature"), 
+            aes(y = chance), linetype = 2, colour = "black") + 
[…]

### 2022-04-11 Analysis/sup_mat.Rmd
created an Rmd

---
title: 'SVG: The Paper'
author: "Alasdair and Anna"
date: "11/04/2022"
output: html_document
---

```{r}
library(tidyverse)
library(patchwork)
```

# Initial Selection

## QJEP Dataset

```{r}
d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))

ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
  facet_wrap(~observer)

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y)) %>%
  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))

plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
plt_x + plt_y
```

### 2022-04-11 Analysis/trial_level_predictions.R

@@ -4,10 +4,10 @@ library(tidybayes)
 library(patchwork)
 library(ggrepel)
 
-source("../functions/get_model_params.R")
+source("functions/get_model_params.R")
 source("comp_weights.R")
 
-d <- read_csv("../reanalysis_data/clarke_2020_qjep.csv") %>%
+d <- read_csv("data/clarke_2020_qjep.csv") %>%
   mutate(condition = as_factor(condition),
          condition = fct_recode(condition, feature = "1", conjunction = "2"))
 
@@ -24,7 +24,7 @@ comp_trials <- function(obs, cond) {
 # a <- bind_rows(a_feat, a_conj)
 # rm(a_feat, a_conj)
 
-a <- readRDS("model_weights.rda")
+a <- readRDS("scratch/model_weights.rda")
 
 a %>% group_by(condition, observer, found) %>%
   summarise(meanb = mean(b),
@@ -55,7 +55,7 @@ ggplot(a_agg, aes(x = found, y = prop_best, colour = condition, fill = condition
   scale_y_continuous("proportion most likely was selected") -> plt_c
 
 plt_b + plt_c + plot_layout(guides = "collect")
-ggsave("qjep_preds.png", width = 9, height = 4)
+ggsave("../Figures/qjep_preds.png", width = 9, height = 4)
 
 a %>% mutate(b_bin = cut(b, breaks = 100, labels = FALSE)) %>%
   group_by(b_bin) %>% 
@@ -75,7 +75,7 @@ ggplot(filter(d, observer == 1, trial == 3, condition == "conjunction"), aes(x, 
 
 
 
-a %>% group_by(observer, condition, trial) %>%
+a %>% group_by(observer, condition) %>%
   summarise(acc = mean(bMax, na.rm = T)) %>%
   arrange((acc))
 

### 2022-04-11 manuscript.tex

--- 2022-04-11 template.tex
@@
 % Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorA}{0000-0002-7368-2351} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0002-4122-9499} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorC}{0000-0003-2677-1965}
 
 % Authors, for the paper (add full first names)
-\Author{Alasdair Clarke $^{1,\dagger,\ddagger}$\orcidA{}, Amelia Hunt $^{1,\ddagger}$ and Anna Hughes $^{2,}$*}
+\Author{Alasdair Clarke $^{1}$\orcidA{}, Amelia Hunt $^{2}$\orcidB{} and Anna Hughes\orcidC{} $^{1,}$*}
 
@@
 % Current address and/or shared authorship
-\firstnote{Current address: Affiliation 3} 
-\secondnote{These authors contributed equally to this work.}
+%\firstnote{Current address: Affiliation 3} 
+%\secondnote{These authors contributed equally to this work.}
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
@@
 
+Briefly overview model and datasets using.
+
 Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
@@
 It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\subsection{Subsection}
+
+\subsection{Initial target selection}
+
+\subsection{Trial-level predictions}
+
+\subsection{Improvement: Adaptive distance? Absolute direction?}
+
 \subsubsection{Subsubsection}
@@
 \begin{figure}[H]
-\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
+\includegraphics[width=10.5 cm]{Figures/qjep_preds.png}
 \caption{This is a figure.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Patents}
-
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
+Remaining open questions
 
@@
 If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}
-
-%% Optional
-\sampleavailability{Samples of the compounds ... are available from the authors.}
 

### 2022-04-12 Analysis/sup_mat.Rmd
Tagu initial selections

@@
 ```
+
+## Tagu dataset
+
+```{r}
+d <- read_csv("data/tagu_2020_prox_mouse.csv", show_col_types = FALSE) %>%
+  filter(found == 1) %>%
+  mutate(condition = as_factor(condition))
+
+ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
+  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
+  facet_wrap(~observer)
+
+d %>% group_by(observer, condition) %>% 
+  summarise(x = median(x), y = median(y)) %>%
+  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) #+
+  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
+
+plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
+plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
+plt_x + plt_y
+```

### 2022-04-12 Analysis/comp_weights.R
Adding comments to compute_weights script

@@ -1,67 +1,0 @@
-comp_weights <- function(trl, params, cond, obs)
-{
-  
-  d_trl <- filter(d, observer == obs, condition == cond, trial == trl)
-  
-  if (nrow(d_trl) == 0) {
-    
-    
-  }
-  else
-  {
-  
-  
-  d_trl$b = NaN
-  d_trl$bMax = NaN
-  d_trl$err = NaN
-  d_trl$model_pref = NaN
-  
-  
-  for (t in 2:40) {
-    
-    prev_targ <- d_trl$targ_type[t-1]
-    
-    
-    x0 <- d_trl$x[t-1]
-    y0 <- d_trl$y[t-1]
-    
-    x00 <- d_trl$x[t-2]
-    y00 <- d_trl$y[t-2]
-    
-    d_remain <- filter(d_trl, found>=t)
-    
-    match_prev = if_else(d_remain$targ_type == prev_targ, 1, -1)
-    
-    if (t == 2) {
-      d_remain %>% mutate(
-        dist = (x0 - x)^2 + (y0 - y)^2,
-        dist = sqrt(dist),
-        prox = exp((-params$bP * dist)),
-        b = params$pA * targ_type + params$pS * match_prev,
-        b = boot::inv.logit(b) * prox,
-        b = b/sum(b)) -> d_remain
-    } else {
-      d_remain %>% mutate(
-        dist = (x0 - x)^2 + (y0 - y)^2,
-        dist = sqrt(dist),
-        phi = atan2(( y0 - y00), (x0 - y00)) * 180/pi,
-        phi = (atan2((y - y0), (x - x0)) * 180/pi) - phi ,
-        phi = pmin(abs((phi %% 360)), abs((-phi %% 360))),
-        phi = phi/180,
-        prox = exp((-params$bP * dist) - (params$bM * phi)),
-        b = params$pA * targ_type + params$pS * match_prev,
-        b = boot::inv.logit(b) * prox,
-        b = b/sum(b)) -> d_remain
-      
-    }
-    
-    d_trl$b[t] <- d_remain$b[which(d_remain$found==t)]
-    d_trl$bMax[t] <- d_trl$b[t] == max(d_remain$b)
-    d_trl$err[t] <-  max(d_remain$b) - d_trl$b[t]
-    d_trl$model_pref[t] <- d_remain$found[which(d_remain$b == max(d_remain$b) )]
-    
-    
-  }}
-  
-  return(d_trl)
-}

### 2022-04-12 Analysis/functions/compute_weights.R

@@ -1,0 +1,81 @@
+compute_weights <- function(trl, params, cond, obs)
+{
+  
+  # function to step through empirical foraging data and compute the item weights
+  # for every target selection
+  
+  # select the revelant trial
+  d_trl <- filter(d, observer == obs, condition == cond, trial == trl)
+  
+  if (nrow(d_trl) == 0) {
+    
+    # if the data for this trial is missing, do nothing
+    
+  }
+  else
+  {
+  
+    # init column for the weight stats we want to select
+    d_trl$b = NaN # weight of target next selected by participant
+    d_trl$selected_max = NaN # did the participant select the most likely target?
+    d_trl$max_b = NaN # weight of most likely target
+    d_trl$model_pref = NaN # item ID for the most likely target
+    
+    # step through each target selection....
+    for (t in 2:40) {
+      
+      # get info about the previously selected item
+      prev_targ <- d_trl$targ_type[t-1]
+      
+      x0 <- d_trl$x[t-1]
+      y0 <- d_trl$y[t-1]
+      
+      # and the item selected before that...
+      x00 <- d_trl$x[t-2]
+      y00 <- d_trl$y[t-2]
+      
+      # get list of items that haven't been selected yet
+      d_remain <- filter(d_trl, found>=t)
+      
+      # check which items match the previously selected item
+      match_prev = if_else(d_remain$targ_type == prev_targ, 1, -1)
+      
+      # compute proximity info
+      d_remain %>% mutate(
+        dist = (x0 - x)^2 + (y0 - y)^2,
+        dist = sqrt(dist)) -> d_remain
+      
+      if (t == 2) {
+        
+        # if it's the second item selection, compute spatial weight based just on distance
+        d_remain %>% mutate( 
+          prox = exp(-params$bP * dist)) -> d_remain 
+        
+      } else {
+        
+        # but if t>2, we first compute phi and then compute spatial weight
+        d_remain %>% mutate(
+          phi = atan2(( y0 - y00), (x0 - y00)) * 180/pi,
+          phi = (atan2((y - y0), (x - x0)) * 180/pi) - phi ,
+          phi = pmin(abs((phi %% 360)), abs((-phi %% 360)))/180,
+          prox = exp((-params$bP * dist) - (params$bM * phi))) -> d_remain
+      }
+      
+      # now compute weights for each item
[…]

### 2022-04-12 Analysis/functions/get_model_params.R

@@ -1,10 +1,9 @@
-get_model_params <- function() {
+get_model_params <- function(filename) {
   
   
   cond_levels = c("feature", "conjunction")
   
-  m <- readRDS("../saved_models/all_qjep_2020.rds")
-  
+  m <- readRDS(filename)
   
   m %>% spread_draws(b[cond], u[cond, obs]) %>%
     mutate(cond = as.factor(cond),

### 2022-04-12 Analysis/testing_init_selection.R

@@ -1,0 +1,44 @@
+library(tidyverse)
+library(rstan)
+library(tidybayes)
+
+options(digits = 2, mc.cores = 10)
+d <- read_csv("data/clarke_2020_qjep.csv") %>%
+  filter(found == 1)
+
+
+stan_data <- list(N = nrow(d),
+                  L = max(d$observer),
+                  Z = d$observer,
+                  x = d$x,
+                  y = d$y)
+
+m <- stan("models/initial_selection_models/init_sel.stan",
+                data = stan_data,
+                chains = 4,
+                iter = 1000,
+                refresh = 100)
+
+
+
+saveRDS(m, "scratch/init_sel_model.rds")
+
+gather_draws(m, u[dim, observer]) %>% 
+  ungroup() %>%
+  select(-.variable) %>%
+  rename(obs_mu = ".value") %>%
+  full_join(gather_draws(m, mu[dim])) %>%
+  mutate(obs_mu = .value + obs_mu) -> a 
+
+
+d %>% pivot_longer(c(x, y), names_to = "dim", values_to = "value") %>%
+  mutate(dim = if_else(dim == "x", 1, 2)) -> d_plt
+
+a %>% ggplot(aes(obs_mu, group = observer)) + geom_density() + 
+  facet_grid(observer~dim, scales = "free") + 
+  geom_density(data = d_plt, aes(value), colour = "purple")
+
+%>%
+  ggplot(aes(.value, group = observer)) + 
+  geom_density(alpha = 0.1) + 
+  facet_wrap(~.variable)

### 2022-04-12 Analysis/trial_level_predictions.R

@@ -5,26 +5,30 @@ library(patchwork)
 library(ggrepel)
 
 source("functions/get_model_params.R")
-source("comp_weights.R")
+source("functions/compute_weights.R")
 
+# read in data
 d <- read_csv("data/clarke_2020_qjep.csv") %>%
   mutate(condition = as_factor(condition),
          condition = fct_recode(condition, feature = "1", conjunction = "2"))
 
-fit <- get_model_params() %>% rename(observer = "obs")
+# read in model
+
+fit <- get_model_params("scratch/all_qjep_2020.rds") %>% rename(observer = "obs")
 
 comp_trials <- function(obs, cond) {
   params <- filter(fit,  observer == obs, condition == cond )
-  a <- map_dfr(1:20, comp_weights, params = params, cond = cond, obs = obs)
+  a <- map_dfr(1:20, compute_weights, params = params, cond = cond, obs = obs)
   return(a)
 }
 
-# a_feat <- map_dfr(unique(d$observer), comp_trials, cond = "feature")
-# a_conj <- map_dfr(unique(d$observer), comp_trials, cond = "conjunction")
-# a <- bind_rows(a_feat, a_conj)
-# rm(a_feat, a_conj)
+a_feat <- map_dfr(unique(d$observer), comp_trials, cond = "feature")
+a_conj <- map_dfr(unique(d$observer), comp_trials, cond = "conjunction")
+a <- bind_rows(a_feat, a_conj)
+rm(a_feat, a_conj)
 
-a <- readRDS("scratch/model_weights.rda")
+saveRDS(a, "scratch/qjep_model_weights.rda")
+a <- readRDS("scratch/qjep_model_weights.rda")
 
 a %>% group_by(condition, observer, found) %>%
   summarise(meanb = mean(b),

### 2022-04-12 Analysis/sup_mat.Rmd
Adding comments to compute_weights script
setting up Rmd etc

@@
 library(patchwork)
+library(tidybayes)
+```
+
+```{r}
+# set ggplot2 options
+theme_set(theme_minimal())
+
+our_cols <- c("#1b9e77", "#7570b3")
+options(ggplot2.discrete.fill = our_cols ,
+        ggplot2.discrete.colour = our_cols)
+```
+
+# Trial Level Posterior Predictions
+
+```{r echo = FALSE}
+source("functions/get_model_params.R")
+source("functions/compute_weights.R")
+```
+
+## Clarke et al (2022)
+
+```{r}
+a <- readRDS("scratch/qjep_model_weights.rda")
+
+a %>% group_by(condition, observer, found) %>%
+  summarise(meanb = mean(b),
+            prop_best = mean(selected_max), .groups = "drop") %>%
+  filter(found > 1) %>%
+  mutate(chance = 1/(41-found))-> a_agg
+```
+
+```{r, fig.cap = "(Left) The average weight assigned to each selected target by our model.
+(Right) The proportion of trials the item with the largest assigned weight as selected by the participant.
+Each dot shows data from an individual particpant in a condition and the shaded region indicates the invertal in which we expect 67% of participants to fall."}
+
+# plot target selected weights
+ggplot(a_agg, aes(x = found, y = meanb, colour = condition, fill = condition)) + 
+  geom_jitter(data = filter(a_agg, found<40), width = 0.1, height = 0, alpha = 0.2) + 
+  stat_lineribbon(.width = 0.67, alpha = 0.50) +
+  geom_path(data = filter(a_agg, observer == 1, condition == "feature"), 
+                          aes(y = chance), linetype = 2, colour = "black") + 
+  geom_point(data = tibble(x=40, y=1), aes(x, y), size = 1.5, colour = "black", fill = "grey") + 
+  scale_x_continuous(breaks = c(2, 10, 20, 40), "target selection", expand = c(0.01, 0.01)) + 
+  scale_y_continuous("average weight from model", expand = c(0.01, 0.01)) -> plt_b
+
+ggplot(a_agg, aes(x = found, y = prop_best, colour = condition, fill = condition)) + 
+  geom_jitter(data = filter(a_agg, found<40), width = 0.1, height = 0.00, alpha = 0.2) + 
+  stat_lineribbon(.width = 0.67, alpha = 0.50) +
+  geom_path(data = filter(a_agg, observer == 1, condition == "feature"), 
+            aes(y = chance), linetype = 2, colour = "black") + 
+  geom_point(data = tibble(x=40, y=1), aes(x, y), size = 1.5, colour = "black", fill = "grey") + 
+  scale_x_continuous(breaks = c(2, 10, 20, 40), "target selection", expand = c(0.01, 0.01)) + 
+  scale_y_continuous("proportion most likely was selected", expand = c(0.01, 0.01)) -> plt_c
+
+plt_b + plt_c + plot_layout(guides = "collect")  &
+  theme(legend.position = 'bottom',
+        legend.direction = 'horizontal')
+ggsave("../Figures/qjep_preds.png", width = 9, height = 4)
 ```

### 2022-04-12 Analysis/trial_level_predictions.R

@@ -12,16 +12,17 @@ d <- read_csv("data/clarke_2020_qjep.csv") %>%
   mutate(condition = as_factor(condition),
          condition = fct_recode(condition, feature = "1", conjunction = "2"))
 
-# read in model
-
+# read in model and extract weights
 fit <- get_model_params("scratch/all_qjep_2020.rds") %>% rename(observer = "obs")
 
+## function to compute weights for all items in all trials for a participant
 comp_trials <- function(obs, cond) {
   params <- filter(fit,  observer == obs, condition == cond )
   a <- map_dfr(1:20, compute_weights, params = params, cond = cond, obs = obs)
   return(a)
 }
 
+# run for all participants...
 a_feat <- map_dfr(unique(d$observer), comp_trials, cond = "feature")
 a_conj <- map_dfr(unique(d$observer), comp_trials, cond = "conjunction")
 a <- bind_rows(a_feat, a_conj)
@@ -30,35 +31,36 @@ rm(a_feat, a_conj)
 saveRDS(a, "scratch/qjep_model_weights.rda")
 a <- readRDS("scratch/qjep_model_weights.rda")
 
+
+
 a %>% group_by(condition, observer, found) %>%
   summarise(meanb = mean(b),
-            prop_best = mean(bMax)) %>%
+            prop_best = mean(selected_max)) %>%
   filter(found > 1) %>%
   mutate(chance = 1/(41-found))-> a_agg
 
+# plot target selected weights
 ggplot(a_agg, aes(x = found, y = meanb, colour = condition, fill = condition)) + 
-  geom_jitter(width = 0.2, height = 0, alpha = 0.25) + 
-  stat_lineribbon(alpha = 0.25) + 
+  geom_jitter(data = filter(a_agg, found<40), width = 0.1, height = 0, alpha = 0.2) + 
+  stat_lineribbon(.width = 0.67, alpha = 0.50) +
   geom_path(data = filter(a_agg, observer == 1, condition == "feature"), 
                           aes(y = chance), linetype = 2, colour = "black") + 
-  theme_minimal() +
-  ggthemes::scale_fill_fivethirtyeight() + 
-  ggthemes::scale_colour_fivethirtyeight() +
-  scale_x_continuous("target selection") + 
-  scale_y_continuous("average weight from model") -> plt_b
[…]

### 2022-04-12 Analysis/index.Rmd
playing with bookdown

--- 2022-04-12 Analysis/sup_mat.Rmd
@@
 date: "11/04/2022"
-output: html_document
+output:
+  tufte::tufte_html:
+    toc: TRUE
+    number_sections: true
 ---
 
-```{r}
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+```
+
+```{r, message=FALSE}
+# attach packages
 library(tidyverse)
@@
 # set ggplot2 options
-theme_set(theme_minimal())
+theme_set(ggthemes::theme_tufte())
 
@@
 
-# Trial Level Posterior Predictions
+# Trial Level Posterior Predictions{#label}
 
@@
 
-```{r, fig.cap = "(Left) The average weight assigned to each selected target by our model.
-(Right) The proportion of trials the item with the largest assigned weight as selected by the participant.
+```{r, fig.cap = "(*left*) The average weight assigned to each selected target by our model.
+(*right*) The proportion of trials the item with the largest assigned weight as selected by the participant.
 Each dot shows data from an individual particpant in a condition and the shaded region indicates the invertal in which we expect 67% of participants to fall."}
@@
 ggsave("../Figures/qjep_preds.png", width = 9, height = 4)
+```
+
+From this figure we can see a few interesting things to note:
+
+- large individual differences in how well our model can capture and predict behaviour
+- feature search is more predictable than conjunction search
+- our model appears to be overly conservative
+
+### Individual Differences
+
+How often does each participant select the target with the largest weight? And is this explained by differences in proximity weighting?
+
+```{r, fig.cap = "Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. (The dots indicate outliers.)"}
+a_agg %>% group_by(observer, condition) %>%
+  summarise(accuracy = mean(prop_best), .groups = "drop") %>%
+  ggplot(aes(x= condition, y = accuracy, fill = condition)) + 
+  geom_boxplot() +
+  geom_line(aes(group = observer), alpha = 0.25, colour = "sienna4") +
+  scale_y_continuous("model accuracy",  limits = c(0.3, 0.8), breaks = seq(0.3, 0.8, 0.1))
+
+```
+
+### Calibration
+
+```{r}
+a %>% mutate(b_bin = cut(max_b, breaks = 100, labels = FALSE)) %>%
+  group_by(condition, b_bin) %>% 
+  summarise(acc = mean(selected_max), .groups = "drop") %>%
+  mutate(b_bin = as.numeric(b_bin)/100) %>%
+  filter(is.finite(acc)) %>%
+  ggplot(aes(b_bin, acc, colour = condition)) + 
+  geom_point() + 
+  geom_line(stat = "smooth", method = "loess", formula = y ~ x, alpha = 0.65, size = 2, se = F) +
+  geom_abline(linetype = 2) +
+  scale_x_continuous("largest item weight") +
+  scale_y_continuous("proportion of times selected") + 
+  coord_fixed()
 ```

### 2022-04-12 Analysis/functions/compute_weights.R

@@ -71,7 +71,7 @@ compute_weights <- function(trl, params, cond, obs)
       # finally compute some stats about the item weights
       d_trl$b[t] <- d_remain$b[which(d_remain$found==t)]
       d_trl$selected_max[t] <- d_trl$b[t] == max(d_remain$b)
-      d_trl$max_b[t] <-  max(d_remain$b) - d_trl$b[t]
+      d_trl$max_b[t] <-  max(d_remain$b)
       d_trl$model_pref[t] <- d_remain$found[which(d_remain$b == max(d_remain$b) )]
       
     }

### 2022-04-12 Analysis/trial_level_predictions.R

@@ -7,6 +7,8 @@ library(ggrepel)
 source("functions/get_model_params.R")
 source("functions/compute_weights.R")
 
+
+
 # read in data
 d <- read_csv("data/clarke_2020_qjep.csv") %>%
   mutate(condition = as_factor(condition),
@@ -15,12 +17,6 @@ d <- read_csv("data/clarke_2020_qjep.csv") %>%
 # read in model and extract weights
 fit <- get_model_params("scratch/all_qjep_2020.rds") %>% rename(observer = "obs")
 
-## function to compute weights for all items in all trials for a participant
-comp_trials <- function(obs, cond) {
-  params <- filter(fit,  observer == obs, condition == cond )
-  a <- map_dfr(1:20, compute_weights, params = params, cond = cond, obs = obs)
-  return(a)
-}
 
 # run for all participants...
 a_feat <- map_dfr(unique(d$observer), comp_trials, cond = "feature")
@@ -63,16 +59,19 @@ plt_b + plt_c + plot_layout(guides = "collect")  &
         legend.direction = 'horizontal')
 ggsave("../Figures/qjep_preds.png", width = 9, height = 4)
 
-a %>% mutate(b_bin = cut(b, breaks = 100, labels = FALSE)) %>%
-  group_by(b_bin) %>% 
-  summarise(acc = mean(bMax)) %>%
+a %>% mutate(b_bin = cut(max_b, breaks = 100, labels = FALSE)) %>%
+  group_by(condition, b_bin) %>% 
+  summarise(acc = mean(selected_max)) %>%
   mutate(b_bin = as.numeric(b_bin)/100) %>%
-  ggplot(aes(b_bin, acc)) + geom_path() +
+  filter(is.finite(acc)) %>%
+  ggplot(aes(b_bin, acc, colour = condition)) + 
+  geom_point() + 
+  geom_line(stat = "smooth", method = "loess", alpha = 0.5, size = 2, se = F) +
   geom_abline(linetype = 2)
 
 
 
-mistakes <- filter(a, observer == 1, trial == 3, condition == "conjunction", err> 0.5) %>%
+mistakes <- filter(a, observer == 1, trial == 3, condition == "conjunction", err> 0.75) %>%
   select(x, y, found, err, model_pref)
 
 ggplot(filter(d, observer == 1, trial == 3, condition == "conjunction"), aes(x, y, colour = targ_type)) +

### 2022-04-13 Analysis/index.Rmd
acc by bP

@@
 knitr::opts_chunk$set(echo = FALSE)
+options(digits = 3)
 ```
@@
 # set ggplot2 options
-theme_set(ggthemes::theme_tufte())
+theme_set(ggthemes::theme_tufte() + theme(plot.background = element_rect(fill = "grey95", colour = "grey95")))
 
@@
 ```
+
+Terminology questions:
+- item v target
+- participant v observer
 
@@
 
-```{r}
-a <- readRDS("scratch/qjep_model_weights.rda")
+We will start by looking at the visual foraging data from Clarke et al (2022), QJEP.
+As the current version of our model only takes the $p_A$ bias into account for the initial taret selection, we will ignore these data points for now.
+
+```{r, echo = TRUE}
+# item weights pre-computed - see xxxxx.R
+a <- readRDS("scratch/qjep_model_weights.rda") %>%
+  filter(found != 1) # remove initial selections
+
+# compute the average weight for each participant x condition x item selection
+# also compute the proportion of times in which the item selected by the 
+# participant was judged the most likely to be selected by our model.
 
@@
             prop_best = mean(selected_max), .groups = "drop") %>%
-  filter(found > 1) %>%
+  # finally, also compute what we would expect under a null-model
   mutate(chance = 1/(41-found))-> a_agg
@@
 
-### Individual Differences
+### Calibration
 
-How often does each participant select the target with the largest weight? And is this explained by differences in proximity weighting?
+Is our model calibrated? By this we mean, if our model assigns an item a probability $p$ of being selected next, then is it actually be selected (by the human participant) this often?
 
-```{r, fig.cap = "Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. (The dots indicate outliers.)"}
-a_agg %>% group_by(observer, condition) %>%
-  summarise(accuracy = mean(prop_best), .groups = "drop") %>%
-  ggplot(aes(x= condition, y = accuracy, fill = condition)) + 
-  geom_boxplot() +
-  geom_line(aes(group = observer), alpha = 0.25, colour = "sienna4") +
-  scale_y_continuous("model accuracy",  limits = c(0.3, 0.8), breaks = seq(0.3, 0.8, 0.1))
+We will calculate this as follows: for each target selection (on each trial, for each participant) we look at the weight assigned to the most likely item, and then look at whether it was selected or not.
 
+```{r, echo = TRUE}
+n_breaks = 25
+
+a %>% mutate(b_bin = cut(max_b, breaks = n_breaks, labels = FALSE)) %>%
+  group_by(condition, b_bin) %>% 
+  summarise(acc = mean(selected_max), .groups = "drop") %>%
+  mutate(b_bin = as.numeric(b_bin)/n_breaks) -> a_cut
 ```
 
-### Calibration
+We can see from the Figure below that our model is well-calibrated, (at least in terms of the target with the highest assigned weight).
 
-```{r}
-a %>% mutate(b_bin = cut(max_b, breaks = 100, labels = FALSE)) %>%
-  group_by(condition, b_bin) %>% 
-  summarise(acc = mean(selected_max), .groups = "drop") %>%
-  mutate(b_bin = as.numeric(b_bin)/100) %>%
-  filter(is.finite(acc)) %>%
-  ggplot(aes(b_bin, acc, colour = condition)) + 
+```{r, fig.cap = "Calibration plot for our foraging model.
+The *x*-axis gives the largest weight assigned by the model while the *y*-axis shows how often that target was actually selected by a human participant."}
+
+ggplot(a_cut, aes(b_bin, acc, colour = condition, shape = condition)) + 
   geom_point() + 
-  geom_line(stat = "smooth", method = "loess", formula = y ~ x, alpha = 0.65, size = 2, se = F) +
+  geom_line(stat = "smooth", method = "loess", 
+            formula = y ~ x, alpha = 0.65, size = 2, se = F) +
   geom_abline(linetype = 2) +
@@
   coord_fixed()
+```
+
+If anything, our model is a little conservative: items are selected around 5% more often than we'd expect.
+
+```{r, echo = TRUE}
+mean(a_cut$acc - a_cut$b_bin)
+```
+
+```{r}
+rm(a_cut)
+```
+
+We can also repeat this calculate for all other items during/in a trial - is our model accurate/calibrated in cases when 
+the participant did not select the item withe highest model weight?
+
+<TODO>
+
+### Individual Differences
+
+How often does each participant select the target with the largest weight?
+
+```{r, fig.cap = "Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. (The dots indicate outliers.)", echo= TRUE}
+
+a_agg %>% group_by(observer, condition) %>%
+  summarise(accuracy = mean(prop_best), .groups = "drop") -> a_acc
+
+ggplot(a_acc, aes(x= condition, y = accuracy, fill = condition)) + 
+  geom_boxplot() +
+  geom_line(aes(group = observer), alpha = 0.25, colour = "sienna4") +
+  scale_y_continuous("model accuracy",  
+                     limits = c(0.3, 0.8), breaks = seq(0.3, 0.8, 0.1))
+```
+
+Is this explained by differences in proximity weighting? i.e., are participants with weaker proximity biases harder to predict? Yes!
+
+```{r, fig.cap = "Accuracy of our model appears to vary with the strength of an individual's proximity bias."}
+# computed in xxxx.R
+fit <- readRDS("scratch/qjep_model_fit.rda") %>%
+  full_join(a_acc, by = c("observer", "condition"))
+
+ggplot(fit, aes(bP, accuracy, colour = condition)) + 
+  geom_point() +
+  geom_smooth(method = "lm", formula = y ~ x, se = FALSE)
+```
+Furthermore, this appears to account for most of the difference between the *feature* and *conjunction* conditions.
+
+```{r, echo = TRUE}
+summary(lm(accuracy ~ condition * bP, fit))
 ```

### 2022-04-13 Analysis/trial_level_predictions.R

@@ -16,7 +16,7 @@ d <- read_csv("data/clarke_2020_qjep.csv") %>%
 
 # read in model and extract weights
 fit <- get_model_params("scratch/all_qjep_2020.rds") %>% rename(observer = "obs")
-
+saveRDS(fit, "scratch/qjep_model_fit.rda")
 
 # run for all participants...
 a_feat <- map_dfr(unique(d$observer), comp_trials, cond = "feature")

### 2022-04-13 Analysis/index.Rmd
Update index.Rmd

@@
 title: 'SVG: The Paper'
-author: "Alasdair and Anna"
-date: "11/04/2022"
+author: "Alasdair Clarke, Amelia Hunt &  Anna Hughes"
+date: "13/04/2022"
 output:
@@
 
-```{r, fig.cap = "Accuracy of our model appears to vary with the strength of an individual's proximity bias."}
+```{r, fig.cap = "Accuracy of our model varies with the strength of an individual's proximity bias."}
 # computed in xxxx.R

### 2022-04-13 Analysis/index.Rmd
trial level plot nearly working

@@
 library(tidybayes)
+library(ggrepel)
 ```
@@
 # set ggplot2 options
-theme_set(ggthemes::theme_tufte() + theme(plot.background = element_rect(fill = "grey95", colour = "grey95")))
+theme_set(ggthemes::theme_tufte() + theme(plot.background = element_rect(fill = "#fffff8", colour = "#fffff8")))
+
+# some more colours
+#Isfahan2 = list(c("#d7aca1", "#ddc000", "#79ad41", "#34b6c6", "#4063a3"), c(4, 2, 3, 5, 1), colo
 
@@
 ```{r, echo = TRUE}
+# read in data
+d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
+  mutate(condition = as_factor(condition),
+         condition = fct_recode(condition, feature = "1", conjunction = "2"),
+         targ_type = as_factor(targ_type))
+
 # item weights pre-computed - see xxxxx.R
@@
 ```
+### Examples of Trials
 
-# Initial Selection
+Let's score every trial by how well the model captures behaviour, and then plot some different examples
 
-## QJEP Dataset
-
-```{r}
-d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
-  filter(found == 1) %>%
-  mutate(condition = as_factor(condition))
-
-ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
-  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
-  facet_wrap(~observer)
-
-d %>% group_by(observer, condition) %>% 
-  summarise(x = median(x), y = median(y)) %>%
-  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
-  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
-
-plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
-plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
-plt_x + plt_y
+```{r, echo = TRUE}
+a %>% group_by(observer, condition, trial) %>% 
+  summarise(prop_max = mean(selected_max), .groups = "drop") %>% 
+  arrange(desc(prop_max)) %>%
+  ungroup() -> a_trl
 ```
 
-## Tagu dataset
+```{r, fig.cap = "Histogram of how predictiable indivuidual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
+ggplot(a_trl, aes(prop_max)) + 
+  geom_histogram(fill = "#34b6c6", breaks = seq(0, 1, 0.025)) +
+  scale_x_continuous("trial predictability")
+```
 
-```{r}
-d <- read_csv("data/tagu_2020_prox_mouse.csv", show_col_types = FALSE) %>%
-  filter(found == 1) %>%
-  mutate(condition = as_factor(condition))
+Let's plot some examples oh highly predictable (top 5%), and unpredictable (bottom 5%) trials.
 
-ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
-  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
-  facet_wrap(~observer)
+```{r, echo = TRUE}
+qs <- quantile(a_trl$prop_max, c(0.05, 0.95))
 
-d %>% group_by(observer, condition) %>% 
-  summarise(x = median(x), y = median(y)) %>%
-  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) #+
-  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
+trls_hard <- filter(a_trl, prop_max < qs[1]) %>% sample_n(3)
+trls_easy <- filter(a_trl, prop_max > qs[2]) %>% sample_n(3)
 
-plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
-plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
-plt_x + plt_y
+# 
+source("plot_trial.R")
+
+plts <- map(1:3, plot_trial, trls_easy, a, d)
+
+#plts[1] + plts[2] + plts[3]
+
+plot(plot_trial(1, trls_hard, a, d))
+
 ```

### 2022-04-13 Analysis/plot_trial.R

@@ -1,0 +1,46 @@
+mistake_x_y <- function(ii, trl, mistakes) {
+  mistake <- mistakes[ii, ]
+  
+  t1 <- filter(trl, found == mistake$found-1)
+  t2 <- filter(trl, found == mistake$model_pref)
+  
+  dout <- tibble(id = ii, 
+                 x1 = t1$x, y1 = t1$y,
+                 x2 = t2$x, y2 = t2$y)
+  return(dout)
+}
+
+
+
+plot_trial <- function(id, trls, as, d) {
+  trl_id <- trls[id,]
+  
+  trl <- filter(d, 
+                observer == trl_id$observer, 
+                condition == trl_id$condition, 
+                trial == trl_id$trial)
+  
+  mistakes <- filter(as, 
+                      observer == trl_id$observer, 
+                      condition == trl_id$condition, 
+                      trial == trl_id$trial) %>% 
+    filter(selected_max == 0)
+  
+  mistakes_xy <- map_df(1:nrow(mistakes), mistake_x_y, trl, mistakes)
+  
+  p <- ggplot(trl, aes(x, y)) +
+    geom_segment(data = mistakes_xy, size = 1,
+                 aes(x = x1, y = y1, xend = x2, yend = y2), colour = "darkred",
+                 arrow = arrow(length = unit(0.2, "inches"))) + 
+    geom_text_repel(aes(label = found)) + 
+    geom_path(colour = "darkgrey") +
+    geom_point(aes(colour = targ_type, shape = targ_type), size = 4) +
+    theme_void() + theme(legend.position = "none") + 
+    coord_fixed() + 
+    ggtitle(paste0("model accuracy = ", round(trl_id$prop_max, 2))) 
+  
+  return(p)
+ 
+ 
+}
+    

### 2022-04-13 Analysis/index.Rmd
a few minor edits

@@
 ```{r, echo = TRUE}
-qs <- quantile(a_trl$prop_max, c(0.05, 0.95))
+qs <- quantile(a_trl$prop_max, c(0.05, 0.40, 0.60, 0.95))
 
 trls_hard <- filter(a_trl, prop_max < qs[1]) %>% sample_n(3)
-trls_easy <- filter(a_trl, prop_max > qs[2]) %>% sample_n(3)
+trls_mid  <- filter(a_trl, prop_max > qs[2], prop_max < qs[3]) %>% sample_n(3)
+trls_easy <- filter(a_trl, prop_max > qs[4]) %>% sample_n(3)
 
 # 
-source("plot_trial.R")
+source("functions/plot_trial.R")
+```
 
+```{r fig.cap = "A random selection of *good* trials."}
 plts <- map(1:3, plot_trial, trls_easy, a, d)
 
-#plts[1] + plts[2] + plts[3]
+plts[[1]] + plts[[2]] 
+```
 
-plot(plot_trial(1, trls_hard, a, d))
+Here are some typical trials:
 
+```{r fig.cap = "A random selection of *typical* trials."}
+plts <- map(1:3, plot_trial, trls_mid, a, d)
+
+plts[[1]] + plts[[2]] 
 ```
+
+Now let's look at less predictable trials:
+
+```{r fig.cap = "A random selection of *hard* trials."}
+plts <- map(1:3, plot_trial, trls_hard, a, d)
+
+plts[[1]] + plts[[2]] + plts[[3]]
+```
+
+# Initial Selection
+
+## QJEP Dataset
+
+```{r}
+d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
+  filter(found == 1) %>%
+  mutate(condition = as_factor(condition))
+
+ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
+  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
+  facet_wrap(~observer)
+
+d %>% group_by(observer, condition) %>% 
+  summarise(x = median(x), y = median(y)) %>%
+  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
+  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
+
+plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
+plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
+plt_x + plt_y
+```
+
+## Tagu dataset
+
+```{r}
+d <- read_csv("data/tagu_2020_prox_mouse.csv", show_col_types = FALSE) %>%
+  filter(found == 1) %>%
+  mutate(condition = as_factor(condition))
+
+ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
+  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
+  facet_wrap(~observer)
+
+d %>% group_by(observer, condition) %>% 
+  summarise(x = median(x), y = median(y)) %>%
+  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) #+
+#coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
+
+plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
+plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
+plt_x + plt_y
+```

### 2022-04-14 Analysis/index.Rmd
minor edits

@@
 
-Let's plot some examples oh highly predictable (top 5%), and unpredictable (bottom 5%) trials.
+Let's plot some examples oh highly predictable (top 5%), typical (middle 10%) and unpredictable (bottom 5%) trials.
 
@@
 
+We can see that for these highly predictable trials, we make very few mistakes, and those that we do make appear to be related to some sort of shortest-path optimization on the part of the participant.
+
 ```{r fig.cap = "A random selection of *good* trials."}
@@
 
-Here are some typical trials:
+Here are some typical trials. Possible we have the path-length minimisation issue again.
 
@@
 
-plts[[1]] + plts[[2]] + plts[[3]]
+plts[[1]] + plts[[2]] 
 ```

### 2022-04-14 Analysis/functions/plot_trial.R
messing about with arrows

@@ -29,12 +29,12 @@ plot_trial <- function(id, trls, as, d) {
   mistakes_xy <- map_df(1:nrow(mistakes), mistake_x_y, trl, mistakes)
   
   p <- ggplot(trl, aes(x, y)) +
-    geom_segment(data = mistakes_xy, size = 1,
-                 aes(x = x1, y = y1, xend = x2, yend = y2), colour = "darkred",
-                 arrow = arrow(length = unit(0.2, "inches"))) + 
     geom_text_repel(aes(label = found)) + 
     geom_path(colour = "darkgrey") +
     geom_point(aes(colour = targ_type, shape = targ_type), size = 4) +
+    geom_segment(data = mistakes_xy, size = 1,
+                 aes(x = x1, y = y1, xend = x2, yend = y2), colour = "darkred",
+                 arrow = arrow(length = unit(0.1, "inches"))) + 
     theme_void() + theme(legend.position = "none") + 
     coord_fixed() + 
     ggtitle(paste0("model accuracy = ", round(trl_id$prop_max, 2))) 

### 2022-04-14 Analysis/index.Rmd
messing about with arrows
some minor typos (all the important stuff)

@@
 We will start by looking at the visual foraging data from Clarke et al (2022), QJEP.
-As the current version of our model only takes the $p_A$ bias into account for the initial taret selection, we will ignore these data points for now.
+As the current version of our model only takes the $p_A$ bias into account for the initial target selection, we will ignore these data points for now.
 
@@
 (*right*) The proportion of trials the item with the largest assigned weight as selected by the participant.
-Each dot shows data from an individual particpant in a condition and the shaded region indicates the invertal in which we expect 67% of participants to fall."}
+Each dot shows data from an individual particpant in a condition and the shaded region indicates the interval in which we expect 67% of participants to fall."}
 
@@
 We can also repeat this calculate for all other items during/in a trial - is our model accurate/calibrated in cases when 
-the participant did not select the item withe highest model weight?
+the participant did not select the item with the highest model weight?
 
@@
 
-plts[[1]] + plts[[2]] 
+plts[[1]] + plts[[2]] +
+  plot_layout(nrow = 1, widths = c(1,1)) &
+   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
+   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8"))
 ```

### 2022-04-14 Analysis/index.Rmd
Added a note on path lengths

--- 2022-04-14 Analysis/index.Rmd
@@
 
-plts[[1]] + plts[[2]] 
+plts[[1]] + plts[[2]] +
+  plot_layout(nrow = 1, widths = c(1,1)) &
+   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
+   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8"))
 ```
+
+# Shortest Path Analysis
+
+It looks like some of the target selections that our model fails to capture are when participants select a further away target in order to mimimise overall path length.
+Here we will compare our model's predicted path length against the empirical paths.
 

### 2022-04-14 Analysis/index.Rmd
a little tidy up

--- 2022-04-14 Analysis/index.Rmd
@@
 
-# item weights pre-computed - see xxxxx.R
+# item weights pre-computed - see scripts/extract_item_weights_using_model.R
 a <- readRDS("scratch/qjep_model_weights.rda") %>%
@@
 
+# Shortest Path Analysis
+
+It looks like some of the target selections that our model fails to capture are when participants select a further away target in order to mimimise overall path length.
+Here we will compare our model's predicted path length against the empirical paths.
+
 # Initial Selection

### 2022-04-14 Analysis/scripts/extract_item_weights_using_model.R

@@ -1,0 +1,29 @@
+library(tidyverse)
+library(rstan)
+library(tidybayes)
+
+
+# this function takes a dataset and fitted model, then steps through the data 
+# and computes the weights assigned to each item by the model
+
+source("../functions/get_model_params.R")
+source("../functions/compute_weights.R")
+
+# read in data
+d <- read_csv("../data/clarke_2020_qjep.csv") %>%
+  mutate(condition = as_factor(condition),
+         condition = fct_recode(condition, feature = "1", conjunction = "2"))
+
+# read in model and extract weights
+fit <- get_model_params("../scratch/all_qjep_2020.rds") %>% rename(observer = "obs")
+saveRDS(fit, "../scratch/qjep_model_fit.rda")
+
+# run for all participants...
+a_feat <- map_dfr(unique(d$observer), comp_trials, cond = "feature")
+a_conj <- map_dfr(unique(d$observer), comp_trials, cond = "conjunction")
+a <- bind_rows(a_feat, a_conj)
+rm(a_feat, a_conj)
+
+saveRDS(a, "../scratch/qjep_model_weights.rda")
+
+

### 2022-04-14 Analysis/index.Rmd
more anal

@@
 
-```{r, fig.cap = "Accuracy of our model varies with the strength of an individual's proximity bias."}
+```{r, fig.cap = "Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
 # computed in xxxx.R
 fit <- readRDS("scratch/qjep_model_fit.rda") %>%
-  full_join(a_acc, by = c("observer", "condition"))
+  full_join(a_acc, by = c("observer", "condition")) %>%
+  mutate(is_outlier = if_else(observer %in% c(35, 45), TRUE, FALSE))
 
-ggplot(fit, aes(bP, accuracy, colour = condition)) + 
-  geom_point() +
-  geom_smooth(method = "lm", formula = y ~ x, se = FALSE)
+fit_plt <- pivot_longer(fit, c(pA, pS, bP, bM), 
+                     names_to = "parameter", values_to = "value")
+
+ggplot(fit_plt, aes(value, accuracy, colour = condition)) + 
+  geom_point(aes(shape = is_outlier)) +
+  geom_smooth(data = filter(fit_plt, is_outlier == 0), method = "lm", formula = y ~ x, se = FALSE) + 
+  scale_shape_manual(values = c(19, 4), guide = "none") + 
+  facet_wrap(~parameter, scales = "free") +
+  theme(legend.position = "bottom")
 ```
-Furthermore, this appears to account for most of the difference between the *feature* and *conjunction* conditions.
+As the two outlier participants appear to be doing something different, not captured especially well by our model, we will remove them from the rest of this analysis.
+
+After removing them, we can see that individual differences in proximity tuning account for nearly all of the differences in predictability from person to person, and also between the *feature* and *conjunction* conditions.
 
 ```{r, echo = TRUE}
-summary(lm(accuracy ~ condition * bP, fit))
+summary(lm(accuracy ~ condition * bP, 
+           data = filter(fit, is_outlier == 0)))
+
+summary(lm(accuracy ~ bP + pS + bM + bP, 
+           data = filter(fit, is_outlier == 0)))
+
 ```
+
 ### Examples of Trials
@@
 ```{r, echo = TRUE}
-a %>% group_by(observer, condition, trial) %>% 
+a %>% filter(!(observer %in% c(35, 45))) %>%
+  group_by(observer, condition, trial) %>% 
   summarise(prop_max = mean(selected_max), .groups = "drop") %>% 
@@
 
-```{r fig.cap = "A random selection of *good* trials."}
+```{r fig.cap = "A random selection of *good* trials. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation."}
 plts <- map(1:3, plot_trial, trls_easy, a, d)
@@
 
-Here are some typical trials. Possible we have the path-length minimisation issue again.
+Here are some typical trials. Possible we have the path-length minimization issue again.
 
-```{r fig.cap = "A random selection of *typical* trials."}
+```{r fig.cap = "A random selection of *typical* trials. Along with path-minimising behaviour, we can also see some disagreement around switching item type."}
 plts <- map(1:3, plot_trial, trls_mid, a, d)
@@
 
-Now let's look at less predictable trials:
+Now let's look at less predictable (bottom 5%-tile) trials. Even here, the model does a relatively good job.
 
-```{r fig.cap = "A random selection of *hard* trials."}
+```{r fig.cap = "A random selection of *hard* trials. It is harder to make out much of a pattern here, but we can see that the human participants jump around more."}
 plts <- map(1:3, plot_trial, trls_hard, a, d)

### 2022-04-14 Analysis/functions/compute_weights.R

@@ -1,3 +1,13 @@
+
+compute_weights_trials <- function(obs, cond) {
+  params <- filter(fit,  observer == obs, condition == cond )
+  a <- map_dfr(1:20, compute_weights, params = params, cond = cond, obs = obs)
+  a <- map_dfr(1:20, compute_weights, params = params, cond = cond, obs = obs)
+  return(a)
+}
+
+
+
 compute_weights <- function(trl, params, cond, obs)
 {
   
@@ -19,6 +29,8 @@ compute_weights <- function(trl, params, cond, obs)
     d_trl$b = NaN # weight of target next selected by participant
     d_trl$selected_max = NaN # did the participant select the most likely target?
     d_trl$max_b = NaN # weight of most likely target
+    d_trl$max_b2 = NaN # weight of 2nd most likely target
+    d_trl$max_b3 = NaN # weight of 3rd most likely target
     d_trl$model_pref = NaN # item ID for the most likely target
     
     # step through each target selection....
@@ -69,9 +81,12 @@ compute_weights <- function(trl, params, cond, obs)
         
    
       # finally compute some stats about the item weights
+      d_remain <- d_remain %>% arrange(desc(b))
       d_trl$b[t] <- d_remain$b[which(d_remain$found==t)]
       d_trl$selected_max[t] <- d_trl$b[t] == max(d_remain$b)
-      d_trl$max_b[t] <-  max(d_remain$b)
+      d_trl$max_b[t] <-  d_remain$b[1]
+      d_trl$max_b2[t] <- d_remain$b[2]
+      d_trl$max_b3[t] <- d_remain$b[3]
       d_trl$model_pref[t] <- d_remain$found[which(d_remain$b == max(d_remain$b) )]
       
     }

### 2022-04-14 Analysis/scripts/extract_item_weights_using_model.R

@@ -18,9 +18,12 @@ d <- read_csv("../data/clarke_2020_qjep.csv") %>%
 fit <- get_model_params("../scratch/all_qjep_2020.rds") %>% rename(observer = "obs")
 saveRDS(fit, "../scratch/qjep_model_fit.rda")
 
+
+
+
 # run for all participants...
-a_feat <- map_dfr(unique(d$observer), comp_trials, cond = "feature")
-a_conj <- map_dfr(unique(d$observer), comp_trials, cond = "conjunction")
+a_feat <- map_dfr(unique(d$observer), compute_weights_trials, cond = "feature")
+a_conj <- map_dfr(unique(d$observer), compute_weights_trials, cond = "conjunction")
 a <- bind_rows(a_feat, a_conj)
 rm(a_feat, a_conj)
 

### 2022-04-14 Analysis/index.Rmd
some mini tidying

@@
   scale_x_continuous("largest item weight") +
-  scale_y_continuous("proportion of times selected") + 
-  coord_fixed()
+  scale_y_continuous("proportion of times selected") #+ 
+  #coord_fixed()
 ```
@@
    theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
-   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8"))
+   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
+   theme(text=element_text(size=14,  family="serif"))
 ```

### 2022-04-14 Analysis/index.Rmd
2nd and 3rd place candidates

@@
 ```{r, echo = TRUE}
-n_breaks = 25
+my_breaks = seq(0.0, 1, 0.05)
 
-a %>% mutate(b_bin = cut(max_b, breaks = n_breaks, labels = FALSE)) %>%
+a %>% mutate(b_bin = cut(max_b, breaks = my_breaks, labels = FALSE)) %>%
   group_by(condition, b_bin) %>% 
   summarise(acc = mean(selected_max), .groups = "drop") %>%
-  mutate(b_bin = as.numeric(b_bin)/n_breaks) -> a_cut
+  mutate(b_bin = as.numeric(b_bin)/(length(my_breaks)-1)) -> a_cut
 ```
@@
 
-We can also repeat this calculate for all other items during/in a trial - is our model accurate/calibrated in cases when 
-the participant did not select the item with the highest model weight?
+We can also repeat this calculate for the 2nd and 3rd ranked candidate items.
+
+```{r fig.cap = "This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model."}
+a %>% select(max_b2, max_b3, selected_max2, selected_max3) %>%
+  unite(`2`, max_b2, selected_max2) %>%
+  unite(`3`, max_b3, selected_max3) %>%
+  pivot_longer(c(`2`, `3`), names_to = "rank", values_to = "b") %>%
+  separate(b, into = c("b", "selected"), sep = "_", convert = TRUE) %>%
+  mutate(b_bin = cut(b, breaks = my_breaks, labels = FALSE)) %>%
+  group_by(b_bin) %>% 
+  summarise(acc = mean(selected), .groups = "drop") %>%
+   mutate(b_bin = as.numeric(b_bin)/(length(my_breaks)-1)) %>%
+  filter(is.finite(acc)) %>%
+  ggplot(aes(b_bin, acc)) + 
+  geom_point() + 
+  geom_line(stat = "smooth", method = "loess", 
+            formula = y ~ x, alpha = 0.65, size = 2, se = F) +
+  geom_abline(linetype = 2) +
+  scale_x_continuous("runner up item weights") +
+  scale_y_continuous("proportion of times selected") + 
+  coord_fixed()
+```
 
@@
 ```
+
+## Item Density

### 2022-04-14 Analysis/functions/compute_weights.R

@@ -30,7 +30,9 @@ compute_weights <- function(trl, params, cond, obs)
     d_trl$selected_max = NaN # did the participant select the most likely target?
     d_trl$max_b = NaN # weight of most likely target
     d_trl$max_b2 = NaN # weight of 2nd most likely target
+    d_trl$selected_max2 = NaN # did the participant select the most likely target?
     d_trl$max_b3 = NaN # weight of 3rd most likely target
+    d_trl$selected_max3 = NaN # did the participant select the most likely target?
     d_trl$model_pref = NaN # item ID for the most likely target
     
     # step through each target selection....
@@ -86,7 +88,9 @@ compute_weights <- function(trl, params, cond, obs)
       d_trl$selected_max[t] <- d_trl$b[t] == max(d_remain$b)
       d_trl$max_b[t] <-  d_remain$b[1]
       d_trl$max_b2[t] <- d_remain$b[2]
+      d_trl$selected_max2[t] <- d_trl$b[t] == d_trl$max_b2[t]
       d_trl$max_b3[t] <- d_remain$b[3]
+      d_trl$selected_max3[t] <- d_trl$b[t] == d_trl$max_b3[t]
       d_trl$model_pref[t] <- d_remain$found[which(d_remain$b == max(d_remain$b) )]
       
     }

### 2022-04-14 Analysis/scripts/extract_item_weights_using_model.R

@@ -2,7 +2,6 @@ library(tidyverse)
 library(rstan)
 library(tidybayes)
 
-
 # this function takes a dataset and fitted model, then steps through the data 
 # and computes the weights assigned to each item by the model
 
@@ -12,14 +11,12 @@ source("../functions/compute_weights.R")
 # read in data
 d <- read_csv("../data/clarke_2020_qjep.csv") %>%
   mutate(condition = as_factor(condition),
-         condition = fct_recode(condition, feature = "1", conjunction = "2"))
+         condition = fct_recode(condition, feature = "1", conjunction = "2"),
+         targ_type = as.numeric(targ_type))
 
 # read in model and extract weights
 fit <- get_model_params("../scratch/all_qjep_2020.rds") %>% rename(observer = "obs")
 saveRDS(fit, "../scratch/qjep_model_fit.rda")
-
-
-
 
 # run for all participants...
 a_feat <- map_dfr(unique(d$observer), compute_weights_trials, cond = "feature")
@@ -28,5 +25,3 @@ a <- bind_rows(a_feat, a_conj)
 rm(a_feat, a_conj)
 
 saveRDS(a, "../scratch/qjep_model_weights.rda")
-
-

### 2022-04-14 Analysis/scripts/trial_level_predictions.R

@@ -1,92 +1,0 @@
-library(tidyverse)
-library(rstan)
-library(tidybayes)
-library(patchwork)
-library(ggrepel)
-
-source("functions/get_model_params.R")
-source("functions/compute_weights.R")
-
-
-
-# read in data
-d <- read_csv("data/clarke_2020_qjep.csv") %>%
-  mutate(condition = as_factor(condition),
-         condition = fct_recode(condition, feature = "1", conjunction = "2"))
-
-# read in model and extract weights
-fit <- get_model_params("scratch/all_qjep_2020.rds") %>% rename(observer = "obs")
-saveRDS(fit, "scratch/qjep_model_fit.rda")
-
-# run for all participants...
-a_feat <- map_dfr(unique(d$observer), comp_trials, cond = "feature")
-a_conj <- map_dfr(unique(d$observer), comp_trials, cond = "conjunction")
-a <- bind_rows(a_feat, a_conj)
-rm(a_feat, a_conj)
-
-saveRDS(a, "scratch/qjep_model_weights.rda")
-a <- readRDS("scratch/qjep_model_weights.rda")
-
-
-
-a %>% group_by(condition, observer, found) %>%
-  summarise(meanb = mean(b),
-            prop_best = mean(selected_max)) %>%
-  filter(found > 1) %>%
-  mutate(chance = 1/(41-found))-> a_agg
-
-# plot target selected weights
-ggplot(a_agg, aes(x = found, y = meanb, colour = condition, fill = condition)) + 
-  geom_jitter(data = filter(a_agg, found<40), width = 0.1, height = 0, alpha = 0.2) + 
-  stat_lineribbon(.width = 0.67, alpha = 0.50) +
-  geom_path(data = filter(a_agg, observer == 1, condition == "feature"), 
-                          aes(y = chance), linetype = 2, colour = "black") + 
-  geom_point(data = tibble(x=40, y=1), aes(x, y), size = 1.5, colour = "black", fill = "grey") + 
-  scale_x_continuous(breaks = c(2, 10, 20, 40), "target selection", expand = c(0.01, 0.01)) + 
-  scale_y_continuous("average weight from model", expand = c(0.01, 0.01)) -> plt_b
-
-ggplot(a_agg, aes(x = found, y = prop_best, colour = condition, fill = condition)) + 
[…]

### 2022-04-14 Analysis/scripts/compute_empirical_paths.R
Working on path length stuff

@@ -1,0 +1,25 @@
+
+library(tidyverse)
+
+
+d <- read_csv("../data/clarke_2020_qjep.csv") %>%
+  mutate(condition = as_factor(condition),
+         condition = fct_recode(condition, feature = "1", conjunction = "2"),
+         targ_type = as.numeric(targ_type))
+
+
+calc_trl_path <- function(obs, trl, cond) {
+  dtrl <- filter(d, observer == obs, trial == trl, condition == cond) %>%
+    mutate(x0 = lag(x),
+           y0 = lag(y),
+           d = sqrt((x - x0)^2 + (y - y0)^2)) %>%
+    select(observer, condition, trial,x, x0, d)
+  
+  path_length = sum(dtrl$d, na.rm = TRUE)
+  return(path_length)
+}
+
+trial_list <- filter(d, found == 1) %>%
+  select(obs = "observer", trl = "trial", cond = "condition")
+
+paths <- pmap_df(trial_list, calc_trl_path)

### 2022-04-14 Analysis/scripts/compute_shortest_path.R

@@ -1,0 +1,16 @@
+library(igraph)
+library(tidyverse)
+
+
+d <- read_csv("../data/clarke_2020_qjep.csv") %>%
+  mutate(condition = as_factor(condition),
+         condition = fct_recode(condition, feature = "1", conjunction = "2"),
+         targ_type = as.numeric(targ_type))
+
+
+obs = 1
+trl = 1
+cond= 1
+
+
+dtrl <- filter(d, observer == obs, trial == trl, condiition == cond)

### 2022-04-19 Analysis/index.Rmd
figure update
minor
work on path length

@@
 # some more colours
-#Isfahan2 = list(c("#d7aca1", "#ddc000", "#79ad41", "#34b6c6", "#4063a3"), c(4, 2, 3, 5, 1), colo
+col3 = c("#d7aca1", "#ddc000","#34b6c6",  "#79ad41", "#4063a3")
 
@@
 
-If anything, our model is a little conservative: items are selected around 5% more often than we'd expect.
-
-```{r, echo = TRUE}
-mean(a_cut$acc - a_cut$b_bin)
-```
-
 ```{r}
@@
 
-<TODO>
+Here we can see that these candidate items are typically underweight.
 
@@
 
-# Shortest Path Analysis
+# Path Length Analysis
 
@@
 Here we will compare our model's predicted path length against the empirical paths.
+
+- We will provide the model/simulation with the initial target selection.
+
+```{r, fig.cap = "(*left*) Histogram comparing the empirical path lengths to simulations from our fitted model.
+Difference indicates the human path length - the simulated path length.
+(*right*) Histogram comparing the median path lengths per participant."}
+path_lengths <- readRDS("scratch/path_lengths.rda") %>%
+  rename(observer = "obs",
+         condition = "cond",
+         human = "human_path_length",
+         model = "model_path_length") %>% 
+  mutate(difference  = human - model) %>%
+  pivot_longer(c(human, model, difference), names_to = "type", values_to = "path_length")
+
+ggplot(path_lengths, aes(path_length, fill = type)) + 
+  geom_histogram(bins = 25, alpha = 0.5, position = "identity") +
+  geom_vline(xintercept = 0, linetype = 2) + 
+  theme(legend.position = "bottom")  +
+  scale_x_continuous("path length")  +
+  scale_x_continuous("median path length") +
+  scale_fill_manual(values = col3) -> plt1
+
+path_lengths %>% group_by(observer, type) %>%
+  summarise(path_length = median(path_length), .groups = "drop") %>%
+  ggplot(aes(path_length, fill = type)) + 
+  geom_histogram(bins = 25, alpha = 0.5, position = "identity") +
+  geom_vline(xintercept = 0, linetype = 2) + 
+  theme(legend.position = "bottom") +
+  scale_x_continuous("median path length") +
+  scale_fill_manual(values = col3) -> plt2
+
+plt1 + plt2 + plot_layout(guides = "collect")  &
+  theme(legend.position = 'bottom', legend.title = element_blank())
+```
+
+We can see that overall, the model is not making substantially longer paths through the items than our human participants.
+However, there is some variability in that some participants routinely select paths shorter than our model would, and others do not.
+
+Perhaps this is related to predictability (i.e., how well the model can predict a participant's trial level behaviour)?
+
+```{r fig.cap = "(*left*) A histogram showing the proportion of trials each participant managed a shorter path through the targets than the model's prediction.
+(*right*) Scatter plot showing the relationship between predictability (accuracy) and whether the model over or under estimates path length.
+Xs mark the outlier participants discussed above."}
+path_lengths %>% filter(type == "difference") %>%
+  mutate(shorter = path_length < 0) %>%
+  group_by(observer, condition) %>%
+  summarise(prop_shorter = mean(shorter), .groups = "drop") -> path_lengths_obs
+
+path_lengths_obs %>%
+  ggplot(aes(prop_shorter, fill = condition)) + 
+  geom_histogram(alpha = 0.5, breaks = seq(0, 1, 0.2), position = "identity") +
+  scale_x_continuous("prop. shorter than model", breaks = seq(0, 1, 0.2)) -> plt1
+
+path_lengths <- full_join(path_lengths_obs, fit,
+                          by = c("observer", "condition"))
+
+ggplot(path_lengths, aes(accuracy, prop_shorter, colour = condition)) + 
+  geom_point(aes(shape = is_outlier)) +
+  geom_smooth(data = filter(path_lengths, is_outlier == 0), 
+              method = "lm", formula = y ~ x, se = FALSE) + 
+  scale_shape_manual(values = c(19, 4), guide = "none") + 
+  scale_y_continuous("prop. shorter than model", breaks = seq(0, 1, 0.2)) +
+  coord_cartesian(ylim = c(0, 1)) -> plt2
+
+plt1 + plt2 + plot_layout(guides = "collect")  &
+  theme(legend.position = 'bottom')
+
+```
+
+```{r}
+
+```
 

### 2022-04-19 Analysis/functions/compute_weights.R

@@ -98,3 +98,4 @@ compute_weights <- function(trl, params, cond, obs)
   
   return(d_trl)
 }
+

### 2022-04-19 Analysis/functions/sim_foraging_bag.R

@@ -1,163 +1,0 @@
-library(tidyverse)
-
-############################################
-# Functions for data generation
-############################################
-simulate_observer <- function(ob_id = 1, observer_sig = 0.1) {
-  
-  # generate random weights
-  obs_w_pref <- boot::inv.logit(boot::logit(prob_a) + rnorm(1, 0, observer_sig))
-  obs_w_stay <- boot::inv.logit(boot::logit(prob_s) + rnorm(1, 0, observer_sig))
-  
-  
-  d_ob <- map_df(1:n_conditions, 
-                 simulate_data, 
-                 n_trials = n_trials, n_targ = n_targ, prob_a =  obs_w_pref, prob_s =  obs_w_stay ) %>%
-    mutate(
-      observer = ob_id,
-      condition = as.factor(condition), 
-      obs_a = obs_w_pref[condition],
-      obs_s = obs_w_stay[condition])
-  
-  return(d_ob)
-  
-}
-
-
-simulate_data <- function(cc = 1, n_trials = 100, n_targ = 50, n_found =  NA, prob_a = 0.5, prob_s = 0.5, p_quit = 0.00) {
-  
-  # generate n_trials worth of data, all with the same parameters
-  # include some basic run length statistics in the output
-  
-  if (is.na(n_found)) {
-    n_found = n_targ
-  }
-  
-  d <- map_df(1:n_trials, gen_foraging_seq, 
-              ps = prob_s[cc], pa = prob_a[cc], n_tot = n_targ, n_found = n_found, p_q = p_quit) %>% 
-    pivot_wider(names_from = "pick", values_from = "found") 
-  
-  ## add run-length and number-of-run stats
-  d <- cbind(d, map_df(1:n_trials, get_run_info, d))
-  
-  d$condition = as.integer(cc)
-  d$prob_a = prob_a[cc]
-  d$prob_s = prob_s[cc]
-  d$nA = as.integer(ceiling(n_targ/2))
-  d$nB = as.integer(n_targ - d$nA)
-  
-  d <- select(d, condition, trial, nA, nB, prob_a, prob_s, n_found, max_run_length, all_run_lengths, n_runs, starts_with("t"))
-  
-  return(d)
-}
-
-gen_foraging_seq <- function(t = 1, ps = 0.5, pa = 0.5, p_q = 0, n_tot = 40, n_found = NA) {
-  
[…]

### 2022-04-19 Analysis/functions/sim_foraging_momentum.R

@@ -27,7 +27,7 @@ sim_momentum_post <- function(df_params, n_trials = 10, n = 40)
   return(d)
   
 }
-  
+
 get_runs <- function(d) {
   
   dout <- tibble()
@@ -74,7 +74,7 @@ sim_momentum_trials <- function(n = 10, m = 10, tune_prox = 1, tune_angle = 5, b
   )
   
   #dat <- sim_spatial_trial(params)
-  dat <- map_df(1:n_trials, sim_spatial_trial, params = params) %>%
+  dat <- map_df(1:n_trials, sim_momentumtrial, params = params) %>%
     rename(targ_type = "type") %>% 
     mutate(observer = 1, condition = 1) %>%
     select(observer, condition, trial, id, targ_type, found, x, y, phi, dist)
@@ -82,35 +82,46 @@ sim_momentum_trials <- function(n = 10, m = 10, tune_prox = 1, tune_angle = 5, b
   return(dat)
 }
 
-sim_spatial_trial <- function(params, trial = 1)
+sim_momentum_trial <- function(params, trial = 1, 
+                               d_trial = NULL, init_sel = NA)
 {
   
   # n is total number of targets
   # m is the number that we want to find
-
-  d_trial <- 
-    tibble(
-      trial = trial,
-          id = 1:params$n,
-          x  = runif(params$n),
-          y = runif(params$n),
-          type = sample(rep(c(0, 1), params$n/2)),
-          found = -1,
-          dist = NA,
-          phi = NA)
   
+  # if d_trial is null, create a random trial,
+  # otherwise, use the one we have been given
+  
+  if (is.null(d_trial)) {
+    d_trial <- 
+      tibble(
+        trial = trial,
+        id = 1:params$n,
+        x  = runif(params$n),
+        y = runif(params$n),
+        type = sample(rep(c(0, 1), params$n/2)),
+        found = -1,
+        dist = NA,
+        phi = NA)
+  }
+  
+  # convert d_trial$type from {0, 1} to {-1, 1}
+  # this is just for mathematical convenience 
   d_trial$type[which(d_trial$type == 0)] <- -1
   
-  if (params$spat_config==TRUE) 
+  # the spat_config toggle will set all items on one 
+  # side of the display to -1, and all items on the 
+  # other to 1.
[…]

### 2022-04-19 Analysis/functions/sim_foraging_spatial.R

@@ -1,104 +1,0 @@
-library(tidyverse)
-
-
-sim_spatial_trials <- function(n = 10, m = 10, tune_prox = 1, b_pref = 0, b_switch = 0, n_trials = 10, spat_config = FALSE) 
-{
-  # n is number of targets present
-  # m is number of targets to find
-  
-  params <- list(
-    n = n,
-    m = m,
-    tune_prox = tune_prox,
-    b_pref = b_pref,
-    b_switch = b_switch,
-    spat_config = spat_config
-  )
-  
-  dat <- map_df(1:n_trials, sim_spatial_trial, params = params)
-  
-  return(dat)
-}
-
-sim_spatial_trial <- function(params, trial = 1)
-{
-  
-  # n is total number of targets
-  # m is the number that we want to find
-
-  d_trial <- tibble(
-    trial = trial,
-    id = 1:params$n,
-    x  = runif(params$n),
-    y = runif(params$n),
-    type = rbinom(params$n, 1, 0.5),
-    found = -1,
-    dist = NA)
-  
-  if (params$spat_config==TRUE) 
-  {
-    
-    d_trial %>% mutate(
-      type = if_else(x < 0.5, 0, 1)
-    ) -> d_trial
-    
-  }
-  
-  #d_trial <- mutate(d_trial, type = if_else(type ==0, -1, 1))
-  
-  # compute proximity info
-  delta <- as.matrix(dist(select(d_trial, x, y), upper = TRUE, diag = TRUE))
-  delta <- as_tibble(delta) 
-  names(delta) = paste("dt", 1:params$n, sep = "_")
-  d_trial <- bind_cols(d_trial, delta)
-  
-  #### TODO
-  # use the precompute prox info in the simulation below
-  
-  d_remain <- d_trial %>% 
-    mutate(
-      dist = 0,
-      prox = 0,
-      b = boot::inv.logit(params$b_pref * type),
-      b = b/sum(b))
-  
-  # pick a first point at random
-  d_found <- sample_n(d_remain, 1, weight = b) %>%
-    mutate(t = 1)
-  
-  # remove this point from the stimuli
-  d_remain <- filter(d_remain, id != d_found$id)
-  d_trial$found[d_found$id[1]] <- 1
-  
- # varname <- paste("dt",d_found$id[1], sep = "_" )
- # d_trial[which(d_trial$found == -1),][varname] = 999
-  
-  for (t in 2:params$m) {
-    
[…]

### 2022-04-19 Analysis/scripts/compute_empirical_paths.R

@@ -1,5 +1,5 @@
-
 library(tidyverse)
+source("../functions/sim_foraging_momentum.R")
 
 
 d <- read_csv("../data/clarke_2020_qjep.csv") %>%
@@ -7,19 +7,74 @@ d <- read_csv("../data/clarke_2020_qjep.csv") %>%
          condition = fct_recode(condition, feature = "1", conjunction = "2"),
          targ_type = as.numeric(targ_type))
 
+fit <- readRDS("../scratch/qjep_model_fit.rda")
 
 calc_trl_path <- function(obs, trl, cond) {
-  dtrl <- filter(d, observer == obs, trial == trl, condition == cond) %>%
+  
+  # function to compute path length for a trial
+  # trial is specified with obs(erver), trial and condition
+  dtrl <- filter(d, 
+                 observer == obs, trial == trl, condition == cond)  %>%
     mutate(x0 = lag(x),
            y0 = lag(y),
            d = sqrt((x - x0)^2 + (y - y0)^2)) %>%
-    select(observer, condition, trial,x, x0, d)
+    select(observer, condition, trial, id, targ_type,  x, y, d)
   
-  path_length = sum(dtrl$d, na.rm = TRUE)
+ 
+  
+  # also compute the model's path length 
+  # (allow it to start at the same item)
+  
+  d_trial = select(dtrl, trial, id, type = "targ_type", x,y) %>%
+    mutate(found = -1, dist = NA, phi = NA )
+  
+  params = filter(fit, 
+                  observer ==obs,
+                  condition == cond) %>%
+    mutate(spat_config = FALSE) %>%
+    mutate(b_pref = boot::logit(pA),
+           b_switch = boot::logit(pS),
+           tune_prox = bP,
+           tune_angle = bM,
+           m = nrow(d_trial))
+  
+  sim_trial <- sim_momentum_trial(params, trial = trl, d_trial = d_trial,
+                     init_sel = dtrl$id[1]) %>%
+    arrange(found) %>%
+    select(trial, x, y, found) %>% 
+    mutate(x0 = lag(x),
+           y0 = lag(y),
+           d = sqrt((x - x0)^2 + (y - y0)^2))
+  
+  path_length = tibble(human = sum(dtrl$d, na.rm = TRUE),
+                       simul = sum(sim_trial$d, na.rm = TRUE))
+ 
   return(path_length)
 }
 
 trial_list <- filter(d, found == 1) %>%
[…]

### 2022-04-19 Analysis/scripts/compute_shortest_path.R

@@ -1,16 +1,0 @@
-library(igraph)
-library(tidyverse)
-
-
-d <- read_csv("../data/clarke_2020_qjep.csv") %>%
-  mutate(condition = as_factor(condition),
-         condition = fct_recode(condition, feature = "1", conjunction = "2"),
-         targ_type = as.numeric(targ_type))
-
-
-obs = 1
-trl = 1
-cond= 1
-
-
-dtrl <- filter(d, observer == obs, trial == trl, condiition == cond)

### 2022-04-19 Analysis/index.Rmd
tidying up figure heights a little

@@
 
-```{r, fig.cap = "Calibration plot for our foraging model.
-The *x*-axis gives the largest weight assigned by the model while the *y*-axis shows how often that target was actually selected by a human participant."}
+We can also repeat this calculate for the 2nd and 3rd ranked candidate items.
+
+```{r, fig.height=3.5, fig.cap = "(*left*) Calibration plot for our foraging model.
+The *x*-axis gives the largest weight assigned by the model while the *y*-axis shows how often that target was actually selected by a human participant.
+(*right*) This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model."}
 
@@
   scale_x_continuous("largest item weight") +
-  scale_y_continuous("proportion of times selected") #+ 
-  #coord_fixed()
-```
+  scale_y_continuous("proportion of times selected") +
+  theme(legend.position = "bottom") -> plt1
 
-```{r}
-rm(a_cut)
-```
-
-We can also repeat this calculate for the 2nd and 3rd ranked candidate items.
-
-```{r fig.cap = "This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model."}
 a %>% select(max_b2, max_b3, selected_max2, selected_max3) %>%
@@
   scale_x_continuous("runner up item weights") +
-  scale_y_continuous("proportion of times selected") + 
-  coord_fixed()
+  scale_y_continuous("proportion of times selected") -> plt2
+
+plt1 + plt2
+
+```
+
+```{r}
+rm(a_cut)
 ```
@@
 
-```{r, fig.cap = "Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. (The dots indicate outliers.)", echo= TRUE}
+```{r, fig.height=3.5, fig.cap = "Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. (The dots indicate outliers.)", echo= TRUE}
 
@@
 
-```{r, fig.cap = "Histogram of how predictiable indivuidual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
+```{r fig.height=3.5, fig.cap = "Histogram of how predictiable indivuidual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
 ggplot(a_trl, aes(prop_max)) + 
@@
 
-```{r, fig.cap = "(*left*) Histogram comparing the empirical path lengths to simulations from our fitted model.
+```{r, fig.height=3.5, fig.cap = "(*left*) Histogram comparing the empirical path lengths to simulations from our fitted model.
 Difference indicates the human path length - the simulated path length.
@@
 
-```{r fig.cap = "(*left*) A histogram showing the proportion of trials each participant managed a shorter path through the targets than the model's prediction.
+```{r fig.height=3, fig.cap = "(*left*) A histogram showing the proportion of trials each participant managed a shorter path through the targets than the model's prediction.
 (*right*) Scatter plot showing the relationship between predictability (accuracy) and whether the model over or under estimates path length.

### 2022-04-19 Analysis/index.Rmd
a new colour and some typos

@@
 # some more colours
-col3 = c("#d7aca1", "#ddc000","#34b6c6",  "#79ad41", "#4063a3")
+col3 = c("#d04e00", "#ddc000","#34b6c6",  "#79ad41", "#4063a3")
 
@@
 ```{r, fig.cap = "(*left*) The average weight assigned to each selected target by our model.
-(*right*) The proportion of trials the item with the largest assigned weight as selected by the participant.
+(*right*) The proportion of trials the item with the largest assigned weight was selected by the participant.
 Each dot shows data from an individual particpant in a condition and the shaded region indicates the interval in which we expect 67% of participants to fall."}
@@
 
-Is our model calibrated? By this we mean, if our model assigns an item a probability $p$ of being selected next, then is it actually be selected (by the human participant) this often?
+Is our model calibrated? By this we mean, if our model assigns an item a probability $p$ of being selected next, then is it actually selected (by the human participant) this often?
 
@@
 
-We can see from the Figure below that our model is well-calibrated, (at least in terms of the target with the highest assigned weight).
+We can see from the Figure below that our model is well-calibrated (at least in terms of the target with the highest assigned weight).
 
-We can also repeat this calculate for the 2nd and 3rd ranked candidate items.
+We can also repeat this calculation for the 2nd and 3rd ranked candidate items.
 
@@
 
-```{r fig.height=3.5, fig.cap = "Histogram of how predictiable indivuidual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
+```{r fig.height=3.5, fig.cap = "Histogram of how predictiable individual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
 ggplot(a_trl, aes(prop_max)) + 
@@
 
-It looks like some of the target selections that our model fails to capture are when participants select a further away target in order to mimimise overall path length.
+It looks like some of the target selections that our model fails to capture are when participants select a further away target in order to minimise overall path length.
 Here we will compare our model's predicted path length against the empirical paths.

### 2022-04-19 manuscript.tex
Updates from Overleaf

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\setcounter{section}{-1} %% Remove this when starting to work on the template.
-\section{How to Use this Template}
-
-The template details the sections that can be used in a manuscript.
-Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section).
-Please check the instructions on the authors' page of the journal to verify the correct order and names.
-For any questions, please contact the editorial office of the journal or support@mdpi.com.
-For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References).
-Only journal Laws uses \footnote.
 
@@
 \section{Introduction}
+
+Foraging, the act of searching for and gathering multiple targets (such as food), has been studied in both non-human animal contexts
 
@@
 As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
-Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
+
+Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %=====================================
-%\bibliography{your_external_BibTeX_file}
+\bibliography{literature.bib}
 
@@
 
-% If authors have biography, please use the format below
-%\section*{Short Biography of Authors}
-%\bio
-%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
-%{\textbf{Firstname Lastname} Biography of first author}
-%
-%\bio
-%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
-%{\textbf{Firstname Lastname} Biography of second author}
-
-% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
-% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
-% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
-328; \citeyear{ref-journal-3b}, p.475).
-This produces: Wong (1999, p.
-328; 2000, p.
-475)
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-04-19 Analysis/index.Rmd
adding hex maps

@@
 
+ggplot(d, aes(x, y)) + geom_hex(bins = 12) +
+  scale_fill_viridis_c() -> plt_all
+
 d %>% group_by(observer, condition) %>% 
-  summarise(x = median(x), y = median(y)) %>%
-  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
-  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
+  summarise(x = median(x), y = median(y),
+            .groups = "drop") %>%
+  ggplot(aes(x, y)) + geom_hex(bins = 12) +
+  scale_fill_viridis_c() -> plt_med
+
+plt_all 
+plt_med
 

### 2022-04-19 Analysis/index.Rmd
removing old plots

--- 2022-04-19 Analysis/index.Rmd
@@
 
-ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
-  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
-  facet_wrap(~observer)
+ggplot(d, aes(x, y)) + geom_hex(bins = 12) +
+  scale_fill_viridis_c()
+```
+
+```{r fig.cap="Distirbution of median intial selection."}
 
 d %>% group_by(observer, condition) %>% 
-  summarise(x = median(x), y = median(y)) %>%
-  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
-  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
+  summarise(x = median(x), y = median(y),
+            .groups = "drop") %>%
+  ggplot(aes(x, y)) + geom_hex(bins = 12) +
+  scale_fill_viridis_c()
 
-plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
-plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
-plt_x + plt_y
 ```
@@
 
-ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
-  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
-  facet_wrap(~observer)
-
-d %>% group_by(observer, condition) %>% 
-  summarise(x = median(x), y = median(y)) %>%
-  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) #+
-#coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
-
-plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
-plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
-plt_x + plt_y
 ```

### 2022-04-19 Analysis/index.Rmd
hexes

--- 2022-04-19 Analysis/index.Rmd
@@
 
+ggplot(d, aes(x, y)) + geom_hex(aes(colour = ..count..), bins = 12) +
+  scale_fill_viridis_c() + scale_color_viridis_c() +
+  theme(axis.line=element_blank(),axis.text.x=element_blank(),
+          axis.text.y=element_blank(),axis.ticks=element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank(),legend.position="none",
+          panel.background=element_rect(color  = "#808080", size = 2,linetype = 'dotted', fill ="#808080"),
+        panel.border= element_rect(colour = "black", fill=NA, size=5),
+        panel.grid.major=element_blank(),
+        panel.grid.minor=element_blank()) -> plt_all
+
 d %>% group_by(observer, condition) %>% 
-  summarise(x = median(x), y = median(y)) %>%
-  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
-  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
+  summarise(x = median(x), y = median(y),
+            .groups = "drop") %>%
+  ggplot(aes(x, y)) + geom_hex(bins = 12) +
+  scale_fill_viridis_c()+ scale_color_viridis_c() +
+  theme(axis.line=element_blank(),axis.text.x=element_blank(),
+          axis.text.y=element_blank(),axis.ticks=element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank(),legend.position="none",
+          panel.background=element_rect(color  = "#808080", size = 2,linetype = 'dotted', fill ="#808080"),
+        panel.border= element_rect(colour = "black", fill=NA, size=5),
+        panel.grid.major=element_blank(),
+        panel.grid.minor=element_blank()) -> plt_med
+
+plt_all 
+plt_med
 

### 2022-04-20 Analysis/index.Rmd
some small edits

--- 2022-04-19 Analysis/index.Rmd
@@
 # participant was judged the most likely to be selected by our model.
-
 a %>% group_by(condition, observer, found) %>%
@@
 ```{r, echo = TRUE}
-my_breaks = seq(0.0, 1, 0.05)
+my_breaks <- seq(0.0, 1, 0.05)
 
@@
 We can see from the Figure below that our model is well-calibrated (at least in terms of the target with the highest assigned weight).
-
-We can also repeat this calculation for the 2nd and 3rd ranked candidate items.
+If we repeat this calculation for the 2nd and 3rd ranked candidate items we can see that we slightly underweight these items, but we are still pretty accurate.
 
@@
 plt1 + plt2
-
 ```
@@
 ```{r}
-rm(a_cut)
+rm(a_cut, my_breaks, plt1, plt2)
 ```
-
-Here we can see that these candidate items are typically underweight.
 
@@
 ```{r, echo = TRUE}
+dm <- filter(fit, is_outlier == 0)
+
 summary(lm(accuracy ~ condition * bP, 
-           data = filter(fit, is_outlier == 0)))
+           data = dm))
 
 summary(lm(accuracy ~ bP + pS + bM + bP, 
-           data = filter(fit, is_outlier == 0)))
+           data = dm))
 
+rm(dm)
 ```
@@
 trls_easy <- filter(a_trl, prop_max > qs[4]) %>% sample_n(3)
-
-# 
-source("functions/plot_trial.R")
 ```
@@
 ```{r fig.cap = "A random selection of *good* trials. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation."}
+
+source("functions/plot_trial.R")
 plts <- map(1:3, plot_trial, trls_easy, a, d)
@@
    theme(text=element_text(size=14,  family="serif"))
+```
+
+```{r}
+rm(trls_easy, trls_mid, trls_hard, plts, qs)
 ```
@@
   theme(legend.position = 'bottom')
-
 ```
@@
 ```{r}
-
+rm(path_lengths, plt1, plt2)
 ```
@@
 
-```{r}
+```{r echo = TRUE}
+# Reimport data again (as we removed the inital target selection earlier)
 d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
@@
   mutate(condition = as_factor(condition))
-
-ggplot(d, aes(x, y)) + geom_hex(bins = 12) +
-  scale_fill_viridis_c()
 ```
 
-```{r fig.cap="Distirbution of median intial selection."}
+```{r fig.height = 3.5, fig.cap="(*left*) Density plot for initial target selections, over all participants and all trials.
+(*right*) Median $x$ and $y$ coordinates for the initial target selection for each participant."}
+my_theme <- theme(axis.line=element_blank(),axis.text.x=element_blank(),
+          axis.text.y=element_blank(),axis.ticks=element_blank(),
+          axis.title.x=element_blank(),
+          axis.title.y=element_blank(),legend.position="none",
+          panel.background=element_rect(color  = "#808080", size = 2,linetype = 'dotted', fill ="#808080"),
+        panel.border= element_rect(colour = "black", fill=NA, size=5),
+        panel.grid.major=element_blank(),
+        panel.grid.minor=element_blank())
+
+ggplot(d, aes(x, y)) + geom_hex(aes(colour = ..count..), bins = 12) +
+  scale_fill_viridis_c() + scale_color_viridis_c() +
+  my_theme -> plt_all
 
@@
   ggplot(aes(x, y)) + geom_hex(bins = 12) +
-  scale_fill_viridis_c()
+  scale_fill_viridis_c()+ scale_color_viridis_c() +
+  my_theme -> plt_med
 
+plt_all + plt_med
+
+rm(plt_all, plt_med)
 ```
+
+We can model this as a mixture of Gaussians.
 
@@
 
+ggplot(d, aes(x, y)) + geom_hex(aes(colour = ..count..), bins = 12) +
+  scale_fill_viridis_c() + scale_color_viridis_c() +
+  my_theme -> plt_all
+
+d %>% group_by(observer, condition) %>% 
+  summarise(x = median(x), y = median(y),
+            .groups = "drop") %>%
+  ggplot(aes(x, y)) + geom_hex(bins = 12) +
+  scale_fill_viridis_c()+ scale_color_viridis_c() +
+  my_theme -> plt_med
+
+plt_all + plt_med 
 ```

### 2022-04-20 Analysis/index.Rmd
init sel

@@
 library(ggrepel)
+library(truncnorm)
 ```
@@
 
-We can model this as a mixture of Gaussians.
+We can model this as multi-level Gaussian?
+
+```{r fig.cap=3.5}
+
+m <- readRDS("scratch/init_sel_model.rds")
+z <- seq(0, 1, 0.01)
+
+gather_draws(m, u[dim, observer]) %>% 
+  ungroup() %>%
+  select(-.variable) %>%
+  rename(obs_b = ".value") %>%
+  full_join(gather_draws(m, b[dim])) %>%
+  mutate(obs_b = .value + obs_b,
+         .variable = if_else(dim %in% c(1,2), "mu", "sd"),
+         dim = if_else(dim %in% c(1,3), "x", "y")) %>%
+  select(observer, dim, .iteration, obs_b, param = ".variable") %>%
+  mutate(obs_b = if_else(param == "sd", exp(obs_b), obs_b)) -> a
+
+ggplot(a, aes(obs_b, group = observer)) + 
+  geom_density(alpha = 0.25) +
+  facet_grid(param ~ dim, scales = "free")
+
+a %>% group_by(observer, param, dim) %>%
+  summarise(value = mean(obs_b) , .groups = "drop") %>%
+  pivot_wider(names_from = param, values_from = value) %>%
+  rename(mean = "mu") -> am
+
+obs_fits_x <- pmap_dfc(filter(am,  dim == "x") %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
+  mutate(z = z) %>%
+  pivot_longer(-z, names_to = "observer", values_to = "v") %>%
+  ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
+  scale_x_continuous("x")
+
+obs_fits_y <- pmap_dfc(filter(am,  dim == "y") %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
+  mutate(z = z) %>%
+  pivot_longer(-z, names_to = "observer", values_to = "v") %>%
+  ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
+  scale_x_continuous("y") + 
+  coord_flip()
+
+obs_fits_x + obs_fits_y
+
+```
 

### 2022-04-20 Analysis/index.Rmd
init sel model fits

@@
     number_sections: true
+    fig_height: 4 
 ---
@@
   ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
-  scale_x_continuous("x")
+  scale_x_continuous("x") + scale_y_continuous("likelihood")
 
@@
   ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
-  scale_x_continuous("y") + 
-  coord_flip()
+  scale_x_continuous("y") + scale_y_continuous("likelihood")
 

### 2022-04-20 Analysis/index.Rmd
removing Tagoooo

--- 2022-04-20 Analysis/index.Rmd
@@
 ```
-
-## Clarke et al (2022)
 
@@
 
-### Calibration
+## Calibration
 
@@
 
-### Examples of Trials
+## Examples of Trials
 
@@
 
-## QJEP Dataset
+Previous work (cite Clarke and Tatler etc) has demonstrated that the initial fixation in scene viewing can be well described with truncated Gaussian distribution.
+Here we explore using a similar idea to account for starting locations.
 
 ```{r echo = TRUE}
-# Reimport data again (as we removed the inital target selection earlier)
+# Reimport data again (as we removed the initial target selection earlier)
 d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
@@
 
-We can model this as a mixture of Gaussians.
+We can model this as multi-level Gaussian? Yes, although it seems like people are in one of two clusters.
 
-## Tagu dataset
+```{r fig.cap = "The mean posterior plot for the truncated normal distriubtions for (*left*) $x$ and (*right*) $y$.
+We can see that a two component mixture model will capture most of the variance in intial target selection."}
 
-```{r}
-d <- read_csv("data/tagu_2020_prox_mouse.csv", show_col_types = FALSE) %>%
-  filter(found == 1) %>%
-  mutate(condition = as_factor(condition))
+m <- readRDS("scratch/init_sel_model.rds")
+z <- seq(0, 1, 0.01)
 
-ggplot(d, aes(x, y)) + geom_hex(aes(colour = ..count..), bins = 12) +
-  scale_fill_viridis_c() + scale_color_viridis_c() +
-  my_theme -> plt_all
+gather_draws(m, u[dim, observer]) %>% 
+  ungroup() %>%
+  select(-.variable) %>%
+  rename(obs_b = ".value") %>%
+  full_join(gather_draws(m, b[dim]),
+             by = c("dim", ".chain", ".iteration", ".draw")) %>%
+  mutate(obs_b = .value + obs_b,
+         .variable = if_else(dim %in% c(1,2), "mu", "sd"),
+         dim = if_else(dim %in% c(1,3), "x", "y")) %>%
+  select(observer, dim, .iteration, obs_b, param = ".variable") %>%
+  mutate(obs_b = if_else(param == "sd", exp(obs_b), obs_b)) -> a
 
-d %>% group_by(observer, condition) %>% 
-  summarise(x = median(x), y = median(y),
-            .groups = "drop") %>%
-  ggplot(aes(x, y)) + geom_hex(bins = 12) +
-  scale_fill_viridis_c()+ scale_color_viridis_c() +
-  my_theme -> plt_med
+a %>% group_by(observer, param, dim) %>%
+  summarise(value = mean(obs_b) , .groups = "drop") %>%
+  pivot_wider(names_from = param, values_from = value) %>%
+  rename(mean = "mu") -> am
 
-plt_all + plt_med 
+create_post_plot <- function(dm) {
+
+  pmap(filter(am,  dim == dm) %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
+    set_names(rownames(filter(am,  dim == dm))) %>%
+    bind_rows() %>%
+    mutate(z = z) %>%
+    pivot_longer(-z, names_to = "observer", values_to = "v") %>%
+    ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
+    scale_x_continuous(dm) + scale_y_continuous("likelihood") -> plt
+
+  return(plt)
+}
+
+create_post_plot("x") + create_post_plot("y")
 ```
 
-## Item Density
+Do we want to simplify this model to something in which people have some mix of a (fixed) centre and corner bias?
+
+# Item Density

### 2022-04-20 Analysis/scripts/testing_init_selection.R
blip

@@ -1,9 +1,10 @@
 library(tidyverse)
 library(rstan)
 library(tidybayes)
+library(truncnorm)
 
 options(digits = 2, mc.cores = 10)
-d <- read_csv("data/clarke_2020_qjep.csv") %>%
+d <- read_csv("../data/clarke_2020_qjep.csv") %>%
   filter(found == 1)
 
 
@@ -13,7 +14,7 @@ stan_data <- list(N = nrow(d),
                   x = d$x,
                   y = d$y)
 
-m <- stan("models/initial_selection_models/init_sel.stan",
+m <- stan("../models/initial_selection_models/init_sel.stan",
                 data = stan_data,
                 chains = 4,
                 iter = 1000,
@@ -21,24 +22,42 @@ m <- stan("models/initial_selection_models/init_sel.stan",
 
 
 
-saveRDS(m, "scratch/init_sel_model.rds")
+saveRDS(m, "../scratch/init_sel_model.rds")
+
+m <- readRDS("../scratch/init_sel_model.rds")
 
 gather_draws(m, u[dim, observer]) %>% 
   ungroup() %>%
   select(-.variable) %>%
-  rename(obs_mu = ".value") %>%
-  full_join(gather_draws(m, mu[dim])) %>%
-  mutate(obs_mu = .value + obs_mu) -> a 
+  rename(obs_b = ".value") %>%
+  full_join(gather_draws(m, b[dim])) %>%
+  mutate(obs_b = .value + obs_b,
+         .variable = if_else(dim %in% c(1,2), "mu", "sd"),
+         dim = if_else(dim %in% c(1,3), "x", "y")) %>%
+  select(observer, dim, .iteration, obs_b, param = ".variable") %>%
+  mutate(obs_b = if_else(param == "sd", exp(obs_b), obs_b)) -> a 
+
+ggplot(a, aes(obs_b, group = observer)) + 
+  geom_density(alpha = 0.25) +
+  facet_grid(param ~ dim, scales = "free")
+ 
+a %>% group_by(observer, param, dim) %>%
+  summarise(value = mean(obs_b) , .groups = "drop") %>%
+  pivot_wider(names_from = param, values_from = value) %>%
+  rename(mean = "mu") -> am
+
+obs_fits_x <- pmap_dfc(filter(am,  dim == "x") %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
[…]

### 2022-04-21 manuscript.tex

@@
 
-%--------------------
-% Class Options:
-%--------------------
-%----------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
-
-%---------
-% article
-%---------
-% The default type of manuscript is "article", but can be replaced by: 
-% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
-% supfile = supplementary materials
-
 %----------
@@
 Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
-
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
 
@@
 
-% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
-%\PACS{J0101}
-%\MSC{}
-%\JEL{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Diversity
-%\LSID{\url{http://}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Applied Sciences:
-%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Data:
-%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
-If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
-In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
-
-%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Toxins
-%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Encyclopedia
-%\encyclopediadef{Instead of the abstract}
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
@@
 
-Foraging, the act of searching for and gathering multiple targets (such as food), has been studied in both non-human animal contexts
+Foraging, the act of searching for and gathering multiple targets (such as food), has been studied in both non-human animal contexts \cite{dawkins1971} and in human psychology studies \cite{kristjansson2014}.
+In many cases, the pattern of foraging behaviour has been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run.
+However, we have recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022foraging}.
+By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully re-analyse data from a number of open access datasets \cite{kristjansson2014, thornton2020, clarke2018, tagu2020}.
 
-The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
+While our model is able to do a good job of allowing us to understand biases at the level of a trial (e.g.
+conjunction vs.
+feature search differences \cite{kristjansson2014} or the influence of high value targets compared to low value targets \cite{tagu2020}), we did not originally investigate to what extent our model was able to predict target-by-target behaviour in any given trial.
+However, as the model is based on target-by-target level information, it is possible for us to use this information to ask: to what extent does our model predict foraging behaviour within a trial?
+Can it predict exactly which target a participant will pick next?
+And if the model makes mistakes, can we understand where it is failing, in order to improve our understanding of how human foraging behaviour operates?
 
-Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% Please provide either the correct journal abbreviation (e.g.
-according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
-% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
-
 %=====================================
@@
 
-%=====================================
-% References, variant B: internal bibliography
-%=====================================
-\begin{thebibliography}{999}
-% Reference 1
-\bibitem[Author1(year)]{ref-journal}
-Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
-% Reference 2
-\bibitem[Author2(year)]{ref-book1}
-Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-% Reference 3
-\bibitem[Author3(year)]{ref-book2}
-Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
-% Reference 4
-\bibitem[Author4(year)]{ref-unpublish}
-Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
-% Reference 5
-\bibitem[Author5(year)]{ref-communication}
-Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
-% Reference 6
-\bibitem[Author6(year)]{ref-proceeding}
-Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
-Title of presentation.
-In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
-% Reference 7
-\bibitem[Author7(year)]{ref-thesis}
-Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
-% Reference 8
-\bibitem[Author8(year)]{ref-url}
-Title of Site. Available online: URL (accessed on Day Month Year).
-\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% for journal Sci
-%\reviewreports{\\
-%Reviewer 1 comments and authors’ response\\
-%Reviewer 2 comments and authors’ response\\
-%Reviewer 3 comments and authors’ response
-%}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{adjustwidth}

### 2022-04-21 Analysis/index.Rmd
Init target sel comparison

@@
 
-Do we want to simplify this model to something in which people have some mix of a (fixed) centre and corner bias?
+- Do we want to simplify this model to something in which people have some mix of a (fixed) centre and corner bias?
+
+Do participants who differ in terms of their initial target selection differ in other ways too?
+
+```{r echo = TRUE, fig.cap = "Whether participants have a central or corner bias for the intiial target selection appears to be largely independent of their other model parameters."}
+full_join(fit, filter(am, dim == "x"), by = "observer") %>%
+  pivot_longer(c(pA, pS, bP, bM, accuracy), 
+               names_to = "statistic", values_to = "value") %>%
+  mutate(intial_sel = if_else(mean < 0, "corner", "central")) %>%
+  ggplot(aes(statistic, value, fill = intial_sel)) +
+  geom_boxplot(alpha = 0.5) + 
+  facet_wrap(~statistic, scales = "free", nrow = 1) +
+  theme(legend.position = "bottom") + 
+   scale_fill_manual("intial target selection",
+                     values = c(col3[2], col3[3]))
+```
 

### 2022-04-21 Analysis/scripts/testing_init_selection.R

@@ -61,3 +61,12 @@ obs_fits_y <- pmap_dfc(filter(am,  dim == "y") %>% select(mean, sd), dtruncnorm,
 
 obs_fits_x + obs_fits_y
 
+
+
+m <- stan("../models/initial_selection_models/init_sel2.stan",
+          data = stan_data,
+          chains = 4,
+          iter = 1000,
+          refresh = 100)
+
+

### 2022-04-22 Analysis/index.Rmd
minor edits to rmd formatting

@@
   tufte::tufte_html:
-    toc: TRUE
     number_sections: true
     fig_height: 4
+    bibliography: literature.bib
+    link-citations: yes  
 ---
@@
 
-We will start by looking at the visual foraging data from Clarke et al (2022), QJEP.
+We will use the visual foraging data from @clarke2022 to assess the model's trial level performance.
 As the current version of our model only takes the $p_A$ bias into account for the initial target selection, we will ignore these data points for now.
@@
          targ_type = as_factor(targ_type))
+```
 
+We will use the model fit as detailed in @clarke2020compbio.
+For simplicity sake, we will characterise all of our estimated posterior probability densities with just the mean value.
+This gives us four parameters per participant: $b_S, b_A, b_P, b_D$.
+
+Using these fitted values, we can now step through each target selection in the dataset and computer the probability weights our model assigns to each remaining target.
+For each target selection, we record:
+
+- the item assigned the highest weight by our model.
+- whether this item was then selected by the human participant.
+
+```{r echo = TRUE}
 # item weights pre-computed - see scripts/extract_item_weights_using_model.R
@@
 ```
+
+We can then plot this data to show how our ability to predict which target will be selected next varies throughout a trial.
+We can see a difference between *feature* and *conjunction* foraging, with *feature* foraging being more predictable.
 
@@
 ```
-
-From this figure we can see a few interesting things to note:
-
-- large individual differences in how well our model can capture and predict behaviour
-- feature search is more predictable than conjunction search
-- our model appears to be overly conservative
 
@@
 
-```{r, fig.cap = "Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
+```{r fig.height = 6, fig.cap = "Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
 # computed in xxxx.R
@@
 ```
+
 As the two outlier participants appear to be doing something different, not captured especially well by our model, we will remove them from the rest of this analysis.
@@
            data = dm))
+```
 
-summary(lm(accuracy ~ bP + pS + bM + bP, 
+We can see that the difference in the proximity parameter between conditions appears to account for most of the variables in our model's accuracy from one participant to the next.
+
+We can also see if the other parameters have an effect.
+
+```{r echo=TRUE}
+summary(lm(accuracy ~ pA + pS + bM + bP, 
            data = dm))
+```
 
+Both $p_A$ and $b_M$ also have an effect on our model's accuracy, but note there is only a small increases in $R^2$ from just using $b_P$.
+
+```{r}
 rm(dm)
@@
 
-Let's score every trial by how well the model captures behaviour, and then plot some different examples
+Let's score every trial by how well the model captures behaviour, and then plot some different examples.
 
@@
 ggplot(a_trl, aes(prop_max)) + 
-  geom_histogram(fill = "#34b6c6", breaks = seq(0, 1, 0.025)) +
+  geom_histogram(fill = "#d04e00", breaks = seq(0, 1, 0.025), alpha = 0.5) +
   scale_x_continuous("trial predictability")
@@
 Difference indicates the human path length - the simulated path length.
-(*right*) Histogram comparing the median path lengths per participant."}
+(*right*) Histogram comparing the median path lengths per participant.", message=FALSE}
 path_lengths <- readRDS("scratch/path_lengths.rda") %>%

### 2022-04-25 Analysis/index.Rmd
post weights figure

@@
 
+ggsave("../Figures/qjep_preds.png", width = 8, height = 4)
+
 ggplot(a_agg, aes(x = found, y = prop_best, colour = condition, fill = condition)) + 
@@
         legend.direction = 'horizontal')
-ggsave("../Figures/qjep_preds.png", width = 9, height = 4)
+
 ```

### 2022-04-25 manuscript.tex
Updates from Overleaf

@@
 
-Briefly overview model and datasets using.
+\subsection{Datasets}
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+We will use two previously published datasets to explore how well our model can account for trial-level behaviour.
+We will start with the visual foraging data from \cite{clarke2022qjep}.
+This is an attractive dataset for our needs as it is very close to the ``classic'' visual foraging paradigm \citep{kristjansson2014}, yet with a substantially larger sample of participants.
+(The key difference between paradigms is that \cite{kristjansson2014} used an ipad and finger foraging, while \cite{clarke2022qjep} used a desktop computer and mouse clicks).
+Furthermore, we have already demonstrated that our model can capture individual differences in foraging behaviour \citep{clarke2022foraging}.
+As such, we will only give a brief overview of the data here and refer the reader to these earlier papers for a more details.
 
-Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
+To test how well our methods generalise, we will introduce a new dataset that was not analysed in our previous modelling paper.
+This \cite{prpic2019} data comes from a study in which participants played a simple computer game in which they controlled a squirrel hunting for acorns.
+The game makes us a 3D virtual world and player are provided with a 1st person (2nd??) view.
+This differs from the top down displays typically used in other visual foraging studies and so makes a good test of generalisability.
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
-\begin{quote}
-This is an example of a quote.
-\end{quote}
+\subsubsection{Clarke et al 2022}
+
+\subsubsection{Ppric et al}
+
+\subsection{A Model for Visual Foraging}
+
+We will make use of the foraging model from \cite{clarke2022foraging}.
+This treats foraging as a sampling without replacement process in which each item $i$ has probability $p_i$ of being selected as the next target.
+The $p_i$ depend on four parameters:
+
+\begin{itemize}
+    \item $b_A$ - preference for selecting items of type $A$ rather than $B$.
+    \item $b_S$ - preference for selections items of the same type as the previously selected item.
+    \item $\sigma_d$ - preference for selecting items close to the previously selected item.
+    \item $\sigma_{\theta}$ - preference to keep selecting items along a straight line versus changing direction.
+\end{itemize}
+
+These combine to give:
+
+\begin{equation}
+    w_i = g\left(b_at_i + b_sm(t_i, t_{i-1})\right) \times \rho_d(i, i-1) \rho_{\theta}(i, i-1)
+\end{equation}
+
+where $t_i = 1$ if item $i$ is of class $A$ and 0 otherwise, $m(t_i, t_{i-1}) =1$ if item $i$ is the same class as the previously selected item.
+$\rho_d$ and $\rho_{\theta}$ measures proximity and the effect of direction:
+
+\begin{equation}
+    \rho_d = e^{-\sigma_dd(i,j)}
+\end{equation}
+\begin{equation}
+    \rho_{\theta} = e^{-\sigma_d\theta(i,j)}
+\end{equation}
+
+$d(i,j)$ is simply the Euclidean distance between items $i$ and $j$, while $\theta$ is defined as:
+\begin{equation}
+    \theta(i,j) = \frac{f(\text{atan2}(i, j) - \text{atan2}(i-1, i))}{\pi}
+\end{equation}
+
+with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$.
+This model is implemented in a multi-level framework, allowing each of the four parameters to vary from participant to participant.
+Further details including priors and full code can be found with \cite{clarke2022foraging}.
+
+Note: while our model returns estimates of full posterior probability distribution for each parameter, to reduce computational complexity and make it easier to compare to the empirical data, we will work with the means of these distributions for our parameter values.
+
+\subsection{Software environment}
+
+ We used R, Stan, tidyverse version etc.
 
@@
 \section{Results}
-
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
 
@@
 
+To assess how well our model can account for behaviour at the level of individual trials, we start by stepping through each trial in the data from \cite{clarke2022qjep}.
+For each target selection, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model.
+
+\begin{figure}[H]
+\includegraphics[width=12 cm]{Figures/qjep_preds.png}
+\caption{This is a figure.
+Schemes follow the same formatting.
+If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
+(\textbf{b}) Description of what is contained in the second panel.
+Figures should be placed in the main text near to the first time they are cited.
+A caption on a single line should be centered.\label{fig1}}
+\end{figure}
+
 \subsection{Improvement: Adaptive distance? Absolute direction?}
-
-\subsubsection{Subsubsection}
-
-Bulleted lists look like this:
-\begin{itemize}
-\item	First bullet;
-\item	Second bullet;
-\item	Third bullet.
-\end{itemize}
-
-Numbered lists can be added as follows:
-\begin{enumerate}
-\item	First item; 
-\item	Second item;
-\item	Third item.
-\end{enumerate}
 
@@
 
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{Figures/qjep_preds.png}
-\caption{This is a figure.
-Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.\label{fig1}}
-\end{figure}   
 \unskip

### 2022-04-25 manuscript.tex
adding methods section

@@
 \begin{figure}[H]
+\centering
 \includegraphics[width=12 cm]{Figures/qjep_preds.png}
-\caption{This is a figure.
-Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.\label{fig1}}
+\caption{Posterior probabilities for target selections during a visual foraging task. Each dot represents...}
 \end{figure}

### 2022-05-03 Analysis/index.Rmd
editing figure

@@
 (*right*) The proportion of trials the item with the largest assigned weight was selected by the participant.
-Each dot shows data from an individual particpant in a condition and the shaded region indicates the interval in which we expect 67% of participants to fall."}
+Each dot shows data from an individual participant in a condition and the shaded region indicates the interval in which we expect 67% of participants to fall."}
 
@@
   scale_y_continuous("average weight from model", expand = c(0.01, 0.01)) -> plt_b
-
-ggsave("../Figures/qjep_preds.png", width = 8, height = 4)
 
@@
         legend.direction = 'horizontal')
+
+rm(plt_c)
 
@@
 
-ggplot(a_cut, aes(b_bin, acc, colour = condition, shape = condition)) + 
+ggplot(a_cut, aes(b_bin, acc, colour = condition, fill = condition, shape = condition)) + 
   geom_point() + 
@@
  plt1 + plt2
+
+ggsave("../Figures/qjep_preds.png", 
+       plt_b + plt1 + plt2 + plot_layout(guides = "collect") & theme(legend.position = "bottom"),
+       width = 10, height = 4)
+
 ```

### 2022-05-03 Analysis/index.Rmd
graph

@@
 ggsave("../Figures/qjep_preds.png", 
-       plt_b + plt1 + plt2 + plot_layout(guides = "collect") & theme(legend.position = "bottom"),
+       plt_b + plt1 + plt2 + 
+         plot_layout(guides = "collect") & theme(legend.position = "bottom"),
        width = 10, height = 4)
 
+rm(plt1, plt2, plt_a)
 ```
@@
   scale_y_continuous("model accuracy",  
-                     limits = c(0.3, 0.8), breaks = seq(0.3, 0.8, 0.1))
+                     limits = c(0.3, 0.8), breaks = seq(0.3, 0.8, 0.1)) -> plt_a
+
+plt_a
 ```
@@
   theme(legend.position = "bottom")
+
+plt_b <- ggplot(filter(fit_plt, parameter == "bP"), 
+                aes(value, accuracy, colour = condition)) + 
+  geom_point(aes(shape = is_outlier)) +
+  geom_smooth(data = filter(fit_plt, is_outlier == 0, parameter == "bP"), method = "lm", formula = y ~ x, se = FALSE) + 
+  scale_shape_manual(values = c(19, 4), guide = "none") + 
+  theme(legend.position = "bottom")
+
+ggsave("../Figures/qjep_indiv_diff.png", 
+       plt_a + plt_b + 
+         plot_layout(guides = "collect") & theme(legend.position = "bottom"), width = 8, height = 4)
 ```

### 2022-05-03 manuscript.tex
Updates from Overleaf

@@
 For each target selection, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model.
+As can be seen in Figure \ref{fig:cal}, the model is putting somewhere between 25\% and 75\% of the weight on the target that is selected next easily outperforming a chance $1/n$ baseline.
+We can also see  that the model is well calibrated in that the probabilities assigned to the largest target manage to capture how well often that target is actually selected.
+However, we can see a decrease in accuracy when it comes to how often ``runner-up`` candidate items are selected as our model appears to systematically undervalue these (presumably by putting too much of the probabilistic weight on low chance items).
 
@@
 \includegraphics[width=12 cm]{Figures/qjep_preds.png}
-\caption{Posterior probabilities for target selections during a visual foraging task. Each dot represents...}
+\caption{(\textit{left}) Posterior probabilities for target selections during a visual foraging task.
+Each dot shows the  data from an individual participant, averaged over trials, in a condition and the shaded region indicates the interval in which we expect 67\% of participants to fall.
+The dashed line indicates chance performance.
+(\textit{centre})  Calibration plot for our foraging model.
+The *x*-axis gives the largest weight assigned by the model while the *y*-axis shows how often that target was actually selected by a human participant.
+(\textit{right}) This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model.}
+\label{fig:cal}
 \end{figure}
+
+Figure \ref{fig:cal} hints at some individual differences when it comes to how predictable the model is: we can see a lot of variation in the size of the weights
 

### 2022-05-04 Analysis/index.Rmd
graph edit

@@
 plt_b + plt_c + plot_layout(guides = "collect")  &
-  theme(legend.position = 'bottom',
+  theme(legend.position = 'right',
         legend.direction = 'horizontal')
@@
   scale_y_continuous("model accuracy",  
-                     limits = c(0.3, 0.8), breaks = seq(0.3, 0.8, 0.1)) -> plt_a
+                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1)) -> plt_a
 
@@
   scale_shape_manual(values = c(19, 4), guide = "none") + 
-  theme(legend.position = "bottom")
+  theme(legend.position = "none") + 
+   scale_y_continuous("model accuracy",  
+                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1))
 
@@
        plt_a + plt_b + 
-         plot_layout(guides = "collect") & theme(legend.position = "bottom"), width = 8, height = 4)
+         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
 ```

### 2022-05-04 Analysis/index.Rmd
scan path plot for paper

@@
 options(digits = 3)
+set.seed(2022)
 ```
@@
 plt_b + plt_c + plot_layout(guides = "collect")  &
-  theme(legend.position = 'right',
+  theme(legend.position = 'bottom',
         legend.direction = 'horizontal')
@@
 
-ggsave("../Figures/qjep_preds.png", 
+ggsave("../Figures/qjep_preds.pdf", 
        plt_b + plt1 + plt2 + 
@@
 
-ggsave("../Figures/qjep_indiv_diff.png", 
+ggsave("../Figures/qjep_indiv_diff.pdf", 
        plt_a + plt_b + 
@@
 source("functions/plot_trial.R")
-plts <- map(1:3, plot_trial, trls_easy, a, d)
+plts1 <- map(1:3, plot_trial, trls_easy, a, d)
 
-plts[[1]] + plts[[2]] +
+plts1[[1]] + plts1[[2]] +
   plot_layout(nrow = 1, widths = c(1,1)) &
@@
 ```{r fig.cap = "A random selection of *typical* trials. Along with path-minimising behaviour, we can also see some disagreement around switching item type."}
-plts <- map(1:3, plot_trial, trls_mid, a, d)
+plts2 <- map(1:3, plot_trial, trls_mid, a, d)
 
-plts[[1]] + plts[[2]] +
+plts2[[1]] + plts2[[2]] +
   plot_layout(nrow = 1, widths = c(1,1)) &
@@
 ```{r fig.cap = "A random selection of *hard* trials. It is harder to make out much of a pattern here, but we can see that the human participants jump around more."}
-plts <- map(1:3, plot_trial, trls_hard, a, d)
+plts3 <- map(1:3, plot_trial, trls_hard, a, d)
 
-plts[[1]] + plts[[2]] +
+plts3[[1]] + plts3[[2]] +
   plot_layout(nrow = 1, widths = c(1,1)) &
@@
 ```{r}
-rm(trls_easy, trls_mid, trls_hard, plts, qs)
+ggsave("../Figures/qjep_ex_paths.pdf",
+      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]]), 
+       width = 8, height = 8)
+
+rm(trls_easy, trls_mid, trls_hard, plts, qs, plts1, plts2, plts3)
 ```

### 2022-05-04 Analysis/index_prpic.Rmd
Starting work on Ppric

--- 2022-05-04 Analysis/index.Rmd
@@
 # read in data
-d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
+d <- read_csv("data/squirrel_spatial.csv", show_col_types = FALSE) %>%
   mutate(condition = as_factor(condition),
@@
 # item weights pre-computed - see scripts/extract_item_weights_using_model.R
-a <- readRDS("scratch/qjep_model_weights.rda") %>%
+a <- readRDS("scratch/prpic_model_weights.rda") %>%
   filter(found != 1) # remove initial selections
@@
 ```
-
-Let's plot some examples oh highly predictable (top 5%), typical (middle 10%) and unpredictable (bottom 5%) trials.
-
-```{r, echo = TRUE}
-qs <- quantile(a_trl$prop_max, c(0.05, 0.40, 0.60, 0.95))
-
-trls_hard <- filter(a_trl, prop_max < qs[1]) %>% sample_n(3)
-trls_mid  <- filter(a_trl, prop_max > qs[2], prop_max < qs[3]) %>% sample_n(3)
-trls_easy <- filter(a_trl, prop_max > qs[4]) %>% sample_n(3)
-```
-
-We can see that for these highly predictable trials, we make very few mistakes, and those that we do make appear to be related to some sort of shortest-path optimization on the part of the participant.
-
-```{r fig.cap = "A random selection of *good* trials. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation."}
-
-source("functions/plot_trial.R")
-plts1 <- map(1:3, plot_trial, trls_easy, a, d)
-
-plts1[[1]] + plts1[[2]] +
-  plot_layout(nrow = 1, widths = c(1,1)) &
-   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
-   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
-   theme(text=element_text(size=14,  family="serif"))
-```
-
-Here are some typical trials. Possible we have the path-length minimization issue again.
-
-```{r fig.cap = "A random selection of *typical* trials. Along with path-minimising behaviour, we can also see some disagreement around switching item type."}
-plts2 <- map(1:3, plot_trial, trls_mid, a, d)
-
-plts2[[1]] + plts2[[2]] +
-  plot_layout(nrow = 1, widths = c(1,1)) &
-   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
-   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
-   theme(text=element_text(size=14,  family="serif"))
-```
-
-Now let's look at less predictable (bottom 5%-tile) trials. Even here, the model does a relatively good job.
-
-```{r fig.cap = "A random selection of *hard* trials. It is harder to make out much of a pattern here, but we can see that the human participants jump around more."}
-plts3 <- map(1:3, plot_trial, trls_hard, a, d)
-
-plts3[[1]] + plts3[[2]] +
-  plot_layout(nrow = 1, widths = c(1,1)) &
-   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
-   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
-   theme(text=element_text(size=14,  family="serif"))
-```
-
-```{r}
-ggsave("../Figures/qjep_ex_paths.pdf",
-      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]]), 
-       width = 8, height = 8)
-
-rm(trls_easy, trls_mid, trls_hard, plts, qs, plts1, plts2, plts3)
-```
-
-# Path Length Analysis
-
-It looks like some of the target selections that our model fails to capture are when participants select a further away target in order to minimise overall path length.
-Here we will compare our model's predicted path length against the empirical paths.
-
-- We will provide the model/simulation with the initial target selection.
-
-```{r, fig.height=3.5, fig.cap = "(*left*) Histogram comparing the empirical path lengths to simulations from our fitted model.
-Difference indicates the human path length - the simulated path length.
-(*right*) Histogram comparing the median path lengths per participant.", message=FALSE}
-path_lengths <- readRDS("scratch/path_lengths.rda") %>%
-  rename(observer = "obs",
-         condition = "cond",
-         human = "human_path_length",
-         model = "model_path_length") %>% 
-  mutate(difference  = human - model) %>%
-  pivot_longer(c(human, model, difference), names_to = "type", values_to = "path_length")
-
-ggplot(path_lengths, aes(path_length, fill = type)) + 
-  geom_histogram(bins = 25, alpha = 0.5, position = "identity") +
-  geom_vline(xintercept = 0, linetype = 2) + 
-  theme(legend.position = "bottom")  +
-  scale_x_continuous("path length")  +
-  scale_x_continuous("median path length") +
-  scale_fill_manual(values = col3) -> plt1
-
-path_lengths %>% group_by(observer, type) %>%
-  summarise(path_length = median(path_length), .groups = "drop") %>%
-  ggplot(aes(path_length, fill = type)) + 
-  geom_histogram(bins = 25, alpha = 0.5, position = "identity") +
-  geom_vline(xintercept = 0, linetype = 2) + 
-  theme(legend.position = "bottom") +
-  scale_x_continuous("median path length") +
-  scale_fill_manual(values = col3) -> plt2
-
-plt1 + plt2 + plot_layout(guides = "collect")  &
-  theme(legend.position = 'bottom', legend.title = element_blank())
-```
-
-We can see that overall, the model is not making substantially longer paths through the items than our human participants.
-However, there is some variability in that some participants routinely select paths shorter than our model would, and others do not.
-
-Perhaps this is related to predictability (i.e., how well the model can predict a participant's trial level behaviour)?
-
-```{r fig.height=3, fig.cap = "(*left*) A histogram showing the proportion of trials each participant managed a shorter path through the targets than the model's prediction.
-(*right*) Scatter plot showing the relationship between predictability (accuracy) and whether the model over or under estimates path length.
-Xs mark the outlier participants discussed above."}
-path_lengths %>% filter(type == "difference") %>%
-  mutate(shorter = path_length < 0) %>%
-  group_by(observer, condition) %>%
-  summarise(prop_shorter = mean(shorter), .groups = "drop") -> path_lengths_obs
-
-path_lengths_obs %>%
-  ggplot(aes(prop_shorter, fill = condition)) + 
-  geom_histogram(alpha = 0.5, breaks = seq(0, 1, 0.2), position = "identity") +
-  scale_x_continuous("prop. shorter than model", breaks = seq(0, 1, 0.2)) -> plt1
-
-path_lengths <- full_join(path_lengths_obs, fit,
-                          by = c("observer", "condition"))
-
-ggplot(path_lengths, aes(accuracy, prop_shorter, colour = condition)) + 
-  geom_point(aes(shape = is_outlier)) +
-  geom_smooth(data = filter(path_lengths, is_outlier == 0), 
-              method = "lm", formula = y ~ x, se = FALSE) + 
-  scale_shape_manual(values = c(19, 4), guide = "none") + 
-  scale_y_continuous("prop. shorter than model", breaks = seq(0, 1, 0.2)) +
-  coord_cartesian(ylim = c(0, 1)) -> plt2
-
-plt1 + plt2 + plot_layout(guides = "collect")  &
-  theme(legend.position = 'bottom')
-```
-
-```{r}
-rm(path_lengths, plt1, plt2)
-```
-
-# Initial Selection
-
-Previous work (cite Clarke and Tatler etc) has demonstrated that the initial fixation in scene viewing can be well described with truncated Gaussian distribution.
-Here we explore using a similar idea to account for starting locations.
-
-```{r echo = TRUE}
-# Reimport data again (as we removed the initial target selection earlier)
-d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
-  filter(found == 1) %>%
-  mutate(condition = as_factor(condition))
-```
-
-```{r fig.height = 3.5, fig.cap="(*left*) Density plot for initial target selections, over all participants and all trials.
-(*right*) Median $x$ and $y$ coordinates for the initial target selection for each participant."}
-my_theme <- theme(axis.line=element_blank(),axis.text.x=element_blank(),
-          axis.text.y=element_blank(),axis.ticks=element_blank(),
-          axis.title.x=element_blank(),
-          axis.title.y=element_blank(),legend.position="none",
-          panel.background=element_rect(color  = "#808080", size = 2,linetype = 'dotted', fill ="#808080"),
-        panel.border= element_rect(colour = "black", fill=NA, size=5),
-        panel.grid.major=element_blank(),
-        panel.grid.minor=element_blank())
-
-ggplot(d, aes(x, y)) + geom_hex(aes(colour = ..count..), bins = 12) +
-  scale_fill_viridis_c() + scale_color_viridis_c() +
-  my_theme -> plt_all
-
-d %>% group_by(observer, condition) %>% 
-  summarise(x = median(x), y = median(y),
-            .groups = "drop") %>%
-  ggplot(aes(x, y)) + geom_hex(bins = 12) +
-  scale_fill_viridis_c()+ scale_color_viridis_c() +
-  my_theme -> plt_med
-
-plt_all + plt_med
-
-rm(plt_all, plt_med)
-```
-
-We can model this as multi-level Gaussian? Yes, although it seems like people are in one of two clusters.
-
-```{r fig.cap = "The mean posterior plot for the truncated normal distriubtions for (*left*) $x$ and (*right*) $y$.
-We can see that a two component mixture model will capture most of the variance in intial target selection."}
-
-m <- readRDS("scratch/init_sel_model.rds")
-z <- seq(0, 1, 0.01)
-
-gather_draws(m, u[dim, observer]) %>% 
-  ungroup() %>%
-  select(-.variable) %>%
-  rename(obs_b = ".value") %>%
-  full_join(gather_draws(m, b[dim]),
-             by = c("dim", ".chain", ".iteration", ".draw")) %>%
-  mutate(obs_b = .value + obs_b,
-         .variable = if_else(dim %in% c(1,2), "mu", "sd"),
-         dim = if_else(dim %in% c(1,3), "x", "y")) %>%
-  select(observer, dim, .iteration, obs_b, param = ".variable") %>%
-  mutate(obs_b = if_else(param == "sd", exp(obs_b), obs_b)) -> a
-
-a %>% group_by(observer, param, dim) %>%
-  summarise(value = mean(obs_b) , .groups = "drop") %>%
-  pivot_wider(names_from = param, values_from = value) %>%
-  rename(mean = "mu") -> am
-
-create_post_plot <- function(dm) {
-
-  pmap(filter(am,  dim == dm) %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
-    set_names(rownames(filter(am,  dim == dm))) %>%
-    bind_rows() %>%
-    mutate(z = z) %>%
-    pivot_longer(-z, names_to = "observer", values_to = "v") %>%
-    ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
-    scale_x_continuous(dm) + scale_y_continuous("likelihood") -> plt
-
-  return(plt)
-}
-
-create_post_plot("x") + create_post_plot("y")
-```
-
-- Do we want to simplify this model to something in which people have some mix of a (fixed) centre and corner bias?
-
-Do participants who differ in terms of their initial target selection differ in other ways too?
-
-```{r echo = TRUE, fig.cap = "Whether participants have a central or corner bias for the intiial target selection appears to be largely independent of their other model parameters."}
-full_join(fit, filter(am, dim == "x"), by = "observer") %>%
-  pivot_longer(c(pA, pS, bP, bM, accuracy), 
-               names_to = "statistic", values_to = "value") %>%
-  mutate(intial_sel = if_else(mean < 0, "corner", "central")) %>%
-  ggplot(aes(statistic, value, fill = intial_sel)) +
-  geom_boxplot(alpha = 0.5) + 
-  facet_wrap(~statistic, scales = "free", nrow = 1) +
-  theme(legend.position = "bottom") + 
-   scale_fill_manual("intial target selection",
-                     values = c(col3[2], col3[3]))
-```
-
-# Item Density

### 2022-05-04 Analysis/functions/compute_weights.R

@@ -1,9 +1,11 @@
 
-compute_weights_trials <- function(obs, cond) {
+compute_weights_trials <- function(obs, cond, n_trials = 20) {
+  
   params <- filter(fit,  observer == obs, condition == cond )
-  a <- map_dfr(1:20, compute_weights, params = params, cond = cond, obs = obs)
-  a <- map_dfr(1:20, compute_weights, params = params, cond = cond, obs = obs)
+  a <- map_dfr(1:n_trial, compute_weights, params = params, cond = cond, obs = obs)
+  
   return(a)
+  
 }
 
 
@@ -14,8 +16,9 @@ compute_weights <- function(trl, params, cond, obs)
   # function to step through empirical foraging data and compute the item weights
   # for every target selection
   
-  # select the revelant trial
+  # select the relevant trial
   d_trl <- filter(d, observer == obs, condition == cond, trial == trl)
+  n_targ <- max(d_trl$found)
   
   if (nrow(d_trl) == 0) {
     
@@ -36,7 +39,7 @@ compute_weights <- function(trl, params, cond, obs)
     d_trl$model_pref = NaN # item ID for the most likely target
     
     # step through each target selection....
-    for (t in 2:40) {
+    for (t in 2:n_targ) {
       
       # get info about the previously selected item
       prev_targ <- d_trl$targ_type[t-1]

### 2022-05-04 Analysis/scripts/extract_item_weights_using_model.R

@@ -1,27 +1,0 @@
-library(tidyverse)
-library(rstan)
-library(tidybayes)
-
-# this function takes a dataset and fitted model, then steps through the data 
-# and computes the weights assigned to each item by the model
-
-source("../functions/get_model_params.R")
-source("../functions/compute_weights.R")
-
-# read in data
-d <- read_csv("../data/clarke_2020_qjep.csv") %>%
-  mutate(condition = as_factor(condition),
-         condition = fct_recode(condition, feature = "1", conjunction = "2"),
-         targ_type = as.numeric(targ_type))
-
-# read in model and extract weights
-fit <- get_model_params("../scratch/all_qjep_2020.rds") %>% rename(observer = "obs")
-saveRDS(fit, "../scratch/qjep_model_fit.rda")
-
-# run for all participants...
-a_feat <- map_dfr(unique(d$observer), compute_weights_trials, cond = "feature")
-a_conj <- map_dfr(unique(d$observer), compute_weights_trials, cond = "conjunction")
-a <- bind_rows(a_feat, a_conj)
-rm(a_feat, a_conj)
-
-saveRDS(a, "../scratch/qjep_model_weights.rda")

### 2022-05-04 Analysis/scripts/extract_item_weights_using_model_clarke.R

@@ -1,0 +1,27 @@
+library(tidyverse)
+library(rstan)
+library(tidybayes)
+
+# this function takes a dataset and fitted model, then steps through the data 
+# and computes the weights assigned to each item by the model
+
+source("../functions/get_model_params.R")
+source("../functions/compute_weights.R")
+
+# read in data
+d <- read_csv("../data/clarke_2020_qjep.csv") %>%
+  mutate(condition = as_factor(condition),
+         condition = fct_recode(condition, feature = "1", conjunction = "2"),
+         targ_type = as.numeric(targ_type))
+
+# read in model and extract weights
+fit <- get_model_params("../scratch/all_qjep_2020.rds") %>% rename(observer = "obs")
+saveRDS(fit, "../scratch/qjep_model_fit.rda")
+
+# run for all participants...
+a_feat <- map_dfr(unique(d$observer), compute_weights_trials, cond = "feature")
+a_conj <- map_dfr(unique(d$observer), compute_weights_trials, cond = "conjunction")
+a <- bind_rows(a_feat, a_conj)
+rm(a_feat, a_conj)
+
+saveRDS(a, "../scratch/qjep_model_weights.rda")

### 2022-05-04 Analysis/scripts/extract_item_weights_using_model_prpic.R

@@ -1,0 +1,27 @@
+library(tidyverse)
+library(rstan)
+library(tidybayes)
+
+# this function takes a dataset and fitted model, then steps through the data 
+# and computes the weights assigned to each item by the model
+
+source("../functions/get_model_params.R")
+source("../functions/compute_weights.R")
+
+# read in data
+d <- read_csv("../data/squirrel_spatial.csv") %>%
+  mutate(condition = as_factor(condition),
+         condition = fct_recode(condition, feature = "1", conjunction = "2"),
+         targ_type = as.numeric(targ_type))
+
+# read in model and extract weights
+fit <- get_model_params("../scratch/squirrel.model") %>% rename(observer = "obs")
+saveRDS(fit, "../scratch/prpic_model_fit.rda")
+
+# run for all participants...
+a_feat <- map_dfr(unique(d$observer), compute_weights_trials, cond = "feature", n_trials = 5)
+a_conj <- map_dfr(unique(d$observer), compute_weights_trials, cond = "conjunction", n_trials = 5)
+a <- bind_rows(a_feat, a_conj)
+rm(a_feat, a_conj)
+
+saveRDS(a, "../scratch/prpic_model_weights.rda")

### 2022-05-04 Analysis/index.Rmd
RT v accuracy stuff for clarke2022 qjep

@@
 
+## Are more predictable people faster at the task?
+
+```{r}
+drt <- filter(d, found == 40) %>% group_by(observer, condition) %>%
+  summarise(median_rt = median(RT), .groups = "drop") %>% 
+  full_join(dm, by = c("observer", "condition"))
+
+ggplot(drt, aes(accuracy, median_rt, colour = condition)) +
+         geom_point(alpha = 0.5) + 
+  geom_smooth(method = "lm") -> plt1
+
+ggplot(drt, aes(bP, median_rt, colour = condition)) +
+         geom_point(alpha = 0.5) + 
+  geom_smooth(method = "lm") -> plt2
+
+plt1 + plt2 + plot_layout(guides = "collect")
+
+summary(lm(median_rt ~ accuracy*condition, data = drt))
+summary(lm(median_rt ~ bP*condition, data = drt))
+
+```
+
 ```{r}

### 2022-05-05 Analysis/index.Rmd
Prpic model param plot

--- 2022-05-04 Analysis/index.Rmd
@@
 
+## Are more predictable people faster at the task?
+
+```{r}
+drt <- filter(d, found == 40) %>% group_by(observer, condition) %>%
+  summarise(median_rt = median(RT), .groups = "drop") %>% 
+  full_join(dm, by = c("observer", "condition"))
+
+ggplot(drt, aes(accuracy, median_rt, colour = condition)) +
+         geom_point(alpha = 0.5) + 
+  geom_smooth(method = "lm")
+
+summary(lm(median_rt ~ accuracy*condition, data = drt))
+
+```
+
 ```{r}

### 2022-05-05 Analysis/functions/plot_spatial_model.R

@@ -163,7 +163,7 @@ plot_fixed_effects <- function(fit, cond_levels = c("feature", "conjunction"), f
    scale_x_continuous("weight", limits = c(0.4, 1), breaks = seq(0.5, 1, 0.25)) +
     geom_vline(xintercept = 0.5, linetype = 2) + 
     theme_bw() + 
-   theme(legend.position = "top") -> plt_AS
+   theme(legend.position = "right") -> plt_AS
   
   f <- filter(fit, param == "bP") 
   

### 2022-05-05 manuscript.tex
Updates from Overleaf

@@
 In many cases, the pattern of foraging behaviour has been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run.
-However, we have recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022foraging}.
-By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully re-analyse data from a number of open access datasets \cite{kristjansson2014, thornton2020, clarke2018, tagu2020}.
+However, we have recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022}.
+By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully re-analyse data from a number of open access datasets \cite{kristjansson2014, thornton2020, clarke2022, tagu2020}.
 
@@
 We will use two previously published datasets to explore how well our model can account for trial-level behaviour.
-We will start with the visual foraging data from \cite{clarke2022qjep}.
+We will start with the visual foraging data from \cite{clarke2022}.
 This is an attractive dataset for our needs as it is very close to the ``classic'' visual foraging paradigm \citep{kristjansson2014}, yet with a substantially larger sample of participants.
-(The key difference between paradigms is that \cite{kristjansson2014} used an ipad and finger foraging, while \cite{clarke2022qjep} used a desktop computer and mouse clicks).
-Furthermore, we have already demonstrated that our model can capture individual differences in foraging behaviour \citep{clarke2022foraging}.
+(The key difference between paradigms is that \cite{kristjansson2014} used an ipad and finger foraging, while \cite{clarke2022} used a desktop computer and mouse clicks).
+Furthermore, we have already demonstrated that our model can capture individual differences in foraging behaviour \citep{clarke2022}.
 As such, we will only give a brief overview of the data here and refer the reader to these earlier papers for a more details.
@@
 
-We will make use of the foraging model from \cite{clarke2022foraging}.
+We will make use of the foraging model from \cite{clarke2022}.
 This treats foraging as a sampling without replacement process in which each item $i$ has probability $p_i$ of being selected as the next target.
@@
 
-To assess how well our model can account for behaviour at the level of individual trials, we start by stepping through each trial in the data from \cite{clarke2022qjep}.
+To assess how well our model can account for behaviour at the level of individual trials, we start by stepping through each trial in the data from \cite{clarke2022}.
 For each target selection, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model.
@@
 \centering
-\includegraphics[width=12 cm]{Figures/qjep_preds.png}
+\includegraphics[width=12 cm]{Figures/qjep_preds.pdf}
 \caption{(\textit{left}) Posterior probabilities for target selections during a visual foraging task.
@@
 Figure \ref{fig:cal} hints at some individual differences when it comes to how predictable the model is: we can see a lot of variation in the size of the weights
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=12 cm]{Figures/qjep_indiv_diff.pdf}
+\caption{(\textit{left}) Posterior probabilities for target selections during a visual foraging task.
+Each dot shows the  data from an individual participant, averaged over trials, in a condition and the shaded region indicates the interval in which we expect 67\% of participants to fall.
+The dashed line indicates chance performance.
+(\textit{centre})  Calibration plot for our foraging model.
+The *x*-axis gives the largest weight assigned by the model while the *y*-axis shows how often that target was actually selected by a human participant.
+(\textit{right}) This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model.}
+\label{fig:cal}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=12 cm]{Figures/qjep_ex_paths.pdf}
+\caption{(\textit{top}) Two randomly selected trials in which the model does a good job in accounting for human behaviour.
+When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation.
+(\textit{bottom}) Two randomly selected examples in which the model does a less good job in accounting for the order in which human participants selected the items.}
+\label{fig:qjep_paths}
+\end{figure}
 

### 2022-05-05 Analysis/index_prpic.Rmd
Prpic model param plot
working on graph a little

@@
 
-Terminology questions:
-- item v target
-- participant v observer
+# Ppric Model
+
+```{r, echo = TRUE}
+# read in data
+d <- read_csv("data/squirrel_spatial.csv", show_col_types = FALSE) %>%
+  mutate(condition = as_factor(condition),
+         condition = fct_recode(condition, feature = "1", conjunction = "2"),
+         targ_type = as_factor(targ_type))
+```
+
+```{r}
+m <- readRDS("scratch/squirrel.model")
+source("functions/plot_spatial_model.R")
+plot_fixed_effects(m) + theme(legend.position = "right")
+ggsave("../Figures/prpic_model_params.pdf",  width = 8, height = 6)
+```
 
@@
 As the current version of our model only takes the $p_A$ bias into account for the initial target selection, we will ignore these data points for now.
-
-```{r, echo = TRUE}
-# read in data
-d <- read_csv("data/squirrel_spatial.csv", show_col_types = FALSE) %>%
-  mutate(condition = as_factor(condition),
-         condition = fct_recode(condition, feature = "1", conjunction = "2"),
-         targ_type = as_factor(targ_type))
-```
 
@@
   summarise(meanb = mean(b),
-            prop_best = mean(selected_max), .groups = "drop") %>%
-  # finally, also compute what we would expect under a null-model
-  mutate(chance = 1/(41-found))-> a_agg
+            prop_best = mean(selected_max), .groups = "drop") -> a_agg
 ```
@@
   stat_lineribbon(.width = 0.67, alpha = 0.50) +
-  geom_path(data = filter(a_agg, observer == 1, condition == "feature"), 
-                          aes(y = chance), linetype = 2, colour = "black") + 
   geom_point(data = tibble(x=40, y=1), aes(x, y), size = 1.5, colour = "black", fill = "grey") + 
@@
   stat_lineribbon(.width = 0.67, alpha = 0.50) +
-  geom_path(data = filter(a_agg, observer == 1, condition == "feature"), 
-            aes(y = chance), linetype = 2, colour = "black") + 
   geom_point(data = tibble(x=40, y=1), aes(x, y), size = 1.5, colour = "black", fill = "grey") + 
@@
 ```{r, echo = TRUE}
-my_breaks <- seq(0.0, 1, 0.05)
+my_breaks <- seq(0.5, 1, 0.05)
 
@@
   summarise(acc = mean(selected_max), .groups = "drop") %>%
-  mutate(b_bin = as.numeric(b_bin)/(length(my_breaks)-1)) -> a_cut
+  mutate(b_bin = my_breaks[b_bin]) -> a_cut
 ```

### 2022-05-09 manuscript.tex
Updates from Overleaf

@@
 
+\begin{linenomath}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath}
 
@@
 \end{equation}
+\end{linenomath}
+
+\begin{linenomath}
 \begin{equation}
@@
 \end{equation}
+\end{linenomath}
 
 $d(i,j)$ is simply the Euclidean distance between items $i$ and $j$, while $\theta$ is defined as:
+
+\begin{linenomath}
 \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-
-\subsection{Initial target selection}
+\section{Results: Evaluating the Model}
 
@@
 
-\subsection{Improvement: Adaptive distance? Absolute direction?}
+\section{Results: Improving the model}
+
+One weakness of the foraging model by \cite{clarke2022foraging} is that it makes little attempt to the predict which item will be selected first.
+IN this section we aim to improve this by modelling participant bias/preference in their choice of initial target selection.
+Following \cite{clarke_tatler2014, clarke2017} we fit truncated Gaussian distributions to the $(x,y)$ coordinates of the initial target selections
+
+\section{Foraging in 3D virtual environments}
+
+Can we model the data from \cite{prpic2019}?
+
+\subsection{Fitting the Model}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=12 cm]{Figures/prpic_model_params.pdf}
+\caption{(\textit{top}) Figure caption needed}
+\label{fig:qjep_paths}
+\end{figure}
 
@@
 The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-
-This is the example 2 of equation:
-\begin{adjustwidth}{-\extralength}{0cm}
-\begin{equation}
-a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
-\end{equation}
-\end{adjustwidth}
 

### 2022-05-09 Analysis/index.Rmd
saving init sel hex figure
initial sel model

@@
 plt_all + plt_med 
+ggsave("../Figures/init_sel_hex_plot.pdf", width = 8, height = 4)
 
@@
     pivot_longer(-z, names_to = "observer", values_to = "v") %>%
-    ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
-    scale_x_continuous(dm) + scale_y_continuous("likelihood") -> plt
+    ggplot(aes(x = z, y = v, group = observer)) + 
+    geom_path(alpha = 0.25) +
+    scale_x_continuous(dm) + 
+    scale_y_continuous("likelihood") -> plt
 
@@
 
-create_post_plot("x") + create_post_plot("y")
+am %>% select(-sd) %>% 
+  pivot_wider(names_from = "dim", values_from = "mean") %>%
+  ggplot(aes(x, y)) + 
+  geom_point(alpha = 0.5) + 
+  geom_line(data = tibble(), aes(x = c(0, 1), y = c(0, 0)), color = "grey") +
+  geom_line(data = tibble(), aes(x = c(0, 1), y = c(1, 1)), color = "grey") +
+  geom_line(data = tibble(), aes(x = c(0, 0), y = c(0, 1)), color = "grey") +
+  geom_line(data = tibble(), aes(x = c(1, 1), y = c(0, 1)), color = "grey") -> plt_m
+
+create_post_plot("x") + create_post_plot("y") + plt_m
+ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3)
 ```

### 2022-05-09 manuscript.tex

@@
 (\textit{right}) This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model.}
-\label{fig:cal}
+\label{fig:cal2}
 \end{figure}
@@
 
-\section{Results: Improving the model}
+\section{Improving the model: location of the first target selection}
 
@@
 Following \cite{clarke_tatler2014, clarke2017} we fit truncated Gaussian distributions to the $(x,y)$ coordinates of the initial target selections
+
+\subsection{Results}
+
+Figure \ref{fig:qjep_init_sel_hex} shows the distribution of the locations of first target selections.
+We can see that unlike the central bias in fixations during scene viewing, the distribution of initial target locations appear to be bimodal: while most targets are positioned in the top left hand corner <CHECK MATLAB CODE!!!> there is a second smaller distribution of central target selections.
+This appears to be due to different participants choosing to utilise different strategies rather than within-subject variation.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=12 cm]{Figures/init_sel_hex_plot.pdf}
+\caption{Hexagonal heatmaps showing the two-dimensional distribution of the location of initial target selections.
+Grey areas indicate cells with a count of 0/ (\textit{left}) shows the distribution over all initial target selections while (\textit{right}) shows the distribution of each participant's median initial selection.
+}
+\label{fig:qjep_init_sel_hex}
+\end{figure}
 

### 2022-05-09 manuscript.tex

@@
 
+We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnoteP{Full details of the analysis can be found in the supplementary materials}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=12 cm]{Figures/init_sel_mdl.pdf}
+\caption{Posterior fits for (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection.
+Each line represents a different participant.
+(\textit{right}) shows the correlation between participant's mean $x$ and $y$ coordinates.
+The box shows the extent of the stimulus.}
+\label{fig:qjep_init_sel_mdl}
+\end{figure}
+
 \section{Foraging in 3D virtual environments}

### 2022-05-16 manuscript.tex
some mild tidying up of manuscript

@@
 
-We will use two previously published datasets to explore how well our model can account for trial-level behaviour.
+We will a previously published dataset to explore how well our model can account for trial-level behaviour.
 We will start with the visual foraging data from \cite{clarke2022}.
@@
 
-To test how well our methods generalise, we will introduce a new dataset that was not analysed in our previous modelling paper.
-This \cite{prpic2019} data comes from a study in which participants played a simple computer game in which they controlled a squirrel hunting for acorns.
-The game makes us a 3D virtual world and player are provided with a 1st person (2nd??) view.
-This differs from the top down displays typically used in other visual foraging studies and so makes a good test of generalisability.
+To test how well our methods generalise, we will introduce a new dataset that was not analysed in our previous modelling paper....
 
@@
 where $t_i = 1$ if item $i$ is of class $A$ and 0 otherwise, $m(t_i, t_{i-1}) =1$ if item $i$ is the same class as the previously selected item.
-$\rho_d$ and $\rho_{\theta}$ measures proximity and the effect of direction:
+$\rho_d$ and $\rho_{\theta}$ measure proximity and the effect of direction:
 
@@
 For each target selection, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model.
-As can be seen in Figure \ref{fig:cal}, the model is putting somewhere between 25\% and 75\% of the weight on the target that is selected next easily outperforming a chance $1/n$ baseline.
+As can be seen in Figure \ref{fig:cal}, the model is putting somewhere between 25\% and 75\% of the weight on the target that is selected next, easily outperforming a chance $1/n$ baseline.
 We can also see  that the model is well calibrated in that the probabilities assigned to the largest target manage to capture how well often that target is actually selected.
@@
 (\textit{centre})  Calibration plot for our foraging model.
-The *x*-axis gives the largest weight assigned by the model while the *y*-axis shows how often that target was actually selected by a human participant.
+The $x$-axis gives the largest weight assigned by the model while the $y$-axis shows how often that target was actually selected by a human participant.
 (\textit{right}) This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model.}
@@
 
-Figure \ref{fig:cal} hints at some individual differences when it comes to how predictable the model is: we can see a lot of variation in the size of the weights
+Figure \ref{fig:cal2} hints at some individual differences when it comes to how predictable the model is: we can see a lot of variation in the size of the weights.
+However, interestingly, we find that this variability can be explained by our model parameters: nearly all of the differences between people, and between feature and conjunction conditions, can be explained by the $bP$ parameter, which is our proximity bias.
+The model is doing a better job with participants who show a stronger proximity bias.
 
@@
 \includegraphics[width=12 cm]{Figures/qjep_indiv_diff.pdf}
-\caption{(\textit{left}) Posterior probabilities for target selections during a visual foraging task.
-Each dot shows the  data from an individual participant, averaged over trials, in a condition and the shaded region indicates the interval in which we expect 67\% of participants to fall.
-The dashed line indicates chance performance.
-(\textit{centre})  Calibration plot for our foraging model.
-The *x*-axis gives the largest weight assigned by the model while the *y*-axis shows how often that target was actually selected by a human participant.
-(\textit{right}) This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model.}
+\caption{(\textit{left}) Prediction scores for participants.
+Boxplots show quartile range and the grey lines indicate individual participants.
+The dots indicate outliers.
+(\textit{right}) Accuracy of our model varies with the strength of an individual’s \textit{bP} parameter.
+We can see two clear outlier participants (marked with an X).}
 \label{fig:cal2}
@@
 \caption{(\textit{top}) Two randomly selected trials in which the model does a good job in accounting for human behaviour.
+Red arrows indicate places where the model prediction deviates from participant behaviour.
 When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation.
@@
 One weakness of the foraging model by \cite{clarke2022foraging} is that it makes little attempt to the predict which item will be selected first.
-IN this section we aim to improve this by modelling participant bias/preference in their choice of initial target selection.
+In this section we aim to improve this by modelling participant bias/preference in their choice of initial target selection.
 Following \cite{clarke_tatler2014, clarke2017} we fit truncated Gaussian distributions to the $(x,y)$ coordinates of the initial target selections
@@
 This appears to be due to different participants choosing to utilise different strategies rather than within-subject variation.
+However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see Supplementary Material).
 
@@
 
-We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnoteP{Full details of the analysis can be found in the supplementary materials}.
+We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnote{Full details of the analysis can be found in the supplementary materials}.
 
@@
 \end{figure}
-
-\section{Foraging in 3D virtual environments}
-
-Can we model the data from \cite{prpic2019}?
-
-\subsection{Fitting the Model}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=12 cm]{Figures/prpic_model_params.pdf}
-\caption{(\textit{top}) Figure caption needed}
-\label{fig:qjep_paths}
-\end{figure}
-
-The text continues here.
 

### 2022-06-06 Analysis/index.Rmd
changing figure size
init sel model

--- 2022-05-05 Analysis/index.Rmd
@@
 
-We can model this as multi-level Gaussian? Yes, although it seems like people are in one of two clusters.
+## Multi-level Model
+
+We can model this as multi-level beta distribution? Yes, although it seems like people are in one of two clusters.
 
@@
 m <- readRDS("scratch/init_sel_model.rds")
-z <- seq(0, 1, 0.01)
 
@@
   rename(obs_b = ".value") %>%
-  full_join(gather_draws(m, b[dim]),
+  left_join(gather_draws(m, b[dim]), 
             by = c("dim", ".chain", ".iteration", ".draw")) %>%
-  mutate(obs_b = .value + obs_b,
-         .variable = if_else(dim %in% c(1,2), "mu", "sd"),
+  mutate(obs_b = exp(.value + obs_b),
+         .variable = if_else(dim %in% c(1,2), "a", "b"),
          dim = if_else(dim %in% c(1,3), "x", "y")) %>%
-  select(observer, dim, .iteration, obs_b, param = ".variable") %>%
-  mutate(obs_b = if_else(param == "sd", exp(obs_b), obs_b)) -> a
+  select(observer, dim, .iteration, obs_b, param = ".variable") -> a
 
@@
   summarise(value = mean(obs_b) , .groups = "drop") %>%
-  pivot_wider(names_from = param, values_from = value) %>%
-  rename(mean = "mu") -> am
+  pivot_wider(names_from = param, values_from = value) -> am
+
+compute_beta_dist <- function(observer, a, b) {
+  x <- seq(0.01,0.99,0.01)
+  return(tibble(observer = observer, 
+                x=  x,
+                z = dbeta(x, a, b)))
+
+}
 
@@
 
-  pmap(filter(am,  dim == dm) %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
-    set_names(rownames(filter(am,  dim == dm))) %>%
-    bind_rows() %>%
-    mutate(z = z) %>%
-    pivot_longer(-z, names_to = "observer", values_to = "v") %>%
-    ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
-    scale_x_continuous(dm) + scale_y_continuous("likelihood") -> plt
+   pmap_df(filter(am,  dim == dm) %>% select(observer, a, b), 
+                      compute_beta_dist) %>%
+    ggplot(aes(x = x, y = z, group = observer)) + 
+    geom_path(alpha = 0.25) +
+    scale_x_continuous(dm) + 
+    scale_y_continuous("likelihood") -> plt
 
@@
 create_post_plot("x") + create_post_plot("y") 
+ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
 ```
 
-- Do we want to simplify this model to something in which people have some mix of a (fixed) centre and corner bias?
+## Mixture Model
 
-Do participants who differ in terms of their initial target selection differ in other ways too?
+It looks like we can simplify the model somewhat by using a two component mixture model instead!
 
-```{r echo = TRUE, fig.cap = "Whether participants have a central or corner bias for the intiial target selection appears to be largely independent of their other model parameters."}
-full_join(fit, filter(am, dim == "x"), by = "observer") %>%
-  pivot_longer(c(pA, pS, bP, bM, accuracy), 
-               names_to = "statistic", values_to = "value") %>%
-  mutate(intial_sel = if_else(mean < 0, "corner", "central")) %>%
-  ggplot(aes(statistic, value, fill = intial_sel)) +
-  geom_boxplot(alpha = 0.5) + 
-  facet_wrap(~statistic, scales = "free", nrow = 1) +
-  theme(legend.position = "bottom") + 
-   scale_fill_manual("intial target selection",
-                     values = c(col3[2], col3[3]))
+```{r, fig.height = 6, fig.cap = "(*top*) Beta distributions for $x$ and $y$ coordinated"}
+
+m <- readRDS("scratch/init_sel_model2.rds")
+
+sample_beta <- function(c, .draw, dim, a, b) {
+  x <- seq(0.01, 0.99, 0.01)
+  return(tibble(c = c, 
+                draw = .draw,
+                dim = dim,
+                x = x,
+                z = dbeta(x, shape1 = a, shape2 = b)))
+}
+
+gather_draws(m, a_x[c], b_x[c], a_y[c], b_y[c], ndraws = 100) %>%
+  separate(.variable, into = c("param", "dim")) %>%
+  select(-.chain, -.iteration) %>%
+  pivot_wider(names_from = param, values_from = ".value") %>%
+  pmap_df(sample_beta) %>%
+  mutate(c = as_factor(c)) -> plt_dat
+
+plt_dat %>% filter(dim == "x") %>%
+  ggplot(aes(x, z, group = interaction(c, draw), colour = c)) +
+  geom_path(alpha = 0.1) + 
+  facet_wrap(~dim) + 
+  theme(legend.position = "none") -> plt_x
+
+plt_dat %>% filter(dim == "y") %>%
+  ggplot(aes(x, z, group = interaction(c, draw), colour = c)) +
+  geom_path(alpha = 0.1) + 
+  facet_wrap(~dim) + 
+  theme(legend.position = "none") +
+  scale_x_continuous("y") -> plt_y
+
+gather_draws(m, lambda[observer]) %>%
+  ggplot(aes(.value, group = observer)) + 
+  geom_density(alpha = 0.25, fill = "grey") -> plt_lambdas
+
+(plt_x + plt_y) / plt_lambdas
+
 ```

### 2022-06-06 Analysis/scripts/testing_init_selection.R

@@ -6,10 +6,10 @@ library(truncnorm)
 options(digits = 2, mc.cores = 10)
 d <- read_csv("../data/clarke_2020_qjep.csv") %>%
   filter(found == 1) %>%
-  mutate(x = if_else(x == 0, 0.01, x),
-         x = if_else(x == 1, 0.99, x),
-         y = if_else(y == 0, 0.01, y),
-         y = if_else(y == 1, 0.99, y)
+  mutate(x = if_else(x < 0.01, 0.01, x),
+         x = if_else(x > 0.99, 0.99, x),
+         y = if_else(y < 0.01, 0.01, y),
+         y = if_else(y > 0.99, 0.99, y)
          )
 
 
@@ -19,9 +19,9 @@ stan_data <- list(N = nrow(d),
                   x = d$x,
                   y = d$y)
 
-m <- stan("../models/initial_selection_models/init_sel.stan",
+m <- stan("../models/initial_selection_models/init_sel_beta.stan",
                 data = stan_data,
-                chains = 4,
+                chains = 1,
                 iter = 1000,
                 refresh = 100)
 
@@ -35,12 +35,12 @@ gather_draws(m, u[dim, observer]) %>%
   ungroup() %>%
   select(-.variable) %>%
   rename(obs_b = ".value") %>%
-  full_join(gather_draws(m, b[dim])) %>%
-  mutate(obs_b = .value + obs_b,
-         .variable = if_else(dim %in% c(1,2), "mu", "sd"),
+  left_join(gather_draws(m, b[dim]), 
+            by = c("dim", ".chain", ".iteration", ".draw")) %>%
+  mutate(obs_b = exp(.value + obs_b),
+         .variable = if_else(dim %in% c(1,2), "a", "b"),
          dim = if_else(dim %in% c(1,3), "x", "y")) %>%
-  select(observer, dim, .iteration, obs_b, param = ".variable") %>%
-  mutate(obs_b = if_else(param == "sd", exp(obs_b), obs_b)) -> a 
+  select(observer, dim, .iteration, obs_b, param = ".variable") -> a 
 
 ggplot(a, aes(obs_b, group = observer)) + 
   geom_density(alpha = 0.25) +
@@ -48,19 +48,24 @@ ggplot(a, aes(obs_b, group = observer)) +
  
 a %>% group_by(observer, param, dim) %>%
[…]

### 2022-06-06 manuscript.tex

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{A single paragraph of about 200 words maximum.
-For research articles, abstracts should give a pertinent overview of the work.
-We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusion: indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
+\abstract{Foraging refers to search involving multiple targets or multiple types of targets, and as a model task has a long history in animal behaviour and human cognition research.
+Foraging behaviour is usually operationalized using summary statistics, such as average distance covered during target collection (the path length) and the frequency of switching between target types.
+We recently introduced an alternative approach, which is to model each instance of target selection as random selection without replacement.
+Our model produces estimates of a set of foraging biases, such as a bias to select closer targets or targets of a particular category.
+Here we apply this model to predict individual target selection events.
+We add a new start position bias to the model, and generate foraging paths using the parameters estimated from individual participants’ pre-existing data.
+The model predicts which target the participant will select next with a range of accuracy from 43\% to 69\% across participants (chance is 11\%).
+The model therefore explains a substantial proportion of foraging behaviour in this paradigm.
+The situations where the model makes errors reveal useful information to guide future research on those aspects of foraging that we have not yet explained.}
 
 % Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}
+\keyword{foraging; visual search; bayesian model; decision; strategy (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}
 
@@
 Foraging, the act of searching for and gathering multiple targets (such as food), has been studied in both non-human animal contexts \cite{dawkins1971} and in human psychology studies \cite{kristjansson2014}.
-In many cases, the pattern of foraging behaviour has been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run.
+Foraging engages a wide range of different perceptual, cognitive, and decision-related skills, and is an ecologically relevant behaviour for most species, including humans.
+For these and other reasons, a sustained interest in foraging has developed our understanding of how we search for multiple instances of multiple types of targets.
+For example, the classic marginal value theorem \cite {charnov1976} is generally good at predicting when an organism will decide to stop searching in a patch and move on to another, based on the finding rate dropping below an expected rate, and taking into account the relative energy costs of traveling between patches versus staying within a patch.
+There has also been a concerted effort to characterize the spatial patterns of foraging behaviour.
+The Lévy Walk, for example, has been argued to be a good description of the foraging path many species take when the locations of targets are unknown (e.g.
+\citep {bartumeus2005}, but see also \citep{benhamou2007}).
+
+Another general principle of foraging is that of the “search image”, which describes the perceptual features that a foraging animal can use to identify targets or classes of targets \cite{Dukas1993}.
+A limited capacity for complex search images means that dividing attention over more than one kind of potential search target can impede search, particularly when what distinguished targets from distractors is not a simple feature like colour or motion.
+As a result, foragers tend to search in “runs” of one type of target before switching to another.
+In humans, this behaviour has been studied using computer-based displays of targets and distractors (e.g.
+\citep{ kristjansson2014}), in which participants must “collect” targets (by clicking or tapping on them) and ignore distractors.
+When targets can be identified based on a single, easily distinguishable feature (for example, find all the red and green shapes and ignore the blue and yellow shapes) participants tend to switch frequently between different types of targets, taking a relatively efficient path through the array.
+In contrast, when targets are defined based on a combination of more than one feature (e.g.
+find all the red squares and green circles and ignore the red circles and green squares), participants tend to switch far less frequently, often selecting all the targets of one category and then all the targets of the other.
+Consequently, the path taken to collect the targets is less efficient.
+In other words, frequent switching between target types limits the distance travelled between targets, while collecting all the targets of each type before switching to the other type sacrifices some efficiency of movement in service of reducing the mental workload.
+
+Different aspects of foraging behaviour, such as the search image and the search path, clearly interact with one another, but most research has tried to understand them separately.
+In many cases, the pattern of foraging behaviour has also been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run.
 However, we have recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022}.
@@
 To test how well our methods generalise, we will introduce a new dataset that was not analysed in our previous modelling paper....
-
-\subsubsection{Clarke et al 2022}
-
-\subsubsection{Ppric et al}
 

### 2022-06-07 Analysis/index2.Rmd
testing and training

--- 2022-05-05 Analysis/index.Rmd
@@
 ---
-title: 'SVG: The Paper'
+title: 'SVG: The Paper (2nd part of supplementary material)'
 author: "Alasdair Clarke, Amelia Hunt &  Anna Hughes"
@@
 
-We will use the visual foraging data from @clarke2022 to assess the model's trial level performance.
-As the current version of our model only takes the $p_A$ bias into account for the initial target selection, we will ignore these data points for now.
+This is the replication with Kristjansson (2014) data.
 
@@
 # read in data
-d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
+d <- read_csv("data/human_data_2014_prox.csv", show_col_types = FALSE) %>%
   mutate(condition = as_factor(condition),
@@
 # item weights pre-computed - see scripts/extract_item_weights_using_model.R
-a <- readRDS("scratch/qjep_model_weights.rda") %>%
+a <- readRDS("scratch/kristjansson_model_weights.rda") %>%
   filter(found != 1) # remove initial selections
@@
 
-ggsave("../Figures/qjep_preds.pdf", 
-       plt_b + plt1 + plt2 + 
-         plot_layout(guides = "collect") & theme(legend.position = "bottom"),
-       width = 10, height = 4)
+#ggsave("../Figures/qjep_preds.pdf", 
+#       plt_b + plt1 + plt2 + 
+#         plot_layout(guides = "collect") & theme(legend.position = "bottom"),
+#       width = 10, height = 4)
 
-rm(plt1, plt2, plt_a)
 ```
@@
 # computed in xxxx.R
-fit <- readRDS("scratch/qjep_model_fit.rda") %>%
+fit <- readRDS("scratch/kristjansson_model_fit.rda") %>%
   full_join(a_acc, by = c("observer", "condition")) %>%
@@
 
-ggsave("../Figures/qjep_indiv_diff.pdf", 
-       plt_a + plt_b + 
-         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
+#ggsave("../Figures/qjep_indiv_diff.pdf", 
+#       plt_a + plt_b + 
+#         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
 ```
 
-As the two outlier participants appear to be doing something different, not captured especially well by our model, we will remove them from the rest of this analysis.
-
-After removing them, we can see that individual differences in proximity tuning account for nearly all of the differences in predictability from person to person, and also between the *feature* and *conjunction* conditions.
+We can see that individual differences in proximity tuning account for nearly all of the differences in predictability from person to person, and also between the *feature* and *conjunction* conditions.
 
 ```{r, echo = TRUE}
-dm <- filter(fit, is_outlier == 0)
+dm <- filter(fit, is_outlier == 0) # have not currently defined anything as an outlier
 
@@
 
-Both $p_A$ and $b_M$ also have an effect on our model's accuracy, but note there is only a small increases in $R^2$ from just using $b_P$.
-
-## Are more predictable people faster at the task?
-
-```{r}
-drt <- filter(d, found == 40) %>% group_by(observer, condition) %>%
-  summarise(median_rt = median(RT), .groups = "drop") %>% 
-  full_join(dm, by = c("observer", "condition"))
-
-ggplot(drt, aes(accuracy, median_rt, colour = condition)) +
-         geom_point(alpha = 0.5) + 
-  geom_smooth(method = "lm")
-
-summary(lm(median_rt ~ accuracy*condition, data = drt))
-
-```
-
-```{r}
-rm(dm)
-```
-
-## Examples of Trials
-
-Let's score every trial by how well the model captures behaviour, and then plot some different examples.
-
-```{r, echo = TRUE}
-a %>% filter(!(observer %in% c(35, 45))) %>%
-  group_by(observer, condition, trial) %>% 
-  summarise(prop_max = mean(selected_max), .groups = "drop") %>% 
-  arrange(desc(prop_max)) %>%
-  ungroup() -> a_trl
-```
-
-```{r fig.height=3.5, fig.cap = "Histogram of how predictiable individual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
-ggplot(a_trl, aes(prop_max)) + 
-  geom_histogram(fill = "#d04e00", breaks = seq(0, 1, 0.025), alpha = 0.5) +
-  scale_x_continuous("trial predictability")
-```
-
-Let's plot some examples oh highly predictable (top 5%), typical (middle 10%) and unpredictable (bottom 5%) trials.
-
-```{r, echo = TRUE}
-qs <- quantile(a_trl$prop_max, c(0.05, 0.40, 0.60, 0.95))
-
-trls_hard <- filter(a_trl, prop_max < qs[1]) %>% sample_n(3)
-trls_mid  <- filter(a_trl, prop_max > qs[2], prop_max < qs[3]) %>% sample_n(3)
-trls_easy <- filter(a_trl, prop_max > qs[4]) %>% sample_n(3)
-```
-
-We can see that for these highly predictable trials, we make very few mistakes, and those that we do make appear to be related to some sort of shortest-path optimization on the part of the participant.
-
-```{r fig.cap = "A random selection of *good* trials. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation."}
-
-source("functions/plot_trial.R")
-plts1 <- map(1:3, plot_trial, trls_easy, a, d)
-
-plts1[[1]] + plts1[[2]] +
-  plot_layout(nrow = 1, widths = c(1,1)) &
-   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
-   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
-   theme(text=element_text(size=14,  family="serif"))
-```
-
-Here are some typical trials. Possible we have the path-length minimization issue again.
-
-```{r fig.cap = "A random selection of *typical* trials. Along with path-minimising behaviour, we can also see some disagreement around switching item type."}
-plts2 <- map(1:3, plot_trial, trls_mid, a, d)
-
-plts2[[1]] + plts2[[2]] +
-  plot_layout(nrow = 1, widths = c(1,1)) &
-   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
-   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
-   theme(text=element_text(size=14,  family="serif"))
-```
-
-Now let's look at less predictable (bottom 5%-tile) trials. Even here, the model does a relatively good job.
-
-```{r fig.cap = "A random selection of *hard* trials. It is harder to make out much of a pattern here, but we can see that the human participants jump around more."}
-plts3 <- map(1:3, plot_trial, trls_hard, a, d)
-
-plts3[[1]] + plts3[[2]] +
-  plot_layout(nrow = 1, widths = c(1,1)) &
-   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
-   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
-   theme(text=element_text(size=14,  family="serif"))
-```
-
-```{r}
-ggsave("../Figures/qjep_ex_paths.pdf",
-      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]]), 
-       width = 8, height = 8)
-
-rm(trls_easy, trls_mid, trls_hard, plts, qs, plts1, plts2, plts3)
-```
-
-# Path Length Analysis
-
-It looks like some of the target selections that our model fails to capture are when participants select a further away target in order to minimise overall path length.
-Here we will compare our model's predicted path length against the empirical paths.
-
-- We will provide the model/simulation with the initial target selection.
-
-```{r, fig.height=3.5, fig.cap = "(*left*) Histogram comparing the empirical path lengths to simulations from our fitted model.
-Difference indicates the human path length - the simulated path length.
-(*right*) Histogram comparing the median path lengths per participant.", message=FALSE}
-path_lengths <- readRDS("scratch/path_lengths.rda") %>%
-  rename(observer = "obs",
-         condition = "cond",
-         human = "human_path_length",
-         model = "model_path_length") %>% 
-  mutate(difference  = human - model) %>%
-  pivot_longer(c(human, model, difference), names_to = "type", values_to = "path_length")
-
-ggplot(path_lengths, aes(path_length, fill = type)) + 
-  geom_histogram(bins = 25, alpha = 0.5, position = "identity") +
-  geom_vline(xintercept = 0, linetype = 2) + 
-  theme(legend.position = "bottom")  +
-  scale_x_continuous("path length")  +
-  scale_x_continuous("median path length") +
-  scale_fill_manual(values = col3) -> plt1
-
-path_lengths %>% group_by(observer, type) %>%
-  summarise(path_length = median(path_length), .groups = "drop") %>%
-  ggplot(aes(path_length, fill = type)) + 
-  geom_histogram(bins = 25, alpha = 0.5, position = "identity") +
-  geom_vline(xintercept = 0, linetype = 2) + 
-  theme(legend.position = "bottom") +
-  scale_x_continuous("median path length") +
-  scale_fill_manual(values = col3) -> plt2
-
-plt1 + plt2 + plot_layout(guides = "collect")  &
-  theme(legend.position = 'bottom', legend.title = element_blank())
-```
-
-We can see that overall, the model is not making substantially longer paths through the items than our human participants.
-However, there is some variability in that some participants routinely select paths shorter than our model would, and others do not.
-
-Perhaps this is related to predictability (i.e., how well the model can predict a participant's trial level behaviour)?
-
-```{r fig.height=3, fig.cap = "(*left*) A histogram showing the proportion of trials each participant managed a shorter path through the targets than the model's prediction.
-(*right*) Scatter plot showing the relationship between predictability (accuracy) and whether the model over or under estimates path length.
-Xs mark the outlier participants discussed above."}
-path_lengths %>% filter(type == "difference") %>%
-  mutate(shorter = path_length < 0) %>%
-  group_by(observer, condition) %>%
-  summarise(prop_shorter = mean(shorter), .groups = "drop") -> path_lengths_obs
-
-path_lengths_obs %>%
-  ggplot(aes(prop_shorter, fill = condition)) + 
-  geom_histogram(alpha = 0.5, breaks = seq(0, 1, 0.2), position = "identity") +
-  scale_x_continuous("prop. shorter than model", breaks = seq(0, 1, 0.2)) -> plt1
-
-path_lengths <- full_join(path_lengths_obs, fit,
-                          by = c("observer", "condition"))
-
-ggplot(path_lengths, aes(accuracy, prop_shorter, colour = condition)) + 
-  geom_point(aes(shape = is_outlier)) +
-  geom_smooth(data = filter(path_lengths, is_outlier == 0), 
-              method = "lm", formula = y ~ x, se = FALSE) + 
-  scale_shape_manual(values = c(19, 4), guide = "none") + 
-  scale_y_continuous("prop. shorter than model", breaks = seq(0, 1, 0.2)) +
-  coord_cartesian(ylim = c(0, 1)) -> plt2
-
-plt1 + plt2 + plot_layout(guides = "collect")  &
-  theme(legend.position = 'bottom')
-```
-
-```{r}
-rm(path_lengths, plt1, plt2)
-```
-
 # Initial Selection
@@
 # Reimport data again (as we removed the initial target selection earlier)
-d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
+d <- read_csv("data/human_data_2014_prox.csv", show_col_types = FALSE) %>%
   filter(found == 1) %>%
@@
 plt_all + plt_med 
+#ggsave("../Figures/init_sel_hex_plot.pdf", width = 8, height = 4)
 
@@
 ```
-
-We can model this as multi-level Gaussian? Yes, although it seems like people are in one of two clusters.
-
-```{r fig.cap = "The mean posterior plot for the truncated normal distriubtions for (*left*) $x$ and (*right*) $y$.
-We can see that a two component mixture model will capture most of the variance in intial target selection."}
-
-m <- readRDS("scratch/init_sel_model.rds")
-z <- seq(0, 1, 0.01)
-
-gather_draws(m, u[dim, observer]) %>% 
-  ungroup() %>%
-  select(-.variable) %>%
-  rename(obs_b = ".value") %>%
-  full_join(gather_draws(m, b[dim]),
-             by = c("dim", ".chain", ".iteration", ".draw")) %>%
-  mutate(obs_b = .value + obs_b,
-         .variable = if_else(dim %in% c(1,2), "mu", "sd"),
-         dim = if_else(dim %in% c(1,3), "x", "y")) %>%
-  select(observer, dim, .iteration, obs_b, param = ".variable") %>%
-  mutate(obs_b = if_else(param == "sd", exp(obs_b), obs_b)) -> a
-
-a %>% group_by(observer, param, dim) %>%
-  summarise(value = mean(obs_b) , .groups = "drop") %>%
-  pivot_wider(names_from = param, values_from = value) %>%
-  rename(mean = "mu") -> am
-
-create_post_plot <- function(dm) {
-
-  pmap(filter(am,  dim == dm) %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
-    set_names(rownames(filter(am,  dim == dm))) %>%
-    bind_rows() %>%
-    mutate(z = z) %>%
-    pivot_longer(-z, names_to = "observer", values_to = "v") %>%
-    ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
-    scale_x_continuous(dm) + scale_y_continuous("likelihood") -> plt
-
-  return(plt)
-}
-
-create_post_plot("x") + create_post_plot("y")
-```
-
-- Do we want to simplify this model to something in which people have some mix of a (fixed) centre and corner bias?
-
-Do participants who differ in terms of their initial target selection differ in other ways too?
-
-```{r echo = TRUE, fig.cap = "Whether participants have a central or corner bias for the intiial target selection appears to be largely independent of their other model parameters."}
-full_join(fit, filter(am, dim == "x"), by = "observer") %>%
-  pivot_longer(c(pA, pS, bP, bM, accuracy), 
-               names_to = "statistic", values_to = "value") %>%
-  mutate(intial_sel = if_else(mean < 0, "corner", "central")) %>%
-  ggplot(aes(statistic, value, fill = intial_sel)) +
-  geom_boxplot(alpha = 0.5) + 
-  facet_wrap(~statistic, scales = "free", nrow = 1) +
-  theme(legend.position = "bottom") + 
-   scale_fill_manual("intial target selection",
-                     values = c(col3[2], col3[3]))
-```
-
-# Item Density

### 2022-06-07 Analysis/functions/compute_weights.R

@@ -2,7 +2,7 @@
 compute_weights_trials <- function(obs, cond, n_trials = 20) {
   
   params <- filter(fit,  observer == obs, condition == cond )
-  a <- map_dfr(1:n_trial, compute_weights, params = params, cond = cond, obs = obs)
+  a <- map_dfr(1:n_trials, compute_weights, params = params, cond = cond, obs = obs)
   
   return(a)
   

### 2022-06-07 Analysis/scripts/extract_item_weights_using_model_kristjansson.R

@@ -1,0 +1,27 @@
+library(tidyverse)
+library(rstan)
+library(tidybayes)
+
+# this function takes a dataset and fitted model, then steps through the data 
+# and computes the weights assigned to each item by the model
+
+source("../functions/get_model_params.R")
+source("../functions/compute_weights.R")
+
+# read in data
+d <- read_csv("../data/human_data_2014_prox.csv") %>%
+  mutate(condition = as_factor(condition),
+         condition = fct_recode(condition, feature = "1", conjunction = "2"),
+         targ_type = as.numeric(targ_type))
+
+# read in model and extract weights
+fit <- get_model_params("../scratch/arni2014.model") %>% rename(observer = "obs")
+saveRDS(fit, "../scratch/kristjansson_model_fit.rda")
+
+# run for all participants...
+a_feat <- map_dfr(unique(d$observer), compute_weights_trials, cond = "feature")
+a_conj <- map_dfr(unique(d$observer), compute_weights_trials, cond = "conjunction")
+a <- bind_rows(a_feat, a_conj)
+rm(a_feat, a_conj)
+
+saveRDS(a, "../scratch/kristjansson_model_weights.rda")

### 2022-06-07 Analysis/scripts/extract_item_weights_using_model_prpic.R

@@ -1,27 +1,0 @@
-library(tidyverse)
-library(rstan)
-library(tidybayes)
-
-# this function takes a dataset and fitted model, then steps through the data 
-# and computes the weights assigned to each item by the model
-
-source("../functions/get_model_params.R")
-source("../functions/compute_weights.R")
-
-# read in data
-d <- read_csv("../data/squirrel_spatial.csv") %>%
-  mutate(condition = as_factor(condition),
-         condition = fct_recode(condition, feature = "1", conjunction = "2"),
-         targ_type = as.numeric(targ_type))
-
-# read in model and extract weights
-fit <- get_model_params("../scratch/squirrel.model") %>% rename(observer = "obs")
-saveRDS(fit, "../scratch/prpic_model_fit.rda")
-
-# run for all participants...
-a_feat <- map_dfr(unique(d$observer), compute_weights_trials, cond = "feature", n_trials = 5)
-a_conj <- map_dfr(unique(d$observer), compute_weights_trials, cond = "conjunction", n_trials = 5)
-a <- bind_rows(a_feat, a_conj)
-rm(a_feat, a_conj)
-
-saveRDS(a, "../scratch/prpic_model_weights.rda")

### 2022-06-07 Analysis/index2.Rmd
more arni

@@
 # read in data
-d <- read_csv("data/human_data_2014_prox.csv", show_col_types = FALSE) %>%
+d <- read_csv("data/test_arni.csv", show_col_types = FALSE) %>%
   mutate(condition = as_factor(condition),
@@
 
-We will use the model fit as detailed in @clarke2020compbio.
-For simplicity sake, we will characterise all of our estimated posterior probability densities with just the mean value.
-This gives us four parameters per participant: $b_S, b_A, b_P, b_D$.
+Here, we have used half the data as a training set which we used to fit the initial model. This is then used for computing model weights for the test dataset.
+
+For simplicity's sake, we will characterise all of our estimated posterior probability densities with just the mean value. This gives us four parameters per participant: $b_S, b_A, b_P, b_D$.
 
@@
 # item weights pre-computed - see scripts/extract_item_weights_using_model.R
-a <- readRDS("scratch/kristjansson_model_weights.rda") %>%
+a <- readRDS("scratch/kristjansson_model_weights_train.rda") %>%
   filter(found != 1) # remove initial selections
@@
 We can then plot this data to show how our ability to predict which target will be selected next varies throughout a trial.
-We can see a difference between *feature* and *conjunction* foraging, with *feature* foraging being more predictable.
+We can see a difference between *feature* and *conjunction* foraging, with *feature* foraging being more predictable (though the distinction is less clear after the initial 20 target selections).
 
@@
 ```
+Model accuracy is quite high (though lower than for Clarke et al).
 
@@
 # computed in xxxx.R
-fit <- readRDS("scratch/kristjansson_model_fit.rda") %>%
+fit <- readRDS("scratch/kristjansson_model_fit_train.rda") %>%
   full_join(a_acc, by = c("observer", "condition")) %>%
@@
 
-We can also see if the other parameters have an effect.
+We can also see if the other parameters have an effect - which they do seem to.
 
@@
 
-Previous work (cite Clarke and Tatler etc) has demonstrated that the initial fixation in scene viewing can be well described with truncated Gaussian distribution.
-Here we explore using a similar idea to account for starting locations.
+Similar to Clarke et al, there is a bias towards starting in a corner. Interestingly, there isn't much evidence of a central bias (possibly because these trials were completed on an iPad).
 
@@
 # Reimport data again (as we removed the initial target selection earlier)
-d <- read_csv("data/human_data_2014_prox.csv", show_col_types = FALSE) %>%
+d <- read_csv("data/test_arni.csv", show_col_types = FALSE) %>%
   filter(found == 1) %>%

### 2022-06-07 Analysis/scripts/extract_item_weights_using_model_kristjansson.R

@@ -9,14 +9,14 @@ source("../functions/get_model_params.R")
 source("../functions/compute_weights.R")
 
 # read in data
-d <- read_csv("../data/human_data_2014_prox.csv") %>%
+d <- read_csv("../data/test_arni.csv") %>% # using test data (rather than full data)
   mutate(condition = as_factor(condition),
          condition = fct_recode(condition, feature = "1", conjunction = "2"),
          targ_type = as.numeric(targ_type))
 
 # read in model and extract weights
-fit <- get_model_params("../scratch/arni2014.model") %>% rename(observer = "obs")
-saveRDS(fit, "../scratch/kristjansson_model_fit.rda")
+fit <- get_model_params("../scratch/arni2014_train.model") %>% rename(observer = "obs")
+saveRDS(fit, "../scratch/kristjansson_model_fit_train.rda")
 
 # run for all participants...
 a_feat <- map_dfr(unique(d$observer), compute_weights_trials, cond = "feature")
@@ -24,4 +24,4 @@ a_conj <- map_dfr(unique(d$observer), compute_weights_trials, cond = "conjunctio
 a <- bind_rows(a_feat, a_conj)
 rm(a_feat, a_conj)
 
-saveRDS(a, "../scratch/kristjansson_model_weights.rda")
+saveRDS(a, "../scratch/kristjansson_model_weights_train.rda")

### 2022-06-07 Analysis/index.Rmd
Adding predictions to init_sel model

@@
 ```
+How well does the model do in guessing the first target in a trial?
+
+```{r}
+d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
+  mutate(x = if_else(x < 0.01, 0.01, x),
+         x = if_else(x > 0.99, 0.99, x),
+         y = if_else(y < 0.01, 0.01, y),
+         y = if_else(y > 0.99, 0.99, y) ) %>%
+  select(-RT)
+
+get_model_weight <- function(obs, cond, trl) {
+
+  dt <- filter(d, observer == obs, condition == cond, trial == trl)
+
+  mtx <- filter(am, observer == obs, dim == "x")
+  mty <- filter(am, observer == obs, dim == "y")
+
+  wx <- dbeta(dt$x, mtx$a, mtx$b)
+  wy <- dbeta(dt$y, mty$a, mty$b)
+  w <- wx * wy
+  w <- w / sum(w)
+
+  return(tibble(observer = obs,
+                condition = cond, 
+                trial = trl,
+                init_weight = w[1],
+                max_item = which(w == max(w))))
+}
+
+d %>% group_by(observer, condition, trial) %>%
+  summarise(n = n(), .groups = "drop") %>%
+  select(-n, obs = "observer", cond = "condition", trl = "trial") %>%
+  pmap_df(get_model_weight) -> weights
+
+ggplot(weights, aes(init_weight)) + geom_histogram(binwidth = 1/80) +
+  geom_vline(xintercept = 1/40, linetype = 2) -> plt1
+
+weights %>% group_by(observer) %>%
+  summarise(acc = mean(max_item == 1)) %>%
+  ggplot(aes(y = acc)) + geom_boxplot() + 
+  geom_hline(yintercept = 1/40, linetype = 2) + 
+  scale_y_continuous("Prop. trials first sel. correct") -> plt2
+
+plt1 + plt2
+```
 

### 2022-06-07 Analysis/scripts/testing_init_selection.R

@@ -4,13 +4,13 @@ library(tidybayes)
 library(truncnorm)
 
 options(digits = 2, mc.cores = 10)
-d <- read_csv("../data/clarke_2020_qjep.csv") %>%
+
+d <- read_csv("../data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
   filter(found == 1) %>%
   mutate(x = if_else(x < 0.01, 0.01, x),
          x = if_else(x > 0.99, 0.99, x),
          y = if_else(y < 0.01, 0.01, y),
-         y = if_else(y > 0.99, 0.99, y)
-         )
+         y = if_else(y > 0.99, 0.99, y) )
 
 
 stan_data <- list(N = nrow(d),
@@ -19,15 +19,15 @@ stan_data <- list(N = nrow(d),
                   x = d$x,
                   y = d$y)
 
-m <- stan("../models/initial_selection_models/init_sel_beta.stan",
-                data = stan_data,
-                chains = 1,
-                iter = 1000,
-                refresh = 100)
-
-
-
-saveRDS(m, "../scratch/init_sel_model.rds")
+# m <- stan("../models/initial_selection_models/init_sel_beta.stan",
+#                 data = stan_data,
+#                 chains = 1,
+#                 iter = 1000,
+#                 refresh = 100)
+# 
+# 
+# 
+# saveRDS(m, "../scratch/init_sel_model.rds")
 
 m <- readRDS("../scratch/init_sel_model.rds")
 
@@ -70,7 +70,56 @@ obs_fits_x <- pmap_df(filter(am,  dim == "x") %>% select(observer, a, b),
 
 
 obs_fits_x + obs_fits_y
+rm(obs_fits_x, obs_fits_y)
 
+
+## now try guessing initial selections
+
+
+d <- read_csv("../data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
+  mutate(x = if_else(x < 0.01, 0.01, x),
+         x = if_else(x > 0.99, 0.99, x),
+         y = if_else(y < 0.01, 0.01, y),
+         y = if_else(y > 0.99, 0.99, y) ) %>%
+  select(-RT)
+
+
+get_model_weight <- function(obs, cond, trl) {
+  
+  dt <- filter(d, observer == obs, condition == cond, trial == trl)
+  
+  mtx <- filter(am, observer == obs, dim == "x")
+  mty <- filter(am, observer == obs, dim == "y")
+  
[…]

### 2022-06-07 Analysis/scripts/testing_init_selection_2.R

@@ -1,0 +1,40 @@
+library(tidyverse)
+library(rstan)
+library(tidybayes)
+library(truncnorm)
+
+options(digits = 2, mc.cores = 10)
+
+stan_list <- readRDS("../scratch/clarke2020qjep_stan_data.rds")
+
+
+m <- stan("../models/initial_selection_models/momentum_foraging_multi_level.stan",
+          data = stan_data,
+          chains = 1,
+          iter = 1000,
+          refresh = 100,
+          init = list(list(sd_x = c(1, 1))))
+
+saveRDS(m, "../scratch/init_sel_model2.rds")
+
+sample_beta <- function(c, a_y, b_y) {
+  x <- seq(0.01, 0.99, 0.01)
+  return(tibble(c = c, 
+                x = x,
+                y = dbeta(x, shape1 = a_y, shape2 = b_y)))
+}
+
+gather_draws(m, a_y[c], b_y[c]) %>%
+  group_by(c, .variable) %>%
+  summarise(.value = mean(.value)) %>%
+  pivot_wider(names_from = .variable, values_from = ".value") %>%
+  pmap_df(sample_beta) %>%
+  mutate(c = as_factor(c)) %>%
+  ggplot(aes(x, y)) +
+  geom_path() + 
+  facet_wrap(~c)
+
+
+gather_draws(m, lambda[observer]) %>%
+  ggplot(aes(.value, group = observer)) + 
+  geom_density(alpha = 0.25, fill = "grey")

### 2022-06-07 Analysis/index.Rmd
init sel post pred

@@
 
-# Item Density
+## Posterior Predictions
+
+```{r}
+gather_draws(m, a_x[c], b_x[c], a_y[c], b_y[c]) %>%
+  group_by(c, .variable) %>%
+  summarise(value = mean(.value)) %>%
+  pivot_wider(names_from = ".variable", values_from = "value") -> am
+
+c1 <- filter(am, c==1)
+c2 <- filter(am, c==2)
+
+gather_draws(m, lambda[observer]) %>%
+  group_by(observer, .variable) %>%
+  summarise(value = mean(.value)) %>%
+  select(-.variable) -> lambdas
+
+get_model_weight <- function(obs, cond, trl) {
+
+  dt <- filter(d, observer == obs, condition == cond, trial == trl)
+
+  lambda <- filter(lambdas, observer == obs)$value
+
+  wx <- lambda * dbeta(dt$x, c1$a_x, c1$b_x) +
+    (1-lambda) * dbeta(dt$x, c2$a_x, c2$b_x)
+
+  wy <- lambda * dbeta(dt$y, c1$a_y, c1$b_y) +
+    (1-lambda) * dbeta(dt$y, c2$a_y, c2$b_y)
+
+  w <- wx * wy
+  w <- w / sum(w)
+
+  return(tibble(observer = obs,
+                condition = cond, 
+                trial = trl,
+                init_weight = w[1],
+                max_item = which(w == max(w))))
+}
+
+d %>% group_by(observer, condition, trial) %>%
+  summarise(n = n(), .groups = "drop") %>%
+  select(-n, obs = "observer", cond = "condition", trl = "trial") %>%
+  pmap_df(get_model_weight) -> weights2
+
+bind_rows(weights %>% mutate(method = "multi-level"), 
+          weights2 %>% mutate(method = "mixture model")) -> dw
+
+ggplot(dw, aes(init_weight, fill = method)) + 
+  geom_histogram(binwidth = 1/80, position = "identity", alpha = 0.5) +
+  geom_vline(xintercept = 1/40, linetype = 2)  -> plt1
+
+dw %>% group_by(observer, method) %>%
+  summarise(acc = mean(max_item == 1)) %>%
+  ggplot(aes(y = acc, fill = method)) + geom_boxplot() + 
+  geom_hline(yintercept = 1/40, linetype = 2) + 
+  scale_y_continuous("Prop. trials first sel. correct") +
+  theme(legend.position = "none") -> plt2
+
+weights2 %>% group_by(observer) %>%
+  summarise(accuracy = mean(max_item == 1)) %>%
+  full_join(lambdas) %>%
+  rename(lambda = "value") %>%
+  ggplot(aes(lambda, accuracy)) + 
+  geom_point() +
+  geom_smooth(method = "lm", colour = "black") -> plt3
+
+plt1 / (plt2 + plt3)  + plot_layout(guides = "collect")
+
+dw %>% group_by(method, observer) %>%
+  summarise(score = median(init_weight),
+            accuracy = mean(max_item==1)) %>%
+  summarise(mean_score = mean(score),
+            mean_accuracy = mean(accuracy)) %>%
+  knitr::kable()
+
+```

### 2022-06-07 Analysis/scripts/testing_init_selection_2.R

@@ -1,40 +1,0 @@
-library(tidyverse)
-library(rstan)
-library(tidybayes)
-library(truncnorm)
-
-options(digits = 2, mc.cores = 10)
-
-stan_list <- readRDS("../scratch/clarke2020qjep_stan_data.rds")
-
-
-m <- stan("../models/initial_selection_models/momentum_foraging_multi_level.stan",
-          data = stan_data,
-          chains = 1,
-          iter = 1000,
-          refresh = 100,
-          init = list(list(sd_x = c(1, 1))))
-
-saveRDS(m, "../scratch/init_sel_model2.rds")
-
-sample_beta <- function(c, a_y, b_y) {
-  x <- seq(0.01, 0.99, 0.01)
-  return(tibble(c = c, 
-                x = x,
-                y = dbeta(x, shape1 = a_y, shape2 = b_y)))
-}
-
-gather_draws(m, a_y[c], b_y[c]) %>%
-  group_by(c, .variable) %>%
-  summarise(.value = mean(.value)) %>%
-  pivot_wider(names_from = .variable, values_from = ".value") %>%
-  pmap_df(sample_beta) %>%
-  mutate(c = as_factor(c)) %>%
-  ggplot(aes(x, y)) +
-  geom_path() + 
-  facet_wrap(~c)
-
-
-gather_draws(m, lambda[observer]) %>%
-  ggplot(aes(.value, group = observer)) + 
-  geom_density(alpha = 0.25, fill = "grey")

### 2022-06-07 Analysis/index.Rmd
tidy up a little

--- 2022-06-06 Analysis/index.Rmd
@@
 
+```{r}
+# Compute weights for later
+d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
+  mutate(x = if_else(x < 0.01, 0.01, x),
+         x = if_else(x > 0.99, 0.99, x),
+         y = if_else(y < 0.01, 0.01, y),
+         y = if_else(y > 0.99, 0.99, y) ) %>%
+  select(-RT)
+
+get_model_weight <- function(obs, cond, trl) {
+
+  dt <- filter(d, observer == obs, condition == cond, trial == trl)
+
+  mtx <- filter(am, observer == obs, dim == "x")
+  mty <- filter(am, observer == obs, dim == "y")
+
+  wx <- dbeta(dt$x, mtx$a, mtx$b)
+  wy <- dbeta(dt$y, mty$a, mty$b)
+  w <- wx * wy
+  w <- w / sum(w)
+
+  return(tibble(observer = obs,
+                condition = cond, 
+                trial = trl,
+                init_weight = w[1],
+                max_item = which(w == max(w))))
+}
+
+d %>% group_by(observer, condition, trial) %>%
+  summarise(n = n(), .groups = "drop") %>%
+  select(-n, obs = "observer", cond = "condition", trl = "trial") %>%
+  pmap_df(get_model_weight) -> weights
+
+```
+
 ## Mixture Model
@@
 (plt_x + plt_y) / plt_lambdas
+```
+
+## Posterior Predictions
+
+```{r}
+gather_draws(m, a_x[c], b_x[c], a_y[c], b_y[c]) %>%
+  group_by(c, .variable) %>%
+  summarise(value = mean(.value), .groups = "drop") %>%
+  pivot_wider(names_from = ".variable", values_from = "value") -> am
+
+c1 <- filter(am, c==1)
+c2 <- filter(am, c==2)
+
+gather_draws(m, lambda[observer]) %>%
+  group_by(observer, .variable) %>%
+  summarise(value = mean(.value), .groups = "drop") %>%
+  select(-.variable) -> lambdas
+
+get_model_weight <- function(obs, cond, trl) {
+
+  dt <- filter(d, observer == obs, condition == cond, trial == trl)
+
+  lambda <- filter(lambdas, observer == obs)$value
+
+  wx <- lambda * dbeta(dt$x, c1$a_x, c1$b_x) +
+    (1-lambda) * dbeta(dt$x, c2$a_x, c2$b_x)
+
+  wy <- lambda * dbeta(dt$y, c1$a_y, c1$b_y) +
+    (1-lambda) * dbeta(dt$y, c2$a_y, c2$b_y)
+
+  w <- wx * wy
+  w <- w / sum(w)
+
+  return(tibble(observer = obs,
+                condition = cond, 
+                trial = trl,
+                init_weight = w[1],
+                max_item = which(w == max(w))))
+}
+
+d %>% group_by(observer, condition, trial) %>%
+  summarise(n = n(), .groups = "drop") %>%
+  select(-n, obs = "observer", cond = "condition", trl = "trial") %>%
+  pmap_df(get_model_weight) -> weights2
+
+bind_rows(weights %>% mutate(method = "multi-level"), 
+          weights2 %>% mutate(method = "mixture model")) -> dw
+
+ggplot(dw, aes(init_weight, fill = method)) + 
+  geom_histogram(binwidth = 1/80, position = "identity", alpha = 0.5) +
+  geom_vline(xintercept = 1/40, linetype = 2)  -> plt1
+
+dw %>% group_by(observer, method) %>%
+  summarise(acc = mean(max_item == 1), .groups = "drop") %>%
+  ggplot(aes(y = acc, fill = method)) + geom_boxplot() + 
+  geom_hline(yintercept = 1/40, linetype = 2) + 
+  scale_y_continuous("Prop. trials first sel. correct") +
+  theme(legend.position = "none") -> plt2
+
+weights2 %>% group_by(observer) %>%
+  summarise(accuracy = mean(max_item == 1), .groups = "drop") %>%
+  full_join(lambdas, by = "observer") %>%
+  rename(lambda = "value") %>%
+  ggplot(aes(lambda, accuracy)) + 
+  geom_point() +
+  geom_smooth(method = "lm", formula = y ~ x, colour = "black") -> plt3
+
+plt1 / (plt2 + plt3)  + plot_layout(guides = "collect")
+
+dw %>% group_by(method, observer) %>%
+  summarise(score = median(init_weight,),
+            accuracy = mean(max_item==1),
+            .groups = "drop_last") %>%
+  summarise(mean_score = mean(score),
+            mean_accuracy = mean(accuracy),
+            .groups = "drop") %>%
+  knitr::kable()
 
 ```
-
-# Item Density

### 2022-06-07 Analysis/index.Rmd
flipping y in hex plots

@@
 
-ggplot(d, aes(x, y)) + geom_hex(aes(colour = ..count..), bins = 12) +
+ggplot(d, aes(x, 1 - y)) + geom_hex(aes(colour = ..count..), bins = 12) +
   scale_fill_viridis_c() + scale_color_viridis_c() +
@@
             .groups = "drop") %>%
-  ggplot(aes(x, y)) + geom_hex(bins = 12) +
+  ggplot(aes(x, 1 - y)) + geom_hex(bins = 12) +
   scale_fill_viridis_c()+ scale_color_viridis_c() +
@@
 
+ggsave("../Figures/qjep_init_sel_preds.pdf", 
+       plt1 / (plt2 + plt3)  + plot_layout(guides = "collect"),
+       width = 10, height = 6)
+
 dw %>% group_by(method, observer) %>%

### 2022-06-07 Analysis/scripts/testing_init_selection.R
Update testing_init_selection.R

@@ -75,7 +75,6 @@ rm(obs_fits_x, obs_fits_y)
 
 ## now try guessing initial selections
 
-
 d <- read_csv("../data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
   mutate(x = if_else(x < 0.01, 0.01, x),
          x = if_else(x > 0.99, 0.99, x),
@@ -131,6 +130,8 @@ m <- stan("../models/initial_selection_models/init_sel2_beta.stan",
 
 saveRDS(m, "../scratch/init_sel_model2.rds")
 
+m <- readRDS("../scratch/init_sel_model2.rds")
+
 sample_beta <- function(c, a_y, b_y) {
   x <- seq(0.01, 0.99, 0.01)
   return(tibble(c = c, 
@@ -148,7 +149,77 @@ gather_draws(m, a_y[c], b_y[c]) %>%
   geom_path() + 
   facet_wrap(~c)
 
-
 gather_draws(m, lambda[observer]) %>%
   ggplot(aes(.value, group = observer)) + 
   geom_density(alpha = 0.25, fill = "grey")
+
+
+## now try guessing initial selections
+
+d <- read_csv("../data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
+  mutate(x = if_else(x < 0.01, 0.01, x),
+         x = if_else(x > 0.99, 0.99, x),
+         y = if_else(y < 0.01, 0.01, y),
+         y = if_else(y > 0.99, 0.99, y) ) %>%
+  select(-RT)
+
+
+gather_draws(m, a_x[c], b_x[c], a_y[c], b_y[c]) %>%
+  group_by(c, .variable) %>%
+  summarise(value = mean(.value)) %>%
+  pivot_wider(names_from = ".variable", values_from = "value") -> am
+
+c1 <- filter(am, c==1)
+c2 <- filter(am, c==2)
+
+gather_draws(m, lambda[observer]) %>%
+  group_by(observer, .variable) %>%
+  summarise(value = mean(.value)) %>%
+  select(-.variable) -> lambdas
+
+get_model_weight <- function(obs, cond, trl) {
+  
+  dt <- filter(d, observer == obs, condition == cond, trial == trl)
+  
+  lambda <- filter(lambdas, observer == obs)$value
+  
+
+  wx <- lambda * dbeta(dt$x, c1$a_x, c1$b_x) +
+    (1-lambda) * dbeta(dt$x, c2$a_x, c2$b_x) 
+  
[…]

### 2022-06-07 manuscript.tex
Updates from Overleaf

@@
 
-\subsection{Results}
-
 Figure \ref{fig:qjep_init_sel_hex} shows the distribution of the locations of first target selections.
@@
 This appears to be due to different participants choosing to utilise different strategies rather than within-subject variation.
-However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see Supplementary Material).
+However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see Supplementary Material)
 
@@
 
+\subsection{Multi-level Modelling Results}
 We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnote{Full details of the analysis can be found in the supplementary materials}.
@@
 
-\subsection{Figures, Tables and Schemes}
+\subsection{Mixture Modelling}
 
-All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, Table~\ref{tab2}, etc.
+\subsection{Posterior Predictions}
 
-\unskip
+The posterior predictions from the two models are compared in Figure \ref{fig:qjep_init_sel_pred}
 
-\begin{table}[H] 
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
-\bottomrule
-\end{tabularx}
-\end{table}
-\unskip
-
-\begin{table}[H]
-\caption{This is a wide table.\label{tab2}}
-	\begin{adjustwidth}{-\extralength}{0cm}
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\fulllength}{CCCC}
-			\toprule
-			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
-			\midrule
-			Entry 1		& Data			& Data			& Data\\
-			Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
-			\bottomrule
-		\end{tabularx}
-	\end{adjustwidth}
-	\noindent{\footnotesize{\textsuperscript{1} This is a table footnote.}}
-\end{table}
-
-%\begin{listing}[H]
-%\caption{Title of the listing}
-%\rule{\columnwidth}{1pt}
-%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
-%\rule{\columnwidth}{1pt}
-%\end{listing}
-
-Text.
-
-Text.
-
-\subsection{Formatting of Mathematical Components}
-
-This is the example 1 of equation:
-\begin{linenomath}
-\begin{equation}
-a = 1,
-\end{equation}
-\end{linenomath}
-the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-
-% Example of a page in landscape format (with table and table footnote).
-%\startlandscape
-%\begin{table}[H] %% Table in wide page
-%\caption{This is a very wide table.\label{tab3}}
-%	\begin{tabularx}{\textwidth}{CCCC}
-%		\toprule
-%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
-%		\midrule
-%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
-%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
-%		\bottomrule
-%	\end{tabularx}
-%	\begin{adjustwidth}{+\extralength}{0cm}
-%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
-%	\end{adjustwidth}
-%\end{table}
-%\finishlandscape
-
-% Example of a figure that spans the whole page width. The same concept works for tables, too.
 \begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
 \centering
-\includegraphics[width=15cm]{Definitions/logo-mdpi}
-\end{adjustwidth}
-\caption{This is a wide figure.\label{fig2}}
+\includegraphics[width=12 cm]{Figures/qjep_init_sel_preds.pdf}
+\caption{}
+\label{fig:qjep_init_sel_pred}
 \end{figure}
-
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
-
-The text continues here. Proofs must be formatted as follows:
-
-%% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
 

### 2022-06-07 Analysis/index.Rmd
figures
updating figure

@@
 gather_draws(m, lambda[observer]) %>%
-  ggplot(aes(.value, group = observer)) + 
-  geom_density(alpha = 0.25, fill = "grey") -> plt_lambdas
+  median_hdci(.value) %>%
+  arrange(.value) %>%
+  mutate(observer = factor(observer, levels = observer)) %>%
+  ggplot(aes(observer, .value, ymin = .lower, ymax = .upper)) + 
+  geom_errorbar() -> plt_lambdas
 
-(plt_x + plt_y) / plt_lambdas
+(plt_x + plt_y) + plt_lambdas
+
+ggsave("../Figures/init_sel2_mdl.pdf", width = 10, height = 5)
 ```

### 2022-06-07 manuscript.tex
Updates from Overleaf

@@
 % Keywords
-\keyword{foraging; visual search; bayesian model; decision; strategy (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}
+\keyword{foraging; visual search; bayesian model; decision; strategy.}
 
@@
 
-To test how well our methods generalise, we will introduce a new dataset that was not analysed in our previous modelling paper....
+To test how well our methods generalise, we use the dataset from \citep{kristjansson2014}.
+We split this into a training dataset (50\% of the original data i.e.
+10 trials per participant) and a test dataset (the remaining 50\% of the data).
+The foraging model is fit on the training dataset, and the parameters from this model are then used to predict behaviour at the level of individual trials.
+We show that our methods appear to generalise beyond \citep{clarke2022}: further details can be found in the \textit{Supplementary Materials}.
 
@@
     \item $b_A$ - preference for selecting items of type $A$ rather than $B$.
-    \item $b_S$ - preference for selections items of the same type as the previously selected item.
+    \item $b_S$ - preference for selecting items of the same type as the previously selected item.
     \item $\sigma_d$ - preference for selecting items close to the previously selected item.
@@
 
-One weakness of the foraging model by \cite{clarke2022foraging} is that it makes little attempt to the predict which item will be selected first.
-In this section we aim to improve this by modelling participant bias/preference in their choice of initial target selection.
-Following \cite{clarke_tatler2014, clarke2017} we fit truncated Gaussian distributions to the $(x,y)$ coordinates of the initial target selections
+One weakness of the foraging model by \cite{clarke2022foraging} is that it makes little attempt to predict which item will be selected first.
+In this section we aim to improve this by modelling participant bias (or preference) in their choice of initial target selection.
+Following \cite{clarke_tatler2014, clarke2017} we fit truncated Gaussian distributions to the $(x,y)$ coordinates of the initial target selections.
 
 Figure \ref{fig:qjep_init_sel_hex} shows the distribution of the locations of first target selections.
-We can see that unlike the central bias in fixations during scene viewing, the distribution of initial target locations appear to be bimodal: while most targets are positioned in the top left hand corner <CHECK MATLAB CODE!!!> there is a second smaller distribution of central target selections.
+We can see that unlike the central bias in fixations during scene viewing, the distribution of initial target locations appear to be bimodal: while most targets are positioned in the top left hand corner, there is a second smaller distribution of central target selections.
 This appears to be due to different participants choosing to utilise different strategies rather than within-subject variation.
-However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see Supplementary Material)
+However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see \textit{Supplementary Material}).
 
@@
 \subsection{Multi-level Modelling Results}
-We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnote{Full details of the analysis can be found in the supplementary materials}.
+We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnote{Full details of the analysis can be found in the \textit{Supplementary Materials}}.
 
@@
 \subsection{Mixture Modelling}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=12 cm]{Figures/init_sel2_mdl.pdf}
+\caption{Posterior fits for (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection.
+Each line represents a different participant.
+(\textit{right}) shows the correlation between participant's mean $x$ and $y$ coordinates.
+The box shows the extent of the stimulus.}
+\label{fig:qjep_init2_sel_mdl}
+\end{figure}
 

### 2022-06-07 Analysis/index.Rmd
updating figures

--- 2022-06-07 Analysis/index.Rmd
@@
   facet_wrap(~dim) + 
-  theme(legend.position = "none") -> plt_x
+  theme(legend.position = "none")  + 
+    scale_y_continuous("likelihood") -> plt_x
 
@@
   facet_wrap(~dim) + 
-  theme(legend.position = "none") +
-  scale_x_continuous("y") -> plt_y
+  theme(legend.position = "none",
+        axis.title.y = element_blank()) +
+  scale_x_continuous("y") + 
+    scale_y_continuous("likelihood") -> plt_y
 
 gather_draws(m, lambda[observer]) %>%
-  ggplot(aes(.value, group = observer)) + 
-  geom_density(alpha = 0.25, fill = "grey") -> plt_lambdas
+  median_hdci(.value) %>%
+  arrange(.value) %>%
+  mutate(observer = factor(observer, levels = observer)) %>%
+  ggplot(aes(observer, .value, ymin = .lower, ymax = .upper)) + 
+  geom_errorbar() +
+  scale_y_continuous("lambda") + 
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) -> plt_lambdas
 
-(plt_x + plt_y) / plt_lambdas
+(plt_x + plt_y) + plt_lambdas
+
+ggsave("../Figures/init_sel2_mdl.pdf", width = 10, height = 3.5)
 ```

### 2022-06-07 manuscript.tex
Updates from Overleaf

@@
 % Authors, for the paper (add full first names)
-\Author{Alasdair Clarke $^{1}$\orcidA{}, Amelia Hunt $^{2}$\orcidB{} and Anna Hughes\orcidC{} $^{1,}$*}
+\Author{Alasdair D.F. Clarke $^{1}$\orcidA{}, Amelia Hunt $^{2}$\orcidB{} and Anna E. Hughes\orcidC{} $^{1,}$*}
 
@@
 \caption{Hexagonal heatmaps showing the two-dimensional distribution of the location of initial target selections.
-Grey areas indicate cells with a count of 0/ (\textit{left}) shows the distribution over all initial target selections while (\textit{right}) shows the distribution of each participant's median initial selection.
+Grey areas indicate cells with a count of 0.
+(\textit{left}) shows the distribution over all initial target selections while (\textit{right}) shows the distribution of each participant's median initial selection.
 }
@@
 \subsection{Multi-level Modelling Results}
-We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnote{Full details of the analysis can be found in the \textit{Supplementary Materials}}.
+We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnote{Full details of the analysis can be found in the \textit{Supplementary Materials}.}
 
@@
 \includegraphics[width=12 cm]{Figures/init_sel_mdl.pdf}
-\caption{Posterior fits for (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection.
-Each line represents a different participant.
-(\textit{right}) shows the correlation between participant's mean $x$ and $y$ coordinates.
-The box shows the extent of the stimulus.}
+\caption{Posterior fits for (\textit{left}) horizontal and (\textit{right}) vertical locations of the initial target selection. Each line represents a different participant.}
 \label{fig:qjep_init_sel_mdl}
@@
 \includegraphics[width=12 cm]{Figures/init_sel2_mdl.pdf}
-\caption{Posterior fits for (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection.
-Each line represents a different participant.
-(\textit{right}) shows the correlation between participant's mean $x$ and $y$ coordinates.
-The box shows the extent of the stimulus.}
+\caption{Posterior fits for the (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection.
+(\textit{right}) shows the mixing parameters for each participant, with the error bar indicating the $95\%$  HDPI.}
 \label{fig:qjep_init2_sel_mdl}
@@
 
-The posterior predictions from the two models are compared in Figure \ref{fig:qjep_init_sel_pred}
+The posterior predictions from the two models are compared in Figure \ref{fig:qjep_init_sel_pred}.
 
@@
 
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
+To what extent does our model predict behaviour on a trial-by-trial basis?
+Surprisingly well - this is a difficult task, in some cases the model can be over 80\% accurate.
+Are there any examples of similar models that can make such fine grained predictions?
 
-Remaining open questions
+What mistakes does the model make? 
+Runner up item weights are a bit too low - this probably suggests a 'peakier' distribution for real human foragers, with only a few targets seriously considered, and everything else being approximately zero weighted?
+Better at feature search compared to conjunction search, better at people with a stronger proximity bias - people who do unpredictable things are unpredictable?
+Does this suggest that some of our model parameters are less useful at predicting what occurs on a trial-by-trial basis (although they might be useful in aggregate).
+
+To a large extent, initial item selection strategy seems to be stable - either you're someone who starts in the corner, or in the centre of the screen.
+This makes predicting where people start actually also quite accurate.
+Fancy multi-level model not really any better at predicting this than a mixture model.
+But this probably depends on the exact nature of the task (i.e.
+central bias not seen in \citep{kristjansson2014}, presumably because this was carried out on an iPad - affects people's behaviour in some way we don't really understand?)
+
+Remaining open questions?
+Incorporating other biases into initial target selection, e.g. $pA$?
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
-and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
-All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.}
+\authorcontributions{Conceptualization, A.D.F.C., A.H.
+and A.E.H.; methodology, A.D.F.C.; software, A.D.F.C.; formal analysis, A.D.F.C.; data curation, A.D.F.C., and A.E.H.; writing---original draft preparation, A.D.F.C.; writing---review and editing, A.H.
+and A.E.H.; visualization, A.D.F.C.
+and A.E.H.; funding acquisition, A.D.F.C.
+and A.H.
+All authors have read and agreed to the published version of the manuscript.}
 
-\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''.
-Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}
+\funding{This research was funded by NAME OF FUNDER grant number XXX.}
 
-\institutionalreview{In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals.
-Please note that the Editorial Office might ask you for further information.
-Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals.
-You might also choose to exclude this statement if the study did not involve humans or animals.}
+\institutionalreview{Not applicable (secondary data analysis only).}
 
-\informedconsent{Any research article describing a study involving humans should contain this statement.
-Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.
-You might also choose to exclude this statement if the study did not involve humans.
+\informedconsent{Not applicable (secondary data analysis only).}
 
-Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves).
-Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}
-
-\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study.
-Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}.
-You might choose to exclude this statement if the study did not report any data.}
+\dataavailability{Data supporting reported results can be found on Github at XXX.
+The datasets analysed in this study can be found at \url{https://osf.io/y6qbv/} and \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0100752}.}
 
@@
 
-\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Only for journal Encyclopedia
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-\abbreviations{Abbreviations}{
-The following abbreviations are used in this manuscript:\\
-
-\noindent 
-\begin{tabular}{@{}ll}
-MDPI & Multidisciplinary Digital Publishing Institute\\
-DOAJ & Directory of open access journals\\
-TLA & Three letter acronym\\
-LD & Linear dichroism
-\end{tabular}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
-\appendixstart
-\appendix
-\section[\appendixname~\thesection]{}
-\subsection[\appendixname~\thesubsection]{}
-The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
-
-\begin{table}[H] 
-\caption{This is a table caption.\label{tab5}}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
-\bottomrule
-\end{tabularx}
-\end{table}
-
-\section[\appendixname~\thesection]{}
-All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
+\conflictsofinterest{The authors declare no conflict of interest.}
 

### 2022-06-09 Analysis/index.Rmd
new graph for init sel

@@
 
-create_post_plot("x") + create_post_plot("y") 
+am %>% mutate(mu = a/(a+b)) %>%
+  pivot_wider(observer, names_from = "dim", values_from = "mu") %>%
+  ggplot(aes(x, y)) + geom_point(alpha = 0.5) +
+  scale_x_continuous("mean x") + 
+  scale_y_continuous("mean y") -> plt_mu
+
+create_post_plot("x") + create_post_plot("y") + plt_mu
 ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)

### 2022-06-09 manuscript.tex
Updates from Overleaf

@@
 In this section we aim to improve this by modelling participant bias (or preference) in their choice of initial target selection.
-Following \cite{clarke_tatler2014, clarke2017} we fit truncated Gaussian distributions to the $(x,y)$ coordinates of the initial target selections.
+Our approach is inspired by previous work on the central bias in scene viewing \cite{clarke_tatler2014, clarke2017}.
+These studies characterised fit truncated Gaussian distributions to the  $(x,y)$ coordinates of fixation locations.
+Here we will do similar, and fit beta distributions\footnote{We use beta distributions here as ADFC couldn't work out the syntax for specifying a mixture model using truncated Gaussians in Stan.
+But, in hindsight, beta distributions are probably a better choice anyway!} to locations of the initial target selections in the visual foraging task.
 
@@
 However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see \textit{Supplementary Material}).
+We fit two dwill try two different modelling approaches (multi-level and mixture) to
 
@@
 \subsection{Multi-level Modelling Results}
-We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnote{Full details of the analysis can be found in the \textit{Supplementary Materials}.}
+
+We first consider a multi-level model in which we fit beta distributions to the $x$ and $y$ coordinates of each participant's initial target selections\footnote{Full details of the analysis can be found in the \textit{Supplementary Materials}.}:
+
+\begin{equation}
+    x_i \sim Beta(a_{x,i}, b_{x,i})
+    \label{eq:beta1x}
+\end{equation}
+\begin{equation}
+    y_i \sim Beta(a_{y,i}, b_{y,i})
+    \label{eq:beta1y}
+\end{equation}
+
+The results are shown in Figure \ref{fig:qjep_init_sel_mdl} and we can clearly see that most participants either have a strong bias to $x=0$ and $y=0$, or a more diffuse central bias.
 
@@
 
+While the multi-level model outlined above appears to offer a good fit for the between-subject differences in initial target selection location, it comes at the expense of requiring four parameters per participant (= 290 for the 58 participants in our dataset).
+Given that the majority of our participants appear to be following one of two distinct strategies, we can potentially simplify our model by using a two-component mixture model:
+
+\begin{equation}
+    x_i \sim \lambda_i \times Beta(a_{x,1}, b_{x,1}) + (1-\lambda_i) \times Beta(a_{x,2}, b_{x,2})
+    \label{eq:beta2x}
+\end{equation}
+\begin{equation}
+    y_i \sim \lambda_i \times Beta(a_{y,1}, b_{y,1}) + (1-\lambda_i) \times Beta(a_{y,2}, b_{y,2})
+    \label{eq:beta2y}
+\end{equation}
+
+This reduces the number of parameters to eight (to specify the two Beta distributions) and then one $\lambda$ value per participant (= 66 in our dataset).
+While the formulae in Equations \ref{eq:beta2x} and \ref{eq:beta2y} appear more complex than those in Equations \ref{eq:beta1x} and \ref{eq:beta1y}, the model requires less than a quarter as many free parameters!
+
+The model fit is shown in Figure \ref{fig:qjep_init2_sel_mdl}.
+We can see that the two components identified by the model clearly correspond to the top corner and diffuse-central strategies discussed above.
+We can also see from the lambda values that our participants take on a range of different mixtures between the two.
+
 \begin{figure}[H]
 \centering
-\includegraphics[width=12 cm]{Figures/init_sel2_mdl.pdf}
+\includegraphics[width=\textwidth]{Figures/init_sel2_mdl.pdf}
 \caption{Posterior fits for the (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection.
@@
 \includegraphics[width=12 cm]{Figures/qjep_init_sel_preds.pdf}
-\caption{}
+\caption{(\textit{Top}): a count of initial weight values predicted from both methods (mixture and multi-level).
+(\textit{Bottom left}): the proportion of times the first selection was correct for both methods.
+(\textit{Bottom left}): as lambda (the model parameter underlying initial weight) increases, accuracy increases i.e.
+the model is more accurate for the cases where participants are selecting a corner as their initial target selection.}
 \label{fig:qjep_init_sel_pred}

### 2022-06-09 Analysis/index.Rmd
Figure editing

@@
 col3 = c("#d04e00", "#ddc000","#34b6c6",  "#79ad41", "#4063a3")
+col2 = c("#d04e00", "#34b6c6")
 
@@
   geom_histogram(binwidth = 1/80, position = "identity", alpha = 0.5) +
-  geom_vline(xintercept = 1/40, linetype = 2)  -> plt1
+  geom_vline(xintercept = 1/40, linetype = 2) +
+  scale_fill_manual(values = col2)-> plt1
 
@@
   summarise(acc = mean(max_item == 1), .groups = "drop") %>%
-  ggplot(aes(y = acc, fill = method)) + geom_boxplot() + 
+  ggplot(aes(y = acc, fill = method)) + geom_boxplot(alpha = 0.5) + 
   geom_hline(yintercept = 1/40, linetype = 2) + 
   scale_y_continuous("Prop. trials first sel. correct") +
-  theme(legend.position = "none") -> plt2
+  theme(legend.position = "none") +  
+  scale_fill_manual(values = col2) -> plt2
 

### 2022-06-09 manuscript.tex

@@
 \includegraphics[width=12 cm]{Figures/init_sel_mdl.pdf}
-\caption{Posterior fits for (\textit{left}) horizontal and (\textit{right}) vertical locations of the initial target selection. Each line represents a different participant.}
+\caption{Posterior fits for (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection.
+Each line represents a different participant.
+(\textit{right) A scatter plot showing the $x$ and $y$ posterior means for each participant.}
 \label{fig:qjep_init_sel_mdl}
@@
 
-The posterior predictions from the two models are compared in Figure \ref{fig:qjep_init_sel_pred}.
+To compare the two approaches, we assess how well they fit the empirical data: we can use the fitted distributions to calculate the weight assigned to the selected target by each method for each trial in our dataset (Figure \ref{fig:qjep_init_sel_pred}).
+We can see that both models give a similar distribution of target weights and accuracies.
+Overall, both methods  select the correct target in around half of the trials.
+Interesting, as above, there is considerable variation between participants, with participants who favour the top-left corner being easier to predict.
 

### 2022-06-10 Analysis/index.Rmd
some scrappy stuff on timing

@@
 summary(lm(median_rt ~ accuracy*condition, data = drt))
+
+drt <- filter(d, found == 40)
+
+```
+
+```{r}
+# try doing per trial
+a %>% select(observer, condition, trial, found, selected_max) %>%
+  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
+  group_by(observer, condition, trial) %>%
+  summarise(time_taken = max(RT),
+            acc = mean(selected_max, na.rm = T), 
+            .groups = "drop") %>%
+  filter(time_taken < 60)  ->timedat
+
+%>%
+  ggplot(aes(time_taken, acc, colour = condition)) + 
+  geom_jitter(alpha = 0.2, height = 0.005, width = 0) +
+  geom_smooth(method = "lm") + 
+  facet_wrap(~condition)
+
+library(brms)
+
+my_model <- brm(acc ~ time_taken:condition + (1|observer), timedat)
+
+a %>% select(observer, condition, trial, found, selected_max) %>%
+  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
+  arrange(observer, condition, trial, found) %>%
+  mutate(
+    RTd = RT - lag(RT),
+    RTd = if_else(found == 1, 0, RTd)) %>%
+  filter(RTd < 2, is.finite(RTd)) %>%
+  mutate(
+    time_bin = cut(RTd,breaks = seq(0, 2, 0.25), labels = FALSE)) %>%
+  group_by(observer, condition, time_bin) %>%
+  summarise(acc = mean(selected_max)) %>%
+  ggplot(aes(time_bin, acc, group = observer)) +
+  geom_path(alpha = 0.2) +
+  geom_smooth(se= F, alpha = 0.1, method = lm) + 
+  facet_grid(found~condition)
 

### 2022-06-10 Analysis/index.Rmd
working on some timing stuff

--- 2022-06-09 Analysis/index.Rmd
@@
 summary(lm(median_rt ~ accuracy*condition, data = drt))
+
+drt <- filter(d, found == 40)
+
+```
+
+```{r}
+# try doing per trial
+a %>% select(observer, condition, trial, found, selected_max) %>%
+  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
+  group_by(observer, condition, trial) %>%
+  summarise(time_taken = max(RT),
+            acc = mean(selected_max, na.rm = T), 
+            .groups = "drop") %>%
+  filter(time_taken < 60)  ->timedat
+
+timedat %>%
+  ggplot(aes(time_taken, acc, colour = condition)) + 
+  geom_jitter(alpha = 0.2, height = 0.005, width = 0) +
+  geom_smooth(method = "lm") + 
+  facet_wrap(~condition)
+
+library(brms)
+
+my_model <- brm(acc ~ time_taken:condition + (1|observer), timedat)
+
+a %>% select(observer, condition, trial, found, selected_max) %>%
+  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
+  arrange(observer, condition, trial, found) %>%
+  mutate(
+    RTd = log(RT - lag(RT)),
+    RTd = if_else(found == 1, 0, RTd)) %>%
+  filter(RTd < 2, is.finite(RTd)) %>%
+  mutate(
+    time_bin = cut(RTd,breaks = 50, labels = FALSE)) %>%
+  group_by(observer, condition, time_bin) %>%
+  summarise(acc = mean(selected_max)) %>%
+  ggplot(aes(time_bin, acc, group = observer)) +
+  geom_path(alpha = 0.2) +
+  geom_smooth(se= F, alpha = 0.1, method = lm) + 
+  facet_grid(found~condition)
 

### 2022-06-30 Analysis/index.Rmd
Trial level

@@
 
+# Trial level
+
+```{r}
+
+a %>% group_by(condition, observer, trial) %>%
+  summarise(meanb = mean(b),
+            prop_best = mean(selected_max), .groups = "drop") -> a_trl
+
+ggplot(a_trl, aes(trial, meanb, group = observer)) + geom_jitter(alpha = 0.25) + 
+  geom_path(alpha = 0.1) + facet_wrap(~condition) +
+  geom_smooth(method = "lm", group = 1)
+
+```
+
 # Path Length Analysis

### 2022-07-04 Analysis/index.Rmd
some edits

@@
 
-library(brms)
-
-my_model <- brm(acc ~ time_taken:condition + (1|observer), timedat)
+# library(brms)
+# 
+# my_model <- brm(acc ~ time_taken:condition + (1|observer), timedat)
 
@@
   mutate(
-    RTd = log(RT - lag(RT)),
+    RTd = RT - lag(RT),
     RTd = if_else(found == 1, 0, RTd)) %>%
@@
   geom_smooth(se= F, alpha = 0.1, method = lm) + 
-  facet_grid(found~condition)
+  facet_grid(~condition)
 

### 2022-07-04 Analysis/index.Rmd
rerunning

@@
             .groups = "drop") %>%
-  filter(time_taken < 60)  ->timedat
+  filter(time_taken < 60) -> timedat
 

### 2022-07-04 Analysis/index.Rmd
timing trial model

--- 2022-07-04 Analysis/index.Rmd
@@
 library(truncnorm)
+library(modelr)
+library(brms)
 ```
@@
 
-## Are more predictable people faster at the task?
+## The relationship between time and model accuracy
 
-```{r}
-drt <- filter(d, found == 40) %>% group_by(observer, condition) %>%
-  summarise(median_rt = median(RT), .groups = "drop") %>% 
-  full_join(dm, by = c("observer", "condition"))
+### Faster people are more predictable
 
-ggplot(drt, aes(accuracy, median_rt, colour = condition)) +
-         geom_point(alpha = 0.5) + 
-  geom_smooth(method = "lm")
+Is this worth doing?
 
-summary(lm(median_rt ~ accuracy*condition, data = drt))
+### Shorter trials are more predictable
 
-drt <- filter(d, found == 40)
-
-```
-
-```{r}
-# try doing per trial
+```{r fig.cap="The relationship between the time taken to complete a trial and how predictible it is.
+Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model.
+The lines give posterior samples from each indivdiaul observer."}
 a %>% select(observer, condition, trial, found, selected_max) %>%
@@
             .groups = "drop") %>%
-  filter(time_taken < 60)  ->timedat
+  filter(time_taken < 60) %>%
+  mutate(time_taken_s = as.numeric(scale(log(time_taken)))) -> timedat
 
-timedat %>%
-  ggplot(aes(time_taken, acc, colour = condition)) + 
-  geom_jitter(alpha = 0.2, height = 0.005, width = 0) +
-  geom_smooth(method = "lm") + 
-  facet_wrap(~condition)
+write_csv(timedat, "scratch/time_per_trial.csv")
 
-# library(brms)
+m <- readRDS("scratch/time_model_acc_model.rds")
+
+fixef(m) %>% knitr::kable()
+
+```
+
+```{r fig.cap="The relationship between the time taken to complete a trial and how predictible it is.
+Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model.
+The lines give posterior samples from each indivdiaul observer."}
+timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5)) %>%
+  add_epred_draws(m, re_formula = NA, ndraws = 100) %>%
+  ggplot(aes(time_taken_s, fill = condition)) + 
+  stat_lineribbon(aes(y = .epred), alpha = 0.5, .width = c(0.53, 0.97)) +
+  geom_jitter(data = timedat, aes(y = acc, colour = condition), 
+              alpha = 0.05, width = 0, height = 0.005, colour = "black") +
+  scale_x_continuous("scaled log response time (log seconds)") + 
+  scale_y_continuous("model accuracy")  + 
+  scale_colour_discrete(guide = "none") +
+  coord_cartesian(ylim = c(0.4, 0.9)) +
+  guides(fill = guide_legend(reverse = TRUE)) +
+  facet_wrap(~ condition) -> plt
+
+timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5), observer) %>%
+  add_epred_draws(m, re_formula = NULL, ndraws = 1) -> d_pred
+
+plt + geom_path(data  = d_pred,
+                aes(y = .epred, 
+                    group = interaction(condition, observer)),
+                alpha = 0.25)
+
+```
+
+```{r}
+
 # 

### 2022-07-04 Analysis/scripts/fit_time_model.R

@@ -1,0 +1,22 @@
+library(tidyverse)
+library(brms)
+library(tidybayes)
+library(modelr)
+
+options(mc.cores = 4)
+
+d <- read_csv("../scratch/time_per_trial.csv") 
+
+my_priors <- c(prior(normal(0.6, 0.1), class = "b", coef = "conditionfeature"),
+               prior(normal(0.6, 0.1), class = "b", coef = "conditionconjunction"),
+               prior(normal(0.0, 0.1), class = "b", coef = "conditionfeature:time_taken_s"),
+               prior(normal(0.0, 0.1), class = "b", coef = "conditionconjunction:time_taken_s"))
+
+m <- brm(acc ~ 0 + condition + time_taken_s:condition + 
+           (0 + condition +  time_taken_s:condition|observer),
+         data = d,
+         family = "normal",
+         prior = my_priors)
+
+saveRDS(m, "../scratch/time_model_acc_model.rds")
+

### 2022-07-07 manuscript.tex

@@
 In many cases, the pattern of foraging behaviour has also been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run.
-However, we have recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022}.
-By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully re-analyse data from a number of open access datasets \cite{kristjansson2014, thornton2020, clarke2022, tagu2020}.
+However, we have recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022foraging}.
+By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully re-analyse data from a number of open access datasets \cite{kristjansson2014, thornton2020, clarke2022, tagu_kristjansson_2021}.
 
@@
 However, interestingly, we find that this variability can be explained by our model parameters: nearly all of the differences between people, and between feature and conjunction conditions, can be explained by the $bP$ parameter, which is our proximity bias.
-The model is doing a better job with participants who show a stronger proximity bias.
+The model is doing a better job with participants who show a stronger proximity bias (see \textit{Supplementary Materials} for more details).
 
@@
 However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see \textit{Supplementary Material}).
-We fit two dwill try two different modelling approaches (multi-level and mixture) to
+We try two different modelling approaches (multi-level and mixture) to assess whether the less complex mixture model is able to account for the patterns of starting positions seen.
 
@@
 Each line represents a different participant.
-(\textit{right) A scatter plot showing the $x$ and $y$ posterior means for each participant.}
+(\textit{right}) A scatter plot showing the $x$ and $y$ posterior means for each participant.}
 \label{fig:qjep_init_sel_mdl}
@@
 Overall, both methods  select the correct target in around half of the trials.
-Interesting, as above, there is considerable variation between participants, with participants who favour the top-left corner being easier to predict.
+Interestingly, as above, there is considerable variation between participants, with participants who favour the top-left corner being easier to predict.
 
@@
 
-To what extent does our model predict behaviour on a trial-by-trial basis?
-Surprisingly well - this is a difficult task, in some cases the model can be over 80\% accurate.
-Are there any examples of similar models that can make such fine grained predictions?
+In our original model of visual foraging \citep{clarke2022foraging}, we were able to robustly measure aggregate parameters that underlie behaviour, at both an overall mean level across an experiment, and at the level of individual participants.
+In the current manuscript, we asked a more difficult question: could this model make target-by-target predictions, guessing which target would be picked next on any given trial?
+Despite this being a relatively difficult task, we found that our model was in some cases over 80\% accurate, demonstrating that at least in some cases, participants' behaviour in this task is remarkably predictable.
 
-What mistakes does the model make? 
-Runner up item weights are a bit too low - this probably suggests a 'peakier' distribution for real human foragers, with only a few targets seriously considered, and everything else being approximately zero weighted?
-Better at feature search compared to conjunction search, better at people with a stronger proximity bias - people who do unpredictable things are unpredictable?
-Does this suggest that some of our model parameters are less useful at predicting what occurs on a trial-by-trial basis (although they might be useful in aggregate).
+A benefit of our approach is that it is relatively easy to interrogate the model to try to understand why prediction accuracy is higher for some participants and trials than others.
+The model is generally better at feature search compared to conjunction search, and also seems to be better at predicting participants with a stronger proximity bias.
+The model also seems to assign more weight to 'runner-up' items than real humans do, perhaps suggesting a 'peakier' choice distribution for real foragers, with only a few targets seriously considered, and everything else being approximately zero weighted.
 
-To a large extent, initial item selection strategy seems to be stable - either you're someone who starts in the corner, or in the centre of the screen.
-This makes predicting where people start actually also quite accurate.
-Fancy multi-level model not really any better at predicting this than a mixture model.
-But this probably depends on the exact nature of the task (i.e.
-central bias not seen in \citep{kristjansson2014}, presumably because this was carried out on an iPad - affects people's behaviour in some way we don't really understand?)
+However, we can also delve deeper into exploratory hypotheses about other factors that might influence predictability.
+One suggestion is that the people who our model is able to predict are in some way the most 'optimal'.
+If this is the case, we might expect that model predictability should correlate with how good people are at the task, although we do not find any evidence that model accuracy correlates with reaction time on a by-participant or by-trial basis (see \textit{Supplementary Materials}).
+This may be due to the fact that this task was not time-limited, and instead participants were encouraged to be as accurate as possible (in fact, the trial restarted if the participant clicked on a non-target \citep{clarke2022}).
+However, there is some evidence that on a target-by-target basis, faster moves from one target to the next are more easily predicted by the model (see \textit{Supplementary Materials}).
+This likely is linked to the fact that our model is better at predicting participants with a stronger proximity bias, as targets that are closer to the previous target are also likely to be selected more quickly.
+Intuitively, it makes sense that the model struggles to make predictions when a participant has exhausted a local patch and may need to make a bigger jump to a more distant area to carry on collecting targets, as there may be multiple candidates and distance may no longer be such a good predictor (for example, people may choose to move to the next most densely populated patch).
 
-Remaining open questions?
-Incorporating other biases into initial target selection, e.g. $pA$?
+There has been some previous work on within-trial behaviour in the context of foraging.
+For example, \citep{tagu2020} found that inter-target times vary across a trial (with targets selected later in the trial being slower) and inter-target distances also vary (with targets selected later in the trial having greater inter-target distances).
+Similarly, \citep{thornton2022foraging} showed that switches between target categories can be characterised by a change in foraging 'tempo', and if participants are forced to forage at a particular speed, by asking them to synchronise with an auditory signal, higher tempos led to a systematic decrease in the probability of participants switching between target categories.
+In the current version of the model, we do not consider time explicitly (although distance is likely to be highly correlated with time in this task).
+However, it would be possible to extend the model to incorporate timing information, and this may help to improve the target-by-target predictions.
+
+From inspection of Figure \ref{fig:qjep_paths}, we noticed that in some cases, participants may be using a type of local path minimisation procedure, selecting a further away target in order to minimise overall path length, which the model does not always seem to predict.
+Could this help to explain some of the mistakes the model makes?
+Overall, the model doesn't seem to make substantially longer paths through the items than the human participants (see \textit{Supplementary Materials}).
+However, there is a relationship between model accuracy and the proportion of times that participants select paths shorter than the model: as model accuracy increases, people seem to be more likely to have paths shorter than the model predicts.
+This seems to suggest that path minimisation is not a good explanation for the targets our model is failing to capture, and instead the people that are difficult to predict are taking longer paths than the model thinks they should take.
+
+Our exploratory analyses seem to hint at the idea that the people who are difficult for the model to predict are those who do not behave in a manner that optimises path length.
+It could be that these participants are simply unpredictable, and do not behave in a consistent manner on a target-by-target basis, making it difficult for a model to predict their behaviour at this level of granularity.
+However, it is possible that there are other factors that we have not taken into account that could further help explain these discrepancies.
+For example, it is possible that relatively unpredictable participants use multiple rules and switch between them in ways that we are not currently capturing in the model.
+Some participants may also lose track of where they are more frequently (perhaps due to attentional lapses) and thus may show foraging patterns that are predictable apart from unpredictable discontinuities, which again may not be easy to model.
+Finally, the displays had artificial discontinuities (i.e.
+screen edges) which may lead to different behaviour in different participants: some may carry out the task as if they are reading, reaching the right hand edge and then swinging back to the left, whereas others may 'bounce' off an edge they have just reached.
+Our model may well be able to predict the latter, but could struggle with the former behaviour.
+
+To a large extent, initial item selection strategy seems to be stable within a participant, with people either starting in the corner or the centre of the screen.
+Our model is therefore also relatively accurate for selecting the initial target, selecting the correct target in around half of the trials (with a mixture model performing similarly to a multi-level model with many more parameters).
+Participants who prefer the top left corner were easiest to predict, probably because these participants formed the majority group in this experiment.
+Our results are congruent with \citep{kristjansson2022moving}, who found a bottom left bias in a 3D environment They suggest this may be an advantageous strategy because it allows your foraging to be more organised (e.g.
+in an 'S-shape', as has been found in real world search tasks \citep{riggs2017importance}).
+The smaller group of participants who prefer to start in the centre of the screen may be displaying similar behaviour to the well-known central bias in eye movements \citep{tatler2007central, tseng2009quantifying, clarke2014deriving} However, it is worth noting that these findings probably depend strongly on the context of the task.
+For example, there was no obvious central bias subgroup in \citep{kristjansson2014}, possibly reflecting the fact that this experiment was carried out on an iPad, compared to the computer screen and mouse used in \citep{clarke2022}.
+One challenge for future modelling work is to what extent we should try to account for these types of task-specific details: by incorporating them, we can generate better predictions for the experiment we are currently modelling, but perhaps at the cost of generalisability to other paradigms.
+
+One of the key benefits of computational models is that they allow us to rigorously test how well we are able to predict behaviour, and can provide insights into what factors we are not capturing that may have important influences on how participants complete a task.
+We have demonstrated that our foraging model \cite{clarke2022foraging} is not only able to predict behaviour on aggregate, but can also make reasonable predictions at the target-by-target level.
+It is particularly good if a participant has a strong proximity bias, and on 'feature' trials where participants are normally switching between target types fairly frequently.
+It is also good at predicting where participants will start on a trial.
+The model finds it more difficult to predict 'discontinuous' jumps, which could be caused by a range of factors: a more difficult foraging task (e.g.
+conjunction searches), local path length minimisation, inattention, or aspects of the physical search space (e.g.
+edges of the screen).
+However, it would be possible to extend the model to incorporate these factors e.g.
+by incorporating a heuristic that would allow for local path minimisation, or introducing time as a predictor in the model.
+Our findings also suggest possible future directions for empirical work, such as evaluating the effect of inattention on foraging behaviour, or how the foraging targets are organised in space.
+We suggest that computational modelling is a powerful tool for helping us to understand behaviour, both by incorporating previous research into a shared framework, and by making testable predictions for future work.
 

### 2022-07-08 manuscript.tex
A few minor edits

@@
 Different aspects of foraging behaviour, such as the search image and the search path, clearly interact with one another, but most research has tried to understand them separately.
-In many cases, the pattern of foraging behaviour has also been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run.
-However, we have recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022foraging}.
+In many cases, the pattern of foraging behaviour has been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run.
+These summary statistics can provide a broad view of switching behaviour, but they can also be biased by the spatial distribution of target types, and by a forager's preference for one target or another.
+To address the need for a more precise set of measurements, we recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022foraging}.
 By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully re-analyse data from a number of open access datasets \cite{kristjansson2014, thornton2020, clarke2022, tagu_kristjansson_2021}.
@@
 conjunction vs.
-feature search differences \cite{kristjansson2014} or the influence of high value targets compared to low value targets \cite{tagu2020}), we did not originally investigate to what extent our model was able to predict target-by-target behaviour in any given trial.
+feature search differences \cite{kristjansson2014} or the influence of high value targets compared to low value targets \cite{tagu2020}), we did not originally investigate to what extent our model was able to predict target-by-target behaviour within any given trial.
 However, as the model is based on target-by-target level information, it is possible for us to use this information to ask: to what extent does our model predict foraging behaviour within a trial?
@@
 
-We will a previously published dataset to explore how well our model can account for trial-level behaviour.
-We will start with the visual foraging data from \cite{clarke2022}.
+We use a previously published dataset to explore how well our model can account for trial-level behaviour: the visual foraging data from \cite{clarke2022}.
 This is an attractive dataset for our needs as it is very close to the ``classic'' visual foraging paradigm \citep{kristjansson2014}, yet with a substantially larger sample of participants.
-(The key difference between paradigms is that \cite{kristjansson2014} used an ipad and finger foraging, while \cite{clarke2022} used a desktop computer and mouse clicks).
-Furthermore, we have already demonstrated that our model can capture individual differences in foraging behaviour \citep{clarke2022}.
-As such, we will only give a brief overview of the data here and refer the reader to these earlier papers for a more details.
+(The key difference between paradigms is that \cite{kristjansson2014} used an ipad and finger foraging, while \cite{clarke2022} used a desktop computer and mouse clicks.) Furthermore, we have already demonstrated that our model can capture individual differences in foraging behaviour \citep{clarke2022}.
+As such, we will only give a brief overview of the data here and refer the reader to these earlier papers for more details.
 
@@
 
-where $t_i = 1$ if item $i$ is of class $A$ and 0 otherwise, $m(t_i, t_{i-1}) =1$ if item $i$ is the same class as the previously selected item.
+where $t_i = 1$ if item $i$ is of class $A$ and 0 otherwise, and  $m(t_i, t_{i-1}) =1$ if item $i$ is the same class as the previously selected item.
 $\rho_d$ and $\rho_{\theta}$ measure proximity and the effect of direction:
@@
 As can be seen in Figure \ref{fig:cal}, the model is putting somewhere between 25\% and 75\% of the weight on the target that is selected next, easily outperforming a chance $1/n$ baseline.
-We can also see  that the model is well calibrated in that the probabilities assigned to the largest target manage to capture how well often that target is actually selected.
+We can also see  that the model is well calibrated in that the probabilities assigned to the largest target manage to capture how often that target is actually selected.
 However, we can see a decrease in accuracy when it comes to how often ``runner-up`` candidate items are selected as our model appears to systematically undervalue these (presumably by putting too much of the probabilistic weight on low chance items).
@@
 The $x$-axis gives the largest weight assigned by the model while the $y$-axis shows how often that target was actually selected by a human participant.
+The dashed line here and in the right plot is the identity line.
 (\textit{right}) This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model.}
@@
 Our approach is inspired by previous work on the central bias in scene viewing \cite{clarke_tatler2014, clarke2017}.
-These studies characterised fit truncated Gaussian distributions to the  $(x,y)$ coordinates of fixation locations.
+These studies fit truncated Gaussian distributions to the  $(x,y)$ coordinates of fixation locations.
 Here we will do similar, and fit beta distributions\footnote{We use beta distributions here as ADFC couldn't work out the syntax for specifying a mixture model using truncated Gaussians in Stan.
@@
 However, there is a relationship between model accuracy and the proportion of times that participants select paths shorter than the model: as model accuracy increases, people seem to be more likely to have paths shorter than the model predicts.
-This seems to suggest that path minimisation is not a good explanation for the targets our model is failing to capture, and instead the people that are difficult to predict are taking longer paths than the model thinks they should take.
+This seems to suggest that path minimisation is not a good explanation for the participants our model is failing to capture, and instead the people that are difficult to predict are taking longer paths than the model thinks they should take.
 
@@
 However, it is possible that there are other factors that we have not taken into account that could further help explain these discrepancies.
-For example, it is possible that relatively unpredictable participants use multiple rules and switch between them in ways that we are not currently capturing in the model.
+For example, it is possible that relatively unpredictable participants use multiple rules and switch between them in ways that we are not currently captured in the model.
 Some participants may also lose track of where they are more frequently (perhaps due to attentional lapses) and thus may show foraging patterns that are predictable apart from unpredictable discontinuities, which again may not be easy to model.
@@
 One of the key benefits of computational models is that they allow us to rigorously test how well we are able to predict behaviour, and can provide insights into what factors we are not capturing that may have important influences on how participants complete a task.
-We have demonstrated that our foraging model \cite{clarke2022foraging} is not only able to predict behaviour on aggregate, but can also make reasonable predictions at the target-by-target level.
+We have demonstrated that our foraging model \cite{clarke2022foraging} is not only able to predict behaviour in aggregate, but can also make reasonable predictions at the target-by-target level.
 It is particularly good if a participant has a strong proximity bias, and on 'feature' trials where participants are normally switching between target types fairly frequently.

### 2022-07-19 Analysis/index.Rmd
plot edits
saving path length figure

@@
 # set ggplot2 options
-theme_set(ggthemes::theme_tufte() + theme(plot.background = element_rect(fill = "#fffff8", colour = "#fffff8")))
+theme_set(ggthemes::theme_tufte() + 
+            theme(plot.background = element_rect(fill = "#fffff8", colour = "#fffff8")))
 
@@
   theme(legend.position = 'bottom', legend.title = element_blank())
+
+# regen with legend in a different position for saving to pdf (see below)
+path_lengths %>% group_by(observer, type) %>%
+  summarise(path_length = median(path_length), .groups = "drop") %>%
+  ggplot(aes(path_length, fill = type)) + 
+  geom_histogram(bins = 25, alpha = 0.5, position = "identity") +
+  geom_vline(xintercept = 0, linetype = 2) + 
+  theme(legend.position = "right") +
+  scale_x_continuous("median path length") +
+  scale_fill_manual(values = col3) -> plt2
 ```
@@
   scale_y_continuous("prop. shorter than model", breaks = seq(0, 1, 0.2)) +
-  coord_cartesian(ylim = c(0, 1)) -> plt2
+  coord_cartesian(ylim = c(0, 1)) -> plt2b
 
-plt1 + plt2 + plot_layout(guides = "collect")  &
+plt1 + plt2b + plot_layout(guides = "collect")  &
   theme(legend.position = 'bottom')
+```
+
+```{r}
+ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 4)
 ```

### 2022-07-19 manuscript.tex

@@
 
+The original implementation of our model has little to say about the initial target selection in each trial: as there is not yet a previous target, the stick/switch and proximity parameters are all ignored leaving just a simple salience parameter that allows us to model one set of targets as being more attractive than the other.
+Taking inspiration from the work on the central viewing bias in the eye movements literature \cite{clarke2014deriving, clarke2017} we develop two models of the spatial bias in initial target selection during visual foraging.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
- We used R, Stan, tidyverse version etc.
+We mainly used R v4.2.0 and rStan v2.26.11 \cite{rstan}. For fitting the model to the data from \cite{clarke2022} we used a university computing cluster with R v and rStan v
 
@@
 
-\subsection{Trial-level predictions}
-
 To assess how well our model can account for behaviour at the level of individual trials, we start by stepping through each trial in the data from \cite{clarke2022}.
-For each target selection, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model.
+For each target selection\footnote{Note: for the reasons discussed above, we ignore the initial target selection for now, as the model has very little to say about it.}, in each trial, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model.
 As can be seen in Figure \ref{fig:cal}, the model is putting somewhere between 25\% and 75\% of the weight on the target that is selected next, easily outperforming a chance $1/n$ baseline.
@@
 Figure \ref{fig:cal2} hints at some individual differences when it comes to how predictable the model is: we can see a lot of variation in the size of the weights.
-However, interestingly, we find that this variability can be explained by our model parameters: nearly all of the differences between people, and between feature and conjunction conditions, can be explained by the $bP$ parameter, which is our proximity bias.
-The model is doing a better job with participants who show a stronger proximity bias (see \textit{Supplementary Materials} for more details).
+However, interestingly, we find that this variability can be explained by our model parameters: nearly all of the differences between different participants, as well as the within-participant differences in the feature and conjunction conditions, can be explained by the $bP$ parameter, which is our proximity bias.
+The model does a better job of predicting which will be selected next when there is a stronger proximity bias (see \textit{Supplementary Materials} for more details).
 
@@
 \end{figure}
+
+We now look at some example trials and compare the behaviour of our human participants to the predicted behaviour from our model (see Figure \ref{fig:qjep_paths}.
+When looking at trials in which our model has done a particularly good job of account for the target selections (model accuracy > 80$\%$) we can see that the \textit{disagreements} appear to often occur in cases when the human participant appears to be carrying out some form of local path length optimisation.
+In general, the cases in which our model suggests a different target from the one the participant actually selected appear reasonable.
+
+For trials in which we do a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants.
+We can see this more clearly
 

### 2022-07-21 Analysis/index.Rmd
figure tweak
a few typos

@@
 We will use the model fit as detailed in @clarke2020compbio.
-For simplicity sake, we will characterise all of our estimated posterior probability densities with just the mean value.
+For simplicity's sake, we will characterise all of our estimated posterior probability densities with just the mean value.
 This gives us four parameters per participant: $b_S, b_A, b_P, b_D$.
 
-Using these fitted values, we can now step through each target selection in the dataset and computer the probability weights our model assigns to each remaining target.
+Using these fitted values, we can now step through each target selection in the dataset and compute the probability weights our model assigns to each remaining target.
 For each target selection, we record:
@@
 Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model.
-The lines give posterior samples from each indivdiaul observer."}
+The lines give posterior samples from each individual observer."}
 timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5)) %>%
@@
 
-We can see that for these highly predictable trials, we make very few mistakes, and those that we do make appear to be related to some sort of shortest-path optimization on the part of the participant.
+We can see that for these highly predictable trials, we make very few mistakes, and those mistakes that we do make appear to be related to some sort of shortest-path optimization on the part of the participant.
 
@@
 
-```{r fig.height=3, fig.cap = "(*left*) A histogram showing the proportion of trials each participant managed a shorter path through the targets than the model's prediction.
+```{r fig.height=3, fig.cap = "(*left*) A histogram showing the proportion of trials on which each participant managed a shorter path through the targets than the model's prediction.
 (*right*) Scatter plot showing the relationship between predictability (accuracy) and whether the model over or under estimates path length.
@@
 ```{r}
-ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 4)
+ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 3)
 ```

### 2022-07-21 Analysis/index.Rmd
finally got the sup mat working, I think

@@
 ```{r echo = TRUE}
-# item weights pre-computed - see scripts/extract_item_weights_using_model.R
+# item weights pre-computed - see scripts/extract_item_weights_using_model_clarke.R
 a <- readRDS("scratch/qjep_model_weights.rda") %>%
@@
 ```{r fig.height = 6, fig.cap = "Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
-# computed in xxxx.R
+# computed in scripts/extract_item_weights_using_model_clarke.R
 fit <- readRDS("scratch/qjep_model_fit.rda") %>%
@@
 
-ggsave("../Figures/qjep_indiv_diff.pdf", 
-       plt_a + plt_b + 
-         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
+#ggsave("../Figures/qjep_indiv_diff.pdf", 
+#       plt_a + plt_b + 
+#         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
 ```
@@
 
-write_csv(timedat, "scratch/time_per_trial.csv")
+#write_csv(timedat, "scratch/time_per_trial.csv")
 
+# see scripts/fit_time_model.R for full model fitting
 m <- readRDS("scratch/time_model_acc_model.rds")
@@
 ```{r}
-ggsave("../Figures/qjep_ex_paths.pdf",
-      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]]), 
-       width = 8, height = 8)
+#ggsave("../Figures/qjep_ex_paths.pdf",
+#      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]]), 
+#       width = 8, height = 8)
 
-rm(trls_easy, trls_mid, trls_hard, plts, qs, plts1, plts2, plts3)
+rm(trls_easy, trls_mid, trls_hard, qs, plts1, plts2, plts3)
 ```
@@
 (*right*) Histogram comparing the median path lengths per participant.", message=FALSE}
+# see scripts/compute_empirical_paths.R
 path_lengths <- readRDS("scratch/path_lengths.rda") %>%
@@
 ```{r}
-ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 3)
+#ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 3)
 ```
@@
 plt_all + plt_med 
-ggsave("../Figures/init_sel_hex_plot.pdf", width = 8, height = 4)
+#ggsave("../Figures/init_sel_hex_plot.pdf", width = 8, height = 4)
 
@@
 
+# see scripts/testing_init_selection.R
 m <- readRDS("scratch/init_sel_model.rds")
@@
 create_post_plot("x") + create_post_plot("y") + plt_mu
-ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
+#ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
 ```
@@
 
-ggsave("../Figures/init_sel2_mdl.pdf", width = 10, height = 3.5)
+#ggsave("../Figures/init_sel2_mdl.pdf", width = 10, height = 3.5)
 ```
@@
 
-ggsave("../Figures/qjep_init_sel_preds.pdf", 
-       plt1 / (plt2 + plt3)  + plot_layout(guides = "collect"),
-       width = 10, height = 6)
+#ggsave("../Figures/qjep_init_sel_preds.pdf", 
+#       plt1 / (plt2 + plt3)  + plot_layout(guides = "collect"),
+#       width = 10, height = 6)
 

### 2022-07-21 Analysis/functions/sim_foraging_momentum.R

@@ -151,7 +151,7 @@ sim_momentum_trial <- function(params, trial = 1,
   for (t in 2:params$m) {
     
     # compute proximity of remaining targets from current target 
-    d_remain <- calc_weights(d_remain, d_found, t)
+    d_remain <- calc_weights(d_remain, d_found, t, params)
     
     # sample the next target
     d_found %>% add_row(
@@ -168,7 +168,7 @@ sim_momentum_trial <- function(params, trial = 1,
   return(d_trial)
 }
 
-calc_weights <- function(d_remain, d_found, t) {
+calc_weights <- function(d_remain, d_found, t, params) {
   
   prev_targ <- d_found$type[t-1]
   match_prev <- if_else(d_remain$type == prev_targ, 1, -1)

### 2022-07-21 Analysis/scripts/testing_init_selection.R

@@ -19,15 +19,15 @@ stan_data <- list(N = nrow(d),
                   x = d$x,
                   y = d$y)
 
-# m <- stan("../models/initial_selection_models/init_sel_beta.stan",
-#                 data = stan_data,
-#                 chains = 1,
-#                 iter = 1000,
-#                 refresh = 100)
-# 
-# 
-# 
-# saveRDS(m, "../scratch/init_sel_model.rds")
+m <- stan("../models/initial_selection_models/init_sel_beta.stan",
+                 data = stan_data,
+                 chains = 1,
+                 iter = 1000,
+                 refresh = 100)
+ 
+ 
+ 
+saveRDS(m, "../scratch/init_sel_model.rds")
 
 m <- readRDS("../scratch/init_sel_model.rds")
 
@@ -63,7 +63,7 @@ obs_fits_x <- pmap_df(filter(am,  dim == "x") %>% select(observer, a, b),
   ggplot(aes(x = x, y = z, group = observer)) + geom_path() +
   scale_x_continuous("x")
 
-obs_fits_x <- pmap_df(filter(am,  dim == "x") %>% select(observer, a, b), 
+obs_fits_y <- pmap_df(filter(am,  dim == "y") %>% select(observer, a, b), 
                       compute_beta_dist) %>%
   ggplot(aes(x = x, y = z, group = observer)) + geom_path() +
   scale_x_continuous("y")

### 2022-07-21 Analysis/index.Rmd
some tidying up of sup mat

@@
 
-### Faster people are more predictable
-
-Is this worth doing?
-
 ### Shorter trials are more predictable
 
-```{r fig.cap="The relationship between the time taken to complete a trial and how predictible it is.
+It seems like shorter trials are easier for the model to predict, in both the feature and conjunction case (though the relationship appears to be clearer in the feature condition).
+
+```{r, message = FALSE, warning = FALSE, fig.cap="The relationship between the time taken to complete a trial and how predictable it is.
 Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model.
 The lines give posterior samples from each indivdiaul observer."}
+
 a %>% select(observer, condition, trial, found, selected_max) %>%
@@
 
-```{r fig.cap="The relationship between the time taken to complete a trial and how predictible it is.
+```{r, message = FALSE, warning = FALSE, fig.cap="The relationship between the time taken to complete a trial and how predictible it is.
 Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model.
 The lines give posterior samples from each individual observer."}
+
 timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5)) %>%
@@
 ```
+This relationship appears to hold true if you look at how long it takes participants to select individual targets as well.
 
-```{r}
+```{r, message = FALSE, warning = FALSE, fig.cap = "The relationship between the time taken to complete a single target selection and how predictible it is."}
 
@@
 
-# Trial level
-
-```{r}
+```{r eval=FALSE, fig.cap="The relationship between mean weight of the next target and trial number", message=FALSE, include=FALSE}
 
@@
   geom_path(alpha = 0.1) + facet_wrap(~condition) +
-  geom_smooth(method = "lm", group = 1)
+  geom_smooth(method = "lm", group = 1) +
+  ylab('Mean weight of next target') +
+  xlab('Trial number')
 
@@
 
-We can model this as multi-level beta distribution? Yes, although it seems like people are in one of two clusters.
+Can we model this as multi-level beta distribution? Yes, although it seems like people are in one of two clusters.
 
 ```{r fig.cap = "The mean posterior plot for the truncated normal distriubtions for (*left*) $x$ and (*right*) $y$.
-We can see that a two component mixture model will capture most of the variance in intial target selection."}
+We can see that a two component mixture model will capture most of the variance in intial target selection.", warning = FALSE}
 
@@
 
-```{r}
+Both models give a similar distribution of target weights and accuracies, and in both cases, participants who start in a corner are easier to predict.
+
+```{r, fig.cap = "(Top): a count of initial weight values predicted from both methods (mixture and multi-level).
+(Bottom left): the proportion of times the first selection was correct for both methods.
+(Bottom right): as lambda (the model parameter underlying initial weight) increases, accuracy increases ie.
+the model is moore accurate for the cases where participants are selecting a corner as their initial target selection."}
 gather_draws(m, a_x[c], b_x[c], a_y[c], b_y[c]) %>%

### 2022-07-29 manuscript.tex

@@
 %=================================================================
-\documentclass[vision,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
+\documentclass[preprints, article,submit,pdftex,moreauthors]{Definitions/mdpi} 
 % For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
@@
 % Full title of the paper (Capitalized)
-\Title{Foraging: The Triumphant Return}
+\Title{A Bayesian statistical model is able to predict target-by-target selection behaviour in a human foraging task}
 
@@
 % Authors, for the paper (add full first names)
-\Author{Alasdair D.F. Clarke $^{1}$\orcidA{}, Amelia Hunt $^{2}$\orcidB{} and Anna E. Hughes\orcidC{} $^{1,}$*}
+\Author{Alasdair D.F. Clarke $^{1}$\orcidA{}, Amelia R. Hunt $^{2}$\orcidB{} and Anna E. Hughes\orcidC{} $^{1,}$*}
 
@@
 % MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
+\AuthorNames{Alasdair D.F. Clarke, Amelia R. Hunt and Anna E. Hughes}
 
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
+\AuthorCitation{Clarke, A.D.F.; Hunt, A.; Hughes, A.E.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 \address{%
-$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
-$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
+$^{1}$ \quad Department of Psychology, University of Essex, Wivenhoe Park, Colchester, UK, CO4 3SQ\\
+$^{2}$ \quad School of Psychology, University of Aberdeen, King's College, Aberdeen, UK, AB24 3FX}
 
 % Contact information of the corresponding author
-\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
+\corres{Correspondence: a.clarke@essex.ac.uk}
 
@@
 The foraging model is fit on the training dataset, and the parameters from this model are then used to predict behaviour at the level of individual trials.
-We show that our methods appear to generalise beyond \citep{clarke2022}: further details can be found in the \textit{Supplementary Materials}.
+We show that our methods appear to generalise beyond \citep{clarke2022}: further details can be found in the \textit{Supplementary Materials: Part 2}.
 
@@
 
-We mainly used R v4.2.0 and rStan v2.26.11 \cite{rstan}. For fitting the model to the data from \cite{clarke2022} we used a university computing cluster with R v and rStan v
+We mainly used R v4.2.0 and rStan v2.26.11 \cite{rstan}. For fitting the model to the data from \cite{clarke2022} we used a university computing cluster with R v3.6.3 and rStan v2.19.2.
 
@@
 To assess how well our model can account for behaviour at the level of individual trials, we start by stepping through each trial in the data from \cite{clarke2022}.
-For each target selection\footnote{Note: for the reasons discussed above, we ignore the initial target selection for now, as the model has very little to say about it.}, in each trial, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model.
+For each target selection\footnote{Note: for the reasons discussed above, we ignore the initial target selection for now, as the model has very little to say about it.
+We return to this issue in section 4.}, in each trial, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model.
 As can be seen in Figure \ref{fig:cal}, the model is putting somewhere between 25\% and 75\% of the weight on the target that is selected next, easily outperforming a chance $1/n$ baseline.
@@
 However, interestingly, we find that this variability can be explained by our model parameters: nearly all of the differences between different participants, as well as the within-participant differences in the feature and conjunction conditions, can be explained by the $bP$ parameter, which is our proximity bias.
-The model does a better job of predicting which will be selected next when there is a stronger proximity bias (see \textit{Supplementary Materials} for more details).
+The model does a better job of predicting which will be selected next when there is a stronger proximity bias (see \textit{Supplementary Materials: Part 1} for more details).
 
@@
 
-We now look at some example trials and compare the behaviour of our human participants to the predicted behaviour from our model (see Figure \ref{fig:qjep_paths}.
+We now look at some example trials and compare the behaviour of our human participants to the predicted behaviour from our model (see Figure \ref{fig:qjep_paths}).
 When looking at trials in which our model has done a particularly good job of account for the target selections (model accuracy > 80$\%$) we can see that the \textit{disagreements} appear to often occur in cases when the human participant appears to be carrying out some form of local path length optimisation.
 In general, the cases in which our model suggests a different target from the one the participant actually selected appear reasonable.
-
-For trials in which we do a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants.
-We can see this more clearly
 
@@
 \label{fig:qjep_paths}
+\end{figure}
+
+For trials in which we do a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants.
+We can see this more clearly in Figure \ref{fig:qjep_path_lengths}: while our model does a good job of capturing the average total path length, there is considerable variation with some participants generating shorter paths and some longer.
+We can see  that this appears to be systematically related to how well our model can predict behaviour.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=12 cm]{Figures/path_length.pdf}
+\caption{(\textit{left}) Histogram showing the distribution of the median path lengths for our human participants and model (fitted to each human participant via the random effect structure).
+(\textit{right}) The relationship between model accuracy and the proportion of trials in which the human participant has a shorter total path length than predicted.}
+\label{fig:qjep_path_lengths}
 \end{figure}
@@
 This appears to be due to different participants choosing to utilise different strategies rather than within-subject variation.
-However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see \textit{Supplementary Material}).
+However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see \textit{Supplementary Materials: Part 1}).
 We try two different modelling approaches (multi-level and mixture) to assess whether the less complex mixture model is able to account for the patterns of starting positions seen.
@@
 
-We first consider a multi-level model in which we fit beta distributions to the $x$ and $y$ coordinates of each participant's initial target selections\footnote{Full details of the analysis can be found in the \textit{Supplementary Materials}.}:
+We first consider a multi-level model in which we fit beta distributions to the $x$ and $y$ coordinates of each participant's initial target selections\footnote{Full details of the analysis can be found in the \textit{Supplementary Materials: Part 1}.}:
 
@@
 (\textit{Bottom left}): the proportion of times the first selection was correct for both methods.
-(\textit{Bottom left}): as lambda (the model parameter underlying initial weight) increases, accuracy increases i.e.
+(\textit{Bottom right}): as lambda (the model parameter underlying initial weight) increases, accuracy increases i.e.
 the model is more accurate for the cases where participants are selecting a corner as their initial target selection.}
@@
 In our original model of visual foraging \citep{clarke2022foraging}, we were able to robustly measure aggregate parameters that underlie behaviour, at both an overall mean level across an experiment, and at the level of individual participants.
-In the current manuscript, we asked a more difficult question: could this model make target-by-target predictions, guessing which target would be picked next on any given trial?
-Despite this being a relatively difficult task, we found that our model was in some cases over 80\% accurate, demonstrating that at least in some cases, participants' behaviour in this task is remarkably predictable.
+In the current manuscript, we asked a more difficult question: could this model make target-by-target predictions, guessing which target would be picked next within a trial?
+Despite this being a relatively difficult task, we found that for some trials our model was over 80\% accurate, demonstrating that at least in some cases, participants' behaviour in this task is remarkably predictable.
 
@@
 The model is generally better at feature search compared to conjunction search, and also seems to be better at predicting participants with a stronger proximity bias.
-The model also seems to assign more weight to 'runner-up' items than real humans do, perhaps suggesting a 'peakier' choice distribution for real foragers, with only a few targets seriously considered, and everything else being approximately zero weighted.
+The model also seems to assign more weight to 'runner-up' items than real humans do, perhaps suggesting a 'peakier' choice distribution, but with fatter tails, for real foragers, with only a few nearby targets seriously considered, but with some low probability of selecting a further away target.
 
@@
 One suggestion is that the people who our model is able to predict are in some way the most 'optimal'.
-If this is the case, we might expect that model predictability should correlate with how good people are at the task, although we do not find any evidence that model accuracy correlates with reaction time on a by-participant or by-trial basis (see \textit{Supplementary Materials}).
-This may be due to the fact that this task was not time-limited, and instead participants were encouraged to be as accurate as possible (in fact, the trial restarted if the participant clicked on a non-target \citep{clarke2022}).
-However, there is some evidence that on a target-by-target basis, faster moves from one target to the next are more easily predicted by the model (see \textit{Supplementary Materials}).
+If this is the case, we might expect that model predictability should correlate with how good people are at the task.
+There is some evidence that on a trial-by-trial basis, shorter trials are easier for the model to predict, and on a target-by-target basis, faster moves from one target to the next are more easily predicted by the model (see \textit{Supplementary Materials: Part 1}).
 This likely is linked to the fact that our model is better at predicting participants with a stronger proximity bias, as targets that are closer to the previous target are also likely to be selected more quickly.
@@
 Similarly, \citep{thornton2022foraging} showed that switches between target categories can be characterised by a change in foraging 'tempo', and if participants are forced to forage at a particular speed, by asking them to synchronise with an auditory signal, higher tempos led to a systematic decrease in the probability of participants switching between target categories.
-In the current version of the model, we do not consider time explicitly (although distance is likely to be highly correlated with time in this task).
+In the current version of the model, we do not consider time explicitly (although distance is likely to be correlated with time in this task).
 However, it would be possible to extend the model to incorporate timing information, and this may help to improve the target-by-target predictions.
@@
 Could this help to explain some of the mistakes the model makes?
-Overall, the model doesn't seem to make substantially longer paths through the items than the human participants (see \textit{Supplementary Materials}).
+Overall, the model doesn't seem to make substantially longer paths through the items than the human participants.
 However, there is a relationship between model accuracy and the proportion of times that participants select paths shorter than the model: as model accuracy increases, people seem to be more likely to have paths shorter than the model predicts.
@@
 Participants who prefer the top left corner were easiest to predict, probably because these participants formed the majority group in this experiment.
-Our results are congruent with \citep{kristjansson2022moving}, who found a bottom left bias in a 3D environment They suggest this may be an advantageous strategy because it allows your foraging to be more organised (e.g.
+Our results are congruent with \citep{kristjansson2022moving}, who found a bottom left bias in a 3D environment.
+They suggest this may be an advantageous strategy because it allows your foraging to be more organised (e.g.
 in an 'S-shape', as has been found in real world search tasks \citep{riggs2017importance}).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Conceptualization, A.D.F.C., A.H.
-and A.E.H.; methodology, A.D.F.C.; software, A.D.F.C.; formal analysis, A.D.F.C.; data curation, A.D.F.C., and A.E.H.; writing---original draft preparation, A.D.F.C.; writing---review and editing, A.H.
+\authorcontributions{Conceptualization, A.D.F.C., A.R.H.
+and A.E.H.; methodology, A.D.F.C.; software, A.D.F.C.; formal analysis, A.D.F.C.; data curation, A.D.F.C., and A.E.H.; writing---original draft preparation, A.D.F.C.; writing---review and editing, A.R.H.
 and A.E.H.; visualization, A.D.F.C.
 and A.E.H.; funding acquisition, A.D.F.C.
-and A.H.
+and A.R.H.
 All authors have read and agreed to the published version of the manuscript.}
 
-\funding{This research was funded by NAME OF FUNDER grant number XXX.}
+\funding{This research was funded by the Economic and Social Research Council grant number ES/S016120/1 to A.D.F.C and A.R.H.}
 

### 2022-08-18 Analysis/index.Rmd
Graphs for ecvp talk

@@
 
-#ggsave("../Figures/qjep_indiv_diff.pdf", 
-#       plt_a + plt_b + 
-#         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
+ggsave("../Figures/qjep_indiv_diff.pdf", 
+       plt_a + plt_b + 
+         plot_layout(guides = "collect") & theme(legend.position = "right") & 
+         theme_bw(), width = 8, height = 4)
 ```
@@
   ggplot(aes(time_taken_s, fill = condition)) + 
-  stat_lineribbon(aes(y = .epred), alpha = 0.5, .width = c(0.53, 0.97)) +
+  stat_lineribbon(aes(y = .epred), alpha = 0.75, .width = c(0.53, 0.97)) +
   geom_jitter(data = timedat, aes(y = acc, colour = condition), 
@@
   guides(fill = guide_legend(reverse = TRUE)) +
-  facet_wrap(~ condition) -> plt
+  facet_wrap(~ condition, nrow = 2) -> plt
 
@@
                     group = interaction(condition, observer)),
-                alpha = 0.25)
+                alpha = 0.25) -> plt
+
+ggsave("../Figures/trial_time.png", plt + theme_bw() + theme(legend.position = "none"), width = 4, height = 6)
 
@@
 ```{r, message = FALSE, warning = FALSE, fig.cap = "The relationship between the time taken to complete a single target selection and how predictible it is."}
-
-# 
-# my_model <- brm(acc ~ time_taken:condition + (1|observer), timedat)
+breaks = c(seq(0.1, 0.8,0.1),1, 1.5, 2, 3, 4, 5, 6)
 
@@
     RTd = RT - lag(RT),
-    RTd = if_else(found == 1, 0, RTd)) %>%
-  filter(RTd < 2, is.finite(RTd)) %>%
+    RTd = if_else(found == 1, 0, RTd),
+    logRTd = log10(RTd)) %>%
+  filter(is.finite(logRTd)) %>%
   mutate(
-    time_bin = cut(RTd,breaks = 50, labels = FALSE)) %>%
-  group_by(observer, condition, time_bin) %>%
-  summarise(acc = mean(selected_max)) %>%
-  ggplot(aes(time_bin, acc, group = observer)) +
-  geom_path(alpha = 0.2) +
-  geom_smooth(se= F, alpha = 0.1, method = lm) + 
-  facet_grid(~condition)
+    time_bin = cut(logRTd,breaks = 25)) %>%
+  separate(time_bin, into = c("binS", "binE"), ",") %>%
+  mutate(binS = parse_number(binS),
+         binE = parse_number(binE),
+         logRTd = (binS + binE)/2,
+         RTd = 10^logRTd) %>%
+  group_by(observer, condition, RTd) %>%
+  summarise(acc = mean(selected_max),
+            n = n()) %>%
+  filter(n > 5) %>%
+  ggplot(aes(x = RTd, y = acc, colour = condition)) + 
+  geom_jitter(height = 0, width = 0.02, alpha = 0.5) +
+  scale_x_log10("inter-item selection time", breaks = breaks) + 
+  scale_y_continuous("model accuracy") + 
+  stat_smooth(method = glm, method.args = list(family = "binomial"), se = FALSE, alpha = 0.5) +
+  theme_bw() + theme(legend.position = "none")
+
+ggsave("../Figures/targ_time.png", width = 7, height = 4)
 
@@
 
-create_post_plot("x") + create_post_plot("y") + plt_mu
-#ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
+create_post_plot("x") + create_post_plot("y") + plt_mu & theme_bw()
+ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
 ```
@@
   facet_wrap(~dim) + 
+  theme_bw() + 
   theme(legend.position = "none")  + 
@@
   facet_wrap(~dim) + 
+  theme_bw() + 
   theme(legend.position = "none",
@@
   scale_y_continuous("lambda") + 
+  theme_bw() + 
   theme(axis.text.x=element_blank(),
@@
 
-#ggsave("../Figures/init_sel2_mdl.pdf", width = 10, height = 3.5)
+ggsave("../Figures/init_sel2_mdl.pdf", width = 10, height = 3.5)
 ```
@@
   summarise(acc = mean(max_item == 1), .groups = "drop") %>%
-  ggplot(aes(y = acc, fill = method)) + geom_boxplot(alpha = 0.5) + 
+  ggplot(aes(x = method, y = acc, fill = method)) + geom_boxplot(alpha = 0.5) + 
   geom_hline(yintercept = 1/40, linetype = 2) + 
@@
 
-#ggsave("../Figures/qjep_init_sel_preds.pdf", 
-#       plt1 / (plt2 + plt3)  + plot_layout(guides = "collect"),
-#       width = 10, height = 6)
+ggsave("../Figures/qjep_init_sel_preds.pdf", 
+       (plt2 / plt3) & theme_bw() & theme(legend.position = "none"),
+       width = 4, height = 8)
 

### 2022-08-18 ECVP2022/make_time_plot.R

@@ -1,0 +1,72 @@
+
+
+a %>% select(observer, condition, trial, found, selected_max) %>%
+  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
+  arrange(observer, condition, trial, found) %>%
+  mutate(
+    dist = sqrt((x-lag(x))^2 + (y-lag(y))^2),
+    RTd = RT - lag(RT),
+    RTd = if_else(found == 1, 0, RTd),
+    logRTd = log2(RTd)) %>%
+  filter(is.finite(logRTd)) %>%
+  mutate(
+    time_bin = cut(logRTd,breaks = 25)) %>%
+  separate(time_bin, into = c("binS", "binE"), ",") %>%
+  mutate(binS = parse_number(binS),
+         binE = parse_number(binE),
+         logRTd = (binS + binE)/2,
+         RTd = 2^logRTd) -> qq
+
+%>%
+  group_by(observer, condition, RTd) %>%
+  summarise(acc = mean(selected_max),
+            n = n()) %>%
+  filter(n > 5) -> b
+
+
+ggplot(b, aes(x = RTd, y = acc, colour = condition)) + 
+  geom_jitter(height = 0, width = 0.01, alpha = 0.5) +
+  scale_x_log10("inter-item selection time") + 
+  scale_y_continuous("model accuracy") + 
+  stat_smooth(method = glm, method.args = list(family = "binomial"), se = FALSE, alpha = 0.5)
+
+
+###########
+
+
+
+a %>% select(observer, condition, trial, found, selected_max) %>%
+  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
+  group_by(observer, condition, trial) %>%
+  summarise(time_taken = max(RT),
+            acc = mean(selected_max, na.rm = T), 
+            .groups = "drop") %>%
+  filter(time_taken < 60) %>%
+  mutate(time_taken_s = as.numeric(scale(log(time_taken)))) -> timedat
+
+
+
+a %>% select(observer, condition, trial, found, selected_max) %>%
+  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
+  arrange(observer, condition, trial, found) %>%
+  mutate(
+    dist = sqrt((x-lag(x))^2 + (y-lag(y))^2),
+    logdist = log(dist),
+    RTd = RT - lag(RT),
+    RTd = if_else(found == 1, 0, RTd),
[…]

### 2022-09-22 Analysis/index_revisions.Rmd
some initial work on revisions

--- 2022-08-18 Analysis/index.Rmd
@@
 
-```{r, message=FALSE}
+```{r, message=FALSE, warning = FALSE}
 # attach packages
@@
 # set ggplot2 options
+#theme_set(ggthemes::theme_tufte() + 
+#            theme(plot.background = element_rect(fill = "#fffff8", colour = "#fffff8")))
+
+# for saving graphs for paper
 theme_set(ggthemes::theme_tufte() + 
-            theme(plot.background = element_rect(fill = "#fffff8", colour = "#fffff8")))
+            theme(plot.background = element_rect(fill = "#ffffff", colour = "#ffffff")))
 
@@
 ```
-
-Terminology questions:
-- item v target
-- participant v observer
 
@@
 
-ggplot(a_cut, aes(b_bin, acc, colour = condition, fill = condition, shape = condition)) + 
+ggplot(a_cut, aes(b_bin, acc, colour = condition, fill = condition)) + 
   geom_point() + 
@@
 
-#ggsave("../Figures/qjep_preds.pdf", 
-#       plt_b + plt1 + plt2 + 
-#         plot_layout(guides = "collect") & theme(legend.position = "bottom"),
-#       width = 10, height = 4)
+# Making a slightly different version of plt_b for the revisions
+ggplot(a_agg, aes(x = found, y = meanb, colour = condition, fill = condition)) + 
+  geom_jitter(data = filter(a_agg, found<40), width = 0.1, height = 0, alpha = 0.2) + 
+  stat_lineribbon(.width = 0.67, alpha = 0.50) +
+  geom_path(data = filter(a_agg, observer == 1), 
+                          aes(y = chance), linetype = 2, colour = "black") + 
+  geom_point(data = tibble(x=40, y=1), aes(x, y), size = 1.5, colour = "black", fill = "grey") + 
+  scale_x_continuous(breaks = c(2, 10, 20, 40), "target selection", expand = c(0.01, 0.01)) + 
+  scale_y_continuous("average weight from model", expand = c(0.01, 0.01)) + facet_grid(~condition) +
+  guides(color = "none", fill = "none") -> plt_b2
+
+ggsave("../Figures/qjep_preds.pdf", 
+       plt_b2 / (plt1 + plt2) + 
+       plot_layout(guides = "collect") & theme(legend.position = 'bottom'),
+       width = 10, height = 6)
 

### 2022-09-22 manuscriptRevisions.tex
some initial work on revisions

--- 2022-07-29 manuscript.tex
@@
 Foraging, the act of searching for and gathering multiple targets (such as food), has been studied in both non-human animal contexts \cite{dawkins1971} and in human psychology studies \cite{kristjansson2014}.
-Foraging engages a wide range of different perceptual, cognitive, and decision-related skills, and is an ecologically relevant behaviour for most species, including humans.
+Foraging engages a wide range of different perceptual, cognitive, decision-related and motor skills, and is an ecologically relevant behaviour for most species, including humans.
 For these and other reasons, a sustained interest in foraging has developed our understanding of how we search for multiple instances of multiple types of targets.
@@
 As can be seen in Figure \ref{fig:cal}, the model is putting somewhere between 25\% and 75\% of the weight on the target that is selected next, easily outperforming a chance $1/n$ baseline.
-We can also see  that the model is well calibrated in that the probabilities assigned to the largest target manage to capture how often that target is actually selected.
+We can also see  that the model is well calibrated in that the probabilities assigned to the most likely target manage to capture how often that target is actually selected.
 However, we can see a decrease in accuracy when it comes to how often ``runner-up`` candidate items are selected as our model appears to systematically undervalue these (presumably by putting too much of the probabilistic weight on low chance items).
@@
 \includegraphics[width=12 cm]{Figures/qjep_preds.pdf}
-\caption{(\textit{left}) Posterior probabilities for target selections during a visual foraging task.
-Each dot shows the  data from an individual participant, averaged over trials, in a condition and the shaded region indicates the interval in which we expect 67\% of participants to fall.
+\caption{(\textit{top left}) Posterior probabilities for target selections during a visual foraging task.
+Each dot shows the data from an individual participant, averaged over trials, in the feature condition and the shaded region indicates the interval in which we expect 67\% of participants to fall.
 The dashed line indicates chance performance.
-(\textit{centre})  Calibration plot for our foraging model.
+(\textit{top right}) As top left, except showing the conjunction condition.
+(\textit{bottom left})  Calibration plot for our foraging model.
 The $x$-axis gives the largest weight assigned by the model while the $y$-axis shows how often that target was actually selected by a human participant.
 The dashed line here and in the right plot is the identity line.
-(\textit{right}) This plot shows how often the 2nd and 3rd ranked items are selected based on the weights assigned by the model.}
+(\textit{bottom right}) This plot shows how often the model selects the 2nd and 3rd ranked items based on the weights assigned by the model.}
 \label{fig:cal}
@@
 We now look at some example trials and compare the behaviour of our human participants to the predicted behaviour from our model (see Figure \ref{fig:qjep_paths}).
-When looking at trials in which our model has done a particularly good job of account for the target selections (model accuracy > 80$\%$) we can see that the \textit{disagreements} appear to often occur in cases when the human participant appears to be carrying out some form of local path length optimisation.
+When looking at trials in which our model has done a particularly good job of accounting for the target selections (model accuracy > 80$\%$) we can see that the \textit{disagreements} often occur in cases when the human participant appears to be carrying out some form of local path length optimisation.
 In general, the cases in which our model suggests a different target from the one the participant actually selected appear reasonable.
@@
 
-For trials in which we do a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants.
+For trials in which the model does a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants.
 We can see this more clearly in Figure \ref{fig:qjep_path_lengths}: while our model does a good job of capturing the average total path length, there is considerable variation with some participants generating shorter paths and some longer.
@@
 Grey areas indicate cells with a count of 0.
-(\textit{left}) shows the distribution over all initial target selections while (\textit{right}) shows the distribution of each participant's median initial selection.
+(\textit{left}) shows the distribution over all initial target selections (i.e.
+multiple trials per participant) while (\textit{right}) shows the distribution of each participant's median initial selection (i.e.
+each participant contributes one data point to the graph).
 }
@@
 This likely is linked to the fact that our model is better at predicting participants with a stronger proximity bias, as targets that are closer to the previous target are also likely to be selected more quickly.
-Intuitively, it makes sense that the model struggles to make predictions when a participant has exhausted a local patch and may need to make a bigger jump to a more distant area to carry on collecting targets, as there may be multiple candidates and distance may no longer be such a good predictor (for example, people may choose to move to the next most densely populated patch).
+Intuitively, it makes sense that the model makes poorer predictions when a participant has exhausted a local patch and may need to make a bigger jump to a more distant area to carry on collecting targets, as there may be multiple candidates and distance may no longer be such a good predictor (for example, people may choose to move to the next most densely populated patch).
 
@@
 Some participants may also lose track of where they are more frequently (perhaps due to attentional lapses) and thus may show foraging patterns that are predictable apart from unpredictable discontinuities, which again may not be easy to model.
+Another possibility is that participants may make exploratory, information-seeking visits to different parts of the array due to uncertainty about the targets present: this may be particularly important for conjunction trials, where peripheral visual information about shape is likely to be poorer.
 Finally, the displays had artificial discontinuities (i.e.
 screen edges) which may lead to different behaviour in different participants: some may carry out the task as if they are reading, reaching the right hand edge and then swinging back to the left, whereas others may 'bounce' off an edge they have just reached.
-Our model may well be able to predict the latter, but could struggle with the former behaviour.
+Our model may well be able to predict the latter, but make less good predictions for the former behaviour.
 

### 2022-09-23 manuscriptRevisions.tex
would help if I saved everything
a bit more revision work

@@
 
-To test how well our methods generalise, we use the dataset from \citep{kristjansson2014}.
-We split this into a training dataset (50\% of the original data i.e.
-10 trials per participant) and a test dataset (the remaining 50\% of the data).
-The foraging model is fit on the training dataset, and the parameters from this model are then used to predict behaviour at the level of individual trials.
-We show that our methods appear to generalise beyond \citep{clarke2022}: further details can be found in the \textit{Supplementary Materials: Part 2}.
-
 \subsection{A Model for Visual Foraging}
@@
 \caption{(\textit{top}) Two randomly selected trials in which the model does a good job in accounting for human behaviour.
+The numbers indicate the order the participant selected targets in.
 Red arrows indicate places where the model prediction deviates from participant behaviour.
@@
 
+\subsection{Replication: \cite{kristjansson2014} dataset}
+
+To test how well our methods generalise, we used the dataset from \citep{kristjansson2014}.
+We split this into a training dataset (50\% of the original data i.e.
+10 trials per participant) and a test dataset (the remaining 50\% of the data).
+The foraging model is fit on the training dataset, and the parameters from this model are then used to predict behaviour at the level of individual trials.
+We show that our methods appear to generalise beyond \citep{clarke2022}: in particular, feature foraging was more predictable than conjunction foraging, and the model is well calibrated, with participants more frequently selecting targets with higher model assigned weights.
+Proximity also seems to be an important factor in determining model accuracy, at least for the feature condition, although the relatively low number of participants in this experiment makes it harder to draw strong conclusions.
+One interesting difference compared to \citep{clarke2022} is in initial target selection: while there was a strong bias towards starting in a corner, there was little evidence of central bias, perhaps because this experiment was completed on an iPad.
+Further details and graphs can be found in the \textit{Supplementary Materials: Part 2}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-09-26 Analysis/index_revisions.Rmd
final stuff for submission

@@
 
-We will use the visual foraging data from @clarke2022 to assess the model's trial level performance.
+We will use the visual foraging data from Clarke (2022) to assess the model's trial level performance.
 As the current version of our model only takes the $p_A$ bias into account for the initial target selection, we will ignore these data points for now.
@@
 
-We will use the model fit as detailed in @clarke2020compbio.
+We will use the model fit as detailed in Clarke (2022).
 For simplicity's sake, we will characterise all of our estimated posterior probability densities with just the mean value.
@@
        plt_a + plt_b + 
-         plot_layout(guides = "collect") & theme(legend.position = "right") & 
-         theme_bw(), width = 8, height = 4)
+         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
 ```
@@
 ```{r}
-#ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 3)
+ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 3)
 ```
@@
 
-Previous work (cite Clarke and Tatler etc) has demonstrated that the initial fixation in scene viewing can be well described with truncated Gaussian distribution.
+Previous work (Clarke and Tatler, 2014) has demonstrated that the initial fixation in scene viewing can be well described with truncated Gaussian distribution.
 Here we explore using a similar idea to account for starting locations.
@@
 
-create_post_plot("x") + create_post_plot("y") + plt_mu & theme_bw()
+create_post_plot("x") + create_post_plot("y") + plt_mu #& theme_bw()
 ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
@@
   facet_wrap(~dim) + 
-  theme_bw() + 
+  #theme_bw() + 
   theme(legend.position = "none")  + 
@@
   facet_wrap(~dim) + 
-  theme_bw() + 
+  #theme_bw() + 
   theme(legend.position = "none",
@@
   scale_y_continuous("lambda") + 
-  theme_bw() + 
+  #theme_bw() + 
   theme(axis.text.x=element_blank(),
@@
   geom_point() +
-  geom_smooth(method = "lm", formula = y ~ x, colour = "black") -> plt3
+  geom_smooth(method = "lm", formula = y ~ x, colour = "black") +
+  geom_hline(yintercept = 1/40, linetype = 2) -> plt3
 
@@
 ggsave("../Figures/qjep_init_sel_preds.pdf",
-       (plt2 / plt3) & theme_bw() & theme(legend.position = "none"),
-       width = 4, height = 8)
+       width = 8, height = 4)
 

### 2022-09-26 manuscriptRevisions.tex
final stuff for submission

@@
 
+We summarise accuracy for each person by calculating the mean proportion of times the model assigns the most weight to the item that was then selected for each participant\footnote{This metric isn't perfect as it averages over all target selections within a trial, and these clearly have different baseline probabilities ($2.5\%-100\%$).
+However, it has the upside of being more intuitive than anything else we could think of.}.
+These accuracy scores can be compared to our uniform chance baseline that gives a value of $10.9\%$ over the course of a trial.
 Figure \ref{fig:cal2} hints at some individual differences when it comes to how predictable the model is: we can see a lot of variation in the size of the weights.

### 2022-10-14 Analysis/index_revisions_2.Rmd
work on more revisions

--- 2022-09-26 Analysis/index_revisions.Rmd
@@
 output:
-  tufte::tufte_html:
+  tufte::tufte_handout:
     number_sections: true
     fig_height: 4
-    bibliography: literature.bib
-    link-citations: yes  
 ---
@@
 # for saving graphs for paper
-theme_set(ggthemes::theme_tufte() + 
+theme_set(ggthemes::theme_tufte(base_size = 16) + 
             theme(plot.background = element_rect(fill = "#ffffff", colour = "#ffffff")))
@@
 
-```{r, fig.cap = "(*left*) The average weight assigned to each selected target by our model.
-(*right*) The proportion of trials the item with the largest assigned weight was selected by the participant.
+```{r, fig.cap = "Left: The average weight assigned to each selected target by our model.
+Right: The proportion of trials the item with the largest assigned weight was selected by the participant.
 Each dot shows data from an individual participant in a condition and the shaded region indicates the interval in which we expect 67% of participants to fall."}
@@
        plot_layout(guides = "collect") & theme(legend.position = 'bottom'),
-       width = 10, height = 6)
+       width = 10, height = 10)
 
@@
 
-### Individual Differences
+## Individual Differences
 
@@
   scale_shape_manual(values = c(19, 4), guide = "none") + 
+  xlab("bP parameter value") +
   theme(legend.position = "none") + 
@@
 
-### Shorter trials are more predictable
+## Shorter trials are more predictable
 

### 2022-10-14 manuscriptRevisions2.tex
work on more revisions

--- 2022-09-26 manuscriptRevisions.tex
@@
 
-We use a previously published dataset to explore how well our model can account for trial-level behaviour: the visual foraging data from \cite{clarke2022}.
-This is an attractive dataset for our needs as it is very close to the ``classic'' visual foraging paradigm \citep{kristjansson2014}, yet with a substantially larger sample of participants.
+We use a previously published dataset to explore how well our model can account for trial-level behaviour: the visual foraging data from Clarke and colleagues \cite{clarke2022}.
+This is an attractive dataset for our needs as it is very close to the ``classic'' visual foraging paradigm conducted by Kristjánsson and colleagues \citep{kristjansson2014}, yet with a substantially larger sample of participants.
 (The key difference between paradigms is that \cite{kristjansson2014} used an ipad and finger foraging, while \cite{clarke2022} used a desktop computer and mouse clicks.) Furthermore, we have already demonstrated that our model can capture individual differences in foraging behaviour \citep{clarke2022}.
@@
 
-We will make use of the foraging model from \cite{clarke2022}.
+We will make use of the foraging model from Clarke et al (2022) \cite{clarke2022foraging}.
 This treats foraging as a sampling without replacement process in which each item $i$ has probability $p_i$ of being selected as the next target.
@@
 
-To assess how well our model can account for behaviour at the level of individual trials, we start by stepping through each trial in the data from \cite{clarke2022}.
+To assess how well our model can account for behaviour at the level of individual trials, we start by stepping through each trial in the data from Clarke and colleagues \cite{clarke2022}.
 For each target selection\footnote{Note: for the reasons discussed above, we ignore the initial target selection for now, as the model has very little to say about it.
@@
 
-One weakness of the foraging model by \cite{clarke2022foraging} is that it makes little attempt to predict which item will be selected first.
+One weakness of the foraging model by Clarke et al (2022) \cite{clarke2022foraging} is that it makes little attempt to predict which item will be selected first.
 In this section we aim to improve this by modelling participant bias (or preference) in their choice of initial target selection.
@@
 These studies fit truncated Gaussian distributions to the  $(x,y)$ coordinates of fixation locations.
-Here we will do similar, and fit beta distributions\footnote{We use beta distributions here as ADFC couldn't work out the syntax for specifying a mixture model using truncated Gaussians in Stan.
-But, in hindsight, beta distributions are probably a better choice anyway!} to locations of the initial target selections in the visual foraging task.
+Here we will do similar, and fit beta distributions\footnote{We use beta distributions here as it is difficult to specify a mixture model using truncated Gaussians in Stan.
+However, beta distributions may well be a more appropriate choice.} to locations of the initial target selections in the visual foraging task.
 
@@
 This reduces the number of parameters to eight (to specify the two Beta distributions) and then one $\lambda$ value per participant (= 66 in our dataset).
-While the formulae in Equations \ref{eq:beta2x} and \ref{eq:beta2y} appear more complex than those in Equations \ref{eq:beta1x} and \ref{eq:beta1y}, the model requires less than a quarter as many free parameters!
+While the formulae in Equations \ref{eq:beta2x} and \ref{eq:beta2y} appear more complex than those in Equations \ref{eq:beta1x} and \ref{eq:beta1y}, the model requires less than a quarter as many free parameters.
 
@@
 The model is generally better at feature search compared to conjunction search, and also seems to be better at predicting participants with a stronger proximity bias.
-The model also seems to assign more weight to 'runner-up' items than real humans do, perhaps suggesting a 'peakier' choice distribution, but with fatter tails, for real foragers, with only a few nearby targets seriously considered, but with some low probability of selecting a further away target.
+The model also seems to assign more weight to 'runner-up' items than real humans do.
+Real foragers thus seem to seriously consider only a few nearby targets (although they do still have some low probability of selecting a further away target), in contrast to the model, in which the item weights assigned fall off more gradually with distance.
 

### 2022-10-14 Analysis/index2_revisions.Rmd
sup mat figure numbers (the manual way)

--- 2022-06-07 Analysis/index2.Rmd
@@
 author: "Alasdair Clarke, Amelia Hunt &  Anna Hughes"
-date: "13/04/2022"
+date: "14/10/2022"
 output:
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
 options(digits = 3)
@@
 
-We can then plot this data to show how our ability to predict which target will be selected next varies throughout a trial.
+We can then plot this data to show how our ability to predict which target will be selected next varies throughout a trial (Figure 1).
 We can see a difference between *feature* and *conjunction* foraging, with *feature* foraging being more predictable (though the distinction is less clear after the initial 20 target selections).
 
-```{r, fig.cap = "(*left*) The average weight assigned to each selected target by our model.
+```{r, fig.cap = "Figure 1: (*left*) The average weight assigned to each selected target by our model.
 (*right*) The proportion of trials the item with the largest assigned weight was selected by the participant.
@@
 
-We can see from the Figure below that our model is well-calibrated (at least in terms of the target with the highest assigned weight).
+We can see from Figure 2 below that our model is well-calibrated (at least in terms of the target with the highest assigned weight).
 If we repeat this calculation for the 2nd and 3rd ranked candidate items we can see that we slightly underweight these items, but we are still pretty accurate.
 
-```{r, fig.height=3.5, fig.cap = "(*left*) Calibration plot for our foraging model.
+```{r, fig.height=3.5, fig.cap = "Figure 2: (*left*) Calibration plot for our foraging model.
 The *x*-axis gives the largest weight assigned by the model while the *y*-axis shows how often that target was actually selected by a human participant.
@@
 
-```{r, fig.height=3.5, fig.cap = "Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. (The dots indicate outliers.)", echo= TRUE}
+```{r, fig.height=3.5, fig.cap = "Figure 3: Prediction scores for participants.
+Boxplots show quartile range and the grey lines indicate individual participants.
+(The dots indicate outliers.)", echo= TRUE}
 
@@
 ```
-Model accuracy is quite high (though lower than for Clarke et al).
 
-Is this explained by differences in proximity weighting? i.e., are participants with weaker proximity biases harder to predict? Yes!
+Figure 3 shows that model accuracy is quite high (though lower than for Clarke et al).
 
-```{r fig.height = 6, fig.cap = "Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
+Is this explained by differences in proximity weighting? i.e., are participants with weaker proximity biases harder to predict? Yes (Figure 4).
+
+```{r fig.height = 6, fig.cap = "Figure 4: Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
 # computed in xxxx.R
@@
 
-Similar to Clarke et al, there is a bias towards starting in a corner. Interestingly, there isn't much evidence of a central bias (possibly because these trials were completed on an iPad).
+Similar to Clarke et al, there is a bias towards starting in a corner (Figure 5). Interestingly, there isn't much evidence of a central bias (possibly because these trials were completed on an iPad).
 
@@
 
-```{r fig.height = 3.5, fig.cap="(*left*) Density plot for initial target selections, over all participants and all trials.
+```{r fig.height = 3.5, fig.cap="Figure 5: (*left*) Density plot for initial target selections, over all participants and all trials.
 (*right*) Median $x$ and $y$ coordinates for the initial target selection for each participant."}

### 2022-10-14 Analysis/index_revisions_2.Rmd
sup mat figure numbers (the manual way)

@@
 author: "Alasdair Clarke, Amelia Hunt &  Anna Hughes"
-date: "13/04/2022"
+date: "14/10/2022"
 output:
-  tufte::tufte_handout:
+  tufte::tufte_html:
     number_sections: true
     fig_height: 4
+    bibliography: literature.bib
+    link-citations: yes  
 ---
@@
 We can then plot this data to show how our ability to predict which target will be selected next varies throughout a trial.
-We can see a difference between *feature* and *conjunction* foraging, with *feature* foraging being more predictable.
+We can see a difference between *feature* and *conjunction* foraging, with *feature* foraging being more predictable (Figure 1).
 
-```{r, fig.cap = "Left: The average weight assigned to each selected target by our model.
-Right: The proportion of trials the item with the largest assigned weight was selected by the participant.
+```{r, fig.cap = "Figure 1.
+(*left*) The average weight assigned to each selected target by our model.
+(*right*) The proportion of trials the item with the largest assigned weight was selected by the participant.
 Each dot shows data from an individual participant in a condition and the shaded region indicates the interval in which we expect 67% of participants to fall."}
@@
 
-```{r fig.height = 6, fig.cap = "Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
+```{r fig.height = 6, fig.cap = "Figure 4: Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
 # computed in scripts/extract_item_weights_using_model_clarke.R
@@
 
-After removing them, we can see that individual differences in proximity tuning account for nearly all of the differences in predictability from person to person, and also between the *feature* and *conjunction* conditions.
+After removing them, we can see that individual differences in proximity tuning account for nearly all of the differences in predictability from person to person, and also between the *feature* and *conjunction* conditions (see Figure 4).
 
@@
 Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model.
-The lines give posterior samples from each indivdiaul observer."}
+The lines give posterior samples from each individual observer."}
 
@@
 
-```{r, message = FALSE, warning = FALSE, fig.cap="The relationship between the time taken to complete a trial and how predictible it is.
+```{r, message = FALSE, warning = FALSE, fig.cap="The relationship between the time taken to complete a trial and how predictable it is.
 Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model.
@@
 ```
-This relationship appears to hold true if you look at how long it takes participants to select individual targets as well.
+This relationship appears to hold true if you look at how long it takes participants to select individual targets as well (Figure 5).
 
-```{r, message = FALSE, warning = FALSE, fig.cap = "The relationship between the time taken to complete a single target selection and how predictible it is."}
+```{r, message = FALSE, warning = FALSE, fig.cap = "Figure 5: The relationship between the time taken to complete a single target selection and how predictable it is."}
 breaks = c(seq(0.1, 0.8,0.1),1, 1.5, 2, 3, 4, 5, 6)
@@
 
-Let's score every trial by how well the model captures behaviour, and then plot some different examples.
+Let's score every trial by how well the model captures behaviour (Figure 6), and then plot some different examples.
 
@@
 
-```{r fig.height=3.5, fig.cap = "Histogram of how predictiable individual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
+```{r fig.height=3.5, fig.cap = "Figure 6: Histogram of how predictiable individual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
 ggplot(a_trl, aes(prop_max)) + 
@@
 
-Let's plot some examples oh highly predictable (top 5%), typical (middle 10%) and unpredictable (bottom 5%) trials.
+Let's plot some examples of highly predictable (top 5%), typical (middle 10%) and unpredictable (bottom 5%) trials.
 
@@
 
-We can see that for these highly predictable trials, we make very few mistakes, and those mistakes that we do make appear to be related to some sort of shortest-path optimization on the part of the participant.
+We can see that for these highly predictable trials (Figure 7), we make very few mistakes, and those mistakes that we do make appear to be related to some sort of shortest-path optimization on the part of the participant.
 
-```{r fig.cap = "A random selection of *good* trials. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation."}
+```{r fig.cap = "Figure 7: A random selection of *good* trials. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation."}
 
@@
 
-Here are some typical trials. Possible we have the path-length minimization issue again.
+Here are some typical trials (Figure 8). Possible we have the path-length minimization issue again.
 
-```{r fig.cap = "A random selection of *typical* trials. Along with path-minimising behaviour, we can also see some disagreement around switching item type."}
+```{r fig.cap = "Figure 8: A random selection of *typical* trials. Along with path-minimising behaviour, we can also see some disagreement around switching item type."}
 plts2 <- map(1:3, plot_trial, trls_mid, a, d)
@@
 
-Now let's look at less predictable (bottom 5%-tile) trials. Even here, the model does a relatively good job.
+Now let's look at less predictable (bottom 5%-tile) trials (Figure 9). Even here, the model does a relatively good job.
 
-```{r fig.cap = "A random selection of *hard* trials. It is harder to make out much of a pattern here, but we can see that the human participants jump around more."}
+```{r fig.cap = "Figure 9: A random selection of *hard* trials. It is harder to make out much of a pattern here, but we can see that the human participants jump around more."}
 plts3 <- map(1:3, plot_trial, trls_hard, a, d)
@@
 
-- We will provide the model/simulation with the initial target selection.
+We will provide the model/simulation with the initial target selection.
 
-```{r, fig.height=3.5, fig.cap = "(*left*) Histogram comparing the empirical path lengths to simulations from our fitted model.
+```{r, fig.height=3.5, fig.cap = "Figure 10: (*left*) Histogram comparing the empirical path lengths to simulations from our fitted model.
 Difference indicates the human path length - the simulated path length.
@@
 
-We can see that overall, the model is not making substantially longer paths through the items than our human participants.
+We can see that overall, the model is not making substantially longer paths through the items than our human participants (Figure 10).
 However, there is some variability in that some participants routinely select paths shorter than our model would, and others do not.
 
-Perhaps this is related to predictability (i.e., how well the model can predict a participant's trial level behaviour)?
+Perhaps this is related to predictability (i.e., how well the model can predict a participant's trial level behaviour - Figure 11)?
 
-```{r fig.height=3, fig.cap = "(*left*) A histogram showing the proportion of trials on which each participant managed a shorter path through the targets than the model's prediction.
+```{r fig.height=3, fig.cap = "Figure 11: (*left*) A histogram showing the proportion of trials on which each participant managed a shorter path through the targets than the model's prediction.
 (*right*) Scatter plot showing the relationship between predictability (accuracy) and whether the model over or under estimates path length.
@@
 Previous work (Clarke and Tatler, 2014) has demonstrated that the initial fixation in scene viewing can be well described with truncated Gaussian distribution.
-Here we explore using a similar idea to account for starting locations.
+Here we explore using a similar idea to account for starting locations (Figure 12).
 
@@
 
-```{r fig.height = 3.5, fig.cap="(*left*) Density plot for initial target selections, over all participants and all trials.
+```{r fig.height = 3.5, fig.cap="Figure 12: (*left*) Density plot for initial target selections, over all participants and all trials.
 (*right*) Median $x$ and $y$ coordinates for the initial target selection for each participant."}
@@
 
-Can we model this as multi-level beta distribution? Yes, although it seems like people are in one of two clusters.
+Can we model this as multi-level beta distribution? Yes, although it seems like people are in one of two clusters (Figure 13).
 
-```{r fig.cap = "The mean posterior plot for the truncated normal distriubtions for (*left*) $x$ and (*right*) $y$.
+```{r fig.cap = "Figure 13: The mean posterior plot for the truncated normal distriubtions for (*left*) $x$ and (*right*) $y$.
 We can see that a two component mixture model will capture most of the variance in intial target selection.", warning = FALSE}
@@
 
-It looks like we can simplify the model somewhat by using a two component mixture model instead!
+It looks like we can simplify the model somewhat by using a two component mixture model instead (Figure 14).
 
-```{r, fig.height = 6, fig.cap = "(*top*) Beta distributions for $x$ and $y$ coordinated"}
+```{r, fig.height = 6, fig.cap = "Figure 14: (*top*) Beta distributions for $x$ and $y$ coordinated"}
 
@@
 
-Both models give a similar distribution of target weights and accuracies, and in both cases, participants who start in a corner are easier to predict.
+Both models give a similar distribution of target weights and accuracies, and in both cases, participants who start in a corner are easier to predict (Figure 15).
 
-```{r, fig.cap = "(Top): a count of initial weight values predicted from both methods (mixture and multi-level).
+```{r, fig.cap = "Figure 15:(Top): a count of initial weight values predicted from both methods (mixture and multi-level).
 (Bottom left): the proportion of times the first selection was correct for both methods.

### 2022-10-14 manuscriptRevisions2.tex
first pass at review comments

@@
 As can be seen in Figure \ref{fig:cal}, the model is putting somewhere between 25\% and 75\% of the weight on the target that is selected next, easily outperforming a chance $1/n$ baseline.
+There are also interesting differences between the two conditions: for example, in the conjunction condition, there is a clear 'jump' around target 20, which probably reflects the tendency for participants to forage in runs, selecting all exemplars of one target and then all exemplars of the other: there is a decrease in accuracy as people switch and then an increase again.
 We can also see that the model is well calibrated in that the probabilities assigned to the most likely target manage to capture how often that target is actually selected.
@@
 
-For trials in which the model does a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants.
+For trials in which the model does a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in terms of proximity in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants.
 We can see this more clearly in Figure \ref{fig:qjep_path_lengths}: while our model does a good job of capturing the average total path length, there is considerable variation with some participants generating shorter paths and some longer.
 We can see  that this appears to be systematically related to how well our model can predict behaviour.
+Interestingly, these poorly predicted example trials appear to have very strong pS biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well.
+This fits with conjunction trials being harder for the model to predict, as these trials generally have fewer switches.
 
@@
 In the current manuscript, we asked a more difficult question: could this model make target-by-target predictions, guessing which target would be picked next within a trial?
-Despite this being a relatively difficult task, we found that for some trials our model was over 80\% accurate, demonstrating that at least in some cases, participants' behaviour in this task is remarkably predictable.
+We found that for some trials our model was over 80\% accurate, demonstrating that at least in some cases, our model is able to make good predictions of target behaviour.
 
@@
 However, it is possible that there are other factors that we have not taken into account that could further help explain these discrepancies.
+Participants who 'stick' to one type of target are likely to have longer path lengths, and it seems that the model does do a poorer job of predicting conjunction trials, which generally have stronger pS biases.
+Thus, one area for future improvement of the model is to try to capture this behaviour better: it may be that a 'floor' parameter (on a participant-by-participant basis) in the spatial fall off, allocating more weight to more distant targets, may help account for currently difficult to predict trial behaviour.
+
+There are also many other factors that the model does not account for.
 For example, it is possible that relatively unpredictable participants use multiple rules and switch between them in ways that we are not currently captured in the model.

### 2022-10-26 manuscriptRevisions2.tex
stupid changes

@@
 
-with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$.
-This model is implemented in a multi-level framework, allowing each of the four parameters to vary from participant to participant.
+with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$ calculating the angular difference.
+$\text{atan2}$ is the direction of travel\footnote{For some reason, the editor insisted that re define atan2.
+This seems odd, as this is a simple funciton that children learn at school.
+But, it is a strange and varied world out there, so who knows.} This model is implemented in a multi-level framework, allowing each of the four parameters to vary from participant to participant.
 Further details including priors and full code can be found with \cite{clarke2022foraging}.

### 2022-10-27 Analysis/index_revisions_2.Rmd
minor edits

@@
   scale_y_continuous("model accuracy",  
-                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1)) -> plt_a
+                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1)) + 
+  theme(legend.position="none")-> plt_a
 
@@
 
-ggplot(fit_plt, aes(value, accuracy, colour = condition)) + 
+plt_b <- ggplot(fit_plt, aes(value, accuracy, colour = condition)) + 
   geom_point(aes(shape = is_outlier)) +
@@
   scale_shape_manual(values = c(19, 4), guide = "none") + 
-  facet_wrap(~parameter, scales = "free") +
-  theme(legend.position = "bottom")
+  facet_wrap(~parameter, scales = "free") #+
+  #theme(legend.position = "bottom")
 
-plt_b <- ggplot(filter(fit_plt, parameter == "bP"), 
-                aes(value, accuracy, colour = condition)) + 
-  geom_point(aes(shape = is_outlier)) +
-  geom_smooth(data = filter(fit_plt, is_outlier == 0, parameter == "bP"), method = "lm", formula = y ~ x, se = FALSE) + 
-  scale_shape_manual(values = c(19, 4), guide = "none") + 
-  xlab("bP parameter value") +
-  theme(legend.position = "none") + 
-   scale_y_continuous("model accuracy",  
-                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1))
+plt_b
+
+#plt_b <- ggplot(filter(fit_plt, parameter == "bP"), 
+#                aes(value, accuracy, colour = condition)) + 
+#  geom_point(aes(shape = is_outlier)) +
+#  geom_smooth(data = filter(fit_plt, is_outlier == 0, parameter == "bP"), method = "lm", formula = y ~ x, se = FALSE) + 
+#  scale_shape_manual(values = c(19, 4), guide = "none") + 
+#  xlab("bP parameter value") +
+#  theme(legend.position = "none") + 
+#   scale_y_continuous("model accuracy",  
+#                     limits = c(0.35, 0.8), breaks = seq(0.3, 0.8, 0.1))
 
@@
        plt_a + plt_b + 
-         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
+         plot_layout(widths = c(1, 2)), width = 12, height = 4)
 ```

### 2022-10-27 manuscriptRevisions2.tex
minor edits

--- 2022-10-14 manuscriptRevisions2.tex
@@
 
-with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$.
+with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$ calculating the angular difference.
+$\text{atan2}$ is the direction of travel from i to j.
 This model is implemented in a multi-level framework, allowing each of the four parameters to vary from participant to participant.
@@
 The dots indicate outliers.
-(\textit{right}) Accuracy of our model varies with the strength of an individual’s \textit{bP} parameter.
+(\textit{right}) How accuracy of our model varies with the strength of an individual’s \textit{bM}, \textit{bP}, \textit{pA} and \textit{pS} parameters.
 We can see two clear outlier participants (marked with an X).}

### 2022-11-01 Analysis/index_revisions_2.Rmd
getting ready for resubmission

@@
 # set ggplot2 options
-#theme_set(ggthemes::theme_tufte() + 
-#            theme(plot.background = element_rect(fill = "#fffff8", colour = "#fffff8")))
+theme_set(ggthemes::theme_tufte() + 
+            theme(plot.background = element_rect(fill = "#fffff8", colour = "#fffff8")))
 
 # for saving graphs for paper
-theme_set(ggthemes::theme_tufte(base_size = 16) + 
-            theme(plot.background = element_rect(fill = "#ffffff", colour = "#ffffff")))
+#theme_set(ggthemes::theme_tufte(base_size = 16) + 
+#            theme(plot.background = element_rect(fill = "#ffffff", colour = "#ffffff")))
 
@@
 
-ggsave("../Figures/qjep_preds.pdf", 
-       plt_b2 / (plt1 + plt2) + 
-       plot_layout(guides = "collect") & theme(legend.position = 'bottom'),
-       width = 10, height = 10)
+#ggsave("../Figures/qjep_preds.pdf", 
+#       plt_b2 / (plt1 + plt2) + 
+#       plot_layout(guides = "collect") & theme(legend.position = 'bottom'),
+#       width = 10, height = 10)
 
@@
 
-ggsave("../Figures/qjep_indiv_diff.pdf", 
-       plt_a + plt_b + 
-         plot_layout(widths = c(1, 2)), width = 12, height = 4)
+#ggsave("../Figures/qjep_indiv_diff.pdf", 
+#       plt_a + plt_b + 
+#         plot_layout(widths = c(1, 2)), width = 12, height = 4)
 ```
@@
 
-ggsave("../Figures/trial_time.png", plt + theme_bw() + theme(legend.position = "none"), width = 4, height = 6)
+#ggsave("../Figures/trial_time.png", plt + theme_bw() + theme(legend.position = "none"), width = 4, height = 6)
 
@@
 
-ggsave("../Figures/targ_time.png", width = 7, height = 4)
+#ggsave("../Figures/targ_time.png", width = 7, height = 4)
 
@@
 create_post_plot("x") + create_post_plot("y") + plt_mu #& theme_bw()
-ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
+#ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
 ```
@@
 
-ggsave("../Figures/qjep_init_sel_preds.pdf",
-       width = 8, height = 4)
+#ggsave("../Figures/qjep_init_sel_preds.pdf",
+#       width = 8, height = 4)
 

### 2022-11-01 Analysis/functions/plot_trial.R

@@ -28,12 +28,12 @@ plot_trial <- function(id, trls, as, d) {
   
   mistakes_xy <- map_df(1:nrow(mistakes), mistake_x_y, trl, mistakes)
   
-  p <- ggplot(trl, aes(x, y)) +
+  p <- ggplot(trl, aes(x, -y)) +
     geom_text_repel(aes(label = found)) + 
     geom_path(colour = "darkgrey") +
     geom_point(aes(colour = targ_type, shape = targ_type), size = 4) +
     geom_segment(data = mistakes_xy, size = 1,
-                 aes(x = x1, y = y1, xend = x2, yend = y2), colour = "darkred",
+                 aes(x = x1, y = -y1, xend = x2, yend = -y2), colour = "darkred",
                  arrow = arrow(length = unit(0.1, "inches"))) + 
     theme_void() + theme(legend.position = "none") + 
     coord_fixed() + 

### 2022-11-08 Proofs/vision-1871367-proofreading.tex
proofs

--- 2022-10-14 manuscriptRevisions2.tex
@@
 %=================================================================
-\documentclass[preprints, article,submit,pdftex,moreauthors]{Definitions/mdpi} 
+\documentclass[vision,article,accept,pdftex,moreauthors]{Definitions/mdpi} 
 % For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
@@
 \copyrightyear{2022}
-%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
-\datereceived{} 
-\dateaccepted{} 
+\externaleditor{Academic Editor:}
+
+\datereceived{01 August 2022} 
+\dateaccepted{02 November 2022} 
 \datepublished{} 
@@
 % Full title of the paper (Capitalized)
-\Title{A Bayesian statistical model is able to predict target-by-target selection behaviour in a human foraging task}
+\Title{A Bayesian Statistical Model Is Able to Predict Target-by-Target Selection Behaviour in a Human Foraging Task}
 
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{Title}
+\TitleCitation{A Bayesian Statistical Model Is Able to Predict Target-by-Target Selection Behaviour in a Human Foraging Task}
 
@@
 % Authors, for the paper (add full first names)
-\Author{Alasdair D.F. Clarke $^{1}$\orcidA{}, Amelia R. Hunt $^{2}$\orcidB{} and Anna E. Hughes\orcidC{} $^{1,}$*}
+\Author{\hl{Alasdair D.F. Clarke} $^{1,}$\hl{*}\orcidA{}, Amelia R. Hunt $^{2}$\orcidB{} and Anna E. Hughes~\orcidC{} $^{1}$}
+%MDPI: Please carefully check the accuracy of names and affiliations.
+Please make sure the Address information is sorted from subordinate to superior: Center / Laboratory / Group / Programme / Unit < Department / Division / Faculty / Campus / Institute / School < College / University
 
-%\longauthorlist{yes}
+%MDPI: According to our system, the correct correspondence author is Alasdair Clarke. Please confirm. RESPONSE: Yes, confirmed.
+%MDPI:This is an important note to let you know that to protect the privacy of the author's contact information, we will only display the corresponding authors' contact information on the published paper.
+However, we hope the contact information of the other authors can also be confirmed or corrected during the proofreading stage, which will be recorded in our database to furnish the author's integrated publication history and also contribute to our future communications.
+RESPONSE: Okay, all confirmed.
 
@@
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Clarke, A.D.F.; Hunt, A.; Hughes, A.E.}
+\AuthorCitation{Clarke, A.D.F.; Hunt, A.R.; Hughes, A.E.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 \address{%
-$^{1}$ \quad Department of Psychology, University of Essex, Wivenhoe Park, Colchester, UK, CO4 3SQ\\
-$^{2}$ \quad School of Psychology, University of Aberdeen, King's College, Aberdeen, UK, AB24 3FX}
+$^{1}$ \quad Department of Psychology, University of Essex, Wivenhoe Park, Colchester~CO4 3SQ,~UK; \hl{anna.hughes@essex.ac.uk} \\
+%MDPI: added the emails from the submitting system, please confirm. RESPONSE: Confirmed.
+
+$^{2}$ \quad School of Psychology, University of Aberdeen, King's College, Aberdeen~AB24 3FX,~UK; \hl{a.hunt@abdn.ac.uk} }
 
@@
 
-% Abstract (Do not insert blank lines, i.e. \\) 
+% Abstract (Do not insert blank lines, i.e., \\) 
 \abstract{Foraging refers to search involving multiple targets or multiple types of targets, and as a model task has a long history in animal behaviour and human cognition research.
@@
 % Keywords
-\keyword{foraging; visual search; bayesian model; decision; strategy.}
+\keyword{foraging; visual search; bayesian model; decision; strategy}
 
@@
 
-Foraging, the act of searching for and gathering multiple targets (such as food), has been studied in both non-human animal contexts \cite{dawkins1971} and in human psychology studies \cite{kristjansson2014}.
+\hl{Foraging}, the act of searching for and gathering multiple targets (such as food), has been studied in both nonhuman animal contexts \cite{dawkins1971} and in human psychology studies~\cite{kristjansson2014}.
 Foraging engages a wide range of different perceptual, cognitive, decision-related and motor skills, and is an ecologically relevant behaviour for most species, including humans.
@@
 There has also been a concerted effort to characterize the spatial patterns of foraging behaviour.
-The Lévy Walk, for example, has been argued to be a good description of the foraging path many species take when the locations of targets are unknown (e.g.
-\citep {bartumeus2005}, but see also \citep{benhamou2007}).
+The Lévy Walk, for example, has been argued to be a good description of the foraging path many species take when the locations of targets are unknown (e.g., \citep {bartumeus2005}, but see also \citep{benhamou2007}).
+%MDPI:Please make sure that all genes and species names as well as all the variables like "p" or "n" are written in italic font.
+Protein names, Latin words and genera/families should be kept in a normal font.
+Greek/Latin expressions and non-common foreign words and phrases should NOT be in Italic format.
+%MDPI:  Abbreviations need to be defined, on their first mention, once in the Abstract, once in the Main Text, once in Figures' description, and once in the Tables' footer.
+Abbreviations used as keywords should be defined too.Please check and make sure that this rule is applied through the whole paper.
 
@@
 As a result, foragers tend to search in “runs” of one type of target before switching to another.
-In humans, this behaviour has been studied using computer-based displays of targets and distractors (e.g.
-\citep{ kristjansson2014}), in which participants must “collect” targets (by clicking or tapping on them) and ignore distractors.
+In humans, this behaviour has been studied using computer-based displays of targets and distractors (e.g., \citep{kristjansson2014}), in which participants must “collect” targets (by clicking or tapping on them) and ignore distractors.
 When targets can be identified based on a single, easily distinguishable feature (for example, find all the red and green shapes and ignore the blue and yellow shapes) participants tend to switch frequently between different types of targets, taking a relatively efficient path through the array.
-In contrast, when targets are defined based on a combination of more than one feature (e.g.
-find all the red squares and green circles and ignore the red circles and green squares), participants tend to switch far less frequently, often selecting all the targets of one category and then all the targets of the other.
+In contrast, when targets are defined based on a combination of more than one feature (e.g., find all the red squares and green circles and ignore the red circles and green squares), participants tend to switch far less frequently, often selecting all the targets of one category and then all the targets of the other.
 Consequently, the path taken to collect the targets is less efficient.
@@
 To address the need for a more precise set of measurements, we recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022foraging}.
-By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully re-analyse data from a number of open access datasets \cite{kristjansson2014, thornton2020, clarke2022, tagu_kristjansson_2021}.
+By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully reanalyse data from a number of open access datasets \cite{kristjansson2014, thornton2022, clarke2022, tagu_kristjansson_2021}.
 
-While our model is able to do a good job of allowing us to understand biases at the level of a trial (e.g.
-conjunction vs.
+While our model is able to do a good job of allowing us to understand biases at the level of a trial (e.g., conjunction vs.
 feature search differences \cite{kristjansson2014} or the influence of high value targets compared to low value targets \cite{tagu2020}), we did not originally investigate to what extent our model was able to predict target-by-target behaviour within any given trial.
@@
 Can it predict exactly which target a participant will pick next?
-And if the model makes mistakes, can we understand where it is failing, in order to improve our understanding of how human foraging behaviour operates?
+If the model makes mistakes, can we understand where it is failing, in order to improve our understanding of how human foraging behaviour operates?
 
@@
 
-We will make use of the foraging model from Clarke et al (2022) \cite{clarke2022foraging}.
+We will make use of the foraging model from Clarke et al.
+(2022) \cite{clarke2022foraging}.
 This treats foraging as a sampling without replacement process in which each item $i$ has probability $p_i$ of being selected as the next target.
@@
 \begin{itemize}
-    \item $b_A$ - preference for selecting items of type $A$ rather than $B$.
-    \item $b_S$ - preference for selecting items of the same type as the previously selected item.
-    \item $\sigma_d$ - preference for selecting items close to the previously selected item.
-    \item $\sigma_{\theta}$ - preference to keep selecting items along a straight line versus changing direction.
+    \item $b_A$---preference for selecting items of type $A$ rather than $B$.
+    \item $b_S$---preference for selecting items of the same type as the previously selected item.
+    \item $\sigma_d$---preference for selecting items close to the previously selected item.
+    \item $\sigma_{\theta}$---preference to keep selecting items along a straight line versus changing direction.
 \end{itemize}
@@
 These combine to give:
-
 \begin{linenomath}
@@
 \end{linenomath}
-
 where $t_i = 1$ if item $i$ is of class $A$ and 0 otherwise, and  $m(t_i, t_{i-1}) =1$ if item $i$ is the same class as the previously selected item.
-$\rho_d$ and $\rho_{\theta}$ measure proximity and the effect of direction:
-
+$\rho_d$ and $\rho_{\theta}$ measure proximity and the effect of~direction:
 \begin{linenomath}
@@
 \end{linenomath}
-
 \begin{linenomath}
@@
 \end{linenomath}
-
 $d(i,j)$ is simply the Euclidean distance between items $i$ and $j$, while $\theta$ is defined as:
-
 \begin{linenomath}
@@
 \end{linenomath}
-
-with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$.
-This model is implemented in a multi-level framework, allowing each of the four parameters to vary from participant to participant.
+with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$ calculating the angular difference.
+$\text{atan2}$ is the direction of travel from i to j.
+This model is implemented in a multilevel framework, allowing each of the four parameters to vary from participant to participant.
 Further details including priors and full code can be found with \cite{clarke2022foraging}.
 
-Note: while our model returns estimates of full posterior probability distribution for each parameter, to reduce computational complexity and make it easier to compare to the empirical data, we will work with the means of these distributions for our parameter values.
+Note: while our model returns estimates of full posterior probability distribution for each parameter, to reduce computational complexity and make it easier to compare to the empirical data, we will work with the means of these distributions for our parameter~values.
 
-\subsection{Software environment}
+\subsection{Software Environment}
 
-We mainly used R v4.2.0 and rStan v2.26.11 \cite{rstan}. For fitting the model to the data from \cite{clarke2022} we used a university computing cluster with R v3.6.3 and rStan v2.19.2.
+We mainly \hl{used} R v4.2.0 and rStan v2.26.11 \cite{rstan} (R Foundation for Statistical Computing, Vienna, Austria).
+For fitting the model to the data from~\cite{clarke2022} we used a university computing cluster with R v3.6.3 and rStan v2.19.2.%MDPI:For all equipment/software/products used, the following information should be given: company name, city, state abbreviation (if its from USA or Canada), and country must be provided.
+Please apply this rule through the whole Materials and Methods section
 
@@
 To assess how well our model can account for behaviour at the level of individual trials, we start by stepping through each trial in the data from Clarke and colleagues \cite{clarke2022}.
-For each target selection\footnote{Note: for the reasons discussed above, we ignore the initial target selection for now, as the model has very little to say about it.
-We return to this issue in section 4.}, in each trial, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model.
+For each target selection \hl{(}Note: for the reasons discussed above, we ignore the initial target selection for now, as the model has very little to say about it.
+We return to this issue in Section \ref{s4}\hl{)}, %MDPI: footer is not allowed in this type article, we moved it to the (), please confirm.
+RESPONSE: Confirmed
+in each trial, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model.
 As can be seen in Figure \ref{fig:cal}, the model is putting somewhere between 25\% and 75\% of the weight on the target that is selected next, easily outperforming a chance $1/n$ baseline.
-There are also interesting differences between the two conditions: for example, in the conjunction condition, there is a clear 'jump' around target 20, which probably reflects the tendency for participants to forage in runs, selecting all exemplars of one target and then all exemplars of the other: there is a decrease in accuracy as people switch and then an increase again.
+There are also interesting differences between the two conditions.
+For example, in the conjunction condition, there is a clear 'jump' around target 20, which probably reflects the tendency for participants to forage in runs, selecting all exemplars of one target and then all exemplars of the other: there is a decrease in accuracy as people switch and then an increase again.
 We can also see that the model is well calibrated in that the probabilities assigned to the most likely target manage to capture how often that target is actually selected.
@@
 \begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
 \centering
-\includegraphics[width=12 cm]{Figures/qjep_preds.pdf}
-\caption{(\textit{top left}) Posterior probabilities for target selections during a visual foraging task.
+\includegraphics[width=17.8 cm]{Figures/qjep_preds.pdf}
+\end{adjustwidth}
+\caption{({\textbf{\hl{top left}}}) Posterior probabilities for target selections during a visual foraging task.
 Each dot shows the data from an individual participant, averaged over trials, in the feature condition and the shaded region indicates the interval in which we expect 67\% of participants to fall.
 The dashed line indicates chance performance.
-(\textit{top right}) As top left, except showing the conjunction condition.
-(\textit{bottom left})  Calibration plot for our foraging model.
+(\textbf{\hl{top right}}) As top left, except showing the conjunction condition.
+(\textbf{\hl{bottom left}})  Calibration plot for our foraging model.
 The $x$-axis gives the largest weight assigned by the model while the $y$-axis shows how often that target was actually selected by a human participant.
 The dashed line here and in the right plot is the identity line.
-(\textit{bottom right}) This plot shows how often the model selects the 2nd and 3rd ranked items based on the weights assigned by the model.}
+(\textbf{\hl{bottom right}}) This plot shows how often the model selects the 2nd and 3rd ranked items based on the weights assigned by the model.} %mdpi: we removed the subfigure label from italic to be not italic and added bold of it according to our rule, please confirm, same in below figures.
+RESPONSE: Confirmed.
+
+% Also, please divide the figure into 4 subfigures and  note them accordingly.
+Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
+Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+
+%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
+If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.
+Thank you for your cooperation!
+RESPONSE: We confirm that all the figures are original.
+
 \label{fig:cal}
@@
 
-We summarise accuracy for each person by calculating the mean proportion of times the model assigns the most weight to the item that was then selected for each participant\footnote{This metric isn't perfect as it averages over all target selections within a trial, and these clearly have different baseline probabilities ($2.5\%-100\%$).
-However, it has the upside of being more intuitive than anything else we could think of.}.
+We summarise accuracy for each person by calculating the mean proportion of times the model assigns the most weight to the item that was then selected for each participant \hl{(}This metric isn't perfect as it averages over all target selections within a trial, and these clearly have different baseline probabilities: 2.5--100\%.
+However, it has the upside of being more intuitive than anything else we could think of\hl{)}.
+%MDPI: footer is not allowed in this type article, we moved it to the (), please confirm.
+RESPONSE: Slightly modified, but confirmed.
 These accuracy scores can be compared to our uniform chance baseline that gives a value of $10.9\%$ over the course of a trial.
@@
 However, interestingly, we find that this variability can be explained by our model parameters: nearly all of the differences between different participants, as well as the within-participant differences in the feature and conjunction conditions, can be explained by the $bP$ parameter, which is our proximity bias.
-The model does a better job of predicting which will be selected next when there is a stronger proximity bias (see \textit{Supplementary Materials: Part 1} for more details).
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=12 cm]{Figures/qjep_indiv_diff.pdf}
-\caption{(\textit{left}) Prediction scores for participants.
-Boxplots show quartile range and the grey lines indicate individual participants.
-The dots indicate outliers.
-(\textit{right}) Accuracy of our model varies with the strength of an individual’s \textit{bP} parameter.
-We can see two clear outlier participants (marked with an X).}
-\label{fig:cal2}
-\end{figure}
+The model does a better job of predicting which will be selected next when there is a stronger proximity bias (see {\hl{Supplementary Materials: Part 1}} for more details).
 
@@
 \begin{figure}[H]
-\centering
+\includegraphics[width=13.5 cm]{Figures/qjep_indiv_diff.pdf}
+\caption{({\textbf{\hl{left}}}) Prediction scores for participants.
+Boxplots show quartile range and the grey lines indicate individual participants.
+The dots indicate outliers.
+(\textbf{\hl{right}}) How accuracy of our model varies with the strength of an individual’s \textit{bM}, \textit{bP}, \textit{pA} and \textit{pS} parameters.
+We can see two clear outlier participants (marked with an X).} %MDPI: please divide the figure into 2 subfigures and  note them accordingly.
+Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
+Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
+If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.Thank you for your cooperation!
+RESPONSE: Confirmed.
+
+\label{fig:cal2}
+\end{figure}   
+\vspace{-12pt}
+
+\begin{figure}[H]
 \includegraphics[width=12 cm]{Figures/qjep_ex_paths.pdf}
-\caption{(\textit{top}) Two randomly selected trials in which the model does a good job in accounting for human behaviour.
+\caption{(\textbf{\hl{top}}) Two randomly selected trials in which the model does a good job in accounting for human behaviour.
 The numbers indicate the order the participant selected targets in.
@@
 When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation.
-(\textit{bottom}) Two randomly selected examples in which the model does a less good job in accounting for the order in which human participants selected the items.}
+(\textbf{\hl{bottom}}) Two randomly selected examples in which the model does a less good job in accounting for the order in which human participants selected the items.}%MDPI: please divide the figure into subfigures and  note them accordingly.
+Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
+Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+Please add explanation for all the symbols/colors
+%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
+If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.
+Thank you for your cooperation!
+RESPONSE: Confirmed
+
 \label{fig:qjep_paths}
@@
 We can see  that this appears to be systematically related to how well our model can predict behaviour.
-Interestingly, these poorly predicted example trials appear to have very strong pS biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well.
+Interestingly, in some cases, poorly predicted trials appear to have very strong pS biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well.
 This fits with conjunction trials being harder for the model to predict, as these trials generally have fewer switches.
+\vspace{-10pt}
+\begin{figure}[H]
+\includegraphics[width=13.5 cm]{Figures/path_length.pdf}
+\caption{({\textbf{\hl{left}}}) Histogram showing the distribution of the median path lengths for our human participants and model (fitted to each human participant via the random effect structure).
+(\textbf{\hl{right}}) The relationship between model accuracy and the proportion of trials in which the human participant has a shorter total path length than predicted.}%MDPI:please divide the figure into 2 subfigures and  note them accordingly.
+Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
+Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
+If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.
+Thank you for your cooperation!
+RESPONSE: Confirmed
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=12 cm]{Figures/path_length.pdf}
-\caption{(\textit{left}) Histogram showing the distribution of the median path lengths for our human participants and model (fitted to each human participant via the random effect structure).
-(\textit{right}) The relationship between model accuracy and the proportion of trials in which the human participant has a shorter total path length than predicted.}
 \label{fig:qjep_path_lengths}
@@
 
-\section{Improving the model: location of the first target selection}
+\section{Improving the Model: Location of the First Target Selection \label{s4}}
 
-One weakness of the foraging model by Clarke et al (2022) \cite{clarke2022foraging} is that it makes little attempt to predict which item will be selected first.
+One weakness of the foraging model by Clarke et al.
+(2022) \cite{clarke2022foraging} is that it makes little attempt to predict which item will be selected first.
 In this section we aim to improve this by modelling participant bias (or preference) in their choice of initial target selection.
-Our approach is inspired by previous work on the central bias in scene viewing \cite{clarke_tatler2014, clarke2017}.
+Our approach is inspired by previous work on the central bias in scene viewing \cite{clarke2014deriving, clarke2017}.
 These studies fit truncated Gaussian distributions to the  $(x,y)$ coordinates of fixation locations.
-Here we will do similar, and fit beta distributions\footnote{We use beta distributions here as it is difficult to specify a mixture model using truncated Gaussians in Stan.
-However, beta distributions may well be a more appropriate choice.} to locations of the initial target selections in the visual foraging task.
+Here we will do similar, and fit beta distributions \hl{(}We use beta distributions here as it is difficult to specify a mixture model using truncated Gaussians in Stan.
+However, beta distributions may well be a more appropriate choice\hl{)} %MDPI: footer is not allowed in this type article, move it to the (), please confirm.
+RESPONSE: Confirmed.
+to locations of the initial target selections in the visual foraging task.
 
@@
 This appears to be due to different participants choosing to utilise different strategies rather than within-subject variation.
-However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see \textit{Supplementary Materials: Part 1}).
-We try two different modelling approaches (multi-level and mixture) to assess whether the less complex mixture model is able to account for the patterns of starting positions seen.
+However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see {\hl{Supplementary Materials: Part 1}}).
+We try two different modelling approaches (multilevel and mixture) to assess whether the less complex mixture model is able to account for the patterns of starting positions seen.
 
 \begin{figure}[H]
-\centering
 \includegraphics[width=12 cm]{Figures/init_sel_hex_plot.pdf}
@@
 Grey areas indicate cells with a count of 0.
-(\textit{left}) shows the distribution over all initial target selections (i.e.
-multiple trials per participant) while (\textit{right}) shows the distribution of each participant's median initial selection (i.e.
-each participant contributes one data point to the graph).
-}
+({\textbf{\hl{left}}}) shows the distribution over all initial target selections (i.e., multiple trials per participant) while ({\textbf{\hl{right}}}) shows the distribution of each participant's median initial selection (i.e., each participant contributes one data point to the~graph).
+}%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
+If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.
+Thank you for your cooperation!
+RESPONSE: Confirmed.
+
 \label{fig:qjep_init_sel_hex}
@@
 
-\subsection{Multi-level Modelling Results}
+\subsection{Multi-Level Modelling Results}
 
-We first consider a multi-level model in which we fit beta distributions to the $x$ and $y$ coordinates of each participant's initial target selections\footnote{Full details of the analysis can be found in the \textit{Supplementary Materials: Part 1}.}:
-
+We first consider a multi-level model in which we fit beta distributions to the $x$ and $y$ coordinates of each participant's initial target selections \hl{(}Full details of the analysis can be found in the \hl{Supplementary Materials: Part 1}\hl{)}:%MDPI: footer is not allowed in this type article, move it to the (), please confirm.
+RESPONSE: Confirmed
 \begin{equation}
@@
 The results are shown in Figure \ref{fig:qjep_init_sel_mdl} and we can clearly see that most participants either have a strong bias to $x=0$ and $y=0$, or a more diffuse central bias. 
+\vspace{-6pt}
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}
+\centering
+\includegraphics[width=17.5 cm]{Figures/init_sel_mdl.pdf}
+\end{adjustwidth}
+\caption{Posterior fits for ({\textbf{\hl{left}}}) horizontal and ({\textbf{\hl{middle}}}) vertical locations of the initial target selection.
+Each line represents a different participant.
+({\textbf{\hl{right}}}) A scatter plot showing the $x$ and $y$ posterior means for each participant.}%MDPI: please divide the figure into 3 subfigures and  note them accordingly.
+Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
+Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
+If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.
+Thank you for your cooperation!
+RESPONSE: Confirmed
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=12 cm]{Figures/init_sel_mdl.pdf}
-\caption{Posterior fits for (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection.
-Each line represents a different participant.
-(\textit{right}) A scatter plot showing the $x$ and $y$ posterior means for each participant.}
 \label{fig:qjep_init_sel_mdl}
@@
 Given that the majority of our participants appear to be following one of two distinct strategies, we can potentially simplify our model by using a two-component mixture model:
-
+\clearpage
 \begin{equation}
@@
 This reduces the number of parameters to eight (to specify the two Beta distributions) and then one $\lambda$ value per participant (= 66 in our dataset).
-While the formulae in Equations \ref{eq:beta2x} and \ref{eq:beta2y} appear more complex than those in Equations \ref{eq:beta1x} and \ref{eq:beta1y}, the model requires less than a quarter as many free parameters.
+While the formulae in Equations \eqref{eq:beta2x} and \eqref{eq:beta2y} appear more complex than those in Equations \eqref{eq:beta1x} and \eqref{eq:beta1y}, the model requires less than a quarter as many free parameters.
 
@@
 We can also see from the lambda values that our participants take on a range of different mixtures between the two.
+\vspace{-12pt}
+\begin{figure}[H]
+\begin{adjustwidth}{-\extralength}{0cm}%\centering
+\centering
+\includegraphics[width=1.3\textwidth]{Figures/init_sel2_mdl.pdf}
+\end{adjustwidth}
+\caption{Posterior fits for the ({\textbf{\hl{left}}}) horizontal and ({\textbf{\hl{middle}}}) vertical locations of the initial target selection.
+({\textbf{\hl{right}}}) shows the mixing parameters for each participant, with the error bar indicating the $95\%$ HDPI.}%MDPI:Please define "x" and "y" from subfigures 1 and 2.
+Also, please divide the figure into 3 subfigures.
+Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
+Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
+If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.
+Thank you for your cooperation!
+RESPONSE: Confirmed
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=\textwidth]{Figures/init_sel2_mdl.pdf}
-\caption{Posterior fits for the (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection.
-(\textit{right}) shows the mixing parameters for each participant, with the error bar indicating the $95\%$ HDPI.}
 \label{fig:qjep_init2_sel_mdl}
@@
 
-To compare the two approaches, we assess how well they fit the empirical data: we can use the fitted distributions to calculate the weight assigned to the selected target by each method for each trial in our dataset (Figure \ref{fig:qjep_init_sel_pred}).
+To compare the two approaches, we assess how well they fit the empirical data: we can use the fitted distributions to calculate the weight assigned to the selected target by each method for each trial in our dataset (\hl{Figure} \ref{fig:qjep_init_sel_pred}).
 We can see that both models give a similar distribution of target weights and accuracies.
@@
 Interestingly, as above, there is considerable variation between participants, with participants who favour the top-left corner being easier to predict.
+%MDPI: Please move Figure 8 right after this paragraph ends(Figures and tables need to appear in exact numerical order, right after their first citation)
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=12 cm]{Figures/qjep_init_sel_preds.pdf}
-\caption{(\textit{Top}): a count of initial weight values predicted from both methods (mixture and multi-level).
-(\textit{Bottom left}): the proportion of times the first selection was correct for both methods.
-(\textit{Bottom right}): as lambda (the model parameter underlying initial weight) increases, accuracy increases i.e.
-the model is more accurate for the cases where participants are selecting a corner as their initial target selection.}
-\label{fig:qjep_init_sel_pred}
-\end{figure}
-
-\subsection{Replication: \cite{kristjansson2014} dataset}
-
+\subsection{Replication} 
+%mdpi: ref citation can not be in the section title, please move it to the main text. RESPONSE: Done.
 To test how well our methods generalise, we used the dataset from \citep{kristjansson2014}.
-We split this into a training dataset (50\% of the original data i.e.
-10 trials per participant) and a test dataset (the remaining 50\% of the data).
+We split this into a training dataset (50\% of the original data i.e., 10 trials per participant) and a test dataset (the remaining 50\% of the data).
 The foraging model is fit on the training dataset, and the parameters from this model are then used to predict behaviour at the level of individual trials.
@@
 One interesting difference compared to \citep{clarke2022} is in initial target selection: while there was a strong bias towards starting in a corner, there was little evidence of central bias, perhaps because this experiment was completed on an iPad.
-Further details and graphs can be found in the \textit{Supplementary Materials: Part 2}.
+Further details and graphs can be found in the \hl{Supplementary Materials: Part 2}.
+
+\begin{figure}[H]
+\includegraphics[width=13.8 cm]{Figures/qjep_init_sel_preds.pdf}
+\caption{({\textbf{\hl{Top}}}): a count of initial weight values predicted from both methods (mixture and multi-level).
+({\textbf{\hl{Bottom left}}}): the proportion of times the first selection was correct for both methods.
+({\textbf{\hl{Bottom right}}}): as lambda (the model parameter underlying initial weight) increases, accuracy increases i.e., the model is more accurate for the cases where participants are selecting a corner as their initial target selection.
+The dots each represent an individual participant, and the line is the line of best fit.}% MDPI: please divide the figure into 2 subfigures and  note them accordingly.
+Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
+Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+%MDPI: Please provide a short explanation for the black dots from the 3rd subfigure RESPONSE: Done
+%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
+If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.
+Thank you for your cooperation!
+RESPONSE: Confirmed
+
+\label{fig:qjep_init_sel_pred}
+\end{figure}
 
@@
 If this is the case, we might expect that model predictability should correlate with how good people are at the task.
-There is some evidence that on a trial-by-trial basis, shorter trials are easier for the model to predict, and on a target-by-target basis, faster moves from one target to the next are more easily predicted by the model (see \textit{Supplementary Materials: Part 1}).
+There is some evidence that on a trial-by-trial basis, shorter trials are easier for the model to predict, and on a target-by-target basis, faster moves from one target to the next are more easily predicted by the model (see \hl{Supplementary Materials: Part 1}).
 This likely is linked to the fact that our model is better at predicting participants with a stronger proximity bias, as targets that are closer to the previous target are also likely to be selected more quickly.
@@
 There has been some previous work on within-trial behaviour in the context of foraging.
-For example, \citep{tagu2020} found that inter-target times vary across a trial (with targets selected later in the trial being slower) and inter-target distances also vary (with targets selected later in the trial having greater inter-target distances).
+For example, \citep{tagu2020} found that intertarget times vary across a trial (with targets selected later in the trial being slower) and intertarget distances also vary (with targets selected later in the trial having greater intertarget distances).
 Similarly, \citep{thornton2022foraging} showed that switches between target categories can be characterised by a change in foraging 'tempo', and if participants are forced to forage at a particular speed, by asking them to synchronise with an auditory signal, higher tempos led to a systematic decrease in the probability of participants switching between target categories.
@@
 Could this help to explain some of the mistakes the model makes?
-Overall, the model doesn't seem to make substantially longer paths through the items than the human participants.
+Overall, the model does not seem to make substantially longer paths through the items than the human participants.
 However, there is a relationship between model accuracy and the proportion of times that participants select paths shorter than the model: as model accuracy increases, people seem to be more likely to have paths shorter than the model predicts.
@@
 Another possibility is that participants may make exploratory, information-seeking visits to different parts of the array due to uncertainty about the targets present: this may be particularly important for conjunction trials, where peripheral visual information about shape is likely to be poorer.
-Finally, the displays had artificial discontinuities (i.e.
-screen edges) which may lead to different behaviour in different participants: some may carry out the task as if they are reading, reaching the right hand edge and then swinging back to the left, whereas others may 'bounce' off an edge they have just reached.
+Finally, the displays had artificial discontinuities (i.e., screen edges) which may lead to different behaviour in different participants: some may carry out the task as if they are reading, reaching the right hand edge and then swinging back to the left, whereas others may 'bounce' off an edge they have just reached.
 Our model may well be able to predict the latter, but make less good predictions for the former behaviour.
@@
 To a large extent, initial item selection strategy seems to be stable within a participant, with people either starting in the corner or the centre of the screen.
-Our model is therefore also relatively accurate for selecting the initial target, selecting the correct target in around half of the trials (with a mixture model performing similarly to a multi-level model with many more parameters).
+Our model is therefore also relatively accurate for selecting the initial target, selecting the correct target in around half of the trials (with a mixture model performing similarly to a multilevel model with many more parameters).
 Participants who prefer the top left corner were easiest to predict, probably because these participants formed the majority group in this experiment.
 Our results are congruent with \citep{kristjansson2022moving}, who found a bottom left bias in a 3D environment.
-They suggest this may be an advantageous strategy because it allows your foraging to be more organised (e.g.
-in an 'S-shape', as has been found in real world search tasks \citep{riggs2017importance}).
+They suggest this may be an advantageous strategy because it allows your foraging to be more organised (e.g., in an 'S-shape', as has been found in real world search tasks \citep{riggs2017importance}).
 The smaller group of participants who prefer to start in the centre of the screen may be displaying similar behaviour to the well-known central bias in eye movements \citep{tatler2007central, tseng2009quantifying, clarke2014deriving} However, it is worth noting that these findings probably depend strongly on the context of the task.
@@
 It is also good at predicting where participants will start on a trial.
-The model finds it more difficult to predict 'discontinuous' jumps, which could be caused by a range of factors: a more difficult foraging task (e.g.
-conjunction searches), local path length minimisation, inattention, or aspects of the physical search space (e.g.
-edges of the screen).
-However, it would be possible to extend the model to incorporate these factors e.g.
-by incorporating a heuristic that would allow for local path minimisation, or introducing time as a predictor in the model.
+The model finds it more difficult to predict 'discontinuous' jumps, which could be caused by a range of factors: a more difficult foraging task (e.g., conjunction searches), local path length minimisation, inattention, or aspects of the physical search space (e.g., edges of the screen).
+However, it would be possible to extend the model to incorporate these factors e.g., by incorporating a heuristic that would allow for local path minimisation, or introducing time as a predictor in the model.
 Our findings also suggest possible future directions for empirical work, such as evaluating the effect of inattention on foraging behaviour, or how the foraging targets are organised in space.
@@
 %% optional
-%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
+\supplementary{\hl{The following are available online at} \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
+%mdpi: please fully complete this part with information regarding  supplementary materials, as shown in the above example.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Conceptualization, A.D.F.C., A.R.H.
-and A.E.H.; methodology, A.D.F.C.; software, A.D.F.C.; formal analysis, A.D.F.C.; data curation, A.D.F.C., and A.E.H.; writing---original draft preparation, A.D.F.C.; writing---review and editing, A.R.H.
+\authorcontributions{Conceptualization, A.D.F.C., A.R.H., and A.E.H.; methodology, A.D.F.C.; software, A.D.F.C.; formal analysis, A.D.F.C.; data curation, A.D.F.C.
+and A.E.H.; writing---original draft preparation, A.D.F.C.; writing---review and editing, A.R.H.
 and A.E.H.; visualization, A.D.F.C.
@@
 and A.R.H.
-All authors have read and agreed to the published version of the manuscript.}
+\hl{All authors} have read and agreed to the published version of the manuscript.}%MDPI: Please make sure all the authors were mentioned in this section RESPONSE: Confirmed
 
-\funding{This research was funded by the Economic and Social Research Council grant number ES/S016120/1 to A.D.F.C and A.R.H.}
+\funding{This research was funded by the Economic and Social Research Council grant number ES/S016120/1 to A.D.F.C. and A.R.H.}
 
@@
 \dataavailability{Data supporting reported results can be found on Github at XXX.
-The datasets analysed in this study can be found at \url{https://osf.io/y6qbv/} and \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0100752}.}
+The datasets analysed in this study can be found at \url{https://osf.io/y6qbv/}, \hl{accessed on}, and \linebreak  \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0100752}, \hl{accessed on}.}
+%MDPI: Please add the access date (Format: Date Month Year). e.g., (accessed on 1 January 2020).
 
-\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
-This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}
+\acknowledgments{\hl{The authors would like to thank all the researchers who publicly shared their data.}}%mdpi: In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
+This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).
+RESPONSE: Done.
 
@@
 \reftitle{References}
+\begin{thebibliography}{999}
 
-%=====================================
-% References, variant A: external bibliography
-%=====================================
-\bibliography{literature.bib}
+\bibitem[Dawkins(1971)]{dawkins1971}
+Dawkins, M.
+\newblock Shifts of ‘attention’in chicks during feeding.
+\newblock {\em Anim. Behav.} {\bf 1971}, {\em 19},~575--582.
+
+\bibitem[Kristj{\'a}nsson \em{et~al.}(2014)Kristj{\'a}nsson, J{\'o}hannesson,
+  and Thornton]{kristjansson2014}
+Kristj{\'a}nsson, {\'A}.; J{\'o}hannesson, {\'O}.I.; Thornton, I.M.
+\newblock Common attentional constraints in visual foraging.
+\newblock {\em PLoS ONE} {\bf 2014}, {\em 9},~e100752.
+
+\bibitem[Charnov(1976)]{charnov1976}
+Charnov, E.L.
+\newblock Optimal foraging, the marginal value theorem.
+\newblock {\em Theor. Popul. Biol.} {\bf 1976}, {\em 9},~129--136.
+
+\bibitem[Bartumeus \em{et~al.}(2005)Bartumeus, Da~Luz, Viswanathan, and
+  Catalan]{bartumeus2005}
+Bartumeus, F.; Da~Luz, M.; Viswanathan, G.; Catalan, J.
+\newblock Animal search strategies: A quantitative random-walk analysis.
+\newblock {\em Ecology} {\bf 2005}, {\em 86},~3078--3087.
+\newblock 
+  {{https://doi.org/10.1890/04-1806}}.
+
+\bibitem[Benhamou(2007)]{benhamou2007}
+Benhamou, S.
+\newblock How many animals really do the Lévy walk?
+\newblock {\em Ecology} {\bf 2007}, {\em 88},~1962--1969.
+\newblock  {{https://doi.org/10.1890/06-1769.1}}.
+
+\bibitem[Dukas and Ellner(1993)]{Dukas1993}
+Dukas, R.; Ellner, S.
+\newblock Information processing and prey detection.
+\newblock {\em Ecology} {\bf 1993}, {\em 74},~1337--1346.
+
+\bibitem[Clarke \em{et~al.}(2022)Clarke, Hunt, and Hughes]{clarke2022foraging}
+Clarke, A.D.; Hunt, A.R.; Hughes, A.E.
+\newblock Foraging as sampling without replacement: A Bayesian statistical
+  model for estimating biases in target selection.
+\newblock {\em PLoS Comput. Biol.} {\bf 2022}, {\em 18},~e1009813.
+
+%MDPI: Refs. 8 and 16 are duplicated. Please remove ref. 16 and rearrange all the references to appear in numerical order. Please ensure that there are no duplicated references.
+%MDPI: newly added, please confirm. RESPONSE: The 2022 reference seems to be the correct one - now corrected.
+
+\bibitem[Clarke \em{et~al.}(2022)Clarke, Irons, James, Leber, and
+  Hunt]{clarke2022}
+Clarke, A.D.; Irons, J.L.; James, W.; Leber, A.B.; Hunt, A.R.
+\newblock Stable individual differences in strategies within, but not between,
+  visual search tasks.
+\newblock {\em Q. J. Exp. Psychol.} {\bf 2022}, \hl{\emph{75},  289--296.}
+%MDPI: newly added, please confirm. RESPONSE: Confirm
+
+\bibitem[Tagu and Kristj{\'a}nsson(2021)]{tagu_kristjansson_2021}
+Tagu, J.; Kristj{\'a}nsson, {\'A}.
+\newblock The selection balance: Contrasting value, proximity and priming in a
+  multitarget foraging task. \emph{\hl{Cognition}}  \textbf{2021}, \hl{\emph{218}, 104935}.
+\newblock {{https://doi.org/10.31234/osf.io/48pzy}}.
+%MDPI: newly added, please confirm. RESPONSE: Confirm
+
+\bibitem[Tagu and Kristj{\'a}nsson(2020)]{tagu2020}
+Tagu, J.; Kristj{\'a}nsson, {\'A}.
+\newblock Dynamics of attentional and oculomotor orienting in visual foraging
+  tasks.
+\newblock {\em Q. J. Exp. Psychol.} {\bf 2022}, \hl{\emph{75}, 260--276.}
+%MDPI: newly added, please confirm. RESPONSE: Confirm
+
+\bibitem[Clarke and Tatler(2014)]{clarke2014deriving}
+\hl{Clarke, A.D.; Tatler, B.W.} %MDPI: Refs.
+12 and 15 are duplicated.
+Please remove ref.
+15 and rearrange all the references to appear in numerical order.
+Please ensure that there are no duplicated references.
+RESPONSE: Fixed
+\newblock Deriving an appropriate baseline for describing fixation behaviour.
+\newblock {\em Vis. Res.} {\bf 2014}, {\em 102},~41--51.
+
+\bibitem[Clarke \em{et~al.}(2017)Clarke, Stainer, Tatler, and Hunt]{clarke2017}
+Clarke, A.D.; Stainer, M.J.; Tatler, B.W.; Hunt, A.R.
+\newblock The saccadic flow baseline: Accounting for image-independent biases
+  in fixation behavior.
+\newblock {\em J. Vis.} {\bf 2017}, {\em 17},~12.
+
+\bibitem[{Stan Development Team}(2020)]{rstan}
+{Stan Development Team}.
+\newblock {RStan}: The {R} interface to {Stan}. 
+\newblock \hl{R package version 2.21.2.
+2020.
+} %MDPI: Please provide more information about the type of the article, such as book (please provide the name of the publisher and location of it), online resource (please provide the URL of the website and the date it was accessed (day, month, year)), or journal article (please provide the name of the journal, the year and volume it published, and the page number).
+RESPONSE: This is software: the URL is https://mc-stan.org/.
+
+\bibitem[Thornton \em{et~al.}(2022)Thornton, Nguyen, and
+  Kristj{\'a}nsson]{thornton2022foraging}
+\hl{Thornton, I.M.; Nguyen, T.T.; Kristj{\'a}nsson, {\'A}}.
+\newblock Foraging tempo: Human run patterns in multiple-target search are
+  constrained by the rate of successive responses.
+\newblock {\em Q. J. Exp. Psychol.} {\bf 2022}, {\em
+  75},~297--312.
+
+\bibitem[Kristj{\'a}nsson \em{et~al.}(2022)Kristj{\'a}nsson, Draschkow,
+  P{\'a}lsson, Haraldsson, J{\'o}nsson, and
+  Kristj{\'a}nsson]{kristjansson2022moving}
+Kristj{\'a}nsson, T.; Draschkow, D.; P{\'a}lsson, {\'A}.; Haraldsson, D.;
+  J{\'o}nsson, P.{\"O}.; Kristj{\'a}nsson, {\'A}.
+\newblock Moving foraging into three dimensions: Feature-versus
+  conjunction-based foraging in virtual reality.
+\newblock {\em Q. J. Exp. Psychol.} {\bf 2022}, {\em
+  75},~313--327.
+
+\bibitem[Riggs \em{et~al.}(2017)Riggs, Cornes, Godwin, Liversedge, Guest, and
+  Donnelly]{riggs2017importance}
+Riggs, C.A.; Cornes, K.; Godwin, H.J.; Liversedge, S.P.; Guest, R.; Donnelly,
+  N.
+\newblock The importance of search strategy for finding targets in open
+  terrain.
+\newblock {\em Cogn. Res. Princ. Implic.} {\bf 2017},
+  {\em 2},~1--17.
+
+\bibitem[Tatler(2007)]{tatler2007central}
+Tatler, B.W.
+\newblock The central fixation bias in scene viewing: Selecting an optimal
+  viewing position independently of motor biases and image feature
+  distributions.
+\newblock {\em J. Vis.} {\bf 2007}, {\em 7},~4.
+
+\bibitem[Tseng \em{et~al.}(2009)Tseng, Carmi, Cameron, Munoz, and
+  Itti]{tseng2009quantifying}
+Tseng, P.H.; Carmi, R.; Cameron, I.G.; Munoz, D.P.; Itti, L.
+\newblock Quantifying center bias of observers in free viewing of dynamic
+  natural scenes.
+\newblock {\em J. Vis.} {\bf 2009}, {\em 9},~4.
+
+\end{thebibliography}
 

### 2022-11-08 Revisions 2/manuscriptRevisions2.tex
proofs

--- 2022-10-27 manuscriptRevisions2.tex
@@
 We can see  that this appears to be systematically related to how well our model can predict behaviour.
-Interestingly, these poorly predicted example trials appear to have very strong pS biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well.
+Interestingly, in some cases, poorly predicted trials appear to have very strong pS biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well.
 This fits with conjunction trials being harder for the model to predict, as these trials generally have fewer switches.

### 2022-11-09 Analysis/index_revisions_2.Rmd
final bits and bobs

@@
 #ggsave("../Figures/qjep_preds.pdf", 
-#       plt_b2 / (plt1 + plt2) + 
+#       plt_b2 / (plt1 + plt2) + plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)'))) +
 #       plot_layout(guides = "collect") & theme(legend.position = 'bottom'),
@@
 #ggsave("../Figures/qjep_indiv_diff.pdf", 
-#       plt_a + plt_b + 
+#       plt_a + plt_b + plot_annotation(tag_levels = list(c('(a)', '(b)'))) +
 #         plot_layout(widths = c(1, 2)), width = 12, height = 4)
@@
 #ggsave("../Figures/qjep_ex_paths.pdf",
-#      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]]), 
+#      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]])  + plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)', '(d)'))),
 #       width = 8, height = 8)
@@
 ```{r}
-#ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 3)
+#ggsave("../Figures/path_length.pdf", plt2 + plt2b + plot_annotation(tag_levels = list(c('(a)', '(b)'))), width = 8, height = 3)
 ```
@@
 
-create_post_plot("x") + create_post_plot("y") + plt_mu #& theme_bw()
+create_post_plot("x") + create_post_plot("y") + plt_mu + plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)'))) #& theme_bw() 
 #ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
@@
 
-(plt_x + plt_y) + plt_lambdas
+(plt_x + plt_y) + plt_lambdas + plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)')))
 
@@
 
-plt1 / (plt2 + plt3)  + plot_layout(guides = "collect")
+plt1 / (plt2 + plt3)  + plot_layout(guides = "collect")  + plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)')))
 
 #ggsave("../Figures/qjep_init_sel_preds.pdf",
-#       width = 8, height = 4)
+#       width = 10, height = 6)
 

### 2022-11-09 Proofs/vision-1871367-proofreading.tex
final bits and bobs

@@
 Abbreviations used as keywords should be defined too.Please check and make sure that this rule is applied through the whole paper.
+% RESPONSE: Checked.
 
@@
 To address the need for a more precise set of measurements, we recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022foraging}.
-By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully reanalyse data from a number of open access datasets \cite{kristjansson2014, thornton2022, clarke2022, tagu_kristjansson_2021}.
+By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully reanalyse data from a number of open access datasets \cite{kristjansson2014, thornton2022foraging, clarke2022, tagu_kristjansson_2021}.
 
@@
 with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$ calculating the angular difference.
-$\text{atan2}$ is the direction of travel from i to j.
+$\text{atan2}$ is the direction of travel from \textit{i} to \textit{j}.
 This model is implemented in a multilevel framework, allowing each of the four parameters to vary from participant to participant.
@@
 For fitting the model to the data from~\cite{clarke2022} we used a university computing cluster with R v3.6.3 and rStan v2.19.2.%MDPI:For all equipment/software/products used, the following information should be given: company name, city, state abbreviation (if its from USA or Canada), and country must be provided.
-Please apply this rule through the whole Materials and Methods section
+Please apply this rule through the whole Materials and Methods section RESPONSE: Done.
 
@@
 \end{adjustwidth}
-\caption{({\textbf{\hl{top left}}}) Posterior probabilities for target selections during a visual foraging task.
+\caption{({\textbf{\hl{a}}}) Top left: Posterior probabilities for target selections during a visual foraging task.
 Each dot shows the data from an individual participant, averaged over trials, in the feature condition and the shaded region indicates the interval in which we expect 67\% of participants to fall.
 The dashed line indicates chance performance.
-(\textbf{\hl{top right}}) As top left, except showing the conjunction condition.
-(\textbf{\hl{bottom left}})  Calibration plot for our foraging model.
+Top right: As top left, except showing the conjunction condition.
+(\textbf{\hl{b}})  Calibration plot for our foraging model.
 The $x$-axis gives the largest weight assigned by the model while the $y$-axis shows how often that target was actually selected by a human participant.
 The dashed line here and in the right plot is the identity line.
-(\textbf{\hl{bottom right}}) This plot shows how often the model selects the 2nd and 3rd ranked items based on the weights assigned by the model.} %mdpi: we removed the subfigure label from italic to be not italic and added bold of it according to our rule, please confirm, same in below figures.
+(\textbf{\hl{c}}) This plot shows how often the model selects the 2nd and 3rd ranked items based on the weights assigned by the model.} %mdpi: we removed the subfigure label from italic to be not italic and added bold of it according to our rule, please confirm, same in below figures.
 RESPONSE: Confirmed.
@@
 Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+RESPONSE: Done.
 
@@
 \includegraphics[width=13.5 cm]{Figures/qjep_indiv_diff.pdf}
-\caption{({\textbf{\hl{left}}}) Prediction scores for participants.
+\caption{({\textbf{\hl{a}}}) Prediction scores for participants.
 Boxplots show quartile range and the grey lines indicate individual participants.
 The dots indicate outliers.
-(\textbf{\hl{right}}) How accuracy of our model varies with the strength of an individual’s \textit{bM}, \textit{bP}, \textit{pA} and \textit{pS} parameters.
+(\textbf{\hl{b}}) How accuracy of our model varies with the strength of an individual’s \textit{bM}, \textit{bP}, \textit{pA} and \textit{pS} parameters.
 We can see two clear outlier participants (marked with an X).} %MDPI: please divide the figure into 2 subfigures and  note them accordingly.
@@
 Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+RESPONSE: Done.
 %MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
@@
 \includegraphics[width=12 cm]{Figures/qjep_ex_paths.pdf}
-\caption{(\textbf{\hl{top}}) Two randomly selected trials in which the model does a good job in accounting for human behaviour.
+\caption{(\textbf{\hl{a}}) and (\textbf{\hl{b}}) Two randomly selected trials in which the model does a good job in accounting for human behaviour.
 The numbers indicate the order the participant selected targets in.
@@
 When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation.
-(\textbf{\hl{bottom}}) Two randomly selected examples in which the model does a less good job in accounting for the order in which human participants selected the items.}%MDPI: please divide the figure into subfigures and  note them accordingly.
+(\textbf{\hl{c}}) and (\textbf{\hl{d}}) Two randomly selected examples in which the model does a less good job in accounting for the order in which human participants selected the items.}%MDPI: please divide the figure into subfigures and  note them accordingly.
 Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
 Subfigures should be provided with sub-caption and put sub-caption in figure caption.
-Please add explanation for all the symbols/colors
+Please add explanation for all the symbols/colors RESPONSE: Done
 %MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
@@
 We can see  that this appears to be systematically related to how well our model can predict behaviour.
-Interestingly, in some cases, poorly predicted trials appear to have very strong pS biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well.
+Interestingly, in some cases, poorly predicted trials appear to have very strong \textit{pS} biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well.
 This fits with conjunction trials being harder for the model to predict, as these trials generally have fewer switches.
@@
 \includegraphics[width=13.5 cm]{Figures/path_length.pdf}
-\caption{({\textbf{\hl{left}}}) Histogram showing the distribution of the median path lengths for our human participants and model (fitted to each human participant via the random effect structure).
-(\textbf{\hl{right}}) The relationship between model accuracy and the proportion of trials in which the human participant has a shorter total path length than predicted.}%MDPI:please divide the figure into 2 subfigures and  note them accordingly.
+\caption{({\textbf{\hl{a}}}) Histogram showing the distribution of the median path lengths for our human participants and model (fitted to each human participant via the random effect structure).
+(\textbf{\hl{b}}) The relationship between model accuracy and the proportion of trials in which the human participant has a shorter total path length than predicted.}%MDPI:please divide the figure into 2 subfigures and  note them accordingly.
 Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
 Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+RESPONSE: Done
 %MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
@@
 Grey areas indicate cells with a count of 0.
-({\textbf{\hl{left}}}) shows the distribution over all initial target selections (i.e., multiple trials per participant) while ({\textbf{\hl{right}}}) shows the distribution of each participant's median initial selection (i.e., each participant contributes one data point to the~graph).
+The left panel shows the distribution over all initial target selections (i.e., multiple trials per participant) while the right panel shows the distribution of each participant's median initial selection (i.e., each participant contributes one data point to the~graph).
 }%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
@@
 \end{adjustwidth}
-\caption{Posterior fits for ({\textbf{\hl{left}}}) horizontal and ({\textbf{\hl{middle}}}) vertical locations of the initial target selection.
+\caption{Posterior fits for ({\textbf{\hl{a}}}) horizontal and ({\textbf{\hl{b}}}) vertical locations of the initial target selection.
 Each line represents a different participant.
-({\textbf{\hl{right}}}) A scatter plot showing the $x$ and $y$ posterior means for each participant.}%MDPI: please divide the figure into 3 subfigures and  note them accordingly.
+({\textbf{\hl{c}}}) A scatter plot showing the $x$ and $y$ posterior means for each participant.}%MDPI: please divide the figure into 3 subfigures and  note them accordingly.
 Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
 Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+RESPONSE: Done
 %MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
@@
 \end{adjustwidth}
-\caption{Posterior fits for the ({\textbf{\hl{left}}}) horizontal and ({\textbf{\hl{middle}}}) vertical locations of the initial target selection.
-({\textbf{\hl{right}}}) shows the mixing parameters for each participant, with the error bar indicating the $95\%$ HDPI.}%MDPI:Please define "x" and "y" from subfigures 1 and 2.
+\caption{Posterior fits for the ({\textbf{\hl{a}}}) horizontal and ({\textbf{\hl{b}}}) vertical locations of the initial target selection.
+({\textbf{\hl{c}}}) shows the mixing parameters for each participant, with the error bar indicating the $95\%$ HDPI.}%MDPI:Please define "x" and "y" from subfigures 1 and 2.
 Also, please divide the figure into 3 subfigures.
@@
 Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+RESPONSE: Done
 %MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
@@
 Interestingly, as above, there is considerable variation between participants, with participants who favour the top-left corner being easier to predict.
-%MDPI: Please move Figure 8 right after this paragraph ends(Figures and tables need to appear in exact numerical order, right after their first citation)
+%MDPI: Please move Figure 8 right after this paragraph ends(Figures and tables need to appear in exact numerical order, right after their first citation) RESPONSE: Done
+
+\begin{figure}[H]
+\includegraphics[width=13.8 cm]{Figures/qjep_init_sel_preds.pdf}
+\caption{({\textbf{\hl{a}}}): a count of initial weight values predicted from both methods (mixture and multi-level).
+({\textbf{\hl{b}}}): the proportion of times the first selection was correct for both methods.
+({\textbf{\hl{c}}}): as lambda (the model parameter underlying initial weight) increases, accuracy increases i.e., the model is more accurate for the cases where participants are selecting a corner as their initial target selection.
+The dots each represent an individual participant, and the line is the line of best fit.}% MDPI: please divide the figure into 2 subfigures and  note them accordingly.
+Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
+Subfigures should be provided with sub-caption and put sub-caption in figure caption.
+%MDPI: Please provide a short explanation for the black dots from the 3rd subfigure RESPONSE: Done
+%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
+If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.
+Thank you for your cooperation!
+RESPONSE: Confirmed
 
@@
 Further details and graphs can be found in the \hl{Supplementary Materials: Part 2}.
-
-\begin{figure}[H]
-\includegraphics[width=13.8 cm]{Figures/qjep_init_sel_preds.pdf}
-\caption{({\textbf{\hl{Top}}}): a count of initial weight values predicted from both methods (mixture and multi-level).
-({\textbf{\hl{Bottom left}}}): the proportion of times the first selection was correct for both methods.
-({\textbf{\hl{Bottom right}}}): as lambda (the model parameter underlying initial weight) increases, accuracy increases i.e., the model is more accurate for the cases where participants are selecting a corner as their initial target selection.
-The dots each represent an individual participant, and the line is the line of best fit.}% MDPI: please divide the figure into 2 subfigures and  note them accordingly.
-Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole.
-Subfigures should be provided with sub-caption and put sub-caption in figure caption.
-%MDPI: Please provide a short explanation for the black dots from the 3rd subfigure RESPONSE: Done
-%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.
-If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.
-Thank you for your cooperation!
-RESPONSE: Confirmed
 
@@
 However, it is possible that there are other factors that we have not taken into account that could further help explain these discrepancies.
-Participants who 'stick' to one type of target are likely to have longer path lengths, and it seems that the model does do a poorer job of predicting conjunction trials, which generally have stronger pS biases.
+Participants who 'stick' to one type of target are likely to have longer path lengths, and it seems that the model does do a poorer job of predicting conjunction trials, which generally have stronger \textit{pS} biases.
 Thus, one area for future improvement of the model is to try to capture this behaviour better: it may be that a 'floor' parameter (on a participant-by-participant basis) in the spatial fall off, allocating more weight to more distant targets, may help account for currently difficult to predict trial behaviour.
@@
 %% optional
-\supplementary{\hl{The following are available online at} \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
-%mdpi: please fully complete this part with information regarding  supplementary materials, as shown in the above example.
+\supplementary{\hl{The following are available online at} \linksupplementary{s1}, Document S1: Supplementary Materials 1, Document S2: Supplementary Materials 2}
+%mdpi: please fully complete this part with information regarding  supplementary materials, as shown in the above example. RESPONSE: Done
 
@@
 
-\dataavailability{Data supporting reported results can be found on Github at XXX.
-The datasets analysed in this study can be found at \url{https://osf.io/y6qbv/}, \hl{accessed on}, and \linebreak  \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0100752}, \hl{accessed on}.}
-%MDPI: Please add the access date (Format: Date Month Year). e.g., (accessed on 1 January 2020).
+\dataavailability{Data supporting reported results can be found on Github at \url{https://github.com/scienceanna/foraging_svg}.
+The datasets analysed in this study can be found at \url{https://osf.io/y6qbv/}, \hl{accessed on 25th April 2022}, and \linebreak  \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0100752}, \hl{accessed on 27th May 2022}.}
+%MDPI: Please add the access date (Format: Date Month Year). e.g., (accessed on 1 January 2020). RESPONSE: Done.
 
